### 2021-07-31 supplement/supplement-main.Rmd
everything for supplement, including all analyses, figures, bibliography, word styles doc

---
title: "Beliefs about the development of mental life"
subtitle: "Supplemental materials"
author: "[authors removed to preserve anonymity]"
date: "July 31, 2021"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: true
    toc_depth: 3
bibliography: "references.bib"
# cls: "article.cls"
csl: nature.csl
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
tables: yes
---

```{r setup, set.seed(94305), include = F}
knitr::opts_chunk$set(cache = T)
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(include = F)
```

```{r resave plots}
# do you want to resave the plots?
# resave_plots <- T # uncomment if yes
resave_plots <- F # uncomment if no
```

```{r load packages}
library(ggdendro)
library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(cowplot)
library(tidyverse)
```

```{r load custom funs}
source("../code/custom_funs.R")
```

```{r load data}
# suppress warnings and messages because dplyr is verbose
suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", 
                                         chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", 
                                         chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", 
                                         chdir = TRUE)))
```

\newpage
In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life. We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).

In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007, @weisman.etal2017a, @weisman.etal2017b, @malle2019].

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: [removed to preserve anonymity].

# Extended results

## Study 1

As described in the main text, we began with an expansive exploration of US adults’ attributions of mental life to infants and young children of different ages. We included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction. We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life. Our primary analysis for this preregistered study was an exploratory factor analysis (EFA) of participants’ capacity ratings. This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children. Following previous work on mind perception, we argue that the suites of capacities revealed by EFA offer a meaningful approximation of the latent conceptual structure underlying participants’ reasoning about the developing human mind.

In the main text, we presented the four-factor EFA solution suggested by parallel analysis. Here, we present extended results for this EFA and the alternative EFA solutions suggested by minimizing BIC and by Weisman et al.'s factor retention criteria [@weisman.etal2017a], as well as a visualization of perceptions of development in these mental capacities.

### Exploratory factor analyses (EFAs)

In order to determine how many factors to retain, we examined the results of three factor retention protocols:

(1) Parallel analysis (presented in the main text), which compares the observed correlation structure to the correlation structure arising from random datasets of the same size; 
(2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and 
(3) A set of factor retention criteria that have been used in Weisman et al.’s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation.  (In this protocol, a factor had to meet all three of these criteria in order to be retained).

Our interpretation of how best to characterize our dataset (i.e., how many factors we observe) was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol. Here we present these three factor retention protocols separately.

All factor analyses were conducted using ordinary least squares to find the minimum residual solution via the "fa" function in the "psych" package for R [@revelle2021].

#### Parallel analysis

```{r s1 parallel analysis}
set.seed(94305)
s1_parallel <- fa.parallel(d1_all, plot = F)
```

```{r s1 efa parallel analysis}
s1_efa_par <- fa(d1_all, 
                 nfactors = s1_parallel$nfact, 
                 rotate = "oblimin")
# s1_efa_par %>% fa.sort()
```

As reported in the main text, parallel analysis suggested retaining `r s1_parallel$nfact` factors. We call these factors _cognition and control_, _social connection_, _bodily sensations_, and _negative affect_. Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efaparload); see also Figure 1 (main text). The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs1efaparvacc).

```{r tabs1efaparload, include = T, warning = F, message = F}
tabs1efaparload <- model_parameters(s1_efa_par, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
  rename(`Cog. Ctrl.` = MR1,
         `Soc. Conn.` = MR3,
         `Bod. Sens.` = MR2,
         `Neg. Afft.` = MR4)

tabs1efaparload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+4]) %>%
  column_spec(3, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+5]) %>%
  column_spec(4, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+6]) %>%
  column_spec(5, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+7]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs1efaparvacc, include = T, warning = F, message = F}
s1_efa_par$Vaccounted %>% 
  data.frame() %>% 
  rename(`Cognition and control` = MR1,
         `Social connection` = MR3,
         `Bodily sensations` = MR2,
         `Negative affect` = MR4) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by parallel analysis: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r fig01 code, fig.width = 4.5, fig.asp = 1.2}
heatmap_fun(s1_efa_par, 
            factor_names = c("Cognition and control",
                             "Bodily sensations",
                             "Social connection",
                             "Negative affect"))

# save plot
if (resave_plots == T | !file.exists("../outputs/fig01.pdf")) {
  ggsave("../outputs/fig01.svg")
  ggsave("../outputs/fig01.pdf")
}
```

```{r fig01, fig.cap="Study 1, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
# knitr::include_graphics("../outputs/fig01.pdf")
```

#### Minimizing BIC

```{r s1 minimizing bic}
s1_minbic <- VSS(d1_all, plot = F)

s1_minbic <- s1_minbic$vss.stats %>%
  rownames_to_column("nfact") %>%
  mutate(nfact = as.numeric(nfact)) %>%
  filter(BIC == min(BIC)) %>%
  data.frame()
```

```{r s1 efa minimizing bic}
s1_efa_bic <- fa(d1_all, 
                 nfactors = s1_minbic$nfact, 
                 rotate = "oblimin") # does not converge even with max.iter >> 100000; max.iter does affect printout
# s1_efa_bic %>% fa.sort()
```

Minimizing BIC suggested retaining `r s1_minbic$nfact` factors. (Note, however, that this solution does not converge.) Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efabicload). The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs1efabicvacc).

```{r tabs1efabicload, include = T, warning = F, message = F}
tabs1efabicload <- model_parameters(s1_efa_bic, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F)))

tabs1efabicload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, bold = tabs1efabicload[,s1_minbic$nfact+4]) %>%
  column_spec(3, bold = tabs1efabicload[,s1_minbic$nfact+5]) %>%
  column_spec(4, bold = tabs1efabicload[,s1_minbic$nfact+6]) %>%
  column_spec(5, bold = tabs1efabicload[,s1_minbic$nfact+7]) %>%
  column_spec(6, bold = tabs1efabicload[,s1_minbic$nfact+8]) %>%
  column_spec(7, bold = tabs1efabicload[,s1_minbic$nfact+9]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs1efabicvacc, include = T, warning = F, message = F}
s1_efa_bic$Vaccounted %>% 
  data.frame() %>% 
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by minimizing BIC: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

We consider the first of these factors ("`r names(data.frame(s1_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s1_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensations_, the third ("`r names(data.frame(s1_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth ("`r names(data.frame(s1_efa_bic$loadings[]))[4]`") to resonate with the construct we have called _negative affect_. The fifth factor ("`r names(data.frame(s1_efa_bic$loadings[]))[5]`") appears to pick out capacities particularly relevant to social interaction (e.g., social learning, person recognition, humor, listening), and the sixth factor ("`r names(data.frame(s1_efa_bic$loadings[]))[6]`") appears to pick out negative emotions (e.g., anger, annoyance, boredom, social fear); however, there were no capacities that loaded strongly on either of these capacities.

```{r figS01 code, fig.width = 4.5, fig.asp = 1.2}
heatmap_fun(s1_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS01.pdf")) {
  ggsave("../outputs/figS01.svg")
  ggsave("../outputs/figS01.pdf")
}
```

```{r figS01, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS01.pdf")
```

#### Weisman et al.'s (2017) factor retention criteria

```{r s1 weisman et al criteria}
s1_weismanetal <- reten_fun(d1_all, rot_type = "oblimin")
s1_weismanetal
```

```{r s1 efa weisman et al criteria}
s1_efa_wdm <- fa(d1_all, 
                 nfactors = s1_weismanetal, 
                 rotate = "oblimin") 
# s1_efa_wdm %>% fa.sort()
```

Weisman et al.'s (2017) factor retention criteria suggested retaining `r s1_weismanetal` factors. Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efawdmload). The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs1efawdmvacc).

```{r tabs1efawdmload, include = T, warning = F, message = F}
tabs1efawdmload <- model_parameters(s1_efa_wdm, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F)))

tabs1efawdmload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, bold = tabs1efawdmload[,s1_weismanetal+4]) %>%
  column_spec(3, bold = tabs1efawdmload[,s1_weismanetal+5]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs1efawdmvacc, include = T, warning = F, message = F}
s1_efa_wdm$Vaccounted %>% 
  data.frame() %>% 
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

We consider the first of these factors ("`r names(data.frame(s1_efa_wdm$loadings[]))[1]`") to resonate most strongly with the construct we have called _cognition and control_, and the second ("`r names(data.frame(s1_efa_wdm$loadings[]))[2]`") to resonate most strongly with the construct we have called _bodily sensations_. These factors are also quite similar to the constructs of "agency" and "experience" in Gray et al.'s original studies of mind perception [@gray.etal2007].

```{r figS02 code, fig.width = 4.5, fig.asp = 1.2}
heatmap_fun(s1_efa_wdm)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS02.pdf")) {
  ggsave("../outputs/figS02.svg")
  ggsave("../outputs/figS02.pdf")
}
```

```{r figS02, fig.cap="Study 1, factor solution suggested by minimizing BIC."}
knitr::include_graphics("../outputs/figS02.pdf")
```

### Capacity ratings: Developmental trajectories

Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life. Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life. To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabcapcomp)); for each participant, we then took the average of their responses to capacities in each domain at each target age. As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensations_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.

```{r s1 scales}
d1_scales <- s1_efa_par$loadings[] %>%
  data.frame() %>%
  rownames_to_column("capacity") %>%
  gather(factor, loading, -capacity) %>%
  group_by(capacity) %>%
  top_n(1, abs(loading)) %>%
  ungroup() %>%
  mutate(factor = recode_factor(factor,
                                "MR2" = "Bodily sensations",
                                "MR4" = "Negative affect",
                                "MR3" = "Social connection",
                                "MR1" = "Cognition and control")) %>%
  arrange(factor, desc(loading)) %>%
  mutate(order = 1:nrow(.))
```

```{r s1 cap ratings dataset}
d1_cap_ratings <- d1_all %>%
  rownames_to_column("ResponseId_target") %>%
  separate(ResponseId_target, c("ResponseId", "target")) %>%
  mutate(target_year = recode(target,
                              target00mo = 0, # newborns
                              target0Xmo = 3/365, # 3 days
                              target01mo = 1/12, # 1 month
                              target02mo = 2/12, 
                              target04mo = 4/12, 
                              target06mo = 6/12, 
                              target09mo = 9/12,
                              target12mo = 12/12,
                              target18mo = 18/12,
                              target24mo = 24/12,
                              target36mo = 36/12,
                              target48mo = 48/12,
                              target60mo = 60/12)) %>%
    gather(capacity, response, -ResponseId, -starts_with("target")) %>%
  left_join(d1_scales %>% distinct(factor, capacity))
```

```{r s1 cap ratings summary stats}
d1_cap_ratings_sum <- d1_cap_ratings %>%
  group_by(factor, target_year) %>%
  summarise(median = median(response, na.rm = T),
            mean = mean(response, na.rm = T),
            sd = sd(response, na.rm = T)) %>%
  ungroup() %>%
  arrange(target_year, factor)

d1_cap_ratings_sum %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

```{r s1 gam dataset}
d1_gam <- d1_cap_ratings %>%
  # implement correction for beta distribution
  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
                              response/100 > 0.995 ~ 0.995,
                              TRUE ~ response/100))

contrasts(d1_gam$factor) <- cbind(bod_cog = c(1, 0, 0, 0),
                                  neg_cog = c(0, 1, 0, 0),
                                  soc_cog = c(0, 0, 1, 0))
```

```{r figS03 code, fig.width = 4, fig.asp = 0.5}
d1_gam %>%
  group_by(ResponseId, target_year, factor) %>%
  # # ALTERNATIVE: take just top 5 items per factor (like Study 2)
  # left_join(d1_scales %>% distinct(factor, capacity, loading)) %>%
  # top_n(5, loading) %>%
  summarise(score = mean(response, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = target_year, y = score, color = factor)) +
  facet_grid(~ factor) +
  geom_path(aes(group = ResponseId),
            # color = "#160072",
            alpha = 0.2, size = 0.02) +
  geom_path(data = . %>%
                    group_by(factor, target_year) %>%
                    summarise(mean = mean(score, na.rm = T)) %>%
                    ungroup,
            aes(y = mean),
            color = "black", lty = 2) +
            # color = "#160072",
  geom_pointrange(data = . %>%
                    group_by(factor, target_year) %>%
                    multi_boot_standard(col = "score") %>%
                    ungroup,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black",
                  # color = "#160072",
                  fatten = 1) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = seq(0, 100, 25)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Mean response\n0 = not at all capable, 100 = completely capable") +
  guides(color = guide_none())

# save plot
if (resave_plots == T | !file.exists("../outputs/figS03.pdf")) {
  ggsave("../outputs/figS03.svg")
  ggsave("../outputs/figS03.pdf")
}
```

```{r figS03, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1). Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
knitr::include_graphics("../outputs/figS03.pdf")
```

```{r s1 export results}
# save numerical results
s1_results <- list(demo = d1_demo,
                   efa = s1_efa_par,
                   efa_bic = s1_efa_bic,
                   efa_wdm = s1_efa_wdm,
                   cap_rat_ss = d1_cap_ratings_sum)

saveRDS(s1_results, "../outputs/s1_results.rds")
```

## Study 2

As described in the main text, in Study 2 we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development. The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages.

In the main text, we briefly described the four-factor EFA solution suggested by parallel analysis, and presented the results of a generalized additive model (GAM) predicting participants' responses as a function of target age, domain, and interactions between them. Here, we present the full results for the EFA mentioned in the main text, an alternative EFA solutions suggested by minimizing BIC, and the full results of the GAM.

### Exploratory factor analyses (EFAs)

As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retentia criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol. Here we present these three factor retention protocols separately.

#### Parallel analysis

```{r s2 parallel analysis}
set.seed(94305)
s2_parallel <- fa.parallel(d2_all, plot = F)
```

```{r s2 efa parallel analysis}
s2_efa_par <- fa(d2_all, 
                 nfactors = s2_parallel$nfact, 
                 rotate = "oblimin")
# s2_efa_par %>% fa.sort()
```

As reported in the main text, parallel analysis suggested retaining `r s2_parallel$nfact` factors, and these factors were very similar to those found in Study 1 (_bodily sensations_, _negative affect_, _social connection_, and _cognition and control_); each item loaded most strongly on the factor it was selected to represent. Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs2efaparload); see also Figure 1 (main text). The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs2efaparvacc).

```{r tabs2efaparload, include = T, warning = F, message = F}
tabs2efaparload <- model_parameters(s2_efa_par, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
  rename(`Neg. Afft.` = MR1,
         `Bod. Sens.` = MR3,
         `Cog. Ctrl.` = MR2,
         `Soc. Conn.` = MR4)

tabs2efaparload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 2, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, width = "1cm", bold = tabs2efaparload[,s2_parallel$nfact+4]) %>%
  column_spec(3, width = "1cm", bold = tabs2efaparload[,s2_parallel$nfact+5]) %>%
  column_spec(4, width = "1cm", bold = tabs2efaparload[,s2_parallel$nfact+6]) %>%
  column_spec(5, width = "1cm", bold = tabs2efaparload[,s2_parallel$nfact+7]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs2efaparvacc, include = T, warning = F, message = F}
s2_efa_par$Vaccounted %>% 
  data.frame() %>% 
  rename(`Negative affect` = MR1,
         `Bodily sensations` = MR3,
         `Cognition and control` = MR2,
         `Social connection` = MR4) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 2, factor solution suggested by parallel analysis: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r figS04 code, fig.width = 4.5, fig.asp = 0.5}
heatmap_fun(s2_efa_par, 
            factor_names = c("Negative affect",
                             "Cognition and control",
                             "Bodily sensations",
                             "Social connection"))

# save plot
if (resave_plots == T | !file.exists("../outputs/figS04.pdf")) {
  ggsave("../outputs/figS04.svg")
  ggsave("../outputs/figS04.pdf")
}
```

```{r figS04, fig.cap="Study 2, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
# knitr::include_graphics("../outputs/figS04.pdf")
```

#### Minimizing BIC

```{r s2 minimizing bic}
s2_minbic <- VSS(d2_all, plot = F)

s2_minbic <- s2_minbic$vss.stats %>%
  rownames_to_column("nfact") %>%
  mutate(nfact = as.numeric(nfact)) %>%
  filter(BIC == min(BIC)) %>%
  data.frame()
```

```{r s2 efa minimizing bic}
s2_efa_bic <- fa(d2_all, 
                 nfactors = s2_minbic$nfact, 
                 rotate = "oblimin") # does not converge even with max.iter >> 100000; max.iter does affect printout
# s2_efa_bic %>% fa.sort()
```

Minimizing BIC suggested retaining `r s2_minbic$nfact` factors. (Note, however, that this solution does not converge.) Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs2efabicload). The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs2efabicvacc).

```{r tabs2efabicload, include = T, warning = F, message = F}
tabs2efabicload <- model_parameters(s2_efa_bic, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F)))

tabs2efabicload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 2, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, bold = tabs2efabicload[,s2_minbic$nfact+4]) %>%
  column_spec(3, bold = tabs2efabicload[,s2_minbic$nfact+5]) %>%
  column_spec(4, bold = tabs2efabicload[,s2_minbic$nfact+6]) %>%
  column_spec(5, bold = tabs2efabicload[,s2_minbic$nfact+7]) %>%
  column_spec(6, bold = tabs2efabicload[,s2_minbic$nfact+8]) %>%
  column_spec(7, bold = tabs2efabicload[,s2_minbic$nfact+9]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs2efabicvacc, include = T, warning = F, message = F}
s2_efa_bic$Vaccounted %>% 
  data.frame() %>% 
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 2, factor solution suggested by minimizing BIC: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

We consider the first of these factors ("`r names(data.frame(s2_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s2_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensations_, the third ("`r names(data.frame(s2_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth and fifth ("`r names(data.frame(s2_efa_bic$loadings[]))[4]`" and "`r names(data.frame(s2_efa_bic$loadings[]))[5]`") to resonate with the construct we have called _negative affect_. The sixth factor ("`r names(data.frame(s2_efa_bic$loadings[]))[6]`") appears to pick out capacities particularly relevant to social interaction (e.g., social learning, love). We have no strong intuitions about how to interpret the seventh and eighth factors ("`r names(data.frame(s2_efa_bic$loadings[]))[7]`" and "`r names(data.frame(s2_efa_bic$loadings[]))[8]`").

```{r figS05 code, fig.width = 4.5, fig.asp = 1.2}
heatmap_fun(s2_efa_bic)

# save plot
if (resave_plots == T | !file.exists("../outputs/figS05.pdf")) {
  ggsave("../outputs/figS05.svg")
  ggsave("../outputs/figS05.pdf")
}
```

```{r figS05, fig.cap="Study 2, factor solution suggested by minimizing BIC.", include = F}
knitr::include_graphics("../outputs/figS05.pdf")
```

#### Weisman et al.'s (2017) factor retention criteria

```{r s2 weisman et al criteria}
s2_weismanetal <- reten_fun(d2_all, rot_type = "oblimin")
s2_weismanetal
```

```{r s2 efa weisman et al criteria}
s2_efa_wdm <- fa(d2_all, 
                 nfactors = s2_weismanetal, 
                 rotate = "oblimin") 
# s2_efa_wdm %>% fa.sort()
```

Weisman et al.'s (2017) factor retention criteria suggested retaining `r s2_weismanetal` factors—i.e., the same `r s2_weismanetal`-factor solution suggested by parallel analysis. (See Supplementary Tables \@ref(tab:tabs2efaparload) and \@ref(tab:tabs2efaparvacc).)

### Capacity ratings: Developmental trajectories

Our primary goal in Study 2 was to chart perceptions of the development of mental life over the first five years. As described in the main text, we preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 2:

(1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children.
(2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).

To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge. Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1). Attempting to model random slopes for domain or for target age resulted in model convergence problems. Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution. Domain was dummy-coded with _cognition and control_ as the baseline. The full results of this model are presented in Supplementary Tables \@ref(tab:tabs2gamfixed) and \@ref(tab:tabs2gamsmooth); see Figure 2, Panel A (main text) for a visualization of these perceived trajectories.

In brief, we view these results as confirming our hypotheses that US adults would rate older children as more capable across the board, but that perceptions of the development of children’s capacities would differ across domains. (See main text for extended interpretation.)

```{r s2 scales}
d2_scales <- s2_efa_par$loadings[] %>%
  data.frame() %>%
  rownames_to_column("capacity") %>%
  gather(factor, loading, -capacity) %>%
  group_by(factor) %>%
  top_n(5, loading) %>%
  ungroup() %>%
  mutate(factor = recode_factor(factor,
                                "MR3" = "Bodily sensations",
                                "MR1" = "Negative affect",
                                "MR4" = "Social connection",
                                "MR2" = "Cognition and control")) %>%
  arrange(factor, desc(loading)) %>%
  mutate(order = 1:nrow(.))
```

```{r s2 cap ratings dataset}
d2_cap_ratings <- d2_all %>%
  rownames_to_column("ResponseId_target") %>%
  separate(ResponseId_target, c("ResponseId", "target")) %>%
  mutate(target_year = recode(target,
                              target00mo = 0, # newborns
                              target0Xmo = 3/365, # 3 days
                              target01mo = 1/12, # 1 month
                              target02mo = 2/12, 
                              target04mo = 4/12, 
                              target06mo = 6/12, 
                              target09mo = 9/12,
                              target12mo = 12/12,
                              target18mo = 18/12,
                              target24mo = 24/12,
                              target36mo = 36/12,
                              target48mo = 48/12,
                              target60mo = 60/12)) %>%
    gather(capacity, response, -ResponseId, -starts_with("target")) %>%
  left_join(d2_scales %>% distinct(factor, capacity))
```

```{r s2 cap ratings summary stats}
d2_cap_ratings_sum <- d2_cap_ratings %>%
  group_by(factor, target_year) %>%
  summarise(median = median(response, na.rm = T),
            mean = mean(response, na.rm = T),
            sd = sd(response, na.rm = T)) %>%
  ungroup() %>%
  arrange(target_year, factor)

d2_cap_ratings_sum %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

```{r s2 gam dataset}
d2_gam <- d2_cap_ratings %>%
  # implement correction for beta distribution
  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
                              response/100 > 0.995 ~ 0.995,
                              TRUE ~ response/100))

contrasts(d2_gam$factor) <- cbind(bod_cog = c(1, 0, 0, 0),
                                  neg_cog = c(0, 1, 0, 0),
                                  soc_cog = c(0, 0, 1, 0))
```

```{r s2 gam}
if (!file.exists("../outputs/s2_gam.RDS")) {
  # takes ~20 minutes to run
  s2_gam <- gamm(response ~ s(target_year, by = factor) + factor, 
                 random = list(ResponseId = ~1,
                               capacity = ~1),
                 data = d2_gam,
                 family = betar,
                 method = "REML",
                 niterPQL = 40)

  saveRDS(s2_gam, "../outputs/s2_gam.RDS")

} else {
  s2_gam <- readRDS("../outputs/s2_gam.RDS")
}

summary(s2_gam$gam)
# model_parameters(s2_gam$gam)
```

```{r tabs2gam}
tabs2gam <- model_parameters(s2_gam$gam)
```

```{r tabs2gamfixed, include = T}
tabs2gam %>% 
  filter(Component == "conditional") %>%
  select(-c(df, df_error, Component)) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Cognition and control (intercept)",
    grepl("bod", Parameter) ~ "Bodily sensations vs. Cognition and control",
    grepl("neg", Parameter) ~ "Negative affect vs. Cognition and control",
    grepl("soc", Parameter) ~ "Social connection vs. Cognition and control"),
    p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T, 
        caption = "Study 2, GAM results: Parametric coefficients (fixed effects).",
        digits = 2, align = c("lrrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r tabs2gamsmooth, include = T}
tabs2gam %>% 
  filter(Component == "smooth_terms") %>%
  select(-c(Coefficient, SE, starts_with("CI"), df_error, Component)) %>%
  mutate(Parameter = case_when(
    grepl("Bod", Parameter) ~ "Target year: Bodily sensations",
    grepl("Neg", Parameter) ~ "Target year: Negative affect",
    grepl("Soc", Parameter) ~ "Target year: Social connection",
    grepl("Cog", Parameter) ~ "Target year: Cognition and control"),
    p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  rename(`Estimated df` = df) %>%
  kable("latex", booktabs = T, longtable = T, 
        caption = "Study 2, GAM results: Approximate significance of smooth terms.",
        digits = 2, align = c("lrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r s2 gam predictions}
d2_gam_r1_pred <- d2_gam %>%
  mutate(pred_score = predict.gam(s2_gam$gam, type = "response", 
                                  newdata = d2_gam)) %>%
  group_by(ResponseId, factor, target_year) %>%
  summarise(score = mean(response, na.rm = T),
            pred_score = mean(score, na.rm = T)) %>%
  ungroup()
```

```{r fig02a, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 2). Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
d2_gam_r1_rsq <- round_x(summary(s2_gam$gam)$r.sq, 2)

fig02a <- d2_gam_r1_pred %>%
  ggplot(aes(x = target_year, y = score, color = factor)) +
  facet_grid(~ factor) +
  geom_path(aes(group = ResponseId),
            # color = "#160072",
            alpha = 0.2, size = 0.02) +
  geom_smooth(aes(y = pred_score), 
              color = "#f94802",
              fill = NA, size = 1, lty = 1) +
  geom_pointrange(data = . %>%
                    group_by(factor, target_year) %>%
                    multi_boot_standard(col = "score") %>%
                    ungroup,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black",
                  # color = "#160072",
                  fatten = 1) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = seq(0, 100, 25)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Mean response\n0 = not at all capable, 100 = completely capable",
       caption = bquote(paste("Adjusted R"^"2"*" = ", .(d2_gam_r1_rsq)))) +
  guides(color = guide_none())

# # save plot
# if (resave_plots == T | !file.exists("../outputs/fig02a.pdf")) {
#   ggsave("../outputs/fig02a.svg")
#   ggsave("../outputs/fig02a.pdf")
# }
```

```{r s2 export results}
# save numerical results
s2_results <- list(demo = d2_demo,
                   efa = s2_efa_par,
                   efa_bic = s2_efa_bic,
                   efa_wdm = s2_efa_wdm,
                   cap_rat_ss = d2_cap_ratings_sum,
                   gam = s2_gam)

saveRDS(s2_results, "../outputs/s2_results.rds")
```

## Study 3

As described in the main text, Study 3 was designed with two goals in mind: First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2. Second, we aimed to probe the lay theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).

In the main text, we presented the results of a generalized additive model (GAM) predicting participants' capacity ratings as a function of target age, domain, and interactions between them; briefly described the dimensionality reduction analyses we used to group developmental mechanisms into two types ("intrinsic" and "extrinsic"); presented the results of a multilevel linear regression model predicting participants' ratings of developmental mechanisms as a function of mechanism type, domain, and an interaction between them; briefly mentioned additional models of each domain separately; and provided visualizations of participants' selections of the "most important" mechanism for each capacity, by domain. Here, we present the full results of all of these models, as well as the results of a multilevel logistic regression model of the selection of "most important" mechanism.

### Capacity ratings: Developmental trajectories

We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3 (identical to our hypotheses for Study 2):

(1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children.
(2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).

Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge. Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1). Again, attempting to model random slopes for domain or for target age resulted in model convergence problems. Again, responses were rescaled to range from 0.005 to 0.995, and domain was dummy-coded with _cognition and control_ as the baseline. The full results of this model are presented in Supplementary Tables \@ref(tab:tabs3gamfixed) and \@ref(tab:tabs3gamsmooth); see Figure 2, Panel B (main text) for a visualization of these perceived trajectories.

In brief, we view these results as confirming our hypotheses that US adults would rate older children as more capable across the board, but that perceptions of the development of children’s capacities would differ across domains. (See main text for extended interpretation.)

```{r s3 cap ratings dataset}
d3_cap_ratings <- d3 %>%
  mutate(target_year = target_num/12) %>%
  mutate(factor = recode_factor(domain,
                                "BOD" = "Bodily sensations",
                                "NEG" = "Negative affect",
                                "POS" = "Social connection",
                                "COG" = "Cognition and control")) %>%
  select(-domain)
```

```{r s3 cap ratings summary stats}
d3_cap_ratings_sum <- d3_cap_ratings %>%
  group_by(factor, target_year) %>%
  summarise(median = median(response, na.rm = T),
            mean = mean(response, na.rm = T),
            sd = sd(response, na.rm = T)) %>%
  ungroup() %>%
  arrange(target_year, factor)

d3_cap_ratings_sum %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

```{r s3 gam dataset}
d3_gam <- d3_cap_ratings %>%
  # implement correction for beta distribution
  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
                              response/100 > 0.995 ~ 0.995,
                              TRUE ~ response/100))

contrasts(d3_gam$factor) <- cbind(bod_cog = c(1, 0, 0, 0),
                                  neg_cog = c(0, 1, 0, 0),
                                  soc_cog = c(0, 0, 1, 0))
```

```{r s3 gam}
if (!file.exists("../outputs/s3_gam.RDS")) {
  # takes ~5 minutes to run
  s3_gam <- gamm(response ~ s(target_year, by = factor) + factor, 
                 random = list(ResponseId = ~1,
                               capacity = ~1),
                 data = d3_gam,
                 family = betar,
                 method = "REML",
                 niterPQL = 40)

  saveRDS(s3_gam, "../outputs/s3_gam.RDS")

} else {
  s3_gam <- readRDS("../outputs/s3_gam.RDS")
}

summary(s3_gam$gam)
```

```{r tabs3gam}
tabs3gam <- model_parameters(s3_gam$gam)
```

```{r tabs3gamfixed, include = T}
tabs3gam %>% 
  filter(Component == "conditional") %>%
  select(-c(df, df_error, Component)) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Cognition and control (intercept)",
    grepl("bod", Parameter) ~ "Bodily sensations vs. Cognition and control",
    grepl("neg", Parameter) ~ "Negative affect vs. Cognition and control",
    grepl("soc", Parameter) ~ "Social connection vs. Cognition and control"),
    p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T, 
        caption = "Study 3, GAM results: Parametric coefficients (fixed effects).",
        digits = 2, align = c("lrrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r tabs3gamsmooth, include = T}
tabs3gam %>% 
  filter(Component == "smooth_terms") %>%
  select(-c(Coefficient, SE, starts_with("CI"), df_error, Component)) %>%
  mutate(Parameter = case_when(
    grepl("Bod", Parameter) ~ "Target year: Bodily sensations",
    grepl("Neg", Parameter) ~ "Target year: Negative affect",
    grepl("Soc", Parameter) ~ "Target year: Social connection",
    grepl("Cog", Parameter) ~ "Target year: Cognition and control"),
    p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  rename(`Estimated df` = df) %>%
  kable("latex", booktabs = T, longtable = T, 
        caption = "Study 3, GAM results: Approximate significance of smooth terms.",
        digits = 2, align = c("lrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r s3 gam predictions}
d3_gam_r1_pred <- d3_gam %>%
  mutate(pred = predict.gam(s3_gam$gam, type = "response", 
                            newdata = d3_gam)) %>%
  group_by(ResponseId, factor, target_year) %>%
  summarise(score = mean(response, na.rm = T),
            pred_score = mean(score, na.rm = T)) %>%
  ungroup()
```

```{r fig02b, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 3). Scores were calculated by averaging a participant’s responses to the two capacity items for each domain of mental life. Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
d3_gam_r1_rsq <- round_x(summary(s3_gam$gam)$r.sq, 2)

fig02b <- d3_gam_r1_pred %>%
  ggplot(aes(x = target_year, y = score, color = factor)) +
  facet_grid(~ factor) +
  geom_path(aes(group = ResponseId),
            # color = "#160072",
            alpha = 0.2, size = 0.02) +
  geom_smooth(aes(y = pred_score), 
              color = "#f94802",
              fill = NA, size = 1, lty = 1) +
  geom_pointrange(data = . %>%
                    group_by(factor, target_year) %>%
                    multi_boot_standard(col = "score") %>%
                    ungroup,
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black",
                  # color = "#160072",
                  fatten = 1) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 1, 0.25),
                     labels = seq(0, 100, 25)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Mean response\n0 = not at all capable, 100 = completely capable",
       caption = bquote(paste("Adjusted R"^"2"*" = ", .(d3_gam_r1_rsq)))) +
  guides(color = guide_none())

# # save plot
# if (resave_plots == T | !file.exists("../outputs/fig02b.pdf")) {
#   ggsave("../outputs/fig02b.svg")
#   ggsave("../outputs/fig02b.pdf")
# }
```

```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3). Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions). In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age. In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 1.2}
plot_grid(fig02a, fig02b,
          ncol = 1, labels = "AUTO")

# save plot
if (resave_plots == T | !file.exists("../outputs/fig02.pdf")) {
  ggsave("../outputs/fig02.svg")
  ggsave("../outputs/fig02.pdf")
}
```

### Developmental mechanisms: Ratings

As a first step in assessing the lay theories underlying these perceptions of the development of human mental life, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study. We assessed a wide range of potential developmental mechanisms for children’s capacities. We applied a variety of dimensionality reduction approaches in order to sort these developmental mechanisms into meaningful categories, and then modeled participants' ratings of the importance of these mechanism as a function of domain (_bodily sensations_, _negative affect_, _social connection_, and _cognition and control_).

```{r s3 mech ratings datasets a}
d3_mech_ratings_wide <- d3_dev_factor_rating %>%
  select(-domain) %>%
  spread(dev_factor, response) %>%
  unite(RepsonseId_capacity, c(ResponseId, capacity)) %>%
  column_to_rownames("RepsonseId_capacity")
```

#### Dimensionality reduction

Here we present two dimensionality reduction approaches: EFA via parallel analysis (analogous to the EFAs of mental capacity attributions from Studies 1-2) and hierarchical clustering.

##### EFA (via parallel analysis)

```{r s3 parallel analysis}
set.seed(94305) # this does not appear to work well -- may need to try a few times
s3_parallel <- fa.parallel(d3_mech_ratings_wide, plot = F)
```

```{r s3 efa parallel analysis}
s3_efa_par <- fa(d3_mech_ratings_wide, 
                 nfactors = s3_parallel$nfact, 
                 rotate = "oblimin")
# s3_efa_par %>% fa.sort()
```

Parallel analysis suggested retaining `r s3_parallel$nfact` factors, which we labeled _extrinsic (passive)_, _extrinsic (active)_, _intrinsic (after birth)_, and _intrinsic (before birth)_. Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs3efaload); the amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs3efavacc).

```{r tabs3efaload, include = T, warning = F, message = F}
tabs3efaload <- model_parameters(s3_efa_par, sort = T) %>% 
  data.frame() %>% 
  rename(Capacity = Variable) %>%
  mutate(Capacity = gsub("_", " ", Capacity)) %>%
  mutate_at(vars(starts_with("MR")),
            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
  rename(`Extrinsic (passive)` = MR1,
         `Extrinsic (active)` = MR3,
         `Intrinsic (after birth)` = MR4,
         `Intrinsic (before birth)` = MR2)

tabs3efaload %>%
  select(-ends_with("_bold")) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 3, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
  column_spec(2, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+4]) %>%
  column_spec(3, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+5]) %>%
  column_spec(4, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+6]) %>%
  column_spec(5, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+7]) %>%
  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
```

```{r tabs3efavacc, include = T, warning = F, message = F}
s3_efa_par$Vaccounted %>% 
  data.frame() %>% 
  rename(`Extrinsic (passive)` = MR1,
         `Extrinsic (active)` = MR3,
         `Intrinsic (after birth)` = MR4,
         `Intrinsic (before birth)` = MR2) %>%
  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
        caption = "Study 3, factor solution suggested by parallel analysis: Variance accounted for.") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r figS06 code, fig.width = 4.5, fig.asp = 0.5}
heatmap_fun(s3_efa_par, 
            factor_names = c("Extrinsic (passive)",
                             "Intrinsic (before birth)",
                             "Extrinsic (active)",
                             "Intrinsic (after birth)"))

# save plot
if (resave_plots == T | !file.exists("../outputs/figS06.pdf")) {
  ggsave("../outputs/figS06.svg")
  ggsave("../outputs/figS06.pdf")
}
```

```{r figS06, fig.cap="Study 3, factor solution suggested by parallel analysis."}
# knitr::include_graphics("../outputs/figS06.pdf")
```

##### Hierarchical clustering

In addition to the EFA just described, we also conducted a hierarchical cluster analysis, using Euclidean distance and Ward's agglomeration method. The resulting dendrogram is presented in Supplementary Figure \@ref(fig:figS07). We view this as providing further support for the idea that these mechanisms can be sorted into two high-level categories: "extrinsic" mechanisms (left) and "intrinsic" mechanisms (right).

```{r figS07 code, fig.width = 3, fig.asp = 0.6}
d3_mech_ratings_wide %>% 
  rename_with(~recode(., 
                      "preprogrammed" = "biologically ‘preprogrammed’",
                      "womb_experiences" = "experiences in the womb",
                      "body_grows" = "body grows and matures",
                      "brain_changes" = "brain changes",
                      "senses_improve" = "senses improve",
                      "observes_objects" = "observes objects and physical world",
                      "experiments" = "actively experiments",
                      "observes_people" = "observes people",
                      "interacts_people" = "interacts with people",
                      "people_teach" = "people explicitly teach")) %>%
  remove_missing() %>% 
  as.matrix() %>% 
  t() %>%
  dist(method = "euclidean") %>%
  hclust(method = "ward") %>%
  ggdendrogram(rotate = F) +
  theme(axis.text.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        plot.margin = unit(c(5.5, 5.5, 5.5, 40), "points"))

# save plot
if (resave_plots == T | !file.exists("../outputs/figS07.pdf")) {
  ggsave("../outputs/figS07.svg")
  ggsave("../outputs/figS07.pdf")
}
```

```{r figS07, fig.cap="Hierarchical cluster analysis of importance ratings of developmental mechanisms (Study 3).", include = T}
knitr::include_graphics("../outputs/figS07.pdf")
```

#### Regression models

To assess which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*), we conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs. intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity). We also conducted separate, analogous regression analyses for each domain separately. In these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains. (Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see previous section.)

The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall) (all domains), \@ref(tab:tabs3lmerbod) (*bodily sensations*), \@ref(tab:tabs3lmerneg) (*negative affect*), \@ref(tab:tabs3lmersoc) (*social connection*), and \@ref(tab:tabs3lmercog) (*cognition and control*); see also Figure 3 (main text).

```{r s3 mech ratings datasets b}
d3_mech_ratings <- d3_dev_factor_rating %>%
  mutate(factor = recode_factor(domain,
                                "BOD" = "Bodily sensations",
                                "NEG" = "Negative affect",
                                "POS" = "Social connection",
                                "COG" = "Cognition and control")) %>%
  select(-domain) %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor %in% c("senses_improve", "body_grows", 
                      "womb_experiences", "preprogrammed") ~ "intrinsic",
    dev_factor %in% c("interacts_people", "observes_people", "observes_objects", 
                      "people_teach", "experiments") ~ "extrinsic",
    dev_factor == "brain_changes" ~ NA_character_,
    TRUE ~ NA_character_
  )) %>%
  mutate(dev_factor_cluster = factor(dev_factor_cluster,
                                     levels = c("intrinsic", "extrinsic")))

contrasts(d3_mech_ratings$factor) <- cbind(bod_gm = c(1, -1, 0, 0),
                                           soc_gm = c(0, -1, 1, 0),
                                           cog_gm = c(0, -1, 0, 1))

# contrasts(d3_mech_ratings$factor) <- cbind(bod_gm = c(1, 0, -1, 0),
#                                            neg_gm = c(0, 1, -1, 0),
#                                            cog_gm = c(0, 0, -1, 1))

contrasts(d3_mech_ratings$dev_factor_cluster) <- cbind(ext_gm = c(-1, 1))
```

```{r s3 mech ratings summary stats}
# overall
d3_mech_ratings_sum_a <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean of means for each cluster
  group_by(ResponseId, dev_factor_cluster) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means for each cluster 
  group_by(dev_factor_cluster) %>%
  summarise(median = median(score_a, na.rm = T),
            mean = mean(score_a, na.rm = T),
            sd = sd(score_a, na.rm = T)) %>%
  ungroup() %>%
  arrange(dev_factor_cluster)

d3_mech_ratings_sum_a %>%
  mutate_if(is.numeric, funs(round_x(., 2)))

# by domain
d3_mech_ratings_sum_b <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean for each mechanism, for each domain
  group_by(ResponseId, dev_factor_cluster, dev_factor, factor) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # participant-level mean of means for each cluster, for each domain
  group_by(ResponseId, dev_factor_cluster, factor) %>%
  summarise(score_b = mean(score_a, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means of means for each domain 
  group_by(dev_factor_cluster, factor) %>%
  summarise(median = median(score_b, na.rm = T),
            mean = mean(score_b, na.rm = T),
            sd = sd(score_b, na.rm = T)) %>%
  ungroup() %>%
  arrange(factor, dev_factor_cluster)

d3_mech_ratings_sum_b %>%
  mutate_if(is.numeric, funs(round_x(., 2)))

# mean DIFFERENCES by domain
d3_mech_ratings_sum_c <- d3_mech_ratings %>%
  filter(!is.na(dev_factor_cluster)) %>%
  # participant-level mean for each cluster, for each capacity
  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # participant-level cluster differences for each capacity
  spread(dev_factor_cluster, score_a) %>%
  mutate(diff_a = extrinsic - intrinsic) %>%
  select(-extrinsic, -intrinsic) %>%
  # participant-level mean differences, for each domain
  group_by(ResponseId, factor) %>%
  summarise(diff_b = mean(diff_a, na.rm = T)) %>%
  ungroup() %>%
  # group-level mean of means of mean differences, for each domain 
  group_by(factor) %>%
  summarise(median = median(diff_b, na.rm = T),
            mean = mean(diff_b, na.rm = T),
            sd = sd(diff_b, na.rm = T)) %>%
  ungroup() %>%
  arrange(factor)

d3_mech_ratings_sum_c %>%
  mutate_if(is.numeric, funs(round_x(., 2)))
```

##### All domains

In brief, this analysis suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important, but that the difference between intrinsic and extrinsic mechanisms varied across domains (see interaction terms).

```{r s3 mech ratings lmer}
s3_lmer <- lmer(response ~ dev_factor_cluster * factor + 
                  (1 + dev_factor_cluster + factor | ResponseId) + 
                  (1 | dev_factor) +
                  (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings)

summary(s3_lmer)
# model_parameters(s3_lmer)
```

```{r tabs3lmerall, include = T, message = F, warning = F}
model_parameters(s3_lmer, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Bodily sensations

For capacities in the domain of _bodily sensations_, this analysis suggested that participants rated intrinsic mechanisms as more important drivers of development than extrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer bod}
s3_lmer_bod <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Bodily sensations"))

summary(s3_lmer_bod)
# model_parameters(s3_lmer)
```

```{r tabs3lmerbod, include = T, message = F, warning = F}
model_parameters(s3_lmer_bod, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (bodily sensations): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Negative affect

For capacities in the domain of _negative affect_, this analysis suggested that participants rated intrinsic and extrinsic mechanisms as equally important drivers of development; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer neg}
s3_lmer_neg <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Negative affect"))

summary(s3_lmer_neg)
# model_parameters(s3_lmer)
```

```{r tabs3lmerneg, include = T, message = F, warning = F}
model_parameters(s3_lmer_neg, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (negative affect): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Social connection

For capacities in the domain of _social connection_, this analysis suggested that participants rated extrinsic mechanisms as more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer soc}
s3_lmer_soc <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Social connection"))

summary(s3_lmer_soc)
# model_parameters(s3_lmer)
```

```{r tabs3lmersoc, include = T, message = F, warning = F}
model_parameters(s3_lmer_soc, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (social connection): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Cognition and control

For capacities in the domain of _cognition and control_, this analysis suggested that participants rated extrinsic mechanisms as much more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).

```{r s3 mech ratings lmer cog}
s3_lmer_cog <- lmer(response ~ dev_factor_cluster + 
                      (1 + dev_factor_cluster | ResponseId) + 
                      (1 | dev_factor) + 
                      (1 | capacity),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_mech_ratings %>% 
                  filter(factor == "Cognition and control"))

summary(s3_lmer_cog)
# model_parameters(s3_lmer)
```

```{r tabs3lmercog, include = T, message = F, warning = F}
model_parameters(s3_lmer_cog, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(df = df_error) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel linear model results (cognition and control): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r fig03a, fig.width = 4.5, fig.asp = 1.5}
fig03a <- d3_mech_ratings %>%
  mutate(dev_factor_cluster = case_when(
    is.na(dev_factor_cluster) ~ "Other",
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC mechanisms",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC mechanisms"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC mechanisms", 
                                           "EXTRINSIC mechanisms",
                                           "Other")),
    dev_factor_text = recode_factor(
      dev_factor,
      "preprogrammed" = "biologically ‘preprogrammed’",
      "womb_experiences" = "experiences in the womb",
      "body_grows" = "body grows and matures",
      "brain_changes" = "brain changes",
      "senses_improve" = "senses improve",
      "observes_objects" = "observes objects and physical world",
      "experiments" = "actively experiments",
      "observes_people" = "observes people",
      "interacts_people" = "interacts with people",
      "people_teach" = "people explicitly teach"),
    capacity = str_wrap(gsub("_", " ", capacity), 14)) %>%
  ggplot(aes(x = reorder(str_wrap(dev_factor_text, 20), 
                         as.numeric(dev_factor)), 
             y = response, color = factor)) +
  facet_grid(rows = vars(reorder(capacity, as.numeric(factor))),
             cols = vars(dev_factor_cluster),
             scales = "free", space = "free") +
  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
  geom_jitter(alpha = 0.6, size = 0.02) +
  geom_pointrange(data = . %>%
                    group_by(factor, capacity, 
                             dev_factor_cluster, 
                             dev_factor, dev_factor_text) %>%
                    multi_boot_standard(col = "response") %>%
                    ungroup(),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", fatten = 2) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism",
       y = "Response (0 = not at all important, 6 = extremely important)",
       color = "Domain") +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
```

```{r fig03b, fig.width = 1.5, fig.asp = 6.75/1.5}
fig03b <- d3_mech_ratings %>%
  # filter(!is.na(dev_factor_cluster)) %>%
  filter(!is.na(dev_factor)) %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor == "brain_changes" ~ "brain changes",
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC", 
                                           "EXTRINSIC",
                                           "brain changes"))) %>%  
  # participant-level means for each cluster, by capacity
  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
  summarise(score_a = mean(response, na.rm = T)) %>%
  ungroup() %>%
  # participant-level mean of means for each cluster, by domain
  group_by(ResponseId, dev_factor_cluster, factor) %>%
  summarise(score_b = mean(score_a, na.rm = T)) %>%
  ungroup() %>%
  mutate(blank_var = "  ") %>%
  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
                                 width = 28, side = "left"),
                         as.numeric(dev_factor_cluster)), 
             y = score_b, color = factor)) +
  facet_grid(cols = vars(blank_var),
             rows = vars(reorder(toupper(factor), as.numeric(factor))),
             scales = "free", space = "free") +
  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
  geom_path(data = . %>%
              filter(dev_factor_cluster != "brain changes"),
            aes(group = ResponseId), 
            alpha = 0.1, size = 0.02,
            position = position_jitter(width = 0.2, 
                                       height = 0, 
                                       seed = 94305)) +
  geom_point(alpha = 0.6, size = 0.02,
             position = position_jitter(width = 0.2, 
                                        height = 0, 
                                        seed = 94305)) +
  # group-level mean of means of means for each cluster, by domain
  geom_pointrange(data = . %>%
                    group_by(factor, dev_factor_cluster) %>%
                    multi_boot_standard(col = "score_b") %>%
                    ungroup(),
                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", fatten = 2) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism type",
       y = "Mean response (0 = not at all important, 6 = extremely important)",
       color = "Domain") +
  guides(color = guide_none())
  # guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
# fig03b
```

### Developmental mechanisms: Selection of "most important"

As described in the main text, we also assessed participants' responses to forced-choice questions about the "most important" factor driving the development of each of these capacities. In the main text, we presented a visualization of these choices (Figure 3, Panel C). Here, we present multilevel generalized linear model (logistic regressions) to predict the likelihood of selecting extrinsic vs. intrinsic mechanisms by domain. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: glmer(choice of extrinsic mechanism ~ domain + (1 | participant) + (1 | capacity). We also conducted separate, analogous regression analyses for each domain separately. In these analyses, domain was effect-coded for comparisons to the grand mean collapsing across domains. (As in the previous section, these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses.)

The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3glmerall) (all domains), \@ref(tab:tabs3glmerbod) (*bodily sensations*), \@ref(tab:tabs3glmerneg) (*negative affect*), \@ref(tab:tabs3glmersoc) (*social connection*), and \@ref(tab:tabs3glmercog) (*cognition and control*); see also Figure 3 (main text).

```{r s3 mech choice datasets}
d3_mech_choice <- d3_dev_factor_most_important_choice %>%
  mutate(factor = recode_factor(domain,
                                "BOD" = "Bodily sensations",
                                "NEG" = "Negative affect",
                                "POS" = "Social connection",
                                "COG" = "Cognition and control"),
         dev_factor = recode_factor(
           response,
           "The child is biologically \"preprogrammed\" to have this ability" = "preprogrammed",
           "The child has experiences in the womb that give them this ability" = "womb_experiences",
           "The child's body grows and matures (for example, muscles get stronger, child gets taller)" = "body_grows",
           "The child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" = "brain_changes",
           "The child's senses improve (for example, vision gets sharper, hearing improves)" = "senses_improve",
           "The child observes the objects and the physical world around him or her" = "observes_objects",
           "The child actively experiments with how to do this" = "experiments",
           "The child observes the people around him or her" = "observes_people",
           "The child interacts with the people around him or her" = "interacts_people",
           "People explicitly teach the child how to do this" = "people_teach",
           .default = "other")) %>%
  select(-domain, -response) %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor %in% c("senses_improve", "body_grows", 
                      "womb_experiences", "preprogrammed") ~ "intrinsic",
    dev_factor %in% c("interacts_people", "observes_people", "observes_objects", 
                      "people_teach", "experiments") ~ "extrinsic",
    dev_factor == "brain_changes" ~ NA_character_,
    TRUE ~ NA_character_
  )) %>%
  mutate(dev_factor_cluster = factor(dev_factor_cluster,
                                     levels = c("intrinsic", "extrinsic")))

contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, -1, 0, 0),
                                           soc_gm = c(0, -1, 1, 0),
                                           cog_gm = c(0, -1, 0, 1))

# contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, 0, -1, 0),
#                                            neg_gm = c(0, 1, -1, 0),
#                                            cog_gm = c(0, 0, -1, 1))

contrasts(d3_mech_choice$dev_factor_cluster) <- cbind(ext_gm = c(-1, 1))
```

```{r s3 mech choice summary stats}
# overall
d3_mech_choice_sum_a <- d3_mech_choice %>%
  count(dev_factor_cluster) %>%
  mutate(prop = n/sum(n))

d3_mech_choice_sum_a %>%
  mutate_at(vars(prop), funs(round_x(., 2)))

# by domain
d3_mech_choice_sum_b <- d3_mech_choice %>%
  count(factor, dev_factor_cluster) %>%
  group_by(factor) %>%
  mutate(prop = n/sum(n)) %>%
  ungroup()

d3_mech_choice_sum_b %>%
  mutate_at(vars(prop), funs(round_x(., 2)))
```

##### All domains

This analysis suggested that participants' choice of extrinsic vs. intrinsic mechanisms as the "most important" driver of development varied by domain (see interaction terms).

```{r s3 mech choice glmer}
s3_glmer <- glmer(extrinsic ~ factor + 
                    (1 | ResponseId) + 
                    (1 | capacity),
                  control = glmerControl(optimizer = "bobyqa"),
                  data = d3_mech_choice %>%
                    mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
                                                 dev_factor_cluster == "intrinsic" ~ 0,
                                                 is.na(dev_factor_cluster) ~ NA_real_,
                                                 TRUE ~ NA_real_)),
                  family = "binomial")

summary(s3_glmer)
# model_parameters(s3_glmer)
```

```{r tabs3glmerall, include = T, message = F, warning = F}
model_parameters(s3_glmer, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel generalized linear model results (all domains): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Bodily sensastions

For capacities in the domain of _bodily sensations_, this analysis suggested that participants were much more likely to select intrinsic mechanisms than extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).

```{r s3 mech choice glmer bodily sensations}
s3_glmer_bod <- glmer(extrinsic ~ 1 + 
                        (1 | ResponseId) + 
                        (1 | capacity),
                      control = glmerControl(optimizer = "bobyqa"),
                      data = d3_mech_choice %>%
                        filter(factor == "Bodily sensations") %>%
                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
                                                     dev_factor_cluster == "intrinsic" ~ 0,
                                                     is.na(dev_factor_cluster) ~ NA_real_,
                                                     TRUE ~ NA_real_)),
                      family = "binomial")

summary(s3_glmer_bod)
# model_parameters(s3_glmer)
```

```{r tabs3glmerbod, include = T, message = F, warning = F}
model_parameters(s3_glmer_bod, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel generalized linear model results (bodily sensations): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Negative affect

For capacities in the domain of _negative affect_, this analysis suggested that participants were equally likely to select intrinsic and extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).

```{r s3 mech choice glmer negative affect}
s3_glmer_neg <- glmer(extrinsic ~ 1 + 
                        (1 | ResponseId) + 
                        (1 | capacity),
                      control = glmerControl(optimizer = "bobyqa"),
                      data = d3_mech_choice %>%
                        filter(factor == "Negative affect") %>%
                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
                                                     dev_factor_cluster == "intrinsic" ~ 0,
                                                     is.na(dev_factor_cluster) ~ NA_real_,
                                                     TRUE ~ NA_real_)),
                      family = "binomial")

summary(s3_glmer_neg)
# model_parameters(s3_glmer)
```

```{r tabs3glmerneg, include = T, message = F, warning = F}
model_parameters(s3_glmer_neg, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel generalized linear model results (negative affect): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Social connection

For capacities in the domain of _social connection_, this analysis suggested that participants were equally likely to select intrinsic and extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).

```{r s3 mech choice glmer social connection}
s3_glmer_soc <- glmer(extrinsic ~ 1 + 
                        (1 | ResponseId) + 
                        (1 | capacity),
                      control = glmerControl(optimizer = "bobyqa"),
                      data = d3_mech_choice %>%
                        filter(factor == "Social connection") %>%
                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
                                                     dev_factor_cluster == "intrinsic" ~ 0,
                                                     is.na(dev_factor_cluster) ~ NA_real_,
                                                     TRUE ~ NA_real_)),
                      family = "binomial")

summary(s3_glmer_soc)
# model_parameters(s3_glmer)
```

```{r tabs3glmersoc, include = T, message = F, warning = F}
model_parameters(s3_glmer_soc, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel generalized linear model results (social connection): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

##### Cognition and control

For capacities in the domain of _cognition and control_, this analysis suggested that participants were much more likely to select extrinsic mechanisms than intrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).

```{r s3 mech choice glmer cognition and control}
s3_glmer_cog <- glmer(extrinsic ~ 1 + 
                        (1 | ResponseId) + 
                        (1 | capacity),
                      control = glmerControl(optimizer = "bobyqa"),
                      data = d3_mech_choice %>%
                        filter(factor == "Cognition and control") %>%
                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
                                                     dev_factor_cluster == "intrinsic" ~ 0,
                                                     is.na(dev_factor_cluster) ~ NA_real_,
                                                     TRUE ~ NA_real_)),
                      family = "binomial")

summary(s3_glmer_cog)
# model_parameters(s3_glmer)
```

```{r tabs3glmercog, include = T, message = F, warning = F}
model_parameters(s3_glmer_cog, standardize = "refit") %>%
  filter(Effects == "fixed") %>%
  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
  mutate(Parameter = case_when(
    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
    TRUE ~ Parameter)) %>%
  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
  select(-starts_with("CI")) %>%
  select(Parameter, Coefficient, `95% CI`, everything()) %>%
  rename(`Coefficient (log-odds)` = Coefficient) %>%
  kable("latex", booktabs = T, longtable = T,
        caption = "Study 3, multilevel generalized linear model results (cognition and control): Fixed effects.",
        digits = 2, align = c("lrrrrrr")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)
```

```{r figS08a, fig.width = 4.5, fig.asp = 1.5}
figS08a <- d3_mech_choice %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC mechanisms",
    is.na(dev_factor_cluster) ~ "Other",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC mechanisms"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC mechanisms", 
                                           # "Other",
                                           "EXTRINSIC mechanisms")),
    dev_factor_text = recode_factor(
      dev_factor,
      "preprogrammed" = "biologically ‘preprogrammed’",
      "womb_experiences" = "experiences in the womb",
      "body_grows" = "body grows and matures",
      "brain_changes" = "brain changes",
      "senses_improve" = "senses improve",
      "observes_objects" = "observes objects and physical world",
      "experiments" = "actively experiments",
      "observes_people" = "observes people",
      "interacts_people" = "interacts with people",
      "people_teach" = "people explicitly teach"),
    capacity = str_wrap(gsub("_", " ", capacity), 14)) %>%
  ggplot(aes(x = reorder(str_wrap(dev_factor_text, 20), 
                         as.numeric(dev_factor)), 
             fill = factor, color = factor)) +
  facet_grid(rows = vars(reorder(capacity, as.numeric(factor))),
             cols = vars(dev_factor_cluster),
             scales = "free_x", space = "free_x") +
  geom_bar(stat = "count", alpha = 0.6) +
  scale_fill_viridis_d(end = 0.9, option = "viridis", 
                       aesthetics = c("color", "fill")) +
  scale_y_continuous(breaks = seq(0, 
                                  d3_mech_choice %>% 
                                    distinct(ResponseId) %>% 
                                    count() %>% 
                                    pull(n), 
                                  100),
                     limits = c(0, 
                                d3_mech_choice %>% 
                                  distinct(ResponseId) %>% 
                                  count() %>% 
                                  pull(n))) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism",
       y = "Count of responses",
       color = "Domain", fill = "Domain") +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
```

```{r figS08b, fig.width = 1.5, fig.asp = 6.75/1.5}
figS08b <- d3_mech_choice %>%
  filter(!is.na(dev_factor_cluster)) %>%
  count(dev_factor_cluster, factor) %>%
  mutate(dev_factor_cluster = case_when(
    # is.na(dev_factor_cluster) ~ "Other",
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC", 
                                           "EXTRINSIC")),
                                           # "Other")),
    blank_var = "  ") %>%
  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
                                 width = 28, side = "left"),
                         as.numeric(dev_factor_cluster)),
             y = n,
             fill = factor, color = factor)) +
  facet_grid(cols = vars(blank_var),
             rows = vars(reorder(toupper(factor), as.numeric(factor))),
             scales = "free_x", space = "free_x") +
  geom_bar(stat = "identity", alpha = 0.6) +
  scale_fill_viridis_d(end = 0.9, option = "viridis", aesthetics = c("color", "fill")) +
  scale_y_continuous(breaks = seq(0, 
                                  2 * d3_mech_choice %>% 
                                    distinct(ResponseId) %>% 
                                    count() %>% 
                                    pull(n), 
                                  2 * 100),
                     limits = c(0, 
                                2 * d3_mech_choice %>% 
                                  distinct(ResponseId) %>% 
                                  count() %>% 
                                  pull(n))) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism type",
       y = "Count of responses",
       color = "Domain", fill = "Domain") +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
# figS08b
```

```{r figS08, fig.cap="XX", fig.width = 4.5, fig.asp = 6.75/6}
plot_grid(figS08a + guides(fill = guide_none(), color = guide_none()),
          figS08b + guides(fill = guide_none(), color = guide_none()) + labs(y = NULL), 
          nrow = 1, rel_widths = c(4.5, 1.5), labels = "AUTO")

# save plot
if (resave_plots == T | !file.exists("../outputs/figS08.pdf")) {
  ggsave("../outputs/figS08.svg")
  ggsave("../outputs/figS08.pdf")
}
```

```{r fig03c, fig.width = 1.5, fig.asp = 6.75/1.5}
fig03c <- d3_mech_choice %>%
  # filter(!is.na(dev_factor_cluster)) %>%
  filter(dev_factor != "other") %>%
  mutate(dev_factor_cluster = case_when(
    dev_factor == "brain_changes" ~ "brain changes",
    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
    dev_factor_cluster = factor(dev_factor_cluster,
                                levels = c("INTRINSIC", 
                                           "EXTRINSIC",
                                           "brain changes"))) %>%
  count(dev_factor_cluster, factor) %>%
  mutate(blank_var = "  ") %>%
  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
                                 width = 28, side = "left"),
                         as.numeric(dev_factor_cluster)),
             y = n,
             fill = factor, color = factor)) +
  facet_grid(cols = vars(blank_var),
             rows = vars(reorder(toupper(factor), as.numeric(factor))),
             scales = "free_x", space = "free_x") +
  geom_bar(stat = "identity", alpha = 0.6) +
  scale_fill_viridis_d(end = 0.9, option = "viridis", aesthetics = c("color", "fill")) +
  scale_y_continuous(breaks = seq(0, 
                                  2 * d3_mech_choice %>% 
                                    distinct(ResponseId) %>% 
                                    count() %>% 
                                    pull(n), 
                                  2 * 100),
                     limits = c(0, 
                                2 * d3_mech_choice %>% 
                                  distinct(ResponseId) %>% 
                                  count() %>% 
                                  pull(n))) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA), 
        strip.text = element_text(vjust = 0),
        legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
  labs(x = "Developmental mechanism type",
       y = "Count of responses",
       color = "Domain", fill = "Domain") +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
# fig03c
```

```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism. Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs. intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs. intrinsic mechanisms as the 'most important' driver of development. Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals. The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 5, fig.asp = 6.75/(4.5 + 1.5 + 1.5)}
plot_grid(fig03a + guides(color = guide_none()),
          NULL, # to adjust spacing between panels
          fig03b, # + labs(x = " "),
          NULL,
          fig03c + 
            labs(x = " ",
                 y = "Selection of 'most important' mechanism") +
            scale_y_continuous(limits = c(0, 2*nrow(d3_demo)),
                               breaks = c(0, nrow(d3_demo), 2*nrow(d3_demo)),
                               labels = c("0%", "50%", "100%")) +
            guides(fill = guide_none(),
                   color = guide_none()), 
          nrow = 1, rel_widths = c(4.5, 0.1, 1.5, 0.1, 1.5), 
          labels = c("A", "", "B", "", "C"))

# save plot
if (resave_plots == T | !file.exists("../outputs/fig03.pdf")) {
  ggsave("../outputs/fig03.svg")
  ggsave("../outputs/fig03.pdf")
}
```

```{r s3 export results}
# save numerical results
s3_results <- list(demo = d3_demo,
                   cap_rat_ss = d3_cap_ratings_sum,
                   mech_rat_ss_a = d3_mech_ratings_sum_a,
                   mech_rat_ss_b = d3_mech_ratings_sum_b,
                   mech_rat_ss_c = d3_mech_ratings_sum_c,
                   gam = s3_gam, 
                   lmer = s3_lmer, 
                   lmer_bod = s3_lmer_bod,
                   lmer_neg = s3_lmer_neg,
                   lmer_soc = s3_lmer_soc,
                   lmer_cog = s3_lmer_cog,
                   mech_choice_ss_a = d3_mech_choice_sum_a,
                   mech_choice_ss_b = d3_mech_choice_sum_b,
                   glmer = s3_glmer, 
                   glmer_bod = s3_glmer_bod,
                   glmer_neg = s3_glmer_neg,
                   glmer_soc = s3_glmer_soc,
                   glmer_cog = s3_glmer_cog)

saveRDS(s3_results, "../outputs/s3_results.rds")
```

```{r}
# ADDITIONAL EXPLORATORY ANALYSES  NOT DESCRIBED IN SUPPLEMENT
```

```{r figS09a, fig.width = 4.5, fig.asp = 0.4}
figS09a <- d2_gam %>% 
  group_by(factor, capacity, target_year) %>%
  summarise(var = var(response, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = target_year, y = var, color = factor)) +
  facet_grid(cols = vars(factor)) +
  geom_path(aes(group = capacity), 
            alpha = 0.1, size = 0.5,
            position = position_jitter(width = 0.2, 
                                       height = 0, 
                                       seed = 94305)) +
  geom_point(alpha = 1, size = 0.5,
             position = position_jitter(width = 0.2, 
                                        height = 0, 
                                        seed = 94305)) +
  geom_text(data = . %>% 
              filter(target_year == 5) %>%
              group_by(factor) %>%
              filter(var == max(var) | var == min(var)) %>%
              ungroup(),
            aes(x = 5.2, label = str_wrap(gsub("_", " ", capacity), 18)),
            color = "black", hjust = 0, size = 2) +
  geom_pointrange(data = . %>%
                    group_by(factor) %>%
                    multi_boot_standard(col = "var") %>%
                    ungroup(),
                  aes(x = 2.5, y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", shape = 15, size = 0.5) +
  geom_pointrange(data = . %>%
                    filter(target_year == 0) %>%
                    group_by(factor) %>%
                    multi_boot_standard(col = "var") %>%
                    ungroup(),
                  aes(x = -0.5, y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "#f94802", shape = 15, size = 0.3) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_x_continuous(limits = c(NA, 9), breaks = seq(0, 5, 1)) +
  scale_y_continuous(limits = c(0, 0.16)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Variance") +
  guides(color = guide_none())
```

```{r figS09b, fig.width = 4.5, fig.asp = 0.4}
figS09b <- d3_gam %>% 
  group_by(factor, capacity, target_year) %>%
  summarise(var = var(response, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = target_year, y = var, color = factor)) +
  facet_grid(cols = vars(factor)) +
  geom_path(aes(group = capacity), 
            alpha = 0.1, size = 0.5,
            position = position_jitter(width = 0.2, 
                                       height = 0, 
                                       seed = 94305)) +
  geom_point(alpha = 1, size = 0.5,
             position = position_jitter(width = 0.2, 
                                        height = 0, 
                                        seed = 94305)) +
  geom_text(data = . %>% filter(target_year == 5),
            aes(x = 5.2, label = str_wrap(gsub("_", " ", capacity), 18)),
            color = "black", hjust = 0, size = 2) +
  geom_pointrange(data = . %>%
                    group_by(factor) %>%
                    multi_boot_standard(col = "var") %>%
                    ungroup(),
                  aes(x = 2.5, y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "black", shape = 15, size = 0.5) +
  geom_pointrange(data = . %>%
                    filter(target_year == 0) %>%
                    group_by(factor) %>%
                    multi_boot_standard(col = "var") %>%
                    ungroup(),
                  aes(x = -0.5, y = mean, ymin = ci_lower, ymax = ci_upper),
                  color = "#f94802", shape = 15, size = 0.3) +
  scale_color_viridis_d(end = 0.9, option = "viridis") +
  scale_x_continuous(limits = c(NA, 9), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 0.16)) +
  theme_minimal() +
  theme(panel.background = element_rect(fill = NA)) +
  labs(x = "Target age (years)",
       y = "Variance") +
  guides(color = guide_none())
```

```{r figS09 code, fig.width = 4, fig.asp = 1.2}
plot_grid(figS09a, figS09b,
          ncol = 1, labels = "AUTO")

# save plot
if (resave_plots == T | !file.exists("../outputs/figS09.pdf")) {
  ggsave("../outputs/figS09.svg")
  ggsave("../outputs/figS09.pdf")
}
```

```{r figS09, fig.cap="Variance of capacity attributions in four domains of mental life (Studies 2-3). Lighter dots and lines represent variance across participnts for a particular capacity at a particular target age, red points correpond to mean variance across capacities at birth, black points correspond to mean variance across capacities and across all target ages, and error bars are bootstrapped 95% confidence intervals. In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age. In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity."}
knitr::include_graphics("../outputs/figS09.pdf")
```

# Selection of capacities: Comparison to previous studies

Supplementary Table \@ref(tab:tabs1efaparload) provides an item-by-item comparison of the capacities included in this study to capacities included in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].

```{r capacities comparison df}
d_cap_comp <- read_csv("../data/capacities_comparison.csv") %>%
  mutate_if(is.character, funs(tolower(.))) %>%
  mutate_if(is.character, funs(gsub("recognizing others.", "recognizing others'", .))) %>%
  mutate_if(is.character, funs(gsub("self.control", "self-control", .))) %>%
  left_join(d1_scales %>%
              mutate(capacity = gsub("_", " ", capacity),
                     capacity = gsub("recognizing others ", "recognizing others' ", capacity),
                     capacity = gsub("self.control", "self-control", capacity)) %>%
              rename(`Study 1` = capacity)) %>%
  mutate_at(vars(`Weisman et al. (2017a)`, `Weisman et al. (2017b)`, 
                 `Gray et al. (2007)`, `Malle (2019, Study 1)`, `Malle (2019, Study 2)`),
            funs(case_when(is.na(`Study 1`) & grepl("similar to", .) ~ NA_character_, TRUE ~ .))) %>%
  arrange(order, `Weisman et al. (2017a)`, `Weisman et al. (2017b)`, 
          `Gray et al. (2007)`, `Malle (2019, Study 1)`, `Malle (2019, Study 2)`) %>%
  filter(!(is.na(`Study 1`) & 
             is.na(`Weisman et al. (2017a)`) &
             is.na(`Weisman et al. (2017b)`) &
             is.na(`Gray et al. (2007)`) &
             is.na(`Malle (2019, Study 1)`) & 
             is.na(`Malle (2019, Study 2)`))) %>%
  mutate_if(is.character, funs(replace_na(., "-"))) %>%
  mutate(factor = case_when(is.na(factor) ~ "Not included", TRUE ~ as.character(factor)),
         factor = factor(factor, 
                         levels = c("Bodily sensations", "Negative affect",
                                    "Social connection", "Cognition and control", 
                                    "Not included"))) %>%
  select(factor, everything(), -loading, -order) %>%
  rename(Domain = factor) %>%
  ungroup()
```

```{r tabcapcomp, include = T, warning = F, message = F}
d_cap_comp %>%
  select(-Domain) %>%
  mutate(`Study 1` = case_when(`Study 2` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(1)),
                               TRUE ~ `Study 1`)) %>%
  mutate(`Study 1` = case_when(`Study 3` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(2)),
                               TRUE ~ `Study 1`)) %>%
  select(-`Study 2`, -`Study 3`) %>%
  mutate_at(vars(`Gray et al. (2007)`),
            funs(gsub("\\..*", "", .))) %>%
  kable("latex", booktabs = T, escape = F, longtable = T) %>%
  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 8) %>%
  add_header_above(c("Current studies" = 1,
                     "Previous studies" = 5)) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2:6, width = "2cm") %>%
  pack_rows(group_label = "Bodily sensations", start_row = 1, end_row = 11) %>%
  pack_rows("Negative affect", 12, 16) %>%
  pack_rows("Social connection", 17, 38) %>%
  pack_rows("Cognition and control", 39, 60) %>%
  pack_rows("Not included", 61, nrow(d_cap_comp)) %>%
  footnote(symbol = c("Also used in Study 2; ", "Also unsed in Study 3"),
           symbol_title = "Notes: ",
           footnote_as_chunk = T)
```

\newpage
# References

### 2021-07-31 paper/paper.Rmd
paper

---
title: "Beliefs about the development of mental life"
author: "[Authors removed to preserve anonymity]"
output:
  # word_document:
  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
    latex_engine: xelatex
    fig_caption: yes
    toc: false
bibliography: "../supplement/references.bib"
# cls: "../supplement/article.cls"
csl: "../supplement/nature.csl"
figsintext: yes
header-includes: 
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{float}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load-required-data, include = F}
library(ggdendro)
library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(tidyverse)
library(cowplot)

s1_results <- readRDS("../outputs/s1_results.rds")
s2_results <- readRDS("../outputs/s2_results.rds")
s3_results <- readRDS("../outputs/s3_results.rds")
```

```{r load custom funs, include = F}
source("../code/custom_funs.R")
```

## Abstract

In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life. Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_. Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (e.g., biological "preprogramming," physical maturation, passive observation, social learning). These studies reveal the lay theories that govern US adults’ understanding of the development of the human mind, illuminating the cognitive architecture that supports some of the most important social interactions: caregiving relationships with infants and children.

\newpage

Frustration, compassion, worry, humor, imagination, love—such experiences are fundamental parts of human life. But few people would assert that these capacities are fully developed at birth. In any given interaction with a child, adults come face to face with a being whose experience of the world is like their own, but different; whose mind is capable of some of the thoughts and feelings that an adult’s mind is, but perhaps not all of them. When an adult interacts with the same child over time, they witness innumerable changes in that child’s mental life: A sleepy newborn gradually becomes a child who experiences complex emotions and original ideas and develops personal memories and intricate plans. This familiar but remarkable transformation requires adults to make inferences about a given child’s developing mental capacities in order to interpret that child’s behaviors and respond appropriately.

In this paper, we examine how adults conceptualize the developing minds of infants and children. We draw on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed. In a groundbreaking study, Gray et al. asked participants to compare the mental capacities of a range of humans, animals, technologies, and other entities, and argued that participants’ judgments revealed a fundamental distinction between "agency" (e.g., capacities for self-control, moral reasoning, memory, and planning) and "experience" (e.g., capacities for hunger, fear, pain, and pleasure) [@gray.etal2007]. More recently, Weisman et al. used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a]); see [@malle2019] for a similar three-factor solution.

However, the burgeoning field of mind perception has largely neglected the question of how the mind emerges over development. In many studies, infants and children have simply not been included as targets for mental capacity attributions; instead, participants have been asked to reason about human adults alongside a range of non-human entities, including other animals, technologies, and supernatural beings. Even studies that have probed participants’ mental capacity attributions to infants and children have generally treated them as beings distinct from adults, rather than as snapshots of a single mind as it emerges and changes over time. For example, Gray et al.’s early work on mind perception suggested that a five-month-old infant is an entity that is generally considered to have experience but not agency—in contrast to, say, a five-year-old child (considered to have experience as well as limited agency), a human adult (considered to have maximal experience and agency), or a robot (considered to have agency but not experience) [@gray.etal2007]. Likewise, Weisman et al.’s studies characterized infants and young children—along with, e.g., chimpanzees, elephants, and dolphins—as entities that are perceived to be fully capable of physiological sensations but more limited in their perceptual-cognitive capacities and social-emotional abilities; this is in contrast to human adults, who are perceived to be fully capable across these domains [@weisman.etal2017a].

Although such findings can be reinterpreted as providing preliminary evidence that people consider the minds of infants and children to differ from the minds of adults, they do not address how people conceptualize the development of the mind in early life.

Of course, infants and young children are far from unusual social partners. Caregiving relationships are at the core of human existence; for many people, infants and young children are among the most frequent and highly valued minds that we encounter. Caring for a young child involves making countless decisions under uncertainty: Why is my child crying, smiling, shouting, or biting? Can they understand what I am saying? Does my child love me? As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.

In the current studies we set out to investigate this important and understudied aspect of mind perception: how ordinary people reason about the development of human mental life. In three studies, we assessed US adults’ folk beliefs about children’s developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of "mental life," broadly construed. We focused on development between birth and age five years—a time of particularly dramatic maturation in perceptual acuity, emotional experience, cognitive ability, executive function, social engagement, and many other domains.

# Results

## Study 1

We began with an expansive exploration of US adults’ attributions of mental life to infants and young children of different ages. Drawing inspiration from previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018] as well as standard assessments of infant temperament and behavior [@putnam.etal2006; @rothbart1978], we included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction. We asked participants ($n$ = `r s1_results$demo %>% distinct() %>% nrow()`) to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life: What do people perceive to be the fundamental components of mental life, as they pertain to a developing human child?

We designed Study 1 to explore the correlational structure of participants’ responses, as a window into the underlying conceptual structure that might support their reasoning about the development of mental life. Our primary analysis for this preregistered study was an exploratory factor analysis (EFA) of participants’ capacity ratings. This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children. For example, when a participant indicated that newborns are highly capable of feeling scared, what other capacities did they tend to attribute to newborns? Following previous work on mind perception, we argue that the suites of capacities revealed by applying dimensionality reduction (in our case, EFA) to this covariance structure offer a meaningful approximation of the latent conceptual structure underlying participants’ reasoning about the developing human mind.

A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions. See Figure \@ref(fig:fig01) for all factor loadings after oblique transformation.

The first factor corresponded primarily to capacities related to thinking, reasoning, agency, and executive function—a suite of capacities that we will refer to as _cognition and control_. It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," and "understanding what somebody else is thinking," and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.

The second factor corresponded primarily to social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we will refer to as _social connection_. It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", and "getting pleasure from music", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants’ capacity attributions.

The third factor corresponded primarily to physiological sensations related to biological needs—a suite of capacities that we will refer to as _bodily sensations_. It was the dominant factor for such items as "getting hungry", "feeling pain", "feeling tired", "feeling thirsty", "feeling too hot or too cold", "feeling physically uncomfortable", "hearing sounds", and "being comforted by physical touch", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR2"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR2"]*100, 0)`% of the total variance in participants’ capacity attributions.

Finally, the fourth factor corresponded to negatively-valenced sensations and emotions—a suite of capacities that we will refer to as _negative affect_. It was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected"; the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors). This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.

```{r s1 strong laodings}
s1_strong_loadings <- s1_results$efa$loadings[] %>% 
  data.frame() %>% 
  rownames_to_column("capacity") %>% 
  gather(factor, loading, -capacity) %>% 
  filter(abs(loading) >= 0.6) %>% 
  count(factor)
```

How robust are these findings? The factors we have called _bodily sensations_, _social connection_, and _cognition and control_ each had strong factor loadings ($\geq$ 0.60) for many individual items ($n$ = `r min(s1_strong_loadings$n)`-`r max(s1_strong_loadings$n)`) and each accounted for a substantial amount of the total variance in participants’ capacity attributions (`r round_x(min(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`-`r round_x(max(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`%), indicating three robustly distinct and interpretable factors. In contrast, the fourth factor—_negative affect_—had more moderate loadings even for its strongest-loading items (all loadings < `r abs(s1_results$efa$loadings[][,"MR4"]) %>% max() %>% round(., 2) + 0.01`) and accounted for only `r round_x(s1_results$efa$Vaccounted["Proportion Var","MR4"]*100, 0)`% of the total variance. Nonetheless, we consider the general domain of _negative affect_ to be of particular theoretical and clinical interest.

It is worth noting that a handful of items loaded relatively strongly on two factors (loadings $\geq$ 0.40), suggesting that these factors are not entirely distinct. The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensations_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (like pain) and an affective state (like frustration). Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a sensory ability and a critical part of many social interactions (eye contact). The relatively large degree of overlap between _cognition and control_ and _social connection_, in particular, might indicate that participants believed these two constructs to be more strongly connected than other aspects of life; in fact, these two factors were the most strongly correlated of all pairs of factors ($\phi$ = `r round_x(s1_results$efa$Phi["MR1", "MR3"], 2)`). (The next strongest correlation was between _bodily sensations_ and _social connection_: $\phi$  = `r round_x(s1_results$efa$Phi["MR2", "MR3"], 2)`. All other inter-factor correlations: $\phi \le$ `r round_x((s1_results$efa$Phi[upper.tri(s1_results$efa$Phi) == T] %>% sort(decreasing = T))[3], 2)`.)

What does it mean that these four factors emerged? At a most basic level, our results reflect sets of intercorrelated capacities: When a participant judged that a child of a certain age was highly capable of planning, they also tended to judge that that child was capable of having self control, thinking before they act, and the other capacities with strong factor loadings on the _cognition and control_ factor; and likewise for the suites of capacities that define the other factors revealed by EFA. Therefore, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children [@weisman.etal2017a]. Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants’ perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development. In Studies 2 and 3, we explore these possibilities in greater depth.

```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of participants’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
knitr::include_graphics("../outputs/fig01.pdf")
```

## Study 2

In Study 2 ($n$ = `r s2_results$demo %>% distinct() %>% nrow()`), we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development: What kinds of abilities do people believe are present at birth, and to what degree? To what extent are capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ perceived to change over childhood, and what is the shape of this perceived developmental trajectory?

The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages. Capacities were chosen to represent the four domains of mental life identified through EFA in Study 1: _Bodily sensations_ was represented by the items "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds"; _negative affect_ was represented by "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed"; _social connection_ was represented by "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy"; and _cognition and control_ was represented by "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong". Target ages were based on the developmental milestone ages identified by the CDC [@CDC2021] and on the American Academy of Pediatrics’ recommendations for pediatrician visits [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years. This design allowed us to chart perceived developmental trajectories with a high degree of precision without undue burden to participants.

In terms of the covariance structure of participants' capacity ratings, a preregistered EFA yielded four factors very similar to the four factors from Study 1 (see Supplemental Materials), with all capacity items loading strongly on the factors that they were selected to represent. Minimally, these results suggest that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1. Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors. After all, given that Study 2 featured only 20 of the 60 capacities featured in Study 1, it certainly could have been the case that this analysis would suggest retaining fewer factors (as often occurs with fewer variables). Conversely, given that Study 2 featured 13 within-subjects observations for each capacity compared to the 3 in Study 1, this analysis could have surfaced more than four factors (as often occurs with more observations). Finally, if we had misinterpreted the fundamental semantic content that distinguished the factors in Study 1 and selected inappropriate capacities to represent these factors, the Study 2 analysis could have identified more capacities with cross-loadings. Instead, we believe the results of this analysis offer some validation of the four factors we have called _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.

```{r s2 capacity ratings summary stats, include = F}
s2_cap_rat_newborns_ss <- s2_results$cap_rat_ss %>%
  filter(target_year == 0)
```

```{r s2 gam results, include = F}
s2_gam_ptab <- summary(s2_results$gam$gam)$p.table
s2_gam_stab <- summary(s2_results$gam$gam)$s.table
```

Regressing participants' item-level responses onto target age, domain, and interactions between them (via a multilevel generalized additive model; see Methods) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains. On one extreme, participants attributed some, but relatively little, capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`). Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported relatively small increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`). At the other extreme, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`). See Figure \@ref(fig:fig02), Panel A.

Visual inspection of Figure \@ref(fig:fig02), Panel A clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains. In the domain of _bodily sensations_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life. Participants perceived development in the domains of _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically. In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.

We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains. For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed. In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool). We explore this possibility in Study 3.

```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3). Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions). In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age. In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity."}
knitr::include_graphics("../outputs/fig02.pdf")
```

## Study 3

Study 3 was designed with two goals in mind: First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2. Second, we aimed to probe the lay theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).

### Perceived developmental trajectories

In Study 2, participants focused on one target age at a time, assessing a variety of capacities for that age before proceeding to the next target age (from youngest to oldest). This design was intended to encourage participants to focus primarily on providing a holistic assessment of mental life at a given target age; the trajectories connecting target ages were likely not the participants’ primary concern in the moment of responding. In Study 3, we flipped the design to focus participants’ attention on development more explicitly: Participants were asked to provide judgments of a single capacity for the full range of target ages (arranged from youngest to oldest) on the same "trial," before proceeding to the next capacity. In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years. In order to accommodate the addition of questions probing lay theories of development (see next section), participants assessed only 8 capacities: “getting hungry” and “feeling pain” (representing the domain of *bodily sensations*); “feeling distressed” and “feeling helpless” (*negative affect*); “learning from other people” and “feeling happy” (*social connection*); and “controlling their emotions” and “reasoning about things” (*cognition and control*).

```{r s3 capacity ratings summary stats, include = F}
s3_cap_rat_newborns_ss <- s3_results$cap_rat_ss %>%
  filter(target_year == 0)
```

```{r s3 gam results, include = F}
s3_gam_ptab <- summary(s3_results$gam$gam)$p.table
s3_gam_stab <- summary(s3_results$gam$gam)$s.table
```

The results of Study 3 yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B. As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`). Again, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain of _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`). Finally, as in Study 2, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`). See Figure \@ref(fig:fig02), Panel B.

Visual inspection of Figure \@ref(fig:fig02), Panel B makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2. In the domain of _bodily sensations_, participants perceived hardly any growth over the target age range, and what growth they did perceive was understood to occur rapidly in the first year of life. In the domains of _negative affect_ and _social connection_, participants perceived much more growth over the target age range, and in both cases most of this growth was understood to occur during the first two years of life; again, this was especially pronounced in the domain of _social connection_. Finally, participants perceived development in the domain of _cognition and control_ to be much more gradual and, by extension, more linear across the target age range.

See Supplemental Materials for the full results of this analysis.

### Lay theories of development

Why do people believe certain aspects of mental life, but not others, to be present at birth? What do people perceive to be driving the development of capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_? As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study. We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when peopl perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned. (See [@wang.feigenson2019] for an in-depth investigation of ordinary people’s intuitions about the influences of nature vs. nurture in cognitive development, in particular.)

We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced, even internally inconsistent theories of development, by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.

A variety of dimensionality reduction techniques (see Supplemental Materials) converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (with some indications of two sub-groups within each of these general categories). First, there were what we will call "intrinsic" mechanisms, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]"). Participants clearly distinguished these intrinsic mechanisms from what we will call "extrinsic" mechanisms, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this"). One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry. This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03).)

```{r s3 mechanism ratings summary stats, include = F}
s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means overall
s3_mech_rat_ss_b <- s3_results$mech_rat_ss_b # means by domain
s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # differences by domain
```

```{r s3 lmer results, include = F}
s3_lmer_tab <- model_parameters(s3_results$lmer, standardize = "refit")
s3_lmer_bod_tab <- model_parameters(s3_results$lmer_bod, standardize = "refit")
s3_lmer_neg_tab <- model_parameters(s3_results$lmer_neg, standardize = "refit")
s3_lmer_soc_tab <- model_parameters(s3_results$lmer_soc, standardize = "refit")
s3_lmer_cog_tab <- model_parameters(s3_results$lmer_cog, standardize = "refit")
```

A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).

For capacities in the domain of _bodily sensations_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`). In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`). In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`). See Figure \@ref(fig:fig03), panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.

```{r s3 mechanism choice summary stats, include = F}
# s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions overall
s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b %>% # proportions by domain
  filter(!is.na(dev_factor_cluster)) %>%
  group_by(factor) %>%
  mutate(prop2 = n/sum(n)) %>%
  ungroup()
```

```{r s3 glmer results, include = F}
s3_glmer_tab <- model_parameters(s3_results$glmer, standardize = "refit")
s3_glmer_bod_tab <- model_parameters(s3_results$glmer_bod) # no standardization
s3_glmer_neg_tab <- model_parameters(s3_results$glmer_neg) # no standardization
s3_glmer_soc_tab <- model_parameters(s3_results$glmer_soc) # no standardization
s3_glmer_cog_tab <- model_parameters(s3_results$glmer_cog) # no standardization
```

Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure \@ref(fig:fig03), Panel C. Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensations_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensations", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme). On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices). Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).

In sum, participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains. Capacities for _bodily sensations_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate. Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world. Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).

```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism. Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs. intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs. intrinsic mechanisms as the 'most important' driver of development. Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals. The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains."}
knitr::include_graphics("../outputs/fig03.pdf")
```

# Discussion

In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).

We found that participants considered _bodily sensations_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood. In contrast (and in line with previous work [@wang.feigenson2019]), participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).

Beliefs about the development of the more social-emotional aspects of mental life—*negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensations_ and _cognition and control_. In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree, but not fully, from birth; and to develop rapidly in the first two years of life before tapering off. Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensations_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_. We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure \@ref(fig:fig02). This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.

In some respects, the results of these studies resonate well with previous work on mind perception among US adults. The factors that we refer to as _bodily sensations_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a], and between "affect" and "regulation" [@malle2019]. These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life. (See also [@weisman.etal2021] for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)

However, these studies also highlight one way in which reasoning about the development of human mental life may diverge from reasoning about mental life in general: In their assessments of the mental lives of infants and children at different ages, participants differentiated between what we call _social connection_ (e.g., capacities for excitement, humor, and love) and what we call _negative affect_ (e.g., capacities for distress, helplessness, and frustration). These two factors have no obvious precedents in previous studies of mind perception. In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials), or the narrower focus on humans (and, in particular, infants and children) as the targets of mind perception. Based on the findings of Studies 2 and 3, we propose that _social connection_ and _negative affect_ emerged as distinct factors because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.

What do these studies reveal about US adults' understanding of the contributions of nature vs. nurture to the development of human mental life? One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree. In addition to _bodily sensations_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people". Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely cognitive ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)). Rather than "intuitive empiricists" [@wang.feigenson2019], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.

Adults’ intuitive theories are likely to have important consequences for the children in their care [@haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010]. We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life. During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel. These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable. There is evidence of this across domains of development. For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] and holding versus looking at an object [@west.iverson2017]. Likewise, representations of children’s mental lives, including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills have been shown to play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].

Critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most appropriate in a given cultural setting, most in line with caregivers’ own values and goals, or most beneficial for children  according to experts. For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021] (see also @laranjo.etal2008]). An additional goal is to identify the gaps and misconceptions in these theories that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, experience concern about their child’s developmental progress, or even engage in neglectful or abusive behaviors toward the child. Identifying the antecedents of individual differences in these beliefs could be an especially important step for such clinically-focused applications. As is the case in many domains [@weisman.markman2017], interventions that leverage the power of intuitive theories to encourage positive and responsive caregiving behaviors hold great promise for creating meaningful and lasting behavioral changes in caregiver behavior, with important consequences for child wellbeing.

# Methods

Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: [link](https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34); Study 2: [link](https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18); Study 3: [link](https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4); links have been anonymized). All studies were approved by the [removed to preserve anonymity] Internal Review Board.

## Study 1

### Participants

`r s1_results$demo %>% distinct() %>% nrow()` US adults participated via Amazon Mechanical Turk (MTurk) in July–August 2018. To be eligible for the study, participants were required to have gained approval for at least 95% of their previous work on MTurk, with at least 50 HITs completed; have MTurk accounts based in the US; indicate that they were between the ages of 18-45 years; and report that their English abilities were either "advanced" or "superior" (not "novice," "intermediate," or decline to provide information about English ability). Participants were paid $2.00 for approximately 10-15 minutes of their time.

According to self-report, participants ranged in age from `r min(s1_results$demo$Age)`-`r max(s1_results$demo$Age)` years ($M$ = `r round_x(mean(s1_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s1_results$demo$Age, na.rm = T), 2)` years) and included more men (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) than women (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%; <1% of participants identified as some other gender or declined to disclose). Participants predominantly identified as White (`r round((s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose). `r round(100*(s1_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree. `r round(100*(s1_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.

An additional 77 participants completed the study but were excluded for failing one or more (out of three) embedded attention checks (e.g., failing to choose "34" in response to the question "Please select 34") or for indicating via a multiple choice question at the end of the survey that they had not paid attention, had not avoided distractions, or had not taken the study tasks seriously.

### Materials and procedure

After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages, from newborns to 5-year-olds. We will show you example photos of children at three of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions. There are 60 brief questions for each of the three ages (for example, "To what extent is a newborn capable of feeling happy?"), followed by a few demographic questions about yourself. We are interested in your opinions about these questions. Please do not look up extra information about these questions—we just want to know what you think." Participants were shown an array of pictures of children at several target ages between 0-5 years; see "Target ages and accompanying photographs," below.

Participants then proceeded through three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years. On each trial, they were shown two representative photographs of children at the target age (with the photograph labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").

On the final page of the survey, participants were asked to provide additional demographic information.

#### Capacities

The 60 capacities included in Study 1 were drawn from several areas of previous research. Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@weisman.etal2017b; @weisman.etal2018]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.

This process yielded a list of 60 capacities. Roughly half of this list (29 of 60 items) were drawn from (or closely based on) the items included in Weisman et al.’s recent studies [@weisman.etal2017a]: "being aware of things", "feeling calm", "feeling embarrassed", "feeling guilty", "feeling happy", "feeling love", "feeling pain", "feeling pleasure", "feeling pride", "feeling sad", "feeling safe", "feeling scared", "feeling tired", "getting angry", "getting hungry", "getting hurt feelings", "having goals", "having self-control", "having thoughts", "having wants and desires", "hearing sounds", "making choices", "planning", "reasoning about things", "recognizing others' emotions", "recognizing somebody else", "remembering things", "seeing", and "telling right from wrong". (By extension, the list included close variants on 14 of the 20 capacities evaluated in Gray et al.'s original study [@gray.etal2007]; see Supplemental Material for a comparison of the capacities used here to those used in previous studies of mind perception.)

The other half (31 of 60 items) were novel items, not used in previous studies of mind perception, but common in clinical assessments of infant temperament and behavior: "being afraid of somebody", "being angry at somebody", "being comforted by physical touch", "calming themselves down", "controlling their emotions", "detecting danger", "feeling annoyed", "feeling bored", "feeling confused", "feeling distressed", "feeling excited", "feeling frustrated", "feeling helpless", "feeling hopeless", "feeling lonely", "feeling neglected", "feeling overwhelmed", "feeling physically uncomfortable", "feeling textures (for example, 'smooth', 'rough')", "feeling thirsty", "feeling too hot or too cold", "feeling worried", "finding something funny", "focusing on a goal", "getting pleasure from music", "imagining things", "learning from other people", "listening to somebody", "loving somebody", "thinking before they act", and "understanding what somebody else is thinking".

Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).

#### Target ages and accompanying photographs

In planning this series of studies, we selected 13 target ages based on the developmental milestone ages identified by the CDC [@CDC2021] with the addition of the American Academy of Pediatrics’ recommendations for pediatrician visits before 2 months [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years. We limited Study 1 to just the youngest, median, and oldest target ages—presented to participants as "newborns," "9-month-olds" and "5-year-olds"—in order to maximize the number of capacities included in the study without over-burdening participants.

In selecting photos for each target age, we aimed to have photos of the same (or very similar-looking) children at all target ages so as to emphasize the question of the development of mental capacities over the course of an individual child’s early life. We chose to illustrate each target age with two photos in order to emphasize that we were interested in children’s mental capacities in general, rather than the experiences of a particular child in a particular moment. We also presented participants with instructions that underscored this point (see above). We included one boy and one girl at each target age in order to generalize across perceived sex/gender differences in children’s early mental life. We used photographs of two (apparently) White, non-Hispanic children, for three reasons: (1) In order to avoid introducing spurious differences across target ages by confounding a target’s age and race/ethnicity; (2) In order to match the anticipated race/ethnicity of the majority of participants on MTurk; and (3) Because of the limited set of high-resolution photographs of individual children of color at different points of development currently available to us. Conducting similar studies of adults’ perceptions of the development of mental life with more ethnically and racially diverse participants, and examining the effects of sex, gender, race, and ethnicity on adults’ perceptions of children’s mental life, will be critical next steps in this line of research.

Target ages were presented in chronological order, with participants first assessing all 60 capacities for newborns, then 9-month-old infants, and finally 5-year-old children.

### Analysis plan

To conduct the EFAs reported in Results, we proceeded as if each participant’s ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each. (See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].

In order to determine how many factors to retain, we examined the results of three factor retention protocols: (1) Parallel analysis, which compares the observed correlation structure to the correlation structure arising from random datasets of the same size; (2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and (3) A set of factor retention criteria that have been used in Weisman et al.’s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation (a factor had to meet all three of these criteria in order to be retained). Our interpretation of how best to characterize our dataset (i.e., how many factors we observe) was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.

Parallel analysis suggested a `r s1_results$efa$factors`-factor solution (accounting for `r round(100*(s1_results$efa$Vaccounted["Cumulative Var",ncol(s1_results$efa$Vaccounted)]))`% of the total variance); minimizing BIC suggested a `r s1_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s1_results$efa_bic$Vaccounted["Cumulative Var",ncol(s1_results$efa_bic$Vaccounted)]))`% of the total variance); and Weisman et al.’s (2017) factor retention criteria suggested a `r s1_results$efa_wdm$factors`-factor solution (accounting for `r round(100*(s1_results$efa_wdm$Vaccounted["Cumulative Var",ncol(s1_results$efa_wdm$Vaccounted)]))`% of the total variance). We present the `r s1_results$efa$factors`-factor solution in Results because it was of intermediate size and because we judged the factors it revealed to be intelligible and of theoretical interest; see Supplemental Materials for the other solutions.

## Study 2

### Participants

`r s2_results$demo %>% distinct() %>% nrow()` US adults participated via MTurk in August 2018. Eligibility requirements were identical to Study 1. Participants were paid $2.90 for approximately 15-20 minutes of their time. In response to the overrepresentation of men in Study 1, in Study 2 we recruited men and women through separate "Human Intelligence Tasks" (HITs).

According to self-report, participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%). Participants predominantly identified as White (`r round((s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose). `r round(100*(s2_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree. `r round(100*(s2_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.

An additional 90 participants completed the study but were excluded for failing one or more (out of four) attention checks or indicating that they had not paid attention (see Study 1).

### Materials and procedure

After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study that was nearly identical to that used in Study 1.

Participants then proceeded through 13 trials in which they assessed the mental lives of children at 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years. On each trial, they were shown two representative photographs of children at the target age, and asked to answer the following question for 20 capacities: "To what extent is a [newborn/4-day-old/etc.] capable of [this capacity]?" As in Study 1, participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").

On the final page of the survey, participants were asked to provide additional demographic information.

#### Capacities

In order to ask participants to assess a more fine-grained array of target ages without undue participant burden, we limited our list of capacities to 20 of the 60 capacities used in Study 1. To identify this list, we drew on the results of Study 1, selecting 5 items for each of the 4 factors identified there. For each factor, we aimed to select items that loaded strongly on that factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the latent construct that each factor corresponded to.

To represent _bodily sensations_, we chose the following items: "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds". In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% pull("MR2") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR2") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.

To represent _negative affect_, we chose the following items: "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed". In Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR4") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors. As these numbers suggest, this was a difficult factor to represent, because there were no items that loaded very strongly on the factor (highest loading: `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% max() %>% round_x(., 2)`) and because the highest-loading items tended to cross-load on other factors as well. Nonetheless, we decided to try to represent this latent construct because of its theoretical interest and potential clinical importance.

To represent _social connection_, we chose the following items: "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy". In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% pull("MR3") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR3") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.

Finally, to represent _cognition and control_, we chose the following items: "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong". In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% pull("MR1") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR1") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.

Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).

#### Target ages and accompanying photographs

The target ages for this study (birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years) were based on the developmental milestone ages described in Study 1. The pairs of photos used to illustrate each target age were identical to those used in Study 1; see Study 1, Methods, for more information.

As in Study 1, target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, then 1-month-old infants, and so forth.

### Analysis plan

#### Preregistered confirmatory analysis of conceptual structure

Based on the results of Study 1, we predicted that the correlational structure of participants’ responses would reveal four underlying constructs corresponding to the four factors we identified in Study 1: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_. To test this hypothesis, we performed an EFA, following the methods established in Study 1. We predicted that, using the same guidelines we applied for conducting and interpreting EFA in Study 1, we would find support for a `r s1_results$efa$factors`-factor solution, with factors that were similar to the factors revealed in that study (e.g., similar groups of capacities that loaded strongly on any given factor).

In line with our predictions, both parallel analysis and Weisman et al.’s (2017) factor retention criteria [@weisman.etal2017a] suggested a `r s2_results$efa$factors`-factor solution, which accounted for `r round(100*(s2_results$efa$Vaccounted["Cumulative Var",ncol(s2_results$efa$Vaccounted)]))`% of the total variance in participants’ capacity attributions. In this solution, all items loaded most strongly on the factors that they were selected to represent. Minimizing BIC suggested an `r s2_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s2_results$efa_bic$Vaccounted["Cumulative Var",ncol(s2_results$efa_bic$Vaccounted)]))`% of the total variance); see Supplemental Materials.

#### Preregistered confirmatory analysis of perceived developmental trajectories

We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 2. (1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).

To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge. Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1). Attempting to model random slopes for domain or for target age resulted in model convergence problems. Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution. Domain was dummy-coded with _cognition and control_ as the baseline.

These tests deviated slightly from the preregistered analysis. We originally planned to use "factor scores" (which take into account participants’ responses to all 20 items and the relations of those items to all 4 factors) rather than the summary scores described above as our dependent variable for these tests. We planned to derive these factor scores by projecting Study 2 data into the conceptual space defined by the factor solution for Study 1; however, this projection was impossible to implement, because Study 2 included only a subset of the variables used in Study 1. Furthermore, upon reflection, we decided that using any kind of factor scores (even factor scores derived only from Study 2 data) would be inappropriate for testing our hypotheses, which hinge on assessing the _absolute_ degree to which participants attributed different aspects of mental life to children of different ages; factor scores, which function much like z-scores, are instead designed to capture individual differences in responses (i.e., the degree to which a given participant attributed relatively greater or lesser capacities compared to the average of all participants).

In addition, we note that we originally planned to use a multilevel linear regression to analyze these scores. However, we now consider it misguided to model participants’ responses using gaussian distribution, because—both in principle and in our empirical dataset—capacity ratings behaved asymptotically, plateauing near the ceiling of the scale (100, labeled "completely capable") at some point in development. The approach described here—using the beta distribution—is a far more accurate representation of these responses. Using generalized additive models via the "mgcv" package for R [@wood2017] allowed us to fine-tune the shape of these perceived developmental trajectories via spline-based smoothing (analogous to fitting polynomial terms in the context of linear regression, but without specifying in advance the order of the polynomials included in the model).

## Study 3

### Participants

`r s3_results$demo %>% distinct() %>% nrow()` US adults participated via MTurk in April 2019. Eligibility requirements were identical to Studies 1-2. Participants were paid $2.90 for approximately 15-20 minutes of their time. As in Study 2, we recruited men and women separately.

According to self-report, participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%). Participants predominantly identified as White (`r round((s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose). `r round(100*(s3_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree. `r round(100*(s3_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.

An additional 79 participants completed the study but were excluded for failing two or more (out of eight) embedded attention checks or for failing to provide a reasonable response in well-formed English sentences to an open-ended comprehension check included at the end of the survey.

### Materials and procedure

After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages. We will show you example photos of children at each of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions. We will ask you about 8 different mental capacities: feeling happy, getting hungry, controlling emotions, feeling distressed, feeling pain, reasoning about things, learning from other people, and feeling helpless. For each mental capacity, we will ask you to assess the extent to which newborns (at birth) have this mental capacity, then 4-day-olds, 1-month-olds, 2-month-olds, 4-month-olds, and so on, ending with 5-year-olds. We’ll also ask for your opinion about the different factors that might influence the development of these capacities, such as the child being ‘preprogrammed’ to have certain abilities, or the child learning from the people or objects around him or her. At the end of the survey, we will ask you a few demographic questions about yourself. We are interested in your opinions about these questions. Please do not look up extra information about these questions—we just want to know what you think."

Participants then proceeded through eight trials, in which they assessed each of the eight capacities in turn; the order of capacities was randomized across participants. On each trial, participant assessed children at all 13 target ages used in Study 2 in a fixed order from youngest to oldest. Each age was presented along with a representative pair of photographs (also used in Studies 1 and 2), and participants were asked to answer the following question: "To what extent is a [newborn/4-day-old/1-month-old/etc.] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").

On each trial, at the bottom of the page participants completed a set of questions about the possible mechanisms that drive development for the capacity in question. First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for the following 10 developmental mechanisms: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that given them this ability"; "the child’s body grows and matures (for example, muscles get stronger, child gets taller)"; "the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child’s senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this". These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social). They were then provided an opportunity to write in "any factors that play a role in the development of children’s capacity for [capacity]". Finally, they were asked to choose among these 10 possible mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
On the final page of the survey, participants were asked to provide additional demographic information.

#### Capacities

Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to eight in the current study to maintain an appropriate level of participant burden. To select these eight capacities, we drew on the results of Study 2, selecting two items for each of the four factors identified by EFA. For each domain, we selected items that loaded strongly on the relevant factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the domain that each factor corresponded to. We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensations_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_. Capacities were presented in a random order for each participant.

#### Target ages and accompanying photographs

The 13 target ages for this study were identical to Study 2, with the exception that we added the parenthetical phrase "(at birth)" when referring to newborns. Each target age was presented with the same pair of photographs used in Study 2. Target ages were presented in chronological order on each trial.

### Analysis plan

#### Preregistered confirmatory analysis of perceived developmental trajectories

We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3; these were identical to our hypotheses for Study 2 (which were upheld in that study): (1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).

Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge. Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1). Again, attempting to model random slopes for domain or for target age resulted in model convergence problems. Again, responses were rescaled to range from 0.005 to 0.995, and domain was dummy-coded with _cognition and control_ as the baseline.

(We note that, in contrast to Study 2, in Study 3 we did preregister this analysis, although we preregistered a linear regression rather than a beta regression via generalized additive model; see extended notes on our choice of this analysis approach under Study 2.)

#### Preregistered exploratory analysis of perceived developmental trajectories

Beyond the two hypotheses described in the previous section, we also anticipated that perceptions of developmental trajectories in different domains would vary in their curvilinearity—e.g., development in one domain might be perceived to be gradual and linear, while development in another domain might be perceived to occur in stages, at an exponential rate, or to peak at a specific age. To explore these possibilities, we preregistered a regression analysis adding polynomial effects of target age; however, in our reconceptualization of the appropriate way to analyze our data given the distribution of the response variable (see Study 2), this exploratory analysis was superseded by the generalized additive model.

#### Preregistered exploratory analysis of developmental mechanisms

Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*). We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualtion we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs. intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity). We also conducted separate, analogous regression analyses for each domain separately. In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains. (Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see Results.)

\newpage
# References

### 2021-07-31 supplement/supplement-main.Rmd
add anonymized repo link

@@
 title: "Beliefs about the development of mental life"
-subtitle: "Supplemental materials"
+subtitle: "Supplemental Materials"
 author: "[authors removed to preserve anonymity]"
@@
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: [removed to preserve anonymity].
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
 

### 2021-07-31 paper/paper.Rmd
add anonymized github repo

@@
 
+Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
+The full, editable script for all analyses, figures, and tables (here and in the Supplemental Materials) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
+
 ## Study 1

### 2021-08-01 supplement/supplement-main.Rmd
fix typos in refs, final table

@@
   select(-Domain) %>%
+  mutate_all(~gsub("similar to .", "similar to \\`", .)) %>% 
   mutate(`Study 1` = case_when(`Study 2` != "-" ~ paste0(`Study 1`, 
@@
   pack_rows("Not included", 61, nrow(d_cap_comp)) %>%
-  footnote(symbol = c("Also used in Study 2; ", "Also unsed in Study 3"),
+  footnote(symbol = c("Also used in Study 2; ", "Also used in Study 3"),
            symbol_title = "Notes: ",

### 2021-08-01 supplement/supplement-main.Rmd
more typos and latex problems

@@
   rename_with(~recode(., 
-                      "preprogrammed" = "biologically ‘preprogrammed’",
+                      "preprogrammed" = "biologically 'preprogrammed'",
                       "womb_experiences" = "experiences in the womb",

### 2021-08-01 paper/paper.Rmd
more formatting

@@
 To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1).
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
 Attempting to model random slopes for domain or for target age resulted in model convergence problems.
@@
 Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1).
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
 Again, attempting to model random slopes for domain or for target age resulted in model convergence problems.
@@
 intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity).
+Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_.
 We also conducted separate, analogous regression analyses for each domain separately.

### 2021-08-01 supplement/supplement-main.Rmd
more formatting

@@
 intrinsic mechanisms by domain.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: glmer(choice of extrinsic mechanism ~ domain + (1 | participant) + (1 | capacity).
+Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _glmer(choice of extrinsic mechanism ~ domain + (1 | participant) + (1 | capacity)_.
 We also conducted separate, analogous regression analyses for each domain separately.
@@
 
-```{r figS08, fig.cap="XX", fig.width = 4.5, fig.asp = 6.75/6}
+```{r figS08, fig.cap="Selection of the various mechanisms as the 'most important' driver of development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
+Panel A shows selections for each developmental mechanism and both of the capacities within each domain; Panel B shows selections for extrinsic vs.
+intrinsic mechanisms for each domain of capacities (identical to Figure 3, Panel C, main text).
+Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 4.5, fig.asp = 6.75/6}
 plot_grid(figS08a + guides(fill = guide_none(), color = guide_none()),

### 2021-08-01 paper/paper.Rmd
integrate berent refs

@@
 As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
-We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when peopl perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-(See [@wang.feigenson2019] for an in-depth investigation of ordinary people’s intuitions about the influences of nature vs.
-nurture in cognitive development, in particular.)
+We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
+(See [@wang.feigenson2019; @berent.etal2019; @berent.etal2020] for in-depth investigations of ordinary people’s intuitions about the innateness of cognitive abilities, motor abilities, and emotion.)
 

### 2021-08-01 paper/paper.Rmd
spellcheck

@@
 Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely cognitive ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)).
-Rather than "intuitive empiricists" [@wang.feigenson2019], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
+Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
 
@@
 Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*).
-We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualtion we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
+We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
 intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.

### 2021-08-01 supplement/supplement-main.Rmd
spellcheck

@@
 
-As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retentia criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
+As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retention criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
 Here we present these three factor retention protocols separately.

### 2021-08-02 paper/paper.Rmd
update mind-mindedness

@@
 There is evidence of this across domains of development.
-For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] and holding versus looking at an object [@west.iverson2017].
+For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] or holding versus looking at an object [@west.iverson2017].
 Likewise, representations of children’s mental lives, including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills have been shown to play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].
+Caregivers’ capacity to form an accurate representation of their child’s internal states and to use this representation to guide their caregiving behavior (so called “mind-mindedness”) is positively associated with children’s wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
 

### 2021-08-02 paper/paper.Rmd
typos and minor tweaks to text

@@
 We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
-For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed.
+For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed (see [@berent.etal2019] for empirical evidence in line with this speculation).
 In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
@@
 One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03).)
+This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03)).
 
@@
 We found that participants considered _bodily sensations_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast (and in line with previous work [@wang.feigenson2019]), participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+In contrast (and in line with previous work [@wang.feigenson2019; @berent.etal2019]), participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
 
@@
 Critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most appropriate in a given cultural setting, most in line with caregivers’ own values and goals, or most beneficial for children  according to experts.
-For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021] (see also @laranjo.etal2008]).
+For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021] (see also [@laranjo.etal2008]).
 An additional goal is to identify the gaps and misconceptions in these theories that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, experience concern about their child’s developmental progress, or even engage in neglectful or abusive behaviors toward the child.
@@
 We will show you example photos of children at three of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions.
-There are 60 brief questions for each of the three ages (for example, "To what extent is a newborn capable of feeling happy?"), followed by a few demographic questions about yourself.
+There are 60 brief questions for each of the three ages (for example, 'To what extent is a newborn capable of feeling happy?'), followed by a few demographic questions about yourself.
 We are interested in your opinions about these questions.
@@
 Roughly half of this list (29 of 60 items) were drawn from (or closely based on) the items included in Weisman et al.’s recent studies [@weisman.etal2017a]: "being aware of things", "feeling calm", "feeling embarrassed", "feeling guilty", "feeling happy", "feeling love", "feeling pain", "feeling pleasure", "feeling pride", "feeling sad", "feeling safe", "feeling scared", "feeling tired", "getting angry", "getting hungry", "getting hurt feelings", "having goals", "having self-control", "having thoughts", "having wants and desires", "hearing sounds", "making choices", "planning", "reasoning about things", "recognizing others' emotions", "recognizing somebody else", "remembering things", "seeing", and "telling right from wrong".
-(By extension, the list included close variants on 14 of the 20 capacities evaluated in Gray et al.'s original study [@gray.etal2007]; see Supplemental Material for a comparison of the capacities used here to those used in previous studies of mind perception.)
+By extension, the list included close variants on 14 of the 20 capacities evaluated in Gray et al.'s original study [@gray.etal2007].
 
 The other half (31 of 60 items) were novel items, not used in previous studies of mind perception, but common in clinical assessments of infant temperament and behavior: "being afraid of somebody", "being angry at somebody", "being comforted by physical touch", "calming themselves down", "controlling their emotions", "detecting danger", "feeling annoyed", "feeling bored", "feeling confused", "feeling distressed", "feeling excited", "feeling frustrated", "feeling helpless", "feeling hopeless", "feeling lonely", "feeling neglected", "feeling overwhelmed", "feeling physically uncomfortable", "feeling textures (for example, 'smooth', 'rough')", "feeling thirsty", "feeling too hot or too cold", "feeling worried", "finding something funny", "focusing on a goal", "getting pleasure from music", "imagining things", "learning from other people", "listening to somebody", "loving somebody", "thinking before they act", and "understanding what somebody else is thinking".
+
+(See Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].)
 

### 2021-08-02 supplement/supplement-main.Rmd
minor tweaks to text

@@
 author: "[authors removed to preserve anonymity]"
-date: "July 31, 2021"
+date: "August 2, 2021"
 output:
@@
 
-In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007, @weisman.etal2017a, @weisman.etal2017b, @malle2019].
+In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
 
@@
 Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life.
-To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabcapcomp)); for each participant, we then took the average of their responses to capacities in each domain at each target age.
+To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age.
 As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensations_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.

### 2021-08-07 paper/paper.Rmd
de-anonymize

@@
 title: "Beliefs about the development of mental life"
-author: "[Authors removed to preserve anonymity]"
+author:
+  - Kara Weisman^[Department of Psychology, University of California, Riverside; kgweisman@gmail.com]
+  - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
+  - Kathryn L. Humprheys^[Department of Psychology, Vanderbilt University]
 output:
-  # word_document:
-  #   reference_docx: word-styles-ref.docx
-   bookdown::pdf_document2:
-    latex_engine: xelatex
-    fig_caption: yes
-    toc: false
+  word_document:
+    reference_docx: word-styles-ref.docx
+   # bookdown::pdf_document2:
+   #  latex_engine: xelatex
+   #  fig_caption: yes
+   #  toc: false
 bibliography: "../supplement/references.bib"
-# cls: "../supplement/article.cls"
-csl: "../supplement/nature.csl"
+cls: "../supplement/article.cls"
 figsintext: yes
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: [link](https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34); Study 2: [link](https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18); Study 3: [link](https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4); links have been anonymized).
-All studies were approved by the [removed to preserve anonymity] Internal Review Board.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/); Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/)).
+All studies were approved by the Stanford University Internal Review Board.
 
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the Supplemental Materials) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
+The full, editable script for all analyses, figures, and tables (here and in the Supplemental Materials) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
 

### 2021-08-07 supplement/supplement-main.Rmd
de-anonymize

@@
 subtitle: "Supplemental Materials"
-author: "[authors removed to preserve anonymity]"
-date: "August 2, 2021"
+author:
+  - Kara Weisman^[Department of Psychology, University of California, Riverside; kgweisman@gmail.com]
+  - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
+  - Kathryn L. Humprheys^[Department of Psychology, Vanderbilt University]
+date: "August 7, 2021"
 output:
@@
 bibliography: "references.bib"
-# cls: "article.cls"
-csl: nature.csl
+cls: article.cls
 figsintext: yes
@@
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
 
@@
   kable("latex", booktabs = T, escape = F, longtable = T) %>%
-  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 8) %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
   add_header_above(c("Current studies" = 1,

### 2021-08-08 paper/paper.Rmd
edits for submission, add figs to readme

@@
 output:
-  word_document:
-    reference_docx: word-styles-ref.docx
-   # bookdown::pdf_document2:
-   #  latex_engine: xelatex
-   #  fig_caption: yes
-   #  toc: false
+  # word_document:
+  #   reference_docx: word-styles-ref.docx
+  bookdown::pdf_document2:
+    latex_engine: xelatex
+    fig_caption: yes
+    toc: false
+    number_sections: false
 bibliography: "../supplement/references.bib"
@@
 In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
-Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (e.g., biological "preprogramming," physical maturation, passive observation, social learning).
+Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensations_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
+Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological "preprogramming," physical maturation, passive observation, and social learning).
 These studies reveal the lay theories that govern US adults’ understanding of the development of the human mind, illuminating the cognitive architecture that supports some of the most important social interactions: caregiving relationships with infants and children.
+
+## Significance statement
+
+Caregiving relationships with infants and children are among the most common, important, and complex human social interactions.
+Caring for a young child over time requires an adult to continually update their own mental representations of the child's capacities as the child grows and changes.
+These representations are likely to have important consequences for the child's well-being—particularly in the first few years of life, when the child's communication skills are limited and the caregiver must make inferences about the child's thoughts, feelings, and needs.
+The current studies shed light on this fascinating and understudied aspect of "mind perception," in turn laying the foundation for theory-based interventions to encourage positive and responsive parenting behaviors.
 
@@
 
-It is worth noting that a handful of items loaded relatively strongly on two factors (loadings $\geq$ 0.40), suggesting that these factors are not entirely distinct.
-The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensations_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (like pain) and an affective state (like frustration).
-Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a sensory ability and a critical part of many social interactions (eye contact).
-The relatively large degree of overlap between _cognition and control_ and _social connection_, in particular, might indicate that participants believed these two constructs to be more strongly connected than other aspects of life; in fact, these two factors were the most strongly correlated of all pairs of factors ($\phi$ = `r round_x(s1_results$efa$Phi["MR1", "MR3"], 2)`).
-(The next strongest correlation was between _bodily sensations_ and _social connection_: $\phi$  = `r round_x(s1_results$efa$Phi["MR2", "MR3"], 2)`.
-All other inter-factor correlations: $\phi \le$ `r round_x((s1_results$efa$Phi[upper.tri(s1_results$efa$Phi) == T] %>% sort(decreasing = T))[3], 2)`.)
-
 What does it mean that these four factors emerged?
@@
 
-The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages.
-Capacities were chosen to represent the four domains of mental life identified through EFA in Study 1: _Bodily sensations_ was represented by the items "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds"; _negative affect_ was represented by "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed"; _social connection_ was represented by "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy"; and _cognition and control_ was represented by "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong".
-Target ages were based on the developmental milestone ages identified by the CDC [@CDC2021] and on the American Academy of Pediatrics’ recommendations for pediatrician visits [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
+The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years (see Methods).
 This design allowed us to chart perceived developmental trajectories with a high degree of precision without undue burden to participants.
@@
 In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years.
-In order to accommodate the addition of questions probing lay theories of development (see next section), participants assessed only 8 capacities: “getting hungry” and “feeling pain” (representing the domain of *bodily sensations*); “feeling distressed” and “feeling helpless” (*negative affect*); “learning from other people” and “feeling happy” (*social connection*); and “controlling their emotions” and “reasoning about things” (*cognition and control*).
+In order to accommodate the addition of questions probing lay theories of development (see next section), participants assessed only 2 capacities per domain; see Methods.
 
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/); Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/)).
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/).
 All studies were approved by the Stanford University Internal Review Board.
-
-Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the Supplemental Materials) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
+For extended descriptions of methods, see Supplemental Material.
 
@@
 `r s1_results$demo %>% distinct() %>% nrow()` US adults participated via Amazon Mechanical Turk (MTurk) in July–August 2018.
-To be eligible for the study, participants were required to have gained approval for at least 95% of their previous work on MTurk, with at least 50 HITs completed; have MTurk accounts based in the US; indicate that they were between the ages of 18-45 years; and report that their English abilities were either "advanced" or "superior" (not "novice," "intermediate," or decline to provide information about English ability).
-Participants were paid $2.00 for approximately 10-15 minutes of their time.
-
-According to self-report, participants ranged in age from `r min(s1_results$demo$Age)`-`r max(s1_results$demo$Age)` years ($M$ = `r round_x(mean(s1_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s1_results$demo$Age, na.rm = T), 2)` years) and included more men (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) than women (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%; <1% of participants identified as some other gender or declined to disclose).
+Participants ranged in age from `r min(s1_results$demo$Age)`-`r max(s1_results$demo$Age)` years ($M$ = `r round_x(mean(s1_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s1_results$demo$Age, na.rm = T), 2)` years) and included more men (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) than women (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%; <1% of participants identified as some other gender or declined to disclose).
 Participants predominantly identified as White (`r round((s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
@@
 
-An additional 77 participants completed the study but were excluded for failing one or more (out of three) embedded attention checks (e.g., failing to choose "34" in response to the question "Please select 34") or for indicating via a multiple choice question at the end of the survey that they had not paid attention, had not avoided distractions, or had not taken the study tasks seriously.
-
 ### Materials and procedure
 
-After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages, from newborns to 5-year-olds.
-We will show you example photos of children at three of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions.
-There are 60 brief questions for each of the three ages (for example, 'To what extent is a newborn capable of feeling happy?'), followed by a few demographic questions about yourself.
-We are interested in your opinions about these questions.
-Please do not look up extra information about these questions—we just want to know what you think." Participants were shown an array of pictures of children at several target ages between 0-5 years; see "Target ages and accompanying photographs," below.
-
-Participants then proceeded through three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years.
+Participants completed three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years.
 On each trial, they were shown two representative photographs of children at the target age (with the photograph labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
 
-On the final page of the survey, participants were asked to provide additional demographic information.
-
-#### Capacities
-
 The 60 capacities included in Study 1 were drawn from several areas of previous research.
-Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@weisman.etal2017b; @weisman.etal2018]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.
-
-This process yielded a list of 60 capacities.
-Roughly half of this list (29 of 60 items) were drawn from (or closely based on) the items included in Weisman et al.’s recent studies [@weisman.etal2017a]: "being aware of things", "feeling calm", "feeling embarrassed", "feeling guilty", "feeling happy", "feeling love", "feeling pain", "feeling pleasure", "feeling pride", "feeling sad", "feeling safe", "feeling scared", "feeling tired", "getting angry", "getting hungry", "getting hurt feelings", "having goals", "having self-control", "having thoughts", "having wants and desires", "hearing sounds", "making choices", "planning", "reasoning about things", "recognizing others' emotions", "recognizing somebody else", "remembering things", "seeing", and "telling right from wrong".
-By extension, the list included close variants on 14 of the 20 capacities evaluated in Gray et al.'s original study [@gray.etal2007].
-
-The other half (31 of 60 items) were novel items, not used in previous studies of mind perception, but common in clinical assessments of infant temperament and behavior: "being afraid of somebody", "being angry at somebody", "being comforted by physical touch", "calming themselves down", "controlling their emotions", "detecting danger", "feeling annoyed", "feeling bored", "feeling confused", "feeling distressed", "feeling excited", "feeling frustrated", "feeling helpless", "feeling hopeless", "feeling lonely", "feeling neglected", "feeling overwhelmed", "feeling physically uncomfortable", "feeling textures (for example, 'smooth', 'rough')", "feeling thirsty", "feeling too hot or too cold", "feeling worried", "finding something funny", "focusing on a goal", "getting pleasure from music", "imagining things", "learning from other people", "listening to somebody", "loving somebody", "thinking before they act", and "understanding what somebody else is thinking".
-
-(See Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].)
-
-Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).
-
-#### Target ages and accompanying photographs
+Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@putnam.etal2006; @rothbart1978]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.
+This process yielded a list of 60 capacities; see Figure \@ref(fig:fig01), and see Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception.
+Capacities were presented in a random order.
 
@@
 We limited Study 1 to just the youngest, median, and oldest target ages—presented to participants as "newborns," "9-month-olds" and "5-year-olds"—in order to maximize the number of capacities included in the study without over-burdening participants.
-
-In selecting photos for each target age, we aimed to have photos of the same (or very similar-looking) children at all target ages so as to emphasize the question of the development of mental capacities over the course of an individual child’s early life.
-We chose to illustrate each target age with two photos in order to emphasize that we were interested in children’s mental capacities in general, rather than the experiences of a particular child in a particular moment.
-We also presented participants with instructions that underscored this point (see above).
-We included one boy and one girl at each target age in order to generalize across perceived sex/gender differences in children’s early mental life.
-We used photographs of two (apparently) White, non-Hispanic children, for three reasons: (1) In order to avoid introducing spurious differences across target ages by confounding a target’s age and race/ethnicity; (2) In order to match the anticipated race/ethnicity of the majority of participants on MTurk; and (3) Because of the limited set of high-resolution photographs of individual children of color at different points of development currently available to us.
-Conducting similar studies of adults’ perceptions of the development of mental life with more ethnically and racially diverse participants, and examining the effects of sex, gender, race, and ethnicity on adults’ perceptions of children’s mental life, will be critical next steps in this line of research.
-
 Target ages were presented in chronological order, with participants first assessing all 60 capacities for newborns, then 9-month-old infants, and finally 5-year-old children.
-
-### Analysis plan
-
-To conduct the EFAs reported in Results, we proceeded as if each participant’s ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
-(See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].
-
-In order to determine how many factors to retain, we examined the results of three factor retention protocols: (1) Parallel analysis, which compares the observed correlation structure to the correlation structure arising from random datasets of the same size; (2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and (3) A set of factor retention criteria that have been used in Weisman et al.’s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation (a factor had to meet all three of these criteria in order to be retained).
-Our interpretation of how best to characterize our dataset (i.e., how many factors we observe) was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
-
-Parallel analysis suggested a `r s1_results$efa$factors`-factor solution (accounting for `r round(100*(s1_results$efa$Vaccounted["Cumulative Var",ncol(s1_results$efa$Vaccounted)]))`% of the total variance); minimizing BIC suggested a `r s1_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s1_results$efa_bic$Vaccounted["Cumulative Var",ncol(s1_results$efa_bic$Vaccounted)]))`% of the total variance); and Weisman et al.’s (2017) factor retention criteria suggested a `r s1_results$efa_wdm$factors`-factor solution (accounting for `r round(100*(s1_results$efa_wdm$Vaccounted["Cumulative Var",ncol(s1_results$efa_wdm$Vaccounted)]))`% of the total variance).
-We present the `r s1_results$efa$factors`-factor solution in Results because it was of intermediate size and because we judged the factors it revealed to be intelligible and of theoretical interest; see Supplemental Materials for the other solutions.
 
@@
 Eligibility requirements were identical to Study 1.
-Participants were paid $2.90 for approximately 15-20 minutes of their time.
-In response to the overrepresentation of men in Study 1, in Study 2 we recruited men and women through separate "Human Intelligence Tasks" (HITs).
-
-According to self-report, participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
 Participants predominantly identified as White (`r round((s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
@@
 
-An additional 90 participants completed the study but were excluded for failing one or more (out of four) attention checks or indicating that they had not paid attention (see Study 1).
-
 ### Materials and procedure
 
-After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study that was nearly identical to that used in Study 1.
-
-Participants then proceeded through 13 trials in which they assessed the mental lives of children at 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
+Participants completed 13 trials in which they assessed the mental lives of children at 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
 On each trial, they were shown two representative photographs of children at the target age, and asked to answer the following question for 20 capacities: "To what extent is a [newborn/4-day-old/etc.] capable of [this capacity]?" As in Study 1, participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
-
-On the final page of the survey, participants were asked to provide additional demographic information.
-
-#### Capacities
 
@@
 To identify this list, we drew on the results of Study 1, selecting 5 items for each of the 4 factors identified there.
-For each factor, we aimed to select items that loaded strongly on that factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the latent construct that each factor corresponded to.
-
-To represent _bodily sensations_, we chose the following items: "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
-In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% pull("MR2") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR2") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.
-
-To represent _negative affect_, we chose the following items: "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed".
-In Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR4") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.
-As these numbers suggest, this was a difficult factor to represent, because there were no items that loaded very strongly on the factor (highest loading: `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% max() %>% round_x(., 2)`) and because the highest-loading items tended to cross-load on other factors as well.
-Nonetheless, we decided to try to represent this latent construct because of its theoretical interest and potential clinical importance.
-
-To represent _social connection_, we chose the following items: "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy".
-In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% pull("MR3") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR3") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.
-
-Finally, to represent _cognition and control_, we chose the following items: "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong".
-In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% pull("MR1") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR1") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.
-
-Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).
-
-#### Target ages and accompanying photographs
+For each factor, we aimed to select items that loaded strongly on that factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning, and captured our qualitative understanding of the latent construct that each factor corresponded to.
+To represent _bodily sensations_, we chose the items "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
+To represent _negative affect_, we chose the items "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed".
+To represent _social connection_, we chose the items "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy".
+Finally, to represent _cognition and control_, we chose the items "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong".
+Capacities were presented in a random order.
 
 The target ages for this study (birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years) were based on the developmental milestone ages described in Study 1.
-The pairs of photos used to illustrate each target age were identical to those used in Study 1; see Study 1, Methods, for more information.
-
-As in Study 1, target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, then 1-month-old infants, and so forth.
-
-### Analysis plan
-
-#### Preregistered confirmatory analysis of conceptual structure
-
-Based on the results of Study 1, we predicted that the correlational structure of participants’ responses would reveal four underlying constructs corresponding to the four factors we identified in Study 1: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
-To test this hypothesis, we performed an EFA, following the methods established in Study 1.
-We predicted that, using the same guidelines we applied for conducting and interpreting EFA in Study 1, we would find support for a `r s1_results$efa$factors`-factor solution, with factors that were similar to the factors revealed in that study (e.g., similar groups of capacities that loaded strongly on any given factor).
-
-In line with our predictions, both parallel analysis and Weisman et al.’s (2017) factor retention criteria [@weisman.etal2017a] suggested a `r s2_results$efa$factors`-factor solution, which accounted for `r round(100*(s2_results$efa$Vaccounted["Cumulative Var",ncol(s2_results$efa$Vaccounted)]))`% of the total variance in participants’ capacity attributions.
-In this solution, all items loaded most strongly on the factors that they were selected to represent.
-Minimizing BIC suggested an `r s2_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s2_results$efa_bic$Vaccounted["Cumulative Var",ncol(s2_results$efa_bic$Vaccounted)]))`% of the total variance); see Supplemental Materials.
-
-#### Preregistered confirmatory analysis of perceived developmental trajectories
-
-We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 2.
-(1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
-
-To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
-Attempting to model random slopes for domain or for target age resulted in model convergence problems.
-Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution.
-Domain was dummy-coded with _cognition and control_ as the baseline.
-
-These tests deviated slightly from the preregistered analysis.
-We originally planned to use "factor scores" (which take into account participants’ responses to all 20 items and the relations of those items to all 4 factors) rather than the summary scores described above as our dependent variable for these tests.
-We planned to derive these factor scores by projecting Study 2 data into the conceptual space defined by the factor solution for Study 1; however, this projection was impossible to implement, because Study 2 included only a subset of the variables used in Study 1.
-Furthermore, upon reflection, we decided that using any kind of factor scores (even factor scores derived only from Study 2 data) would be inappropriate for testing our hypotheses, which hinge on assessing the _absolute_ degree to which participants attributed different aspects of mental life to children of different ages; factor scores, which function much like z-scores, are instead designed to capture individual differences in responses (i.e., the degree to which a given participant attributed relatively greater or lesser capacities compared to the average of all participants).
-
-In addition, we note that we originally planned to use a multilevel linear regression to analyze these scores.
-However, we now consider it misguided to model participants’ responses using gaussian distribution, because—both in principle and in our empirical dataset—capacity ratings behaved asymptotically, plateauing near the ceiling of the scale (100, labeled "completely capable") at some point in development.
-The approach described here—using the beta distribution—is a far more accurate representation of these responses.
-Using generalized additive models via the "mgcv" package for R [@wood2017] allowed us to fine-tune the shape of these perceived developmental trajectories via spline-based smoothing (analogous to fitting polynomial terms in the context of linear regression, but without specifying in advance the order of the polynomials included in the model).
+Target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, and so forth.
 
@@
 Eligibility requirements were identical to Studies 1-2.
-Participants were paid $2.90 for approximately 15-20 minutes of their time.
-As in Study 2, we recruited men and women separately.
-
-According to self-report, participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
 Participants predominantly identified as White (`r round((s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
@@
 
-An additional 79 participants completed the study but were excluded for failing two or more (out of eight) embedded attention checks or for failing to provide a reasonable response in well-formed English sentences to an open-ended comprehension check included at the end of the survey.
-
 ### Materials and procedure
 
-After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages.
-We will show you example photos of children at each of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions.
-We will ask you about 8 different mental capacities: feeling happy, getting hungry, controlling emotions, feeling distressed, feeling pain, reasoning about things, learning from other people, and feeling helpless.
-For each mental capacity, we will ask you to assess the extent to which newborns (at birth) have this mental capacity, then 4-day-olds, 1-month-olds, 2-month-olds, 4-month-olds, and so on, ending with 5-year-olds.
-We’ll also ask for your opinion about the different factors that might influence the development of these capacities, such as the child being ‘preprogrammed’ to have certain abilities, or the child learning from the people or objects around him or her.
-At the end of the survey, we will ask you a few demographic questions about yourself.
-We are interested in your opinions about these questions.
-Please do not look up extra information about these questions—we just want to know what you think."
-
-Participants then proceeded through eight trials, in which they assessed each of the eight capacities in turn; the order of capacities was randomized across participants.
+Participants completed eight trials, in which they assessed each of the eight capacities in turn; the order of capacities was randomized across participants.
 On each trial, participant assessed children at all 13 target ages used in Study 2 in a fixed order from youngest to oldest.
@@
 
-On each trial, at the bottom of the page participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for the following 10 developmental mechanisms: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that given them this ability"; "the child’s body grows and matures (for example, muscles get stronger, child gets taller)"; "the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child’s senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this".
-These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
-They were then provided an opportunity to write in "any factors that play a role in the development of children’s capacity for [capacity]".
-Finally, they were asked to choose among these 10 possible mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
-On the final page of the survey, participants were asked to provide additional demographic information.
-
-#### Capacities
+On each trial, participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for 10 developmental mechanisms (see Results) presented in a fixed order.
+Participants were also asked to choose among these 10 mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
 
@@
 
-#### Target ages and accompanying photographs
-
 The 13 target ages for this study were identical to Study 2, with the exception that we added the parenthetical phrase "(at birth)" when referring to newborns.
-Each target age was presented with the same pair of photographs used in Study 2.
-Target ages were presented in chronological order on each trial.
-
-### Analysis plan
-
-#### Preregistered confirmatory analysis of perceived developmental trajectories
-
-We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3; these were identical to our hypotheses for Study 2 (which were upheld in that study): (1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
-
-Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
-Again, attempting to model random slopes for domain or for target age resulted in model convergence problems.
-Again, responses were rescaled to range from 0.005 to 0.995, and domain was dummy-coded with _cognition and control_ as the baseline.
-
-(We note that, in contrast to Study 2, in Study 3 we did preregister this analysis, although we preregistered a linear regression rather than a beta regression via generalized additive model; see extended notes on our choice of this analysis approach under Study 2.)
-
-#### Preregistered exploratory analysis of perceived developmental trajectories
-
-Beyond the two hypotheses described in the previous section, we also anticipated that perceptions of developmental trajectories in different domains would vary in their curvilinearity—e.g., development in one domain might be perceived to be gradual and linear, while development in another domain might be perceived to occur in stages, at an exponential rate, or to peak at a specific age.
-To explore these possibilities, we preregistered a regression analysis adding polynomial effects of target age; however, in our reconceptualization of the appropriate way to analyze our data given the distribution of the response variable (see Study 2), this exploratory analysis was superseded by the generalized additive model.
-
-#### Preregistered exploratory analysis of developmental mechanisms
-
-Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*).
-We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
-intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_.
-We also conducted separate, analogous regression analyses for each domain separately.
-In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
-(Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see Results.)
 

### 2021-08-08 supplement/supplement-main.Rmd
edits for submission, add figs to readme

@@
     toc: true
-    toc_depth: 3
+    toc_depth: 2
+    number_sections: false
 bibliography: "references.bib"
@@
 In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
-
-In these Supplemental Materials, we provide extended information about the results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
+We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+
+In these Supplemental Materials, we provide extended information about the methods and results presented in the main paper, present additional results, and provide an item-by-item comparison of the capacity items used here to items used in previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
 
@@
 
+# Extended methods
+
+```{r}
+# NOTE: this is a bit of a circular process -- results files are generated in this .Rmd file, but they also need to be loaded in order to write the Extended Methods section.
+For this reason, results RDS files are included in the github repo.
+s1_results <- readRDS("../outputs/s1_results.rds")
+s2_results <- readRDS("../outputs/s2_results.rds")
+s3_results <- readRDS("../outputs/s3_results.rds")
+
+# ALSO NOTE: if you encounter problems knitting, try clearing the knit cache.
+```
+
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/).
+All studies were approved by the Stanford University Internal Review Board.
+
+## Study 1
+
+### Participants
+
+`r s1_results$demo %>% distinct() %>% nrow()` US adults participated via Amazon Mechanical Turk (MTurk) in July–August 2018.
+To be eligible for the study, participants were required to have gained approval for at least 95% of their previous work on MTurk, with at least 50 HITs completed; have MTurk accounts based in the US; indicate that they were between the ages of 18-45 years; and report that their English abilities were either "advanced" or "superior" (not "novice," "intermediate," or decline to provide information about English ability).
+Participants were paid $2.00 for approximately 10-15 minutes of their time.
+
+According to self-report, participants ranged in age from `r min(s1_results$demo$Age)`-`r max(s1_results$demo$Age)` years ($M$ = `r round_x(mean(s1_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s1_results$demo$Age, na.rm = T), 2)` years) and included more men (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) than women (`r round((s1_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%; <1% of participants identified as some other gender or declined to disclose).
+Participants predominantly identified as White (`r round((s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
+`r round(100*(s1_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
+`r round(100*(s1_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
+
+An additional 77 participants completed the study but were excluded for failing one or more (out of three) embedded attention checks (e.g., failing to choose "34" in response to the question "Please select 34") or for indicating via a multiple choice question at the end of the survey that they had not paid attention, had not avoided distractions, or had not taken the study tasks seriously.
+
+### Materials and procedure
+
+After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages, from newborns to 5-year-olds.
+We will show you example photos of children at three of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions.
+There are 60 brief questions for each of the three ages (for example, 'To what extent is a newborn capable of feeling happy?'), followed by a few demographic questions about yourself.
+We are interested in your opinions about these questions.
+Please do not look up extra information about these questions—we just want to know what you think." Participants were shown an array of pictures of children at several target ages between 0-5 years; see "Target ages and accompanying photographs," below.
+
+Participants then proceeded through three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years.
+On each trial, they were shown two representative photographs of children at the target age (with the photograph labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+
+On the final page of the survey, participants were asked to provide additional demographic information.
+
+#### Capacities
+
+The 60 capacities included in Study 1 were drawn from several areas of previous research.
+Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@putnam.etal2006; @rothbart1978]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.
+
+This process yielded a list of 60 capacities.
+Roughly half of this list (29 of 60 items) were drawn from (or closely based on) the items included in Weisman et al.'s recent studies [@weisman.etal2017a]: "being aware of things", "feeling calm", "feeling embarrassed", "feeling guilty", "feeling happy", "feeling love", "feeling pain", "feeling pleasure", "feeling pride", "feeling sad", "feeling safe", "feeling scared", "feeling tired", "getting angry", "getting hungry", "getting hurt feelings", "having goals", "having self-control", "having thoughts", "having wants and desires", "hearing sounds", "making choices", "planning", "reasoning about things", "recognizing others' emotions", "recognizing somebody else", "remembering things", "seeing", and "telling right from wrong".
+By extension, the list included close variants on 14 of the 20 capacities evaluated in Gray et al.'s original study [@gray.etal2007].
+
+The other half (31 of 60 items) were novel items, not used in previous studies of mind perception, but common in clinical assessments of infant temperament and behavior: "being afraid of somebody", "being angry at somebody", "being comforted by physical touch", "calming themselves down", "controlling their emotions", "detecting danger", "feeling annoyed", "feeling bored", "feeling confused", "feeling distressed", "feeling excited", "feeling frustrated", "feeling helpless", "feeling hopeless", "feeling lonely", "feeling neglected", "feeling overwhelmed", "feeling physically uncomfortable", "feeling textures (for example, 'smooth', 'rough')", "feeling thirsty", "feeling too hot or too cold", "feeling worried", "finding something funny", "focusing on a goal", "getting pleasure from music", "imagining things", "learning from other people", "listening to somebody", "loving somebody", "thinking before they act", and "understanding what somebody else is thinking".
+
+(See \@ref(label:"Selection of capacities: Comparison to previous studies")  for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].)
+
+Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).
+
+#### Target ages and accompanying photographs
+
+In planning this series of studies, we selected 13 target ages based on the developmental milestone ages identified by the CDC [@CDC2021] with the addition of the American Academy of Pediatrics' recommendations for pediatrician visits before 2 months [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
+We limited Study 1 to just the youngest, median, and oldest target ages—presented to participants as "newborns," "9-month-olds" and "5-year-olds"—in order to maximize the number of capacities included in the study without over-burdening participants.
+
+In selecting photos for each target age, we aimed to have photos of the same (or very similar-looking) children at all target ages so as to emphasize the question of the development of mental capacities over the course of an individual child's early life.
+We chose to illustrate each target age with two photos in order to emphasize that we were interested in children's mental capacities in general, rather than the experiences of a particular child in a particular moment.
+We also presented participants with instructions that underscored this point (see above).
+We included one boy and one girl at each target age in order to generalize across perceived sex/gender differences in children's early mental life.
+We used photographs of two (apparently) White, non-Hispanic children, for three reasons: (1) In order to avoid introducing spurious differences across target ages by confounding a target's age and race/ethnicity; (2) In order to match the anticipated race/ethnicity of the majority of participants on MTurk; and (3) Because of the limited set of high-resolution photographs of individual children of color at different points of development currently available to us.
+Conducting similar studies of adults' perceptions of the development of mental life with more ethnically and racially diverse participants, and examining the effects of sex, gender, race, and ethnicity on adults' perceptions of children's mental life, will be critical next steps in this line of research.
+
+Target ages were presented in chronological order, with participants first assessing all 60 capacities for newborns, then 9-month-old infants, and finally 5-year-old children.
+
+### Analysis plan
+
+To conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
+(See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].
+
+In order to determine how many factors to retain, we examined the results of three factor retention protocols: (1) Parallel analysis, which compares the observed correlation structure to the correlation structure arising from random datasets of the same size; (2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and (3) A set of factor retention criteria that have been used in Weisman et al.'s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation (a factor had to meet all three of these criteria in order to be retained).
+Our interpretation of how best to characterize our dataset (i.e., how many factors we observe) was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
+
+Parallel analysis suggested a `r s1_results$efa$factors`-factor solution (accounting for `r round(100*(s1_results$efa$Vaccounted["Cumulative Var",ncol(s1_results$efa$Vaccounted)]))`% of the total variance); minimizing BIC suggested a `r s1_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s1_results$efa_bic$Vaccounted["Cumulative Var",ncol(s1_results$efa_bic$Vaccounted)]))`% of the total variance); and Weisman et al.'s (2017) factor retention criteria suggested a `r s1_results$efa_wdm$factors`-factor solution (accounting for `r round(100*(s1_results$efa_wdm$Vaccounted["Cumulative Var",ncol(s1_results$efa_wdm$Vaccounted)]))`% of the total variance).
+We present the `r s1_results$efa$factors`-factor solution in the main text because it was of intermediate size and because we judged the factors it revealed to be intelligible and of theoretical interest; we present all three solutions in these Supplemental Materials.
+
+## Study 2
+
+### Participants
+
+`r s2_results$demo %>% distinct() %>% nrow()` US adults participated via MTurk in August 2018.
+Eligibility requirements were identical to Study 1.
+Participants were paid $2.90 for approximately 15-20 minutes of their time.
+In response to the overrepresentation of men in Study 1, in Study 2 we recruited men and women through separate "Human Intelligence Tasks" (HITs).
+
+According to self-report, participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants predominantly identified as White (`r round((s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
+`r round(100*(s2_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
+`r round(100*(s2_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
+
+An additional 90 participants completed the study but were excluded for failing one or more (out of four) attention checks or indicating that they had not paid attention (see Study 1).
+
+### Materials and procedure
+
+After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study that was nearly identical to that used in Study 1.
+
+Participants then proceeded through 13 trials in which they assessed the mental lives of children at 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
+On each trial, they were shown two representative photographs of children at the target age, and asked to answer the following question for 20 capacities: "To what extent is a [newborn/4-day-old/etc.] capable of [this capacity]?" As in Study 1, participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+
+On the final page of the survey, participants were asked to provide additional demographic information.
+
+#### Capacities
+
+In order to ask participants to assess a more fine-grained array of target ages without undue participant burden, we limited our list of capacities to 20 of the 60 capacities used in Study 1.
+To identify this list, we drew on the results of Study 1, selecting 5 items for each of the 4 factors identified there.
+For each factor, we aimed to select items that loaded strongly on that factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the latent construct that each factor corresponded to.
+
+To represent _bodily sensations_, we chose the following items: "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
+In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% pull("MR2") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR2") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.
+
+To represent _negative affect_, we chose the following items: "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed".
+In Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR4") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.
+As these numbers suggest, this was a difficult factor to represent, because there were no items that loaded very strongly on the factor (highest loading: `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_distressed", "feeling_lonely", "feeling_frustrated", "feeling_helpless", "feeling_overwhelmed")) %>% pull("MR4") %>% max() %>% round_x(., 2)`) and because the highest-loading items tended to cross-load on other factors as well.
+Nonetheless, we decided to try to represent this latent construct because of its theoretical interest and potential clinical importance.
+
+To represent _social connection_, we chose the following items: "feeling excited", "finding something funny", "loving somebody", "learning from other people", and "feeling happy".
+In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% pull("MR3") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("feeling_excited", "finding_something_funny", "loving_somebody", "learning_from_other_people", "feeling_happy")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR3") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.
+
+Finally, to represent _cognition and control_, we chose the following items: "planning", "having self-control", "reasoning about things", "controlling their emotions", and "telling right from wrong".
+In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% pull("MR1") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("planning", "having_self_control", "reasoning_about_things", "controlling_their_emotions", "telling_right_from_wrong")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR1") %>% pull(loading) %>% max(abs(.)) %>% round_x(., 2)` on the other three factors.
+
+Capacities were presented in a random order each time they were displayed (i.e., order varied across both target ages and participants).
+
+#### Target ages and accompanying photographs
+
+The target ages for this study (birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years) were based on the developmental milestone ages described in Study 1.
+The pairs of photos used to illustrate each target age were identical to those used in Study 1; see Study 1, Methods, for more information.
+
+As in Study 1, target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, then 1-month-old infants, and so forth.
+
+### Analysis plan
+
+#### Preregistered confirmatory analysis of conceptual structure
+
+Based on the results of Study 1, we predicted that the correlational structure of participants' responses would reveal four underlying constructs corresponding to the four factors we identified in Study 1: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
+To test this hypothesis, we performed an EFA, following the methods established in Study 1.
+We predicted that, using the same guidelines we applied for conducting and interpreting EFA in Study 1, we would find support for a `r s1_results$efa$factors`-factor solution, with factors that were similar to the factors revealed in that study (e.g., similar groups of capacities that loaded strongly on any given factor).
+
+In line with our predictions, both parallel analysis and Weisman et al.'s factor retention criteria suggested a `r s2_results$efa$factors`-factor solution, which accounted for `r round(100*(s2_results$efa$Vaccounted["Cumulative Var",ncol(s2_results$efa$Vaccounted)]))`% of the total variance in participants' capacity attributions.
+In this solution, all items loaded most strongly on the factors that they were selected to represent.
+Minimizing BIC suggested an `r s2_results$efa_bic$factors`-factor solution (accounting for `r round(100*(s2_results$efa_bic$Vaccounted["Cumulative Var",ncol(s2_results$efa_bic$Vaccounted)]))`% of the total variance).
+
+#### Preregistered confirmatory analysis of perceived developmental trajectories
+
+We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 2.
+(1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
+
+To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
+Attempting to model random slopes for domain or for target age resulted in model convergence problems.
+Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution.
+Domain was dummy-coded with _cognition and control_ as the baseline.
+
+These tests deviated slightly from the preregistered analysis.
+We originally planned to use "factor scores" (which take into account participants' responses to all 20 items and the relations of those items to all 4 factors) rather than the summary scores described above as our dependent variable for these tests.
+We planned to derive these factor scores by projecting Study 2 data into the conceptual space defined by the factor solution for Study 1; however, this projection was impossible to implement, because Study 2 included only a subset of the variables used in Study 1.
+Furthermore, upon reflection, we decided that using any kind of factor scores (even factor scores derived only from Study 2 data) would be inappropriate for testing our hypotheses, which hinge on assessing the _absolute_ degree to which participants attributed different aspects of mental life to children of different ages; factor scores, which function much like z-scores, are instead designed to capture individual differences in responses (i.e., the degree to which a given participant attributed relatively greater or lesser capacities compared to the average of all participants).
+
+In addition, we note that we originally planned to use a multilevel linear regression to analyze these scores.
+However, we now consider it misguided to model participants' responses using gaussian distribution, because—both in principle and in our empirical dataset—capacity ratings behaved asymptotically, plateauing near the ceiling of the scale (100, labeled "completely capable") at some point in development.
+The approach described here—using the beta distribution—is a far more accurate representation of these responses.
+Using generalized additive models via the "mgcv" package for R [@wood2017] allowed us to fine-tune the shape of these perceived developmental trajectories via spline-based smoothing (analogous to fitting polynomial terms in the context of linear regression, but without specifying in advance the order of the polynomials included in the model).
+
+## Study 3
+
+### Participants
+
+`r s3_results$demo %>% distinct() %>% nrow()` US adults participated via MTurk in April 2019.
+Eligibility requirements were identical to Studies 1-2.
+Participants were paid $2.90 for approximately 15-20 minutes of their time.
+As in Study 2, we recruited men and women separately.
+
+According to self-report, participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants predominantly identified as White (`r round((s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
+`r round(100*(s3_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
+`r round(100*(s3_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
+
+An additional 79 participants completed the study but were excluded for failing two or more (out of eight) embedded attention checks or for failing to provide a reasonable response in well-formed English sentences to an open-ended comprehension check included at the end of the survey.
+
+### Materials and procedure
+
+After completing a screening questionnaire (in which participants provided information about their gender/sex, age, and English abilities) and providing informed consent, participants were provided with an overview of the study, as follows: "In this study, we will ask you about the mental capacities of children of different ages.
+We will show you example photos of children at each of the following ages to remind you of what children look like at that age, but please think about children of that age in general when answering these questions.
+We will ask you about 8 different mental capacities: feeling happy, getting hungry, controlling emotions, feeling distressed, feeling pain, reasoning about things, learning from other people, and feeling helpless.
+For each mental capacity, we will ask you to assess the extent to which newborns (at birth) have this mental capacity, then 4-day-olds, 1-month-olds, 2-month-olds, 4-month-olds, and so on, ending with 5-year-olds.
+We'll also ask for your opinion about the different factors that might influence the development of these capacities, such as the child being ‘preprogrammed' to have certain abilities, or the child learning from the people or objects around him or her.
+At the end of the survey, we will ask you a few demographic questions about yourself.
+We are interested in your opinions about these questions.
+Please do not look up extra information about these questions—we just want to know what you think."
+
+Participants then proceeded through eight trials, in which they assessed each of the eight capacities in turn; the order of capacities was randomized across participants.
+On each trial, participant assessed children at all 13 target ages used in Study 2 in a fixed order from youngest to oldest.
+Each age was presented along with a representative pair of photographs (also used in Studies 1 and 2), and participants were asked to answer the following question: "To what extent is a [newborn/4-day-old/1-month-old/etc.] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+
+On each trial, at the bottom of the page participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children's capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for the following 10 developmental mechanisms: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that given them this ability"; "the child's body grows and matures (for example, muscles get stronger, child gets taller)"; "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child's senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this".
+These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
+They were then provided an opportunity to write in "any factors that play a role in the development of children's capacity for [capacity]".
+Finally, they were asked to choose among these 10 possible mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
+On the final page of the survey, participants were asked to provide additional demographic information.
+
+#### Capacities
+
+Because Study 3 included additional questions probing participants' theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to eight in the current study to maintain an appropriate level of participant burden.
+To select these eight capacities, we drew on the results of Study 2, selecting two items for each of the four factors identified by EFA.
+For each domain, we selected items that loaded strongly on the relevant factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the domain that each factor corresponded to.
+We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensations_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
+Capacities were presented in a random order for each participant.
+
+#### Target ages and accompanying photographs
+
+The 13 target ages for this study were identical to Study 2, with the exception that we added the parenthetical phrase "(at birth)" when referring to newborns.
+Each target age was presented with the same pair of photographs used in Study 2.
+Target ages were presented in chronological order on each trial.
+
+### Analysis plan
+
+#### Preregistered confirmatory analysis of perceived developmental trajectories
+
+We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3; these were identical to our hypotheses for Study 2 (which were upheld in that study): (1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
+
+Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
+Again, attempting to model random slopes for domain or for target age resulted in model convergence problems.
+Again, responses were rescaled to range from 0.005 to 0.995, and domain was dummy-coded with _cognition and control_ as the baseline.
+
+(We note that, in contrast to Study 2, in Study 3 we did preregister this analysis, although we preregistered a linear regression rather than a beta regression via generalized additive model; see extended notes on our choice of this analysis approach under Study 2.)
+
+#### Preregistered exploratory analysis of perceived developmental trajectories
+
+Beyond the two hypotheses described in the previous section, we also anticipated that perceptions of developmental trajectories in different domains would vary in their curvilinearity—e.g., development in one domain might be perceived to be gradual and linear, while development in another domain might be perceived to occur in stages, at an exponential rate, or to peak at a specific age.
+To explore these possibilities, we preregistered a regression analysis adding polynomial effects of target age; however, in our reconceptualization of the appropriate way to analyze our data given the distribution of the response variable (see Study 2), this exploratory analysis was superseded by the generalized additive model.
+
+#### Preregistered exploratory analysis of developmental mechanisms
+
+Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*).
+We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
+intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
+Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_.
+We also conducted separate, analogous regression analyses for each domain separately.
+In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
+(Note that these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see main text.)
+
 # Extended results
@@
 
-As described in the main text, we began with an expansive exploration of US adults’ attributions of mental life to infants and young children of different ages.
+As described in the main text, we began with an expansive exploration of US adults' attributions of mental life to infants and young children of different ages.
 We included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction.
-We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life.
-Our primary analysis for this preregistered study was an exploratory factor analysis (EFA) of participants’ capacity ratings.
-This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children.
-Following previous work on mind perception, we argue that the suites of capacities revealed by EFA offer a meaningful approximation of the latent conceptual structure underlying participants’ reasoning about the developing human mind.
+We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants' reasoning about the development of mental life.
+Our primary analysis for this preregistered study was an exploratory factor analysis (EFA) of participants' capacity ratings.
+This analysis allowed us to examine which capacities tend to "hang together" in participants' assessments of the mental lives of infants and young children.
+Following previous work on mind perception, we argue that the suites of capacities revealed by EFA offer a meaningful approximation of the latent conceptual structure underlying participants' reasoning about the developing human mind.
 
@@
 (2) Minimizing the Bayesian Information Criterion (BIC), which is one method of optimizing both goodness of fit and parsimony; and 
-(3) A set of factor retention criteria that have been used in Weisman et al.’s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation.
+(3) A set of factor retention criteria that have been used in Weisman et al.'s previous work [@weisman.etal2017a], in which they retained factors with eigenvalues greater than 1.0, which individually accounted for greater than 5% of the shared variance before transformation or rotation, and which were the "dominant" factor (the factor with the strongest absolute factor loading) for at least one mental capacity after transformation.
 (In this protocol, a factor had to meet all three of these criteria in order to be retained).
@@
 The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs1efaparvacc).
+
+It is worth noting that a handful of items loaded relatively strongly on two factors (loadings $\geq$ 0.40), suggesting that these factors are not entirely distinct.
+The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensations_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (like pain) and an affective state (like frustration).
+Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a sensory ability and a critical part of many social interactions (eye contact).
+The relatively large degree of overlap between _cognition and control_ and _social connection_, in particular, might indicate that participants believed these two constructs to be more strongly connected than other aspects of life; in fact, these two factors were the most strongly correlated of all pairs of factors ($\phi$ = `r round_x(s1_results$efa$Phi["MR1", "MR3"], 2)`).
+(The next strongest correlation was between _bodily sensations_ and _social connection_: $\phi$  = `r round_x(s1_results$efa$Phi["MR2", "MR3"], 2)`.
+All other inter-factor correlations: $\phi \le$ `r round_x((s1_results$efa$Phi[upper.tri(s1_results$efa$Phi) == T] %>% sort(decreasing = T))[3], 2)`.)
 
@@
 if (resave_plots == T | !file.exists("../outputs/fig01.pdf")) {
+  ggsave("../outputs/fig01.jpg")
   ggsave("../outputs/fig01.svg")
@@
 
-Weisman et al.'s (2017) factor retention criteria suggested retaining `r s1_weismanetal` factors.
+Weisman et al.'s factor retention criteria suggested retaining `r s1_weismanetal` factors.
 Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efawdmload).
@@
 ```{r figS03, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1).
-Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
+Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
 knitr::include_graphics("../outputs/figS03.pdf")
@@
 
-As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retention criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
+As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.'s factor retention criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol.
 Here we present these three factor retention protocols separately.
@@
 
-Weisman et al.'s (2017) factor retention criteria suggested retaining `r s2_weismanetal` factors—i.e., the same `r s2_weismanetal`-factor solution suggested by parallel analysis.
+Weisman et al.'s factor retention criteria suggested retaining `r s2_weismanetal` factors—i.e., the same `r s2_weismanetal`-factor solution suggested by parallel analysis.
 (See Supplementary Tables \@ref(tab:tabs2efaparload) and \@ref(tab:tabs2efaparvacc).)
@@
 
-(1) We predicted that, on average, participants’ perception of children’s mental capacities would increase as a function of the target child’s age, with participants generally attributing more and greater abilities to older children.
+(1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children.
 (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
@@
 
-In brief, we view these results as confirming our hypotheses that US adults would rate older children as more capable across the board, but that perceptions of the development of children’s capacities would differ across domains.
+In brief, we view these results as confirming our hypotheses that US adults would rate older children as more capable across the board, but that perceptions of the development of children's capacities would differ across domains.
 (See main text for extended interpretation.)
@@
 ```{r fig02a, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 2).
-Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
+Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
 d2_gam_r1_rsq <- round_x(summary(s2_gam$gam)$r.sq, 2)
@@
   labs(x = "Target age (years)",
-       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       y = "Mean response", # \n0 = not at all capable, 100 = completely capable",
        caption = bquote(paste("Adjusted R"^"2"*" = ", .(d2_gam_r1_rsq)))) +
@@
 ```{r fig02b, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 3).
-Scores were calculated by averaging a participant’s responses to the two capacity items for each domain of mental life.
-Lighter lines represent individual participants’ scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
+Scores were calculated by averaging a participant's responses to the two capacity items for each domain of mental life.
+Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
 d3_gam_r1_rsq <- round_x(summary(s3_gam$gam)$r.sq, 2)
@@
   labs(x = "Target age (years)",
-       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       y = "Mean response", # \n0 = not at all capable, 100 = completely capable",
        caption = bquote(paste("Adjusted R"^"2"*" = ", .(d3_gam_r1_rsq)))) +
@@
 ```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
-Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
 In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
-In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 1.2}
+In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 0.7}
 plot_grid(fig02a, fig02b,
@@
 if (resave_plots == T | !file.exists("../outputs/fig02.pdf")) {
+  ggsave("../outputs/fig02.jpg")
   ggsave("../outputs/fig02.svg")
@@
 As a first step in assessing the lay theories underlying these perceptions of the development of human mental life, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
-We assessed a wide range of potential developmental mechanisms for children’s capacities.
+We assessed a wide range of potential developmental mechanisms for children's capacities.
 We applied a variety of dimensionality reduction approaches in order to sort these developmental mechanisms into meaningful categories, and then modeled participants' ratings of the importance of these mechanism as a function of domain (_bodily sensations_, _negative affect_, _social connection_, and _cognition and control_).
@@
 In these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
-(Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see previous section.)
+(Note that these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see previous section.)
 
@@
       dev_factor,
-      "preprogrammed" = "biologically ‘preprogrammed’",
+      "preprogrammed" = "biologically ‘preprogrammed'",
       "womb_experiences" = "experiences in the womb",
@@
 In these analyses, domain was effect-coded for comparisons to the grand mean collapsing across domains.
-(As in the previous section, these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses.)
+(As in the previous section, these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses.)
 
@@
 intrinsic mechanisms for each domain of capacities (identical to Figure 3, Panel C, main text).
-Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
 The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 4.5, fig.asp = 6.75/6}
@@
 intrinsic mechanisms as the 'most important' driver of development.
-Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
 The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 5, fig.asp = 6.75/(4.5 + 1.5 + 1.5)}
@@
 if (resave_plots == T | !file.exists("../outputs/fig03.pdf")) {
+  ggsave("../outputs/fig03.jpg")
   ggsave("../outputs/fig03.svg")
@@
               rename(`Study 1` = capacity)) %>%
-  mutate_at(vars(`Weisman et al. (2017a)`, `Weisman et al. (2017b)`, 
+  rename(`Weisman et al. (2017, PNAS)` = `Weisman et al. (2017a)`,
+         `Weisman et al. (2017, Proc. CogSci)` = `Weisman et al. (2017b)`) %>%
+  mutate_at(vars(`Weisman et al. (2017, PNAS)`, `Weisman et al. (2017, Proc. CogSci)`, 
                  `Gray et al. (2007)`, `Malle (2019, Study 1)`, `Malle (2019, Study 2)`),
             funs(case_when(is.na(`Study 1`) & grepl("similar to", .) ~ NA_character_, TRUE ~ .))) %>%
-  arrange(order, `Weisman et al. (2017a)`, `Weisman et al. (2017b)`, 
+  arrange(order, `Weisman et al. (2017, PNAS)`, `Weisman et al. (2017, Proc. CogSci)`, 
           `Gray et al. (2007)`, `Malle (2019, Study 1)`, `Malle (2019, Study 2)`) %>%
   filter(!(is.na(`Study 1`) & 
-             is.na(`Weisman et al. (2017a)`) &
-             is.na(`Weisman et al. (2017b)`) &
+             is.na(`Weisman et al. (2017, PNAS)`) &
+             is.na(`Weisman et al. (2017, Proc. CogSci)`) &
              is.na(`Gray et al. (2007)`) &

### 2021-08-08 supplement/supplement-main.Rmd
make jpgs for readme

@@
 
+# make jpg version (darker)
+fig02a_jpg <- d2_gam_r1_pred %>%
+  ggplot(aes(x = target_year, y = score, color = factor)) +
+  facet_grid(~ factor) +
+  geom_path(aes(group = ResponseId),
+            # color = "#160072",
+            alpha = 1, size = 0.02) +
+  geom_smooth(aes(y = pred_score), 
+              color = "#f94802",
+              fill = NA, size = 1, lty = 1) +
+  geom_pointrange(data = . %>%
+                    group_by(factor, target_year) %>%
+                    multi_boot_standard(col = "score") %>%
+                    ungroup,
+                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
+                  color = "black",
+                  # color = "#160072",
+                  fatten = 1) +
+  scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(breaks = seq(0, 1, 0.25),
+                     labels = seq(0, 100, 25)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA)) +
+  labs(x = "Target age (years)",
+       y = "Mean response", # \n0 = not at all capable, 100 = completely capable",
+       caption = bquote(paste("Adjusted R"^"2"*" = ", .(d2_gam_r1_rsq)))) +
+  guides(color = guide_none())
+
 # # save plot
@@
 
+# make jpg version (darker)
+fig02b_jpg <- d3_gam_r1_pred %>%
+  ggplot(aes(x = target_year, y = score, color = factor)) +
+  facet_grid(~ factor) +
+  geom_path(aes(group = ResponseId),
+            # color = "#160072",
+            alpha = 1, size = 0.02) +
+  geom_smooth(aes(y = pred_score), 
+              color = "#f94802",
+              fill = NA, size = 1, lty = 1) +
+  geom_pointrange(data = . %>%
+                    group_by(factor, target_year) %>%
+                    multi_boot_standard(col = "score") %>%
+                    ungroup,
+                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
+                  color = "black",
+                  # color = "#160072",
+                  fatten = 1) +
+  scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(breaks = seq(0, 1, 0.25),
+                     labels = seq(0, 100, 25)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA)) +
+  labs(x = "Target age (years)",
+       y = "Mean response", # \n0 = not at all capable, 100 = completely capable",
+       caption = bquote(paste("Adjusted R"^"2"*" = ", .(d3_gam_r1_rsq)))) +
+  guides(color = guide_none())
+
 # # save plot
@@
 if (resave_plots == T | !file.exists("../outputs/fig02.pdf")) {
-  ggsave("../outputs/fig02.jpg")
   ggsave("../outputs/fig02.svg")
   ggsave("../outputs/fig02.pdf")
+}
+```
+
+```{r fig02_jpg, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
+Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
+In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 0.7}
+plot_grid(fig02a_jpg, fig02b_jpg,
+          ncol = 1, labels = "AUTO")
+
+# save plot   
+if (resave_plots == T | !file.exists("../outputs/fig02.jpg")) {
+  ggsave("../outputs/fig02.jpg")
 }
@@
 # fig03b
+
+# jpg version (darker)
+fig03b_jpg <- d3_mech_ratings %>%
+  # filter(!is.na(dev_factor_cluster)) %>%
+  filter(!is.na(dev_factor)) %>%
+  mutate(dev_factor_cluster = case_when(
+    dev_factor == "brain_changes" ~ "brain changes",
+    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
+    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
+    dev_factor_cluster = factor(dev_factor_cluster,
+                                levels = c("INTRINSIC", 
+                                           "EXTRINSIC",
+                                           "brain changes"))) %>%  
+  # participant-level means for each cluster, by capacity
+  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
+  summarise(score_a = mean(response, na.rm = T)) %>%
+  ungroup() %>%
+  # participant-level mean of means for each cluster, by domain
+  group_by(ResponseId, dev_factor_cluster, factor) %>%
+  summarise(score_b = mean(score_a, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(blank_var = "  ") %>%
+  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
+                                 width = 28, side = "left"),
+                         as.numeric(dev_factor_cluster)), 
+             y = score_b, color = factor)) +
+  facet_grid(cols = vars(blank_var),
+             rows = vars(reorder(toupper(factor), as.numeric(factor))),
+             scales = "free", space = "free") +
+  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
+  geom_path(data = . %>%
+              filter(dev_factor_cluster != "brain changes"),
+            aes(group = ResponseId), 
+            alpha = 1, size = 0.02,
+            position = position_jitter(width = 0.2, 
+                                       height = 0, 
+                                       seed = 94305)) +
+  geom_point(alpha = 0.6, size = 0.02,
+             position = position_jitter(width = 0.2, 
+                                        height = 0, 
+                                        seed = 94305)) +
+  # group-level mean of means of means for each cluster, by domain
+  geom_pointrange(data = . %>%
+                    group_by(factor, dev_factor_cluster) %>%
+                    multi_boot_standard(col = "score_b") %>%
+                    ungroup(),
+                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
+                  color = "black", fatten = 2) +
+  scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        legend.position = "top",
+        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Developmental mechanism type",
+       y = "Mean response (0 = not at all important, 6 = extremely important)",
+       color = "Domain") +
+  guides(color = guide_none())
+  # guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+# fig03b_jpg
 ```
@@
 if (resave_plots == T | !file.exists("../outputs/fig03.pdf")) {
-  ggsave("../outputs/fig03.jpg")
   ggsave("../outputs/fig03.svg")
   ggsave("../outputs/fig03.pdf")
+}
+```
+
+```{r fig03_jpg, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
+Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
+intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
+intrinsic mechanisms as the 'most important' driver of development.
+Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 5, fig.asp = 6.75/(4.5 + 1.5 + 1.5)}
+plot_grid(fig03a + guides(color = guide_none()),
+          NULL, # to adjust spacing between panels
+          fig03b_jpg, # + labs(x = " "),
+          NULL,
+          fig03c + 
+            labs(x = " ",
+                 y = "Selection of 'most important' mechanism") +
+            scale_y_continuous(limits = c(0, 2*nrow(d3_demo)),
+                               breaks = c(0, nrow(d3_demo), 2*nrow(d3_demo)),
+                               labels = c("0%", "50%", "100%")) +
+            guides(fill = guide_none(),
+                   color = guide_none()), 
+          nrow = 1, rel_widths = c(4.5, 0.1, 1.5, 0.1, 1.5), 
+          labels = c("A", "", "B", "", "C"))
+
+# save plot
+if (resave_plots == T | !file.exists("../outputs/fig03.jpg")) {
+  ggsave("../outputs/fig03.jpg")
 }

### 2021-08-08 paper/paper.Rmd
tweaks to text

@@
 More recently, Weisman et al.
-used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a]); see [@malle2019] for a similar three-factor solution.
+used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a]; see [@malle2019] for a similar three-factor solution.
+Such findings have inspired a wide range of subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
 
-However, the burgeoning field of mind perception has largely neglected the question of how the mind emerges over development.
+However, the burgeoning field of mind perception has largely neglected the question of how the human mind emerges over development.
 In many studies, infants and children have simply not been included as targets for mental capacity attributions; instead, participants have been asked to reason about human adults alongside a range of non-human entities, including other animals, technologies, and supernatural beings.
@@
 Likewise, Weisman et al.’s studies characterized infants and young children—along with, e.g., chimpanzees, elephants, and dolphins—as entities that are perceived to be fully capable of physiological sensations but more limited in their perceptual-cognitive capacities and social-emotional abilities; this is in contrast to human adults, who are perceived to be fully capable across these domains [@weisman.etal2017a].
-
 Although such findings can be reinterpreted as providing preliminary evidence that people consider the minds of infants and children to differ from the minds of adults, they do not address how people conceptualize the development of the mind in early life.
 
-Of course, infants and young children are far from unusual social partners.
+Yet infants and young children are far from unusual social partners.
 Caregiving relationships are at the core of human existence; for many people, infants and young children are among the most frequent and highly valued minds that we encounter.
@@
 At a most basic level, our results reflect sets of intercorrelated capacities: When a participant judged that a child of a certain age was highly capable of planning, they also tended to judge that that child was capable of having self control, thinking before they act, and the other capacities with strong factor loadings on the _cognition and control_ factor; and likewise for the suites of capacities that define the other factors revealed by EFA.
-Therefore, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children [@weisman.etal2017a].
+Therefore, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children.
 Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants’ perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development.
@@
 
-In terms of the covariance structure of participants' capacity ratings, a preregistered EFA yielded four factors very similar to the four factors from Study 1 (see Supplemental Materials), with all capacity items loading strongly on the factors that they were selected to represent.
-Minimally, these results suggest that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1.
+A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors (see Supplemental Materials).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1.
 Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
@@
 Finally, if we had misinterpreted the fundamental semantic content that distinguished the factors in Study 1 and selected inappropriate capacities to represent these factors, the Study 2 analysis could have identified more capacities with cross-loadings.
-Instead, we believe the results of this analysis offer some validation of the four factors we have called _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
+Instead, the results of this analysis offer some validation of the four factors we have called _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
 
@@
 
-Regressing participants' item-level responses onto target age, domain, and interactions between them (via a multilevel generalized additive model; see Methods) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
+Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
 On one extreme, participants attributed some, but relatively little, capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
@@
 At the other extreme, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`).
-See Figure \@ref(fig:fig02), Panel A.
 
-Visual inspection of Figure \@ref(fig:fig02), Panel A clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
+Visual inspection of Figure \@ref(fig:fig02), Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
 In the domain of _bodily sensations_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
@@
 
-The results of Study 3 yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B.
+This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B.
 As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
@@
 Finally, as in Study 2, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`).
-See Figure \@ref(fig:fig02), Panel B.
 
-Visual inspection of Figure \@ref(fig:fig02), Panel B makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
-In the domain of _bodily sensations_, participants perceived hardly any growth over the target age range, and what growth they did perceive was understood to occur rapidly in the first year of life.
-In the domains of _negative affect_ and _social connection_, participants perceived much more growth over the target age range, and in both cases most of this growth was understood to occur during the first two years of life; again, this was especially pronounced in the domain of _social connection_.
-Finally, participants perceived development in the domain of _cognition and control_ to be much more gradual and, by extension, more linear across the target age range.
-
-See Supplemental Materials for the full results of this analysis.
+Visual inspection of Figure \@ref(fig:fig02), Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
 
@@
 We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-(See [@wang.feigenson2019; @berent.etal2019; @berent.etal2020] for in-depth investigations of ordinary people’s intuitions about the innateness of cognitive abilities, motor abilities, and emotion.)
+(See @wang.feigenson2019; @berent.etal2019; @berent.etal2020 for in-depth investigations of ordinary people’s intuitions about the innateness of cognitive abilities, motor abilities, and emotion.)
 
@@
 
-A variety of dimensionality reduction techniques (see Supplemental Materials) converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (with some indications of two sub-groups within each of these general categories).
-First, there were what we will call "intrinsic" mechanisms, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
-Participants clearly distinguished these intrinsic mechanisms from what we will call "extrinsic" mechanisms, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
+A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials).
+First, there were what we will call _intrinsic mechanisms_, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
+Participants clearly distinguished these intrinsic mechanisms from what we will call _extrinsic mechanisms_, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
 One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
@@
 Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensations_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensations", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
-On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
+On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
 Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).
 
-In sum, participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
+Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
 Capacities for _bodily sensations_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
@@
 
-In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); measured perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
 
@@
 These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life.
-(See also [@weisman.etal2021] for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)
+(See also @weisman.etal2021 for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)
 
@@
 These two factors have no obvious precedents in previous studies of mind perception.
-In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials), or the narrower focus on humans (and, in particular, infants and children) as the targets of mind perception.
+In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials);  the narrower focus on humans as the targets of mind perception; or the emphasis on how mental capacities develop over time.
 Based on the findings of Studies 2 and 3, we propose that _social connection_ and _negative affect_ emerged as distinct factors because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
@@
 Critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most appropriate in a given cultural setting, most in line with caregivers’ own values and goals, or most beneficial for children  according to experts.
-For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021] (see also [@laranjo.etal2008]).
-An additional goal is to identify the gaps and misconceptions in these theories that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, experience concern about their child’s developmental progress, or even engage in neglectful or abusive behaviors toward the child.
+For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021; see also @laranjo.etal2008]; could educating parents about infants' mental capacities and their rapid development spark increased curiosity in new parents, and would this have downstream consequences in their interactions with their children?
+An additional, related goal is to identify the gaps and misconceptions in these theories that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, experience concern about their child’s developmental progress, or even engage in neglectful or abusive behaviors toward the child.
 Identifying the antecedents of individual differences in these beliefs could be an especially important step for such clinically-focused applications.
@@
 All studies were approved by the Stanford University Internal Review Board.
-For extended descriptions of methods, see Supplemental Material.
+For extended descriptions of methods and results, see Supplemental Material.
 
@@
 Participants completed three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years.
-On each trial, they were shown two representative photographs of children at the target age (with the photograph labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").
 
@@
 Eligibility requirements were identical to Study 1.
-Participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants ranged in age from `r min(s2_results$demo$Age)`-`r max(s2_results$demo$Age)` years ($M$ = `r round_x(mean(s2_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s2_results$demo$Age, na.rm = T), 2)` years) and included roughly equal numbers of men (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s2_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
 Participants predominantly identified as White (`r round((s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
@@
 Participants completed 13 trials in which they assessed the mental lives of children at 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
-On each trial, they were shown two representative photographs of children at the target age, and asked to answer the following question for 20 capacities: "To what extent is a [newborn/4-day-old/etc.] capable of [this capacity]?" As in Study 1, participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+On each trial, they were shown two representative photographs of children at the target age, and asked to answer the following question for 20 capacities: "To what extent is a [newborn/4-day-old/etc.] capable of [this capacity]?" As in Study 1, participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").
 
@@
 
-The target ages for this study (birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years) were based on the developmental milestone ages described in Study 1.
+The target ages for this study were based on the developmental milestone ages described in Study 1.
 Target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, and so forth.
@@
 Eligibility requirements were identical to Studies 1-2.
-Participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and (per our recruitment strategy) included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
+Participants ranged in age from `r min(s3_results$demo$Age)`-`r max(s3_results$demo$Age)` years ($M$ = `r round_x(mean(s3_results$demo$Age, na.rm = T), 2)` years, $sd$ = `r round_x(sd(s3_results$demo$Age, na.rm = T), 2)` years) and included roughly equal numbers of men (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Male") %>% pull(prop))*100, 0)`%) and women (`r round((s3_results$demo %>% count(GenderSex) %>% mutate(prop = n/sum(n)) %>% filter(GenderSex == "Female") %>% pull(prop))*100, 0)`%).
 Participants predominantly identified as White (`r round((s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
@@
 On each trial, participant assessed children at all 13 target ages used in Study 2 in a fixed order from youngest to oldest.
-Each age was presented along with a representative pair of photographs (also used in Studies 1 and 2), and participants were asked to answer the following question: "To what extent is a [newborn/4-day-old/1-month-old/etc.] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled as "not at all capable") to 100 (labeled as "completely capable").
+Each age was presented along with a representative pair of photographs (also used in Studies 1 and 2), and participants were asked to answer the following question: "To what extent is a [newborn/4-day-old/1-month-old/etc.] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").
 
 On each trial, participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for 10 developmental mechanisms (see Results) presented in a fixed order.
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for 10 developmental mechanisms presented in a fixed order; see Results for all items.
 Participants were also asked to choose among these 10 mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
 
-Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to eight in the current study to maintain an appropriate level of participant burden.
-To select these eight capacities, we drew on the results of Study 2, selecting two items for each of the four factors identified by EFA.
-For each domain, we selected items that loaded strongly on the relevant factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the domain that each factor corresponded to.
+Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to 8 in the current study to maintain an appropriate level of participant burden.
 We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensations_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.

### 2021-08-08 paper/paper.Rmd
lay to intuitive

@@
 Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological "preprogramming," physical maturation, passive observation, and social learning).
-These studies reveal the lay theories that govern US adults’ understanding of the development of the human mind, illuminating the cognitive architecture that supports some of the most important social interactions: caregiving relationships with infants and children.
+These studies reveal the intuitive theories that govern US adults’ understanding of the development of the human mind, illuminating the cognitive architecture that supports some of the most important social interactions: caregiving relationships with infants and children.
 
@@
 Study 3 was designed with two goals in mind: First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2.
-Second, we aimed to probe the lay theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
+Second, we aimed to probe the intuitive theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
 
@@
 In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years.
-In order to accommodate the addition of questions probing lay theories of development (see next section), participants assessed only 2 capacities per domain; see Methods.
+In order to accommodate the addition of questions probing intuitive theories of development (see next section), participants assessed only 2 capacities per domain; see Methods.
 
@@
 
-### Lay theories of development
+### Intuitive theories of development
 
@@
 
-In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); measured perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); measured perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
 

### 2021-08-08 supplement/supplement-main.Rmd
lay to intuitive

@@
   - Kathryn L. Humprheys^[Department of Psychology, Vanderbilt University]
-date: "August 7, 2021"
+date: "August 8, 2021"
 output:
@@
 In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the lay theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
 
@@
 Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/).
+All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
 All studies were approved by the Stanford University Internal Review Board.
@@
 As described in the main text, Study 3 was designed with two goals in mind: First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2.
-Second, we aimed to probe the lay theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
+Second, we aimed to probe the intuitive theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
 
@@
 
-As a first step in assessing the lay theories underlying these perceptions of the development of human mental life, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
+As a first step in assessing the intuitive theories underlying these perceptions of the development of human mental life, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
 We assessed a wide range of potential developmental mechanisms for children's capacities.

### 2021-08-09 paper/paper.Rmd
small tweaks and typos

@@
   - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
-  - Kathryn L. Humprheys^[Department of Psychology, Vanderbilt University]
+  - Kathryn L. Humphreys^[Department of Psychology, Vanderbilt University]
 output:
@@
 used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a]; see [@malle2019] for a similar three-factor solution.
-Such findings have inspired a wide range of subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
+Such findings have inspired subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
 
@@
 We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
-For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed (see [@berent.etal2019] for empirical evidence in line with this speculation).
+For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed (see @berent.etal2019 for empirical evidence in line with this speculation).
 In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
@@
 We found that participants considered _bodily sensations_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast (and in line with previous work [@wang.feigenson2019; @berent.etal2019]), participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019; @berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
 

### 2021-08-09 supplement/supplement-main.Rmd
small tweaks and typos

@@
   - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
-  - Kathryn L. Humprheys^[Department of Psychology, Vanderbilt University]
-date: "August 8, 2021"
+  - Kathryn L. Humphreys^[Department of Psychology, Vanderbilt University]
+date: "August 9, 2021"
 output:
@@
 
-(See \@ref(label:"Selection of capacities: Comparison to previous studies")  for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].)
+See "Selection of capacities: Comparison to previous studies" for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
 

### 2021-10-16 paper/paper.Rmd
revisions for submission

@@
 title: "Beliefs about the development of mental life"
-author:
-  - Kara Weisman^[Department of Psychology, University of California, Riverside; kgweisman@gmail.com]
-  - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
-  - Kathryn L. Humphreys^[Department of Psychology, Vanderbilt University]
+author: "[authors removed for anonymous review]"
 output:
-  # word_document:
-  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
@@
     number_sections: false
+  #   reference_docx: word-styles-ref.docx
+  # word_document:
 bibliography: "../supplement/references.bib"
-cls: "../supplement/article.cls"
+csl: "../supplement/apa.csl"
+# cls: "../supplement/article.cls"
 figsintext: yes
@@
 
-In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensations_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
+Caregiving relationships with infants and children are among the most common, important, and complex human social interactions.
+Caring for a young child over time requires an adult to continually update their own mental representations of the child’s capacities as the child develops.
+In a series of large-scale studies, we assessed how US adults conceptualize the development of the human mind over the first five years of life.
+Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
 Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological "preprogramming," physical maturation, passive observation, and social learning).
-These studies reveal the intuitive theories that govern US adults’ understanding of the development of the human mind, illuminating the cognitive architecture that supports some of the most important social interactions: caregiving relationships with infants and children.
-
-## Significance statement
-
-Caregiving relationships with infants and children are among the most common, important, and complex human social interactions.
-Caring for a young child over time requires an adult to continually update their own mental representations of the child's capacities as the child grows and changes.
-These representations are likely to have important consequences for the child's well-being—particularly in the first few years of life, when the child's communication skills are limited and the caregiver must make inferences about the child's thoughts, feelings, and needs.
+Adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s thoughts, feelings, and needs.
 The current studies shed light on this fascinating and understudied aspect of "mind perception," in turn laying the foundation for theory-based interventions to encourage positive and responsive parenting behaviors.
@@
 \newpage
-
-Frustration, compassion, worry, humor, imagination, love—such experiences are fundamental parts of human life.
-But few people would assert that these capacities are fully developed at birth.
+Frustration, compassion, worry, humor, imagination, love—such experiences are fundamental parts of human life, but few people would assert that these capacities are fully developed at birth.
 In any given interaction with a child, adults come face to face with a being whose experience of the world is like their own, but different; whose mind is capable of some of the thoughts and feelings that an adult’s mind is, but perhaps not all of them.
@@
 
-In this paper, we examine how adults conceptualize the developing minds of infants and children.
-We draw on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed.
+Indeed, caring for a young child involves making countless decisions under uncertainty: Why is my child crying, smiling, shouting, or biting?
+What do they want, and what do they need?
+Can they understand what I am saying?
+Do they love me?
+As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.
+
+These folk beliefs and intuitive theories are, to date, poorly understood by social scientists.
+A handful of recent studies have examined the extent to which cognitive abilities, knowledge, and emotions are thought to be innate vs.
+learned, with special attention to comparing laypeople’s beliefs about innateness to scientific evidence for or against innateness and universality [@wang.feigenson2019; @berent.etal2019; @berent.etal2020; see @berent2021 for discussion].
+These studies offer a fascinating glimpse of potential gaps, misconceptions, and biases in laypeople’s beliefs about the human mind, but they leave open many questions about the nature of the folk beliefs and intuitive theories themselves.
+What is the cognitive architecture underlying laypeople’s beliefs about the origins of the human mind?
+How do laypeople "carve up" the various sensations, experiences, and abilities that make up human mental life, and—most crucially from the perspective of caregiving—how do laypeople understand changes in mental life across early development?
+
+In this paper, we examine how adults conceptualize the developing minds of infants and children by drawing on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed.
 In a groundbreaking study, Gray et al.
@@
 More recently, Weisman et al.
-used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a]; see [@malle2019] for a similar three-factor solution.
+used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a; see @malle2019 for a similar three-factor solution].
 Such findings have inspired subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
 
-However, the burgeoning field of mind perception has largely neglected the question of how the human mind emerges over development.
+However, the burgeoning field of mind perception has largely neglected the question of how the human mind changes over development.
 In many studies, infants and children have simply not been included as targets for mental capacity attributions; instead, participants have been asked to reason about human adults alongside a range of non-human entities, including other animals, technologies, and supernatural beings.
 Even studies that have probed participants’ mental capacity attributions to infants and children have generally treated them as beings distinct from adults, rather than as snapshots of a single mind as it emerges and changes over time.
-For example, Gray et al.’s early work on mind perception suggested that a five-month-old infant is an entity that is generally considered to have experience but not agency—in contrast to, say, a five-year-old child (considered to have experience as well as limited agency), a human adult (considered to have maximal experience and agency), or a robot (considered to have agency but not experience) [@gray.etal2007].
+For example, Gray et al.’s early work on mind perception suggested that a five-month-old infant is an entity that is generally considered to have experience but not agency—in contrast to, say, a five-year-old child (considered to have experience as well as limited agency), a human adult (considered to have maximal experience and agency), or a robot [considered to have agency but not experience; @gray.etal2007].
 Likewise, Weisman et al.’s studies characterized infants and young children—along with, e.g., chimpanzees, elephants, and dolphins—as entities that are perceived to be fully capable of physiological sensations but more limited in their perceptual-cognitive capacities and social-emotional abilities; this is in contrast to human adults, who are perceived to be fully capable across these domains [@weisman.etal2017a].
@@
 Caregiving relationships are at the core of human existence; for many people, infants and young children are among the most frequent and highly valued minds that we encounter.
-Caring for a young child involves making countless decisions under uncertainty: Why is my child crying, smiling, shouting, or biting?
-Can they understand what I am saying?
-Does my child love me?
-As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.
-
-In the current studies we set out to investigate this important and understudied aspect of mind perception: how ordinary people reason about the development of human mental life.
+In the current studies we set out to shed new light on this important and understudied aspect of mind perception: how laypeople reason about the development of human mental life.
 In three studies, we assessed US adults’ folk beliefs about children’s developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of "mental life," broadly construed.
@@
 
-# Results
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
+All studies were approved by [IRB information removed to preserve anonymity].
+For extended descriptions of methods and results, see Supplemental Material.
 
-## Study 1
+# Study 1
 
@@
 Drawing inspiration from previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018] as well as standard assessments of infant temperament and behavior [@putnam.etal2006; @rothbart1978], we included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction.
-We asked participants ($n$ = `r s1_results$demo %>% distinct() %>% nrow()`) to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life: What do people perceive to be the fundamental components of mental life, as they pertain to a developing human child?
+We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life: What do people perceive to be the fundamental components of mental life, as they pertain to a developing human child?
 
 We designed Study 1 to explore the correlational structure of participants’ responses, as a window into the underlying conceptual structure that might support their reasoning about the development of mental life.
-Our primary analysis for this preregistered study was an exploratory factor analysis (EFA) of participants’ capacity ratings.
+Our primary analysis was a preregistered exploratory factor analysis (EFA) of participants’ capacity ratings.
 This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children.
@@
 
-A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.
-See Figure \@ref(fig:fig01) for all factor loadings after oblique transformation.
-
-The first factor corresponded primarily to capacities related to thinking, reasoning, agency, and executive function—a suite of capacities that we will refer to as _cognition and control_.
-It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," and "understanding what somebody else is thinking," and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.
-
-The second factor corresponded primarily to social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we will refer to as _social connection_.
-It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", and "getting pleasure from music", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants’ capacity attributions.
-
-The third factor corresponded primarily to physiological sensations related to biological needs—a suite of capacities that we will refer to as _bodily sensations_.
-It was the dominant factor for such items as "getting hungry", "feeling pain", "feeling tired", "feeling thirsty", "feeling too hot or too cold", "feeling physically uncomfortable", "hearing sounds", and "being comforted by physical touch", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR2"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR2"]*100, 0)`% of the total variance in participants’ capacity attributions.
-
-Finally, the fourth factor corresponded to negatively-valenced sensations and emotions—a suite of capacities that we will refer to as _negative affect_.
-It was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected"; the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors).
-This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.
-
-```{r s1 strong laodings}
-s1_strong_loadings <- s1_results$efa$loadings[] %>% 
-  data.frame() %>% 
-  rownames_to_column("capacity") %>% 
-  gather(factor, loading, -capacity) %>% 
-  filter(abs(loading) >= 0.6) %>% 
-  count(factor)
-```
-
-How robust are these findings?
-The factors we have called _bodily sensations_, _social connection_, and _cognition and control_ each had strong factor loadings ($\geq$ 0.60) for many individual items ($n$ = `r min(s1_strong_loadings$n)`-`r max(s1_strong_loadings$n)`) and each accounted for a substantial amount of the total variance in participants’ capacity attributions (`r round_x(min(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`-`r round_x(max(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`%), indicating three robustly distinct and interpretable factors.
-In contrast, the fourth factor—_negative affect_—had more moderate loadings even for its strongest-loading items (all loadings < `r abs(s1_results$efa$loadings[][,"MR4"]) %>% max() %>% round(., 2) + 0.01`) and accounted for only `r round_x(s1_results$efa$Vaccounted["Proportion Var","MR4"]*100, 0)`% of the total variance.
-Nonetheless, we consider the general domain of _negative affect_ to be of particular theoretical and clinical interest.
-
-What does it mean that these four factors emerged?
-At a most basic level, our results reflect sets of intercorrelated capacities: When a participant judged that a child of a certain age was highly capable of planning, they also tended to judge that that child was capable of having self control, thinking before they act, and the other capacities with strong factor loadings on the _cognition and control_ factor; and likewise for the suites of capacities that define the other factors revealed by EFA.
-Therefore, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children.
-Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants’ perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development.
-In Studies 2 and 3, we explore these possibilities in greater depth.
-
-```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of participants’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
-knitr::include_graphics("../outputs/fig01.pdf")
-```
-
-## Study 2
-
-In Study 2 ($n$ = `r s2_results$demo %>% distinct() %>% nrow()`), we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development: What kinds of abilities do people believe are present at birth, and to what degree?
-To what extent are capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ perceived to change over childhood, and what is the shape of this perceived developmental trajectory?
-
-The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years (see Methods).
-This design allowed us to chart perceived developmental trajectories with a high degree of precision without undue burden to participants.
-
-A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors (see Supplemental Materials).
-Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1.
-Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
-After all, given that Study 2 featured only 20 of the 60 capacities featured in Study 1, it certainly could have been the case that this analysis would suggest retaining fewer factors (as often occurs with fewer variables).
-Conversely, given that Study 2 featured 13 within-subjects observations for each capacity compared to the 3 in Study 1, this analysis could have surfaced more than four factors (as often occurs with more observations).
-Finally, if we had misinterpreted the fundamental semantic content that distinguished the factors in Study 1 and selected inappropriate capacities to represent these factors, the Study 2 analysis could have identified more capacities with cross-loadings.
-Instead, the results of this analysis offer some validation of the four factors we have called _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
-
-```{r s2 capacity ratings summary stats, include = F}
-s2_cap_rat_newborns_ss <- s2_results$cap_rat_ss %>%
-  filter(target_year == 0)
-```
-
-```{r s2 gam results, include = F}
-s2_gam_ptab <- summary(s2_results$gam$gam)$p.table
-s2_gam_stab <- summary(s2_results$gam$gam)$s.table
-```
-
-Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
-On one extreme, participants attributed some, but relatively little, capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported relatively small increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-At the other extreme, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`).
-
-Visual inspection of Figure \@ref(fig:fig02), Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
-In the domain of _bodily sensations_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
-Participants perceived development in the domains of _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
-In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.
-
-We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
-For example, if participants believe that development in the domain of _bodily sensations_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed (see @berent.etal2019 for empirical evidence in line with this speculation).
-In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
-We explore this possibility in Study 3.
-
-```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
-Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
-In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
-In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity."}
-knitr::include_graphics("../outputs/fig02.pdf")
-```
-
-## Study 3
-
-Study 3 was designed with two goals in mind: First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2.
-Second, we aimed to probe the intuitive theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
-
-### Perceived developmental trajectories
-
-In Study 2, participants focused on one target age at a time, assessing a variety of capacities for that age before proceeding to the next target age (from youngest to oldest).
-This design was intended to encourage participants to focus primarily on providing a holistic assessment of mental life at a given target age; the trajectories connecting target ages were likely not the participants’ primary concern in the moment of responding.
-In Study 3, we flipped the design to focus participants’ attention on development more explicitly: Participants were asked to provide judgments of a single capacity for the full range of target ages (arranged from youngest to oldest) on the same "trial," before proceeding to the next capacity.
-In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years.
-In order to accommodate the addition of questions probing intuitive theories of development (see next section), participants assessed only 2 capacities per domain; see Methods.
-
-```{r s3 capacity ratings summary stats, include = F}
-s3_cap_rat_newborns_ss <- s3_results$cap_rat_ss %>%
-  filter(target_year == 0)
-```
-
-```{r s3 gam results, include = F}
-s3_gam_ptab <- summary(s3_results$gam$gam)$p.table
-s3_gam_stab <- summary(s3_results$gam$gam)$s.table
-```
-
-This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B.
-As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Again, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain of _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
-Finally, as in Study 2, in the domain of _bodily sensations_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensations") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensations_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensations", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensations", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensations", "edf"], 2)`).
-
-Visual inspection of Figure \@ref(fig:fig02), Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
-
-### Intuitive theories of development
-
-Why do people believe certain aspects of mental life, but not others, to be present at birth?
-What do people perceive to be driving the development of capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_?
-As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
-We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-(See @wang.feigenson2019; @berent.etal2019; @berent.etal2020 for in-depth investigations of ordinary people’s intuitions about the innateness of cognitive abilities, motor abilities, and emotion.)
-
-We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced, even internally inconsistent theories of development, by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.
-
-A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials).
-First, there were what we will call _intrinsic mechanisms_, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
-Participants clearly distinguished these intrinsic mechanisms from what we will call _extrinsic mechanisms_, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
-One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03)).
-
-```{r s3 mechanism ratings summary stats, include = F}
-s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means overall
-s3_mech_rat_ss_b <- s3_results$mech_rat_ss_b # means by domain
-s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # differences by domain
-```
-
-```{r s3 lmer results, include = F}
-s3_lmer_tab <- model_parameters(s3_results$lmer, standardize = "refit")
-s3_lmer_bod_tab <- model_parameters(s3_results$lmer_bod, standardize = "refit")
-s3_lmer_neg_tab <- model_parameters(s3_results$lmer_neg, standardize = "refit")
-s3_lmer_soc_tab <- model_parameters(s3_results$lmer_soc, standardize = "refit")
-s3_lmer_cog_tab <- model_parameters(s3_results$lmer_cog, standardize = "refit")
-```
-
-A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).
-
-For capacities in the domain of _bodily sensations_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensations") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
-In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`).
-In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
-See Figure \@ref(fig:fig03), panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.
-
-```{r s3 mechanism choice summary stats, include = F}
-# s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions overall
-s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b %>% # proportions by domain
-  filter(!is.na(dev_factor_cluster)) %>%
-  group_by(factor) %>%
-  mutate(prop2 = n/sum(n)) %>%
-  ungroup()
-```
-
-```{r s3 glmer results, include = F}
-s3_glmer_tab <- model_parameters(s3_results$glmer, standardize = "refit")
-s3_glmer_bod_tab <- model_parameters(s3_results$glmer_bod) # no standardization
-s3_glmer_neg_tab <- model_parameters(s3_results$glmer_neg) # no standardization
-s3_glmer_soc_tab <- model_parameters(s3_results$glmer_soc) # no standardization
-s3_glmer_cog_tab <- model_parameters(s3_results$glmer_cog) # no standardization
-```
-
-Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure \@ref(fig:fig03), Panel C.
-Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensations_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensations", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
-On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
-Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).
-
-Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
-Capacities for _bodily sensations_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
-Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world.
-Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).
-
-```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
-intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
-intrinsic mechanisms as the 'most important' driver of development.
-Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains."}
-knitr::include_graphics("../outputs/fig03.pdf")
-```
-
-# Discussion
-
-In a series of three large-scale studies, we identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); measured perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
-
-We found that participants considered _bodily sensations_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019; @berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
-
-Beliefs about the development of the more social-emotional aspects of mental life—*negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensations_ and _cognition and control_.
-In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree, but not fully, from birth; and to develop rapidly in the first two years of life before tapering off.
-Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensations_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
-We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure \@ref(fig:fig02).
-This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
-
-In some respects, the results of these studies resonate well with previous work on mind perception among US adults.
-The factors that we refer to as _bodily sensations_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a], and between "affect" and "regulation" [@malle2019].
-These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life.
-(See also @weisman.etal2021 for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)
-
-However, these studies also highlight one way in which reasoning about the development of human mental life may diverge from reasoning about mental life in general: In their assessments of the mental lives of infants and children at different ages, participants differentiated between what we call _social connection_ (e.g., capacities for excitement, humor, and love) and what we call _negative affect_ (e.g., capacities for distress, helplessness, and frustration).
-These two factors have no obvious precedents in previous studies of mind perception.
-In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials);  the narrower focus on humans as the targets of mind perception; or the emphasis on how mental capacities develop over time.
-Based on the findings of Studies 2 and 3, we propose that _social connection_ and _negative affect_ emerged as distinct factors because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
-
-What do these studies reveal about US adults' understanding of the contributions of nature vs.
-nurture to the development of human mental life?
-One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree.
-In addition to _bodily sensations_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
-Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely cognitive ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)).
-Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
-
-Adults’ intuitive theories are likely to have important consequences for the children in their care [@haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010].
-We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life.
-During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel.
-These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable.
-There is evidence of this across domains of development.
-For example, parent language use becomes more diverse and complex as children age and in concert with developing sophistication of the child’s own language competence [@rowe.etal2005; @huttenlocher.etal2010], and parents interact differently depending on whether a child is crawling versus walking [@karasik.etal2014] or holding versus looking at an object [@west.iverson2017].
-Likewise, representations of children’s mental lives, including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills have been shown to play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].
-Caregivers’ capacity to form an accurate representation of their child’s internal states and to use this representation to guide their caregiving behavior (so called “mind-mindedness”) is positively associated with children’s wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
-
-Critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most appropriate in a given cultural setting, most in line with caregivers’ own values and goals, or most beneficial for children  according to experts.
-For example, in a recent study drawing on similar foundations to the studies reported here, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021; see also @laranjo.etal2008]; could educating parents about infants' mental capacities and their rapid development spark increased curiosity in new parents, and would this have downstream consequences in their interactions with their children?
-An additional, related goal is to identify the gaps and misconceptions in these theories that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, experience concern about their child’s developmental progress, or even engage in neglectful or abusive behaviors toward the child.
-Identifying the antecedents of individual differences in these beliefs could be an especially important step for such clinically-focused applications.
-As is the case in many domains [@weisman.markman2017], interventions that leverage the power of intuitive theories to encourage positive and responsive caregiving behaviors hold great promise for creating meaningful and lasting behavioral changes in caregiver behavior, with important consequences for child wellbeing.
-
-# Methods
-
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/).
-All studies were approved by the Stanford University Internal Review Board.
-For extended descriptions of methods and results, see Supplemental Material.
-
-## Study 1
+## Methods
 
@@
 
-## Study 2
+## Results
+
+Following recent work on mind perception [@weisman.etal2021], our goal in this analysis was to derive a set of latent constructs that together give rise to people’s intuitions about the development of human mental life between 0-5 years.
+We did not set out to sort each of the 60 capacities into discrete, non-overlapping categories of capacities.
+Instead, we understood each of these specific capacities to reflect a different combination of the same underlying components (much as specific colors of paint can be understood as different combinations of cyan, magenta, and yellow).
+This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors.
+
+A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants’ and young children’s mental lives.
+See Figure \@ref(fig:fig01) for all factor loadings after oblique transformation.
+
+The first factor corresponded primarily to capacities related to thinking, reasoning, agency, and executive function—a suite of capacities that we interpreted as reflecting a higher-order capacity for _cognition and control_.
+It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," "understanding what somebody else is thinking," "focusing on a goal," "feeling guilty," "feeling embarrassed," "feeling pride," "making choices," "calming themselves down," "detecting danger," and "feeling hopeless." This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.
+
+The second factor corresponded primarily to social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_.
+It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others), and because we interpret this factor as indexing participants’ sense of the infant awakening into the human social world.
+This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants’ capacity attributions.
+
+The third factor corresponded primarily to physiological sensations related to biological needs—a suite of capacities that we interpreted as reflecting a higher-order capacity for _bodily sensation_.
+It was the dominant factor for such items as "getting hungry", "feeling pain", "feeling tired", "feeling thirsty", "feeling too hot or too cold", "feeling physically uncomfortable", "hearing sounds", and "being comforted by physical touch", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR2"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR2"]*100, 0)`% of the total variance in participants’ capacity attributions.
+
+Finally, the fourth factor corresponded to negatively-valenced sensations and emotions—a suite of capacities that we interpreted as reflecting a higher-order capacity for _negative affect_.
+It was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected"; the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors).
+This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.
+
+```{r s1 strong laodings}
+s1_strong_loadings <- s1_results$efa$loadings[] %>% 
+  data.frame() %>% 
+  rownames_to_column("capacity") %>% 
+  gather(factor, loading, -capacity) %>% 
+  filter(abs(loading) >= 0.6) %>% 
+  count(factor)
+```
+
+How robust are these findings?
+The factors we have called _bodily sensation_, _social connection_, and _cognition and control_ each had strong factor loadings ($\geq$ 0.60) for many individual items ($n$ = `r min(s1_strong_loadings$n)`-`r max(s1_strong_loadings$n)`) and each accounted for a substantial amount of the total variance in participants’ capacity attributions (`r round_x(min(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`-`r round_x(max(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`%), indicating three robustly distinct and interpretable factors.
+In contrast, the fourth factor—_negative affect_—had more moderate loadings even for its strongest-loading items (all loadings < `r abs(s1_results$efa$loadings[][,"MR4"]) %>% max() %>% round(., 2) + 0.01`) and accounted for only `r round_x(s1_results$efa$Vaccounted["Proportion Var","MR4"]*100, 0)`% of the total variance.
+Nonetheless, because we considered the general domain of _negative affect_ to be of particular theoretical and clinical interest, we opted to retain this factor in subsequent studies.
+
+It is worth noting that a handful of items loaded relatively strongly on two factors (loadings $\geq$ 0.40), suggesting that these factors are not entirely distinct.
+In our view, these cross-loadings were generally sensible.
+The item "feeling distressed", for instance, loaded roughly equally strongly on both bodily sensations and negative affect—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
+Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
+
+What does it mean that these four factors emerged?
+At a most basic level, our results reflect sets of intercorrelated capacities: When a participant judged that a child of a certain age was highly capable of planning, they also tended to judge that that child was capable of having self control, thinking before they act, and the other capacities with strong factor loadings on the _cognition and control_ factor; and likewise for the suites of capacities that define the other factors revealed by EFA.
+As described earlier, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children.
+Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants’ perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development.
+In Studies 2 and 3, we explore these possibilities in greater depth.
+(See also Supplemental Materials for the perceived developmental trajectories surfaced by Study 1.)
+
+```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of participants’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
+knitr::include_graphics("../outputs/fig01.pdf")
+```
+
+# Study 2
+
+In Study 2, we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development: What kinds of abilities do people believe are present at birth, and to what degree?
+To what extent are capacities for _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ perceived to change over childhood, and what is the shape of these perceived developmental trajectories?
+
+The design of Study 2 was nearly identical to Study 1, except that instead of assessing 60 capacities for 3 target ages, each participant assessed 20 capacities for 13 target ages: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years (see Methods).
+This design allowed us to chart perceived developmental trajectories with a high degree of precision without undue burden to participants.
+
+## Methods
 
@@
 For each factor, we aimed to select items that loaded strongly on that factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning, and captured our qualitative understanding of the latent construct that each factor corresponded to.
-To represent _bodily sensations_, we chose the items "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
+To represent _bodily sensation_, we chose the items "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
 To represent _negative affect_, we chose the items "feeling distressed", "feeling lonely", "feeling frustrated", "feeling helpless", and "feeling overwhelmed".
@@
 
-## Study 3
+## Results
+
+A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors (see Supplemental Materials).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1.
+Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
+After all, given that Study 2 featured only 20 of the 60 capacities featured in Study 1, it certainly could have been the case that this analysis would suggest retaining fewer factors (as often occurs with fewer variables).
+Conversely, given that Study 2 featured 13 within-subjects observations for each capacity compared to the 3 in Study 1, this analysis could have surfaced more than four factors (as often occurs with more observations).
+Finally, if we had misinterpreted the fundamental semantic content that distinguished the factors in Study 1 and selected inappropriate capacities to represent these factors, the Study 2 analysis could have identified more capacities with cross-loadings.
+Instead, the results of this analysis offer some validation of the four factors we have called _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_.
+
+```{r s2 capacity ratings summary stats, include = F}
+s2_cap_rat_newborns_ss <- s2_results$cap_rat_ss %>%
+  filter(target_year == 0)
+```
+
+```{r s2 gam results, include = F}
+s2_gam_ptab <- summary(s2_results$gam$gam)$p.table
+s2_gam_stab <- summary(s2_results$gam$gam)$s.table
+```
+
+Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
+On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported smaller increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
+At the other extreme, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+
+Visual inspection of Figure \@ref(fig:fig02), Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
+In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
+Participants perceived development in the domains of _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
+In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.
+
+We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
+For example, if participants believe that development in the domain of _bodily sensation_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed.
+[See @berent.etal2019 for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
+We explore these possibilities in Study 3.
+
+```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
+Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
+In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity."}
+knitr::include_graphics("../outputs/fig02.pdf")
+```
+
+# Study 3
+
+Study 3 was designed with two goals in mind.
+First, we aimed to provide a more direct assessment of the differences in perceived developmental trajectories surfaced by Study 2.
+In Study 2, participants focused on one target age at a time, assessing a variety of capacities for that age before proceeding to the next target age (from youngest to oldest).
+This design was intended to encourage participants to focus primarily on providing a holistic assessment of mental life at a given target age; the trajectories connecting target ages were likely not the participants’ primary concern in the moment of responding.
+In Study 3, we flipped the design to focus participants’ attention on development more explicitly: Participants were asked to provide judgments of a single capacity for the full range of target ages (arranged from youngest to oldest) on the same "trial," before proceeding to the next capacity.
+In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years.
+
+Second, we aimed to probe the intuitive theories that might underlie the differentiation of the four factors surfaced by Studies 1-2 and the perceived developmental trajectories surfaced by Study 2 (and the current study).
+
+## Methods
 
@@
 Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to 8 in the current study to maintain an appropriate level of participant burden.
-We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensations_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
+We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
 Capacities were presented in a random order for each participant.
@@
 
+## Results
+
+### Perceived developmental trajectories
+
+```{r s3 capacity ratings summary stats, include = F}
+s3_cap_rat_newborns_ss <- s3_results$cap_rat_ss %>%
+  filter(target_year == 0)
+```
+
+```{r s3 gam results, include = F}
+s3_gam_ptab <- summary(s3_results$gam$gam)$p.table
+s3_gam_stab <- summary(s3_results$gam$gam)$s.table
+```
+
+This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B.
+As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
+Again, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain of _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
+Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+
+Visual inspection of Figure \@ref(fig:fig02), Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
+
+### Intuitive theories of development
+
+Why do people believe certain aspects of mental life, but not others, to be present at birth?
+What do people perceive to be driving the development of capacities for _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_?
+As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
+We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
+(For in-depth investigations of laypeople’s intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.)
+
+We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.
+
+A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials), which aligned nearly exactly with our _a priori_ ordering of these mechanisms from most "innate" or "biological" to most "learned" or "social" (see Study 3 preregistration).
+First, there were what we will call _intrinsic mechanisms_: mechanisms rooted in innate predispositions or biological maturational processes, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
+Participants clearly distinguished these intrinsic mechanisms from what we will call _extrinsic mechanisms_: mechanisms rooted in observations of and experiences in the world, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
+One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
+This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03)).
+
+```{r s3 mechanism ratings summary stats, include = F}
+s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means overall
+s3_mech_rat_ss_b <- s3_results$mech_rat_ss_b # means by domain
+s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # differences by domain
+```
+
+```{r s3 lmer results, include = F}
+s3_lmer_tab <- model_parameters(s3_results$lmer, standardize = "refit")
+s3_lmer_bod_tab <- model_parameters(s3_results$lmer_bod, standardize = "refit")
+s3_lmer_neg_tab <- model_parameters(s3_results$lmer_neg, standardize = "refit")
+s3_lmer_soc_tab <- model_parameters(s3_results$lmer_soc, standardize = "refit")
+s3_lmer_cog_tab <- model_parameters(s3_results$lmer_cog, standardize = "refit")
+```
+
+A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).
+
+For capacities in the domain of _bodily sensation_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
+In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`).
+In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
+See Figure \@ref(fig:fig03), panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.
+
+```{r s3 mechanism choice summary stats, include = F}
+# s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions overall
+s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b %>% # proportions by domain
+  filter(!is.na(dev_factor_cluster)) %>%
+  group_by(factor) %>%
+  mutate(prop2 = n/sum(n)) %>%
+  ungroup()
+```
+
+```{r s3 glmer results, include = F}
+s3_glmer_tab <- model_parameters(s3_results$glmer, standardize = "refit")
+s3_glmer_bod_tab <- model_parameters(s3_results$glmer_bod) # no standardization
+s3_glmer_neg_tab <- model_parameters(s3_results$glmer_neg) # no standardization
+s3_glmer_soc_tab <- model_parameters(s3_results$glmer_soc) # no standardization
+s3_glmer_cog_tab <- model_parameters(s3_results$glmer_cog) # no standardization
+```
+
+Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure \@ref(fig:fig03), Panel C.
+Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensation_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensation", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
+On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
+Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).
+
+Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
+Capacities for _bodily sensation_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
+Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world.
+Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).
+
+```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
+Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
+intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
+intrinsic mechanisms as the 'most important' driver of development.
+Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains."}
+knitr::include_graphics("../outputs/fig03.pdf")
+```
+
+# Discussion
+
+In a series of three large-scale studies, we identified four core capacities that anchor US adults’ conceptual representations of the development of human mental life over infancy and early childhood (Study 1); measured US adults’ perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four domains (Study 3).
+
+We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019; @berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+
+Beliefs about the development of the more social-emotional aspects of mental life—*negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
+In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree, but not fully, from birth; and to develop rapidly in the first two years of life before tapering off.
+Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
+We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure \@ref(fig:fig02).
+This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
+
+In some respects, the results of these studies resonate well with previous work on mind perception among US adults.
+The factors that we refer to as _bodily sensation_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a], and between "affect" and "regulation" [@malle2019].
+These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life.
+(See also @weisman.etal2021 for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)
+
+However, these studies also highlight one way in which reasoning about the development of human mental life may diverge from reasoning about mental life in general: In their assessments of the mental lives of infants and children at different ages, participants differentiated between what we call _social connection_ (e.g., capacities for excitement, humor, and love) and what we call _negative affect_ (e.g., capacities for distress, helplessness, and frustration).
+These two factors have no obvious precedents in previous studies of mind perception.
+In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials);  the narrower focus on humans as the targets of mind perception; or the emphasis on how mental capacities develop over time.
+Based on the findings of Studies 2 and 3, we propose that _social connection_ and _negative affect_ emerged as distinct factors because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
+
+What do these studies reveal about US adults' understanding of the contributions of nature vs.
+nurture to the development of human mental life?
+One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree.
+In addition to _bodily sensation_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
+Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)).
+Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
+Further work on this topic would do well to integrate the cognitive processing mechanisms featured in the current studies with epistemic states that have been the focus of past research on laypeople’s beliefs about the innateness of "cognitive" abilities [@berent.etal2019; @wang.feigenson2019] to paint a more comprehensive picture of the ways in which intuitive theories of development do and do not align with scientific theories such as nativism, empiricism, and constructivism.
+
+How might the four-way distinction proposed here inform caregiver-child interactions?
+Drawing on theoretical proposals from recent work in mind perception [@weisman.etal2017a], we would argue that what gives meaning to the four factors documented in the current studies is the possibility that they correspond to substantially different causal explanatory frameworks for interpreting, predicting, and responding to the behaviors of a young child—i.e., distinct lenses through which a caregiver might view and understand a child in a given moment.
+Consider a caregiver attempting to navigate the difficult situation of a toddler throwing a "temper tantrum." Through the lens of _bodily sensation_, the caregiver might understand the child as driven by basic biological needs, which could draw the caregiver’s attention to the possibility that the child is hungry, fatigued, injured, or ill, and focus the caregiver’s behaviors on the child’s physical wellbeing.
+Through the lens of _negative affect_, the caregiver might instead understand the child as a moral patient who deserves to be spared unpleasant and harmful experiences, drawing attention to the possibility that the child is upset or afraid and motivating the caregiver to provide comfort.
+Through the lens of _social connection_, the caregiver might understand the child as a social partner, interpreting the child’s distress as an indication that the relationship needs repair and seeking to remedy the disruption.
+And through the lens of _cognition and control_, the caregiver might understand the child as an intentional agent who has been thwarted in the pursuit of certain goals; the caregiver might offer the child assistance toward the goal, or age-appropriate techniques to regulate the child’s negative emotions.
+Of course, by the time a human reaches adulthood, all of these explanatory frameworks are reasonable modes of interpreting an individual’s behavior, because human adults are biological animals, moral patients, social partners, and intentional agents.
+But in the moment of dealing with a distressed child—especially when caring for that child requires making guesses about what kind of care is even required—these four modes of understanding might have important consequences for caregivers’ responses and, in turn, for children’s outcomes.
+
+In other words, adults’ intuitive theories are likely to have important consequences for the children in their care [see also @haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010].
+We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life.
+During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel.
+These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable.
+There is ample evidence that representations of children’s mental lives—including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills—play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].
+At a high level, caregivers’ "mind-mindedness"—that is, their capacity to form an accurate representation of their child’s internal states and to use this representation to guide their caregiving behavior—is positively associated with children’s wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
+The current studies reframe these and similar findings on mind-mindedness as reflecting not only an attentional focus on the part of the caregiver but also the intuitive theories that shape caregivers’ interpretations of and responses to children’s behaviors.
+Our results further highlight the possibility that differentiating between different aspects of "mind" and developmental shifts in mind perception could push this highly influential research program in important new directions.
+For example, perceptions of a child’s capacities in different aspects of mental life might influence caregivers’ tendencies to demonstrate mind-mindedness in some contexts more than others (e.g., when the child is experiencing physical discomfort vs.
+emotional distress, when the child is working on a task vs.
+attempting to strengthen a social bond), or at one developmental stage more than another (e.g., compared to childhood, mind-mindedness may be more apparent with respect to bodily sensation than cognitive and control in infancy).
+
+We conclude by highlighting three related, but meaningfully distinct, approaches to studying the connections between adults’ intuitive theories, parenting behaviors, and children’s wellbeing.
+We introduce these approaches as open questions ripe for future research—and critical next steps for translating this basic research into useful interventions to promote positive caregiver-child relationships and child wellbeing.
+
+First, are the beliefs and intuitive theories documented here accurate with respect to the current scientific understanding of human development?
+Comparing participants’ intuitions to empirical findings from scientific studies of child development has illuminated the ways in which lay people’s reasoning about cognitive development [@berent.etal2019; @wang.feigenson2019] and about emotions [@berent.etal2020] has proved a useful way of illuminating biases and misconceptions in laypeople’s beliefs about innateness.
+Finding creative ways to determine the ground truth of the development of the range of capacities included in the current studies—many of which are phenomenal experiences—will be a particular challenge to this endeavor, but would be both deeply fascinating and of practical interest to predicting downstream consequences for children.
+All else being equal, we would predict that caregivers with more accurate representations of children’s developing minds would make more accurate inferences about their own children and interact with their children in ways that are more developmentally appropriate and better-suited to scaffolding further healthy development [see, e.g., @list.etal2021].
+
+However, accuracy is not the only criterion by which to assess intuitive theories in this domain.
+A second question that could drive extensions of the current work is: How do these beliefs and intuitive theories impact caregivers’ _affective experience_ of caregiving?
+For example, in a recent study drawing on a similar theoretical foundation to the current studies, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021; see also @laranjo.etal2008].
+It is unclear at this point whether this proposed causal pathway—from beliefs through interest and curiosity to behaviors—hinges on caregivers holding scientifically accurate theories of development and forming accurate representations of their own children’s mental lives, or whether even beliefs that do not align with modern scientific understandings of development (e.g., the belief that newborns love and care for their siblings, the belief that toddlers might remember previous lives) could still play a positive motivational role in sustaining caregivers’ interest in their children’s minds and encouraging positive parenting behaviors.
+In either case, based on these findings we would predict that educating parents about infants’ mental capacities and their rapid development might spark increased curiosity in new parents, with positive downstream consequences in their interactions with their children.
+
+Finally, what set of folk beliefs and intuitive theories are most _adaptive_, i.e., most effective at facilitating the kinds of caregiving behaviors that are associated with positive outcomes for children?
+This question is of course deeply related to the issues of accuracy and affective experience just described; for example, under-attributions of any aspect of mental life on the part caregivers likely have negative consequences for the children in their care, while some biases and misconceptions may actually have positive downstream consequences for children.
+Aside from sparking caregivers’ interest in their children, certain over-attributions of mental life might foster among caregivers the very behaviors that create and nurture these nascent capacities.
+For example, crediting an infant with more of a capacity for _social connection_ than may be warranted by empirical research could lead a caregiver to engage in the warm, reciprocal interactions that jumpstart the development of early social skills; or (falsely) assuming that a toddler is capable of feeling and understanding complex emotions like guilt and embarrassment might lead the caregiver to use the kind of language that scaffolds the development of such sophisticated social-emotional representations.
+Conversely, over-attributions of the capacity for _cognition and control_ might result in caregivers attributing overt intentions to annoy or upset their caregiver and could lead caregivers to be overly punitive in their response to what they perceive as deliberate "acting out." We offer these speculative examples to illustrate the many possibilities that adopting the lens of adaptivity could open for researchers and interventionists interested in the effects of caregivers’ intuitive theories on their children’s well-being—but, of course, such interventions would require extensive research focused on caregivers rather than general-population adults, carefully situated within a particular setting so as to promote caregiving behaviors that are beneficial for the children in question.
+
+Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers’ own values and goals.
+Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, become overly concerned about their child’s developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].
+As is the case in many domains [@weisman.markman2017], interventions that leverage the power of intuitive theories to encourage positive and responsive caregiving behaviors hold great promise for creating meaningful and lasting behavioral changes in caregiver behavior, with important consequences for child wellbeing.
+
 \newpage

### 2021-10-16 supplement/supplement-main.Rmd
revisions for submission

@@
 subtitle: "Supplemental Materials"
-author:
-  - Kara Weisman^[Department of Psychology, University of California, Riverside; kgweisman@gmail.com]
-  - Lucy S. King^[Department of Psychiatry and Behavioral Sciences, Tulane University School of Medicine; Department of Psychology, The University of Texas at Austin]
-  - Kathryn L. Humphreys^[Department of Psychology, Vanderbilt University]
-date: "August 9, 2021"
+author: "[authors removed for anonymous review]"
+date: "October 16, 2021"
 output:
-  # word_document:
-  #   reference_docx: word-styles-ref.docx
   bookdown::pdf_document2:
@@
     number_sections: false
+  #   reference_docx: word-styles-ref.docx
+  # word_document:
 bibliography: "references.bib"
-cls: article.cls
+csl: apa.csl
+# cls: article.cls
 figsintext: yes
@@
 In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
 
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (Study 1: https://osf.io/e6ajh/; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce/).
-All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
-All studies were approved by the Stanford University Internal Review Board.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
+All studies were approved by [IRB information removed to preserve anonymity].
+All materials used in these studies are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52 (DOI: 10.17605/OSF.IO/XRZND).
+All studies were approved by [IRB information removed to preserve anonymity].
 
@@
 
-To represent _bodily sensations_, we chose the following items: "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
+To represent _bodily sensation_, we chose the following items: "getting hungry", "feeling pain", "feeling tired", "feeling physically uncomfortable", and "hearing sounds".
 In the oblimin-transformed `r s1_results$efa$factors`-factor solution from Study 1 all of these items had loadings $\geq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% pull("MR2") %>% min() %>% round_x(., 2)` on this factor, and absolute loadings $\leq$ `r s1_results$efa$loadings[] %>% data.frame() %>% rownames_to_column("capacity") %>% filter(capacity %in% c("getting_hungry", "feeling_pain", "feeling_tired", "feeling_physically_uncomfortable", "hearing_sounds")) %>% gather(factor, loading, -capacity) %>% filter(factor != "MR2") %>% pull(loading) %>% max((abs(.))) %>% round_x(., 2)` on the other three factors.
@@
 
-Based on the results of Study 1, we predicted that the correlational structure of participants' responses would reveal four underlying constructs corresponding to the four factors we identified in Study 1: _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_.
+Based on the results of Study 1, we predicted that the correlational structure of participants' responses would reveal four underlying constructs corresponding to the four factors we identified in Study 1: _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_.
 To test this hypothesis, we performed an EFA, following the methods established in Study 1.
@@
 We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 2.
-(1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
+(1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensation_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
 
@@
 For each domain, we selected items that loaded strongly on the relevant factor, did not cross-load strongly on other factors, were sufficiently distinguishable from each other in meaning (i.e., not overly redundant), and captured our qualitative understanding of the domain that each factor corresponded to.
-We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensations_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
+We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
 Capacities were presented in a random order for each participant.
@@
 
-We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3; these were identical to our hypotheses for Study 2 (which were upheld in that study): (1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
+We preregistered two hypotheses about the perceived developmental trajectories we anticipated to observe in Study 3; these were identical to our hypotheses for Study 2 (which were upheld in that study): (1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children; and (2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensation_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
 
@@
 
-Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*).
+Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*).
 We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
@@
 As reported in the main text, parallel analysis suggested retaining `r s1_parallel$nfact` factors.
-We call these factors _cognition and control_, _social connection_, _bodily sensations_, and _negative affect_.
+We call these factors _cognition and control_, _social connection_, _bodily sensation_, and _negative affect_.
 Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efaparload); see also Figure 1 (main text).
@@
 It is worth noting that a handful of items loaded relatively strongly on two factors (loadings $\geq$ 0.40), suggesting that these factors are not entirely distinct.
-The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensations_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (like pain) and an affective state (like frustration).
-Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a sensory ability and a critical part of many social interactions (eye contact).
+The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensation_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (like pain) and an affective state (like frustration).
+Likewise, "seeing" loaded equally strongly on both _bodily sensation_ and _social connection_—perhaps reflecting an understanding of vision as both a sensory ability and a critical part of many social interactions (eye contact).
 The relatively large degree of overlap between _cognition and control_ and _social connection_, in particular, might indicate that participants believed these two constructs to be more strongly connected than other aspects of life; in fact, these two factors were the most strongly correlated of all pairs of factors ($\phi$ = `r round_x(s1_results$efa$Phi["MR1", "MR3"], 2)`).
-(The next strongest correlation was between _bodily sensations_ and _social connection_: $\phi$  = `r round_x(s1_results$efa$Phi["MR2", "MR3"], 2)`.
+(The next strongest correlation was between _bodily sensation_ and _social connection_: $\phi$  = `r round_x(s1_results$efa$Phi["MR2", "MR3"], 2)`.
 All other inter-factor correlations: $\phi \le$ `r round_x((s1_results$efa$Phi[upper.tri(s1_results$efa$Phi) == T] %>% sort(decreasing = T))[3], 2)`.)
@@
          `Social connection` = MR3,
-         `Bodily sensations` = MR2,
+         `bodily sensation` = MR2,
          `Negative affect` = MR4) %>%
@@
             factor_names = c("Cognition and control",
-                             "Bodily sensations",
+                             "Bodily sensation",
                              "Social connection",
@@
 
-We consider the first of these factors ("`r names(data.frame(s1_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s1_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensations_, the third ("`r names(data.frame(s1_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth ("`r names(data.frame(s1_efa_bic$loadings[]))[4]`") to resonate with the construct we have called _negative affect_.
+We consider the first of these factors ("`r names(data.frame(s1_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s1_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensation_, the third ("`r names(data.frame(s1_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth ("`r names(data.frame(s1_efa_bic$loadings[]))[4]`") to resonate with the construct we have called _negative affect_.
 The fifth factor ("`r names(data.frame(s1_efa_bic$loadings[]))[5]`") appears to pick out capacities particularly relevant to social interaction (e.g., social learning, person recognition, humor, listening), and the sixth factor ("`r names(data.frame(s1_efa_bic$loadings[]))[6]`") appears to pick out negative emotions (e.g., anger, annoyance, boredom, social fear); however, there were no capacities that loaded strongly on either of these capacities.
@@
 
-We consider the first of these factors ("`r names(data.frame(s1_efa_wdm$loadings[]))[1]`") to resonate most strongly with the construct we have called _cognition and control_, and the second ("`r names(data.frame(s1_efa_wdm$loadings[]))[2]`") to resonate most strongly with the construct we have called _bodily sensations_.
+We consider the first of these factors ("`r names(data.frame(s1_efa_wdm$loadings[]))[1]`") to resonate most strongly with the construct we have called _cognition and control_, and the second ("`r names(data.frame(s1_efa_wdm$loadings[]))[2]`") to resonate most strongly with the construct we have called _bodily sensation_.
 These factors are also quite similar to the constructs of "agency" and "experience" in Gray et al.'s original studies of mind perception [@gray.etal2007].
@@
 Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life.
-To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensations_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age.
-As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensations_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.
+To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensation_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age.
+As we go on to confirm in Studies 2-3, this visualization suggests that participants perceived capacities for _bodily sensation_ to be substantial at birth and to develop relatively little over the first five years of life; in contrast, they perceived capacities for _negative affect_, _social connection_, and in particular _cognition and control_ to be much more limited at birth and to development dramatically over the first five years of life.
 
@@
   mutate(factor = recode_factor(factor,
-                                "MR2" = "Bodily sensations",
+                                "MR2" = "Bodily sensation",
                                 "MR4" = "Negative affect",
@@
 
-As reported in the main text, parallel analysis suggested retaining `r s2_parallel$nfact` factors, and these factors were very similar to those found in Study 1 (_bodily sensations_, _negative affect_, _social connection_, and _cognition and control_); each item loaded most strongly on the factor it was selected to represent.
+As reported in the main text, parallel analysis suggested retaining `r s2_parallel$nfact` factors, and these factors were very similar to those found in Study 1 (_bodily sensation_, _negative affect_, _social connection_, and _cognition and control_); each item loaded most strongly on the factor it was selected to represent.
 Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs2efaparload); see also Figure 1 (main text).
@@
   rename(`Negative affect` = MR1,
-         `Bodily sensations` = MR3,
+         `bodily sensation` = MR3,
          `Cognition and control` = MR2,
@@
                              "Cognition and control",
-                             "Bodily sensations",
+                             "Bodily sensation",
                              "Social connection"))
@@
 
-We consider the first of these factors ("`r names(data.frame(s2_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s2_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensations_, the third ("`r names(data.frame(s2_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth and fifth ("`r names(data.frame(s2_efa_bic$loadings[]))[4]`" and "`r names(data.frame(s2_efa_bic$loadings[]))[5]`") to resonate with the construct we have called _negative affect_.
+We consider the first of these factors ("`r names(data.frame(s2_efa_bic$loadings[]))[1]`") to resonate with the construct we have called _cognition and control_, the second ("`r names(data.frame(s2_efa_bic$loadings[]))[2]`") to resonate with the construct we have called _bodily sensation_, the third ("`r names(data.frame(s2_efa_bic$loadings[]))[3]`") to resonate with the construct we have called _social connection_, and the fourth and fifth ("`r names(data.frame(s2_efa_bic$loadings[]))[4]`" and "`r names(data.frame(s2_efa_bic$loadings[]))[5]`") to resonate with the construct we have called _negative affect_.
 The sixth factor ("`r names(data.frame(s2_efa_bic$loadings[]))[6]`") appears to pick out capacities particularly relevant to social interaction (e.g., social learning, love).
@@
 (1) We predicted that, on average, participants' perception of children's mental capacities would increase as a function of the target child's age, with participants generally attributing more and greater abilities to older children.
-(2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensations_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
+(2) We predicted that, in the domains of _cognition and control_ and _social connection_, participants would perceive relatively more dramatic developmental changes extending later into childhood (i.e., lower intercepts and steeper slopes), whereas in the domains of _bodily sensation_ and _negative affect_ participants would perceive relatively smaller changes across development (i.e., higher intercepts and shallower slopes).
 
@@
   mutate(factor = recode_factor(factor,
-                                "MR3" = "Bodily sensations",
+                                "MR3" = "Bodily sensation",
                                 "MR1" = "Negative affect",
@@
     Parameter == "(Intercept)" ~ "Cognition and control (intercept)",
-    grepl("bod", Parameter) ~ "Bodily sensations vs. Cognition and control",
+    grepl("bod", Parameter) ~ "Bodily sensation vs. Cognition and control",
     grepl("neg", Parameter) ~ "Negative affect vs. Cognition and control",
@@
   mutate(Parameter = case_when(
-    grepl("Bod", Parameter) ~ "Target year: Bodily sensations",
+    grepl("Bod", Parameter) ~ "Target year: bodily sensation",
     grepl("Neg", Parameter) ~ "Target year: Negative affect",
@@
 d2_gam_r1_pred <- d2_gam %>%
-  mutate(pred_score = predict.gam(s2_gam$gam, type = "response", 
-                                  newdata = d2_gam)) %>%
+  # # ridiculous hacky stuff to avoid having to re-run the GAM to correct typo in "bodily sensationS"
+  # mutate(factor = as.character(factor),
+  #        factor = gsub("Bodily sensation$", "Bodily sensations", factor),
+  #        factor = factor(factor, levels = c("Bodily sensations",
+  #                                           "Negative affect",
+  #                                           "Social connection",
+  #                                           "Cognition and control"))) %>%
+  mutate(pred = predict.gam(s2_gam$gam, type = "response", 
+                            newdata = d2_gam)) %>% #%>%
+                              # mutate(factor = as.character(factor),
+                              #        factor = gsub("Bodily sensation$", 
+                              #                      "Bodily sensations", factor),
+                              #        factor = factor(factor, 
+                              #                        levels = c("Bodily sensations",
+                              #                                   "Negative affect",
+                              #                                   "Social connection",
+                              #                                   "Cognition and control"))))) %>%
+  # mutate(factor = as.character(factor),
+  #        factor = gsub("Bodily sensations", "Bodily sensation", factor),
+  #        factor = factor(factor, levels = c("Bodily sensation",
+  #                                           "Negative affect",
+  #                                           "Social connection",
+  #                                           "Cognition and control"))) %>%
   group_by(ResponseId, factor, target_year) %>%
   summarise(score = mean(response, na.rm = T),
-            pred_score = mean(score, na.rm = T)) %>%
+            pred_score = mean(pred, na.rm = T)) %>%
   ungroup()
@@
   mutate(factor = recode_factor(domain,
-                                "BOD" = "Bodily sensations",
+                                "BOD" = "Bodily sensation",
                                 "NEG" = "Negative affect",
@@
   mutate(Parameter = case_when(
-    grepl("Bod", Parameter) ~ "Target year: Bodily sensations",
+    grepl("Bod", Parameter) ~ "Target year: Bodily sensation",
     grepl("Neg", Parameter) ~ "Target year: Negative affect",
@@
 d3_gam_r1_pred <- d3_gam %>%
+  # ridiculous hacky stuff to avoid having to re-run the GAM to correct typo in "bodily sensationS"
+  # mutate(factor = as.character(factor),
+  #        factor = gsub("Bodily sensation$", "Bodily sensations", factor),
+  #        factor = factor(factor, levels = c("Bodily sensations",
+  #                                           "Negative affect",
+  #                                           "Social connection",
+  #                                           "Cognition and control"))) %>%
   mutate(pred = predict.gam(s3_gam$gam, type = "response", 
-                            newdata = d3_gam)) %>%
+                            newdata = d3_gam)) %>% # %>%
+  #                             mutate(factor = as.character(factor),
+  #                                    factor = gsub("Bodily sensation$", 
+  #                                                  "Bodily sensations", factor),
+  #                                    factor = factor(factor, 
+  #                                                    levels = c("Bodily sensations",
+  #                                                               "Negative affect",
+  #                                                               "Social connection",
+  #                                                               "Cognition and control"))))) %>%
+  # mutate(factor = as.character(factor),
+  #        factor = gsub("Bodily sensations", "Bodily sensation", factor),
+  #        factor = factor(factor, levels = c("Bodily sensation",
+  #                                           "Negative affect",
+  #                                           "Social connection",
+  #                                           "Cognition and control"))) %>%
   group_by(ResponseId, factor, target_year) %>%
   summarise(score = mean(response, na.rm = T),
-            pred_score = mean(score, na.rm = T)) %>%
+            pred_score = mean(pred, na.rm = T)) %>%
   ungroup()
@@
 We assessed a wide range of potential developmental mechanisms for children's capacities.
-We applied a variety of dimensionality reduction approaches in order to sort these developmental mechanisms into meaningful categories, and then modeled participants' ratings of the importance of these mechanism as a function of domain (_bodily sensations_, _negative affect_, _social connection_, and _cognition and control_).
+We applied a variety of dimensionality reduction approaches in order to sort these developmental mechanisms into meaningful categories, and then modeled participants' ratings of the importance of these mechanism as a function of domain (_bodily sensation_, _negative affect_, _social connection_, and _cognition and control_).
 
@@
 
-To assess which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*), we conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
+To assess which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
 intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
@@
 
-The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall) (all domains), \@ref(tab:tabs3lmerbod) (*bodily sensations*), \@ref(tab:tabs3lmerneg) (*negative affect*), \@ref(tab:tabs3lmersoc) (*social connection*), and \@ref(tab:tabs3lmercog) (*cognition and control*); see also Figure 3 (main text).
+The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall) (all domains), \@ref(tab:tabs3lmerbod) (*bodily sensation*), \@ref(tab:tabs3lmerneg) (*negative affect*), \@ref(tab:tabs3lmersoc) (*social connection*), and \@ref(tab:tabs3lmercog) (*cognition and control*); see also Figure 3 (main text).
 
@@
   mutate(factor = recode_factor(domain,
-                                "BOD" = "Bodily sensations",
+                                "BOD"= "Bodily sensation",
                                 "NEG" = "Negative affect",
@@
   mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
@@
 
-##### Bodily sensations
-
-For capacities in the domain of _bodily sensations_, this analysis suggested that participants rated intrinsic mechanisms as more important drivers of development than extrinsic mechanisms; see also Figure 3, panels A-B (main text).
+##### bodily sensation
+
+For capacities in the domain of _bodily sensation_, this analysis suggested that participants rated intrinsic mechanisms as more important drivers of development than extrinsic mechanisms; see also Figure 3, panels A-B (main text).
 
@@
                 data = d3_mech_ratings %>% 
-                  filter(factor == "Bodily sensations"))
+                  filter(factor == "Bodily sensation"))
 
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (bodily sensations): Fixed effects.",
+        caption = "Study 3, multilevel linear model results (bodily sensation): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
   geom_hline(yintercept = 3, lty = 2, color = "darkred") +
+  geom_point(alpha = 0.6, size = 0.02,
+             position = position_jitter(width = 0.2,
+                                        height = 0,
+                                        seed = 94305)) +
   geom_path(data = . %>%
@@
             alpha = 0.1, size = 0.02,
-            position = position_jitter(width = 0.2, 
-                                       height = 0, 
-                                       seed = 94305)) +
-  geom_point(alpha = 0.6, size = 0.02,
             position = position_jitter(width = 0.2,
@@
   geom_hline(yintercept = 3, lty = 2, color = "darkred") +
+  geom_point(alpha = 0.6, size = 0.02,
+             position = position_jitter(width = 0.2, 
+                                        height = 0, 
+                                        seed = 94305)) +
   geom_path(data = . %>%
@@
             alpha = 1, size = 0.02,
-            position = position_jitter(width = 0.2, 
-                                       height = 0, 
-                                       seed = 94305)) +
-  geom_point(alpha = 0.6, size = 0.02,
             position = position_jitter(width = 0.2, 
@@
 
-The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3glmerall) (all domains), \@ref(tab:tabs3glmerbod) (*bodily sensations*), \@ref(tab:tabs3glmerneg) (*negative affect*), \@ref(tab:tabs3glmersoc) (*social connection*), and \@ref(tab:tabs3glmercog) (*cognition and control*); see also Figure 3 (main text).
+The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3glmerall) (all domains), \@ref(tab:tabs3glmerbod) (*bodily sensation*), \@ref(tab:tabs3glmerneg) (*negative affect*), \@ref(tab:tabs3glmersoc) (*social connection*), and \@ref(tab:tabs3glmercog) (*cognition and control*); see also Figure 3 (main text).
 
@@
     TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensations (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
@@
 
-For capacities in the domain of _bodily sensations_, this analysis suggested that participants were much more likely to select intrinsic mechanisms than extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
-
-```{r s3 mech choice glmer bodily sensations}
+For capacities in the domain of _bodily sensation_, this analysis suggested that participants were much more likely to select intrinsic mechanisms than extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
+
+```{r s3 mech choice glmer bodily sensation}
 s3_glmer_bod <- glmer(extrinsic ~ 1 + 
@@
                       data = d3_mech_choice %>%
-                        filter(factor == "Bodily sensations") %>%
+                        filter(factor == "Bodily sensation") %>%
                         mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (bodily sensations): Fixed effects.",
+        caption = "Study 3, multilevel generalized linear model results (bodily sensation): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
          factor = factor(factor, 
-                         levels = c("Bodily sensations", "Negative affect",
+                         levels = c("Bodily sensation", "Negative affect",
                                     "Social connection", "Cognition and control", 
@@
   column_spec(2:6, width = "2cm") %>%
-  pack_rows(group_label = "Bodily sensations", start_row = 1, end_row = 11) %>%
+  pack_rows(group_label= "Bodily sensation", start_row = 1, end_row = 11) %>%
   pack_rows("Negative affect", 12, 16) %>%

### 2021-10-16 paper/paper.Rmd
more anonymizing

@@
 title: "Beliefs about the development of mental life"
-author: "[authors removed for anonymous review]"
+author: '[authors removed for anonymous review]'
 output:
-  bookdown::pdf_document2:
-    latex_engine: xelatex
-    fig_caption: yes
-    toc: false
-    number_sections: false
+  pdf_document:  default
+  # word_document:
   #   reference_docx: word-styles-ref.docx
-  # word_document:
-bibliography: "../supplement/references.bib"
-csl: "../supplement/apa.csl"
-# cls: "../supplement/article.cls"
+bibliography: ../supplement/references.bib
+csl: ../supplement/apa.csl
 figsintext: yes
@@
 
-Caregiving relationships with infants and children are among the most common, important, and complex human social interactions.
-Caring for a young child over time requires an adult to continually update their own mental representations of the child’s capacities as the child develops.
-In a series of large-scale studies, we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-Exploratory factor analysis identified four categories of mental capacities that anchored participants’ representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
-Participants perceived that these four aspects of mental life were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological "preprogramming," physical maturation, passive observation, and social learning).
-Adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s thoughts, feelings, and needs.
-The current studies shed light on this fascinating and understudied aspect of "mind perception," in turn laying the foundation for theory-based interventions to encourage positive and responsive parenting behaviors.
+In a series of studies, we assessed how US adults conceptualize the development of the human mind over the first five years of life.
+Exploratory factor analysis identified four core capacities that anchored participants’ representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
+Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological “preprogramming,” physical maturation, passive observation, and social learning).
+Caregiving relationships with infants and children are among the most common and most complex human social interactions, and adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s rapidly developing thoughts, feelings, and needs.
+The current studies shed light on this fascinating and understudied aspect of “mind perception,” in turn laying the foundation for theory-based interventions to encourage positive and responsive parenting behaviors.
 

### 2021-10-16 supplement/supplement-main.Rmd
more anonymizing

@@
 In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-We identified four distinct suites of mental capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
+We identified four core capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).
 
@@
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261.
 
@@
 For this reason, results RDS files are included in the github repo.
+# To re-make results from scratch, comment out these lines, run this whole .Rmd file, and then uncomment these lines before knitting the supplement.
+
 s1_results <- readRDS("../outputs/s1_results.rds")

### 2021-10-17 paper/paper.Rmd
update abstract

@@
 
+Caregiving relationships with infants and children are among the most common and most complex human social interactions.
+Adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s rapidly developing thoughts, feelings, and needs.
 In a series of studies, we assessed how US adults conceptualize the development of the human mind over the first five years of life.
 Exploratory factor analysis identified four core capacities that anchored participants’ representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
-Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms (such as biological “preprogramming,” physical maturation, passive observation, and social learning).
-Caregiving relationships with infants and children are among the most common and most complex human social interactions, and adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s rapidly developing thoughts, feelings, and needs.
-The current studies shed light on this fascinating and understudied aspect of “mind perception,” in turn laying the foundation for theory-based interventions to encourage positive and responsive parenting behaviors.
+Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms, such as biological “preprogramming,” physical maturation, passive observation, and social learning.
+The current studies shed light on this fascinating and understudied aspect of “mind perception,” in turn highlighting possibilities for theory-based interventions to encourage positive and responsive parenting behaviors.
 
@@
 Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@putnam.etal2006; @rothbart1978]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.
-This process yielded a list of 60 capacities; see Figure \@ref(fig:fig01), and see Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception.
+This process yielded a list of 60 capacities; see Figure 1, and see Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception.
 Capacities were presented in a random order.
@@
 A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants’ and young children’s mental lives.
-See Figure \@ref(fig:fig01) for all factor loadings after oblique transformation.
+See Figure 1 for all factor loadings after oblique transformation.
 
@@
 
-Visual inspection of Figure \@ref(fig:fig02), Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
+Visual inspection of Figure 2, Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
 In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
@@
 
-This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure \@ref(fig:fig02), Panel B.
+This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure 2, Panel B.
 As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
@@
 
-Visual inspection of Figure \@ref(fig:fig02), Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
+Visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
 
@@
 One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure \@ref(fig:fig03)).
+This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure 3).
 
@@
 In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
-See Figure \@ref(fig:fig03), panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.
+See Figure 3, panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.
 
@@
 
-Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure \@ref(fig:fig03), Panel C.
+Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure 3, Panel C.
 Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensation_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensation", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
@@
 Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
-We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure \@ref(fig:fig02).
+We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
 This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
@@
 In addition to _bodily sensation_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
-Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)).
+Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure 3).
 Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.

### 2021-10-18 paper/paper.Rmd
tweaks and typos

@@
   pdf_document:  default
+  #   reference_docx: word-styles-ref.docx
   # word_document:
-  #   reference_docx: word-styles-ref.docx
 bibliography: ../supplement/references.bib
@@
 We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019; @berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019] [@berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
 
 Beliefs about the development of the more social-emotional aspects of mental life—*negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
-In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree, but not fully, from birth; and to develop rapidly in the first two years of life before tapering off.
+In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree from birth [consistent with recent findings on the perceived "innateness" of emotions, @berent.etal2020] but to continue developing rapidly over the first two years of life.
 Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
@@
 emotional distress, when the child is working on a task vs.
-attempting to strengthen a social bond), or at one developmental stage more than another (e.g., compared to childhood, mind-mindedness may be more apparent with respect to bodily sensation than cognitive and control in infancy).
+attempting to strengthen a social bond), or at one developmental stage more than another (e.g., mind-mindedness may be more apparent with respect to _bodily sensation_ in infancy vs.
+_cognitive control_ in later childhood).
 

### 2021-10-27 supplement/supplement-main.Rmd
tweaks and typos
add alpha

@@
 Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
-All studies were approved by [IRB information removed to preserve anonymity].
+
 All materials used in these studies are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52 (DOI: 10.17605/OSF.IO/XRZND).
+
 All studies were approved by [IRB information removed to preserve anonymity].
@@
 
+```{r s2 cap ratings reliability}
+d2_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Bodily sensation") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d2_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Negative affect") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d2_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Social connection") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d2_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Cognition and control") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+```
+
 ```{r s2 cap ratings summary stats}
@@
 
+```{r s3 cap ratings reliability}
+d3_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Bodily sensation") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d3_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Negative affect") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d3_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Social connection") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+
+d3_cap_ratings %>%
+  unite(ResponseId_target, c(ResponseId, target)) %>%
+  distinct(ResponseId_target, factor, capacity, response) %>%
+  filter(factor == "Cognition and control") %>%
+  select(-factor) %>%
+  spread(capacity, response) %>%
+  column_to_rownames("ResponseId_target") %>%
+  psych::alpha()
+```
+
 ```{r s3 cap ratings summary stats}
@@
 
-##### bodily sensation
+##### Bodily sensation
 

### 2022-07-25 supplement/supplement-main.Rmd
add comparison of cap ratings across studies

@@
 
-To conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
+To our knowledge, there is currently no consensus about how to account for within-participant variance alongside between-participant variance in the context of exploratory factor analysis or similar dimensionality reduction analyses.
+Thus, to conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
 (See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].
@@
 On each trial, at the bottom of the page participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children's capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for the following 10 developmental mechanisms: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that given them this ability"; "the child's body grows and matures (for example, muscles get stronger, child gets taller)"; "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child's senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this".
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children's capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled as "not at all important") to 6 (labeled as "extremely important"), for the following 10 developmental mechanisms: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that give them this ability"; "the child's body grows and matures (for example, muscles get stronger, child gets taller)"; "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child's senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this".
 These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
@@
 knitr::include_graphics("../outputs/figS02.pdf")
+```
+
+#### Four-factor solution, varimax rotation
+
+```{r s1 efa varimax rotation}
+s1_efa_4_varimax <- fa(d1_all, 
+                       nfactors = 4, 
+                       rotate = "varimax")
+# s1_efa_4_varimax %>% fa.sort()
+```
+
+Throughout this manuscript we present EFA results after oblique ("oblimin") transformation.
+In recent years, oblique transformation has become the preferred approach for many researchers because it allows factors to be correlated with each others (to the extent that these correlations are suggested by the data), thus imposing fewer restrictions on the types of factor structures the might be surfaced by the analysis.
+
+Here we present one alternative approach, using varimax rotation rather than oblique transformation. This yields a set of orthogonal (uncorrelated) factors.
+
+This rotation is very similar to the oblique transformation that is the focus of our interpretation in the main text.
+We consider the first of these factors ("`r names(data.frame(s1_efa_4_varimax$loadings[]))[1]`") to resonate with the construct we have called _social connection_, the second ("`r names(data.frame(s1_efa_4_varimax$loadings[]))[2]`") to resonate with the construct we have called _bodily sensation_, the third ("`r names(data.frame(s1_efa_4_varimax$loadings[]))[3]`") to resonate with the construct we have called _cognition and control_, and the fourth ("`r names(data.frame(s1_efa_4_varimax$loadings[]))[4]`") to resonate with the construct we have called _negative affect_.
+We do note, however, that in this rotation there were no items that loaded most strongly on this fourth factor, in line with the idea that our results provide only moderate evidence for _negative affect_ as a fourth, distinct, domain in participants' representations of the development of mental life.
+
+Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs1efavarimaxload).
+The amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs1efavarimaxvacc).
+
+```{r tabs1efavarimaxload, include = T, warning = F, message = F}
+tabs1efavarimaxload <- model_parameters(s1_efa_4_varimax, sort = T) %>% 
+  data.frame() %>% 
+  rename(Capacity = Variable) %>%
+  mutate(Capacity = gsub("_", " ", Capacity)) %>%
+  mutate_at(vars(starts_with("MR")),
+            funs("bold" = ifelse(. >= 0.6, T, F)))
+
+tabs1efavarimaxload %>%
+  select(-ends_with("_bold")) %>%
+  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
+        caption = "Study 1, four-factor solution after varimax rotation: Factor loadings, complexity, and uniqueness.") %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
+  column_spec(2, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+4]) %>%
+  column_spec(3, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+5]) %>%
+  column_spec(4, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+6]) %>%
+  column_spec(5, width = "1cm", bold = tabs1efaparload[,s1_parallel$nfact+7]) %>%
+  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
+```
+
+```{r tabs1efavarimaxvacc, include = T, warning = F, message = F}
+s1_efa_4_varimax$Vaccounted %>% 
+  data.frame() %>% 
+  rename(`Cognition and control` = MR3,
+         `Social connection` = MR1,
+         `bodily sensation` = MR2,
+         `Negative affect` = MR4) %>%
+  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
+        caption = "Study 1, four-factor solution after varimax rotation: Variance accounted for.") %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 8)
 ```
@@
                    efa_wdm = s1_efa_wdm,
+                   efa_var = s1_efa_4_varimax,
                    cap_rat_ss = d1_cap_ratings_sum)
@@
 
+```{r}
+d3_dev_factor_rating_wide <- d3_dev_factor_rating %>% 
+  spread(dev_factor, response) %>% 
+  unite("ResponseId_domain_capacity", ResponseId, domain, capacity) %>%
+  column_to_rownames("ResponseId_domain_capacity")
+
+d3_dev_factor_rating_wide %>%
+  psych::alpha()
+
+d3_dev_factor_rating_wide %>%
+  select(senses_improve, body_grows, womb_experiences, preprogrammed) %>%
+  psych::alpha()
+
+d3_dev_factor_rating_wide %>%
+  select(interacts_people, observes_people, observes_objects, 
+         people_teach, experiments) %>%
+  psych::alpha()
+```
+
 #### Regression models
@@
     TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
@@
 
+# Study comparison: Capacity attributions to newborns, 9-months, and 5-year-olds
+
+```{r}
+d123_gam <- full_join(
+  d1_gam %>% mutate(study = "Study 1"),
+  d2_gam %>% mutate(study = "Study 2")) %>%
+  mutate(target_num = target_year*12) %>%
+  left_join(d3_gam %>% distinct(target, target_ord)) %>%
+  full_join(d3_gam %>% mutate(study = "Study 3"))
+```
+
+```{r, fig.width = 5.5, fig.asp = 1}
+figS10a <- d123_gam %>%
+  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
+  filter(capacity %in% (d2_gam %>% distinct(capacity) %>% pull(capacity))) %>%
+  complete(
+    capacity, nesting(study, target, target_year, target_num, target_ord), 
+    fill = list(response = -1)) %>% # introduce -1 to align studies across panels
+  select(-factor) %>%
+  # left_join(d2_gam %>% distinct(capacity, factor)) %>%
+  left_join(d2_scales %>% select(-loading)) %>%
+  mutate(capacity_text = str_wrap(gsub("_", " ", capacity), 40)) %>%
+  ggplot(aes(x = target_ord, y = response, color = study)) +
+  facet_wrap(facets = vars(reorder(capacity_text, as.numeric(order))), nrow = 4) +
+  geom_point(
+    size = 0.02,
+    alpha = 0.6,
+    position = position_jitterdodge(
+      dodge.width = 0.8,
+      jitter.width = 0.2,
+      jitter.height = 0)) +
+  geom_pointrange(
+    data = . %>%
+      group_by(study, target, target_year, target_num, target_ord, 
+               factor, capacity, capacity_text, order) %>%
+      multi_boot_standard(col = "response") %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
+    color = "black", fatten = 2,
+    position = position_dodge(width = 0.8)) +
+  # scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(
+    limits = c(0, 1), # exclude the specious "-1" responses introduced above
+    breaks = seq(0, 1, 0.25),
+    labels = seq(0, 100, 25)) +
+  scale_x_discrete(labels = c("newborns", "9 months", "5 years")) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        legend.position = "top") +
+        # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Target age",
+       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       color = "Study") +
+  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+# figS10a
+```
+
+```{r, fig.width = 5.5, fig.asp = 1}
+figS10b <- d123_gam %>%
+  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
+  filter(capacity %in% (d2_gam %>% distinct(capacity) %>% pull(capacity))) %>%
+  select(-factor) %>%
+  # left_join(d2_gam %>% distinct(capacity, factor)) %>%
+  left_join(d2_scales %>% select(-loading)) %>%
+  group_by(study, ResponseId, target_ord, factor) %>%
+  summarise(score = mean(response, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(blank_var = "(2-5 common capacities)",
+         factor_lab = toupper(factor)) %>%
+  ggplot(aes(x = target_ord, y = score, color = study)) +
+  facet_grid(cols = vars(blank_var),
+             rows = vars(reorder(factor_lab, as.numeric(factor)))) +
+             # switch = "y") +
+  geom_point(
+    size = 0.02,
+    alpha = 0.6,
+    position = position_jitterdodge(
+      dodge.width = 0.8,
+      jitter.width = 0.2,
+      jitter.height = 0)) +
+  geom_pointrange(
+    data = . %>%
+      group_by(study, target_ord, factor, factor_lab) %>%
+      multi_boot_standard(col = "score") %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
+    color = "black", fatten = 7, shape = 18,
+    position = position_dodge(width = 0.8)) +
+  # scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(#position = "right",
+                     breaks = seq(0, 1, 0.25),
+                     labels = seq(0, 100, 25)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        # strip.placement = "outside",
+        panel.spacing.y = unit(1.6, "lines"),
+        legend.position = "top") +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Target age",
+       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       color = "Study") +
+  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+# figS10b
+```
+
+```{r, fig.width = 4, fig.asp = 0.9}
+figS10c <- d123_gam %>%
+  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
+  group_by(study, ResponseId, target_ord, factor) %>%
+  summarise(score = mean(response, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(blank_var = "(all capacities, varies by study)",
+         factor_lab = toupper(factor)) %>%
+  ggplot(aes(x = target_ord, y = score, color = study)) +
+  facet_grid(cols = vars(blank_var),
+             rows = vars(reorder(factor_lab, as.numeric(factor)))) +
+  geom_point(
+    size = 0.02,
+    alpha = 0.6,
+    position = position_jitterdodge(
+      dodge.width = 0.8,
+      jitter.width = 0.2,
+      jitter.height = 0)) +
+  geom_pointrange(
+    data = . %>%
+      group_by(study, target_ord, factor, factor_lab) %>%
+      multi_boot_standard(col = "score") %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
+    color = "black", fatten = 7, shape = 18,
+    position = position_dodge(width = 0.8)) +
+  # scale_color_viridis_d(end = 0.9, option = "viridis") +
+  scale_y_continuous(breaks = seq(0, 1, 0.25),
+                     labels = seq(0, 100, 25)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        panel.spacing.y = unit(1.6, "lines"),
+        legend.position = "top") +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Target age",
+       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       color = "Study") +
+  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+# figS10c
+```
+
+```{r figS10 code, fig.width = 8, fig.asp = 1}
+plot_grid(get_legend(figS10a),
+          plot_grid(figS10a + guides(color = guide_none()), 
+                    figS10b + guides(color = guide_none()) + 
+                      theme(axis.title.y = element_blank(),
+                            strip.text.y = element_blank()),
+                    figS10c + guides(color = guide_none()) +
+                      theme(axis.title.y = element_blank()),
+                    rel_widths = c(1, 0.25, 0.28),
+                    nrow = 1,
+                    labels = "AUTO"),
+          rel_heights = c(0.02, 1),
+          ncol = 1) ### xx bookmark
+
+# save plot
+if (resave_plots == T | !file.exists("../outputs/figS10.pdf")) {
+  ggsave("../outputs/figS10.svg")
+  ggsave("../outputs/figS10.pdf")
+}
+```
+
+```{r figS10, fig.cap="Comparison of capacity ratings across studies (Studies 1-3).
+Panel A is a visualization of responses for each of the capacities and target ages held in common across studies.
+Panel B is a visualization of the resulting 'scores' (mean capacity ratings) for each of the 4 domains identified in these studies (_bodily sensation_, _negative affect_, _social connection_, and _cognition and control_\\)\\, considering only those capacities depicted in Panel A.
+Panel C is a visualization of scores for each of these 4 domains considering all of the capacities included in each study.
+Lighter colorful represent individual participants’ responses or scores, black points correspond to mean responses or scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
+knitr::include_graphics("../outputs/figS10.pdf")
+```
+
+As described in the main text, all of the current studied employed a fixed-order design, in which all participants assessed target ages in a fixed order beginning with the youngest target age (newborns) and proceeding chronologically until the oldest target age (5-year-olds).
+This decision reflects the fact that our priority in these studies was to assess beliefs about the developmental trajectories of capacities, rather than beliefs about capacities at a specific point in development.
+However, one limitation of this fixed-order design is that it makes it difficult to assess the stability of participants’ assessments of the fine-grained differences between specific points in development.
+
+To provide some sense of the stability of participants' representations of specific target ages, Supplementary Figure \@ref(fig:figS10) presents a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds).
+As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here.
+In Study 2, participants assessed the 20 capacities depicted in Panel A, at 13 target ages (including but not limited to the 3 target ages depicted here).
+In Study 3, participants assessed 8 capacities (a subset of the 20 capacities depicted in Panel A), at 13 target ages (including but not limited to the 3 target ages depicted here).
+
 # Selection of capacities: Comparison to previous studies

### 2022-07-25 supplement/supplement-main.Rmd
remove dim reduction for mechanisms

@@
   column_to_rownames("RepsonseId_capacity")
-```
-
-#### Dimensionality reduction
-
-Here we present two dimensionality reduction approaches: EFA via parallel analysis (analogous to the EFAs of mental capacity attributions from Studies 1-2) and hierarchical clustering.
-
-##### EFA (via parallel analysis)
-
-```{r s3 parallel analysis}
-set.seed(94305) # this does not appear to work well -- may need to try a few times
-s3_parallel <- fa.parallel(d3_mech_ratings_wide, plot = F)
-```
-
-```{r s3 efa parallel analysis}
-s3_efa_par <- fa(d3_mech_ratings_wide, 
-                 nfactors = s3_parallel$nfact, 
-                 rotate = "oblimin")
-# s3_efa_par %>% fa.sort()
-```
-
-Parallel analysis suggested retaining `r s3_parallel$nfact` factors, which we labeled _extrinsic (passive)_, _extrinsic (active)_, _intrinsic (after birth)_, and _intrinsic (before birth)_.
-Factor loadings, item complexity, and uniqueness are shown in Supplementary Table \@ref(tab:tabs3efaload); the amount of total and shared variance accounted for by these factors is shown in Supplementary Table \@ref(tab:tabs3efavacc).
-
-```{r tabs3efaload, include = T, warning = F, message = F}
-tabs3efaload <- model_parameters(s3_efa_par, sort = T) %>% 
-  data.frame() %>% 
-  rename(Capacity = Variable) %>%
-  mutate(Capacity = gsub("_", " ", Capacity)) %>%
-  mutate_at(vars(starts_with("MR")),
-            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
-  rename(`Extrinsic (passive)` = MR1,
-         `Extrinsic (active)` = MR3,
-         `Intrinsic (after birth)` = MR4,
-         `Intrinsic (before birth)` = MR2)
-
-tabs3efaload %>%
-  select(-ends_with("_bold")) %>%
-  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 3, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
-  column_spec(2, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+4]) %>%
-  column_spec(3, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+5]) %>%
-  column_spec(4, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+6]) %>%
-  column_spec(5, width = "1.8cm", bold = tabs3efaload[,s3_parallel$nfact+7]) %>%
-  footnote(general = "Factor loadings with absolute values >0.60 are in bold.")
-```
-
-```{r tabs3efavacc, include = T, warning = F, message = F}
-s3_efa_par$Vaccounted %>% 
-  data.frame() %>% 
-  rename(`Extrinsic (passive)` = MR1,
-         `Extrinsic (active)` = MR3,
-         `Intrinsic (after birth)` = MR4,
-         `Intrinsic (before birth)` = MR2) %>%
-  kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 3, factor solution suggested by parallel analysis: Variance accounted for.") %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-```{r figS06 code, fig.width = 4.5, fig.asp = 0.5}
-heatmap_fun(s3_efa_par, 
-            factor_names = c("Extrinsic (passive)",
-                             "Intrinsic (before birth)",
-                             "Extrinsic (active)",
-                             "Intrinsic (after birth)"))
-
-# save plot
-if (resave_plots == T | !file.exists("../outputs/figS06.pdf")) {
-  ggsave("../outputs/figS06.svg")
-  ggsave("../outputs/figS06.pdf")
-}
-```
-
-```{r figS06, fig.cap="Study 3, factor solution suggested by parallel analysis."}
-# knitr::include_graphics("../outputs/figS06.pdf")
-```
-
-##### Hierarchical clustering
-
-In addition to the EFA just described, we also conducted a hierarchical cluster analysis, using Euclidean distance and Ward's agglomeration method.
-The resulting dendrogram is presented in Supplementary Figure \@ref(fig:figS07).
-We view this as providing further support for the idea that these mechanisms can be sorted into two high-level categories: "extrinsic" mechanisms (left) and "intrinsic" mechanisms (right).
-
-```{r figS07 code, fig.width = 3, fig.asp = 0.6}
-d3_mech_ratings_wide %>% 
-  rename_with(~recode(., 
-                      "preprogrammed" = "biologically 'preprogrammed'",
-                      "womb_experiences" = "experiences in the womb",
-                      "body_grows" = "body grows and matures",
-                      "brain_changes" = "brain changes",
-                      "senses_improve" = "senses improve",
-                      "observes_objects" = "observes objects and physical world",
-                      "experiments" = "actively experiments",
-                      "observes_people" = "observes people",
-                      "interacts_people" = "interacts with people",
-                      "people_teach" = "people explicitly teach")) %>%
-  remove_missing() %>% 
-  as.matrix() %>% 
-  t() %>%
-  dist(method = "euclidean") %>%
-  hclust(method = "ward") %>%
-  ggdendrogram(rotate = F) +
-  theme(axis.text.y = element_blank(),
-        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
-        plot.margin = unit(c(5.5, 5.5, 5.5, 40), "points"))
-
-# save plot
-if (resave_plots == T | !file.exists("../outputs/figS07.pdf")) {
-  ggsave("../outputs/figS07.svg")
-  ggsave("../outputs/figS07.pdf")
-}
-```
-
-```{r figS07, fig.cap="Hierarchical cluster analysis of importance ratings of developmental mechanisms (Study 3).", include = T}
-knitr::include_graphics("../outputs/figS07.pdf")
-```
-
-```{r}
-d3_dev_factor_rating_wide <- d3_dev_factor_rating %>% 
-  spread(dev_factor, response) %>% 
-  unite("ResponseId_domain_capacity", ResponseId, domain, capacity) %>%
-  column_to_rownames("ResponseId_domain_capacity")
-
-d3_dev_factor_rating_wide %>%
-  psych::alpha()
-
-d3_dev_factor_rating_wide %>%
-  select(senses_improve, body_grows, womb_experiences, preprogrammed) %>%
-  psych::alpha()
-
-d3_dev_factor_rating_wide %>%
-  select(interacts_people, observes_people, observes_objects, 
-         people_teach, experiments) %>%
-  psych::alpha()
 ```

### 2022-08-01 paper/paper.Rmd
update references and paper main text

@@
 Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms, such as biological “preprogramming,” physical maturation, passive observation, and social learning.
-The current studies shed light on this fascinating and understudied aspect of “mind perception,” in turn highlighting possibilities for theory-based interventions to encourage positive and responsive parenting behaviors.
+The current studies shed light on this fascinating and understudied aspect of “mind perception” among US adults, in turn highlighting possibilities for theory-based interventions to encourage positive and responsive parenting behaviors.
 
@@
 
-In this paper, we examine how adults conceptualize the developing minds of infants and children by drawing on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed.
+In this paper, we examine how US adults conceptualize the developing minds of infants and children by drawing on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed.
 In a groundbreaking study, Gray et al.
@@
 All studies were approved by [IRB information removed to preserve anonymity].
-For extended descriptions of methods and results, see Supplemental Material.
+For extended descriptions of methods and results, see Supplemental Materials.
 
@@
 
-We began with an expansive exploration of US adults’ attributions of mental life to infants and young children of different ages.
+The first question we sought to address in this line of work was: What do US adults perceive to be the fundamental components of mental life, as they pertain to a developing human child?
+To this end, we began with an expansive exploration of US adults’ attributions of mental life to infants and young children in general; this laid the foundation for Studies 2-3, which we designed to assess the perceived developmental trajectories of these attributions across specific target ages.
+
 Drawing inspiration from previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018] as well as standard assessments of infant temperament and behavior [@putnam.etal2006; @rothbart1978], we included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction.
-We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life: What do people perceive to be the fundamental components of mental life, as they pertain to a developing human child?
+We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life.
 
@@
 Participants completed three trials in which they assessed the mental lives of children at three target ages: birth, 9 months, and 5 years.
-On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").
+On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs.
+These photographs (and all materials used in these studies) are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52; DOI: 10.17605/OSF.IO/XRZND).
+Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").
 
@@
 Our goals in selecting items were to: (1) balance the representation of the conceptual organization underlying mental capacity attributions in general, as identified in previous work [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018; @malle2019]; (2) add items relevant to early development, as identified by existing measures of temperament and behavior in early life [@putnam.etal2006; @rothbart1978]; and (3) assess the broadest range of mental capacities within financial and participant burden constraints, as identified by extensive discussions among the authors drawing on our own research and clinical experience with infants and young children.
-This process yielded a list of 60 capacities; see Figure 1, and see Supplemental Material for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception.
+This process yielded a list of 60 capacities; see Figure 1, and see Supplemental Materials for an item-by-item comparison of the capacities used here to those used in previous studies of mind perception.
 Capacities were presented in a random order.
@@
 We limited Study 1 to just the youngest, median, and oldest target ages—presented to participants as "newborns," "9-month-olds" and "5-year-olds"—in order to maximize the number of capacities included in the study without over-burdening participants.
+
 Target ages were presented in chronological order, with participants first assessing all 60 capacities for newborns, then 9-month-old infants, and finally 5-year-old children.
+In this and all studies, we opted for this fixed-order design because our priority was to assess beliefs about the developmental trajectories of capacities, rather than beliefs about capacities at a specific point in development.
+The fixed order of target ages was intended to ensure that questions about developmental trajectories “flowed” in a coherent way [@krosnick.presser2009].
 
@@
 This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors.
+See Supplemental Materials for more details about this analysis, including our decision to treat participants’ ratings of each of the three target ages as if they were a distinct source of data.
 
@@
 See Figure 1 for all factor loadings after oblique transformation.
+(See also Supplemental Materials for the 8-factor solution suggested by minimizing the Bayesian Information Criterion [BIC], and the 2-factor solution suggested by implementing the factor retention criteria employed in [@weisman.etal2017a].)
 
 The first factor corresponded primarily to capacities related to thinking, reasoning, agency, and executive function—a suite of capacities that we interpreted as reflecting a higher-order capacity for _cognition and control_.
-It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," "understanding what somebody else is thinking," "focusing on a goal," "feeling guilty," "feeling embarrassed," "feeling pride," "making choices," "calming themselves down," "detecting danger," and "feeling hopeless." This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.
+It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," "understanding what somebody else is thinking," "focusing on a goal," "feeling guilty," "feeling embarrassed," "feeling pride," "making choices," "calming themselves down," "detecting danger," and "feeling hopeless." (For this and the following factors, we list all of the items with loadings $\geq$ 0.60 in descending order by factor loading; see Figure 1 for the full set of loadings.) This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.
 
-The second factor corresponded primarily to social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_.
-It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others), and because we interpret this factor as indexing participants’ sense of the infant awakening into the human social world.
+The second factor corresponded primarily to what we would describe as social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_.
+It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants’ sense of the infant awakening into the human social and cultural world.
 This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants’ capacity attributions.
@@
 Finally, the fourth factor corresponded to negatively-valenced sensations and emotions—a suite of capacities that we interpreted as reflecting a higher-order capacity for _negative affect_.
-It was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected"; the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors).
+Although there were no items that loaded more strongly than `r round_x(max(s1_results$efa$loadings[,"MR4"]))` on this factor, this factor was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected," and the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors).
 This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.
@@
 In contrast, the fourth factor—_negative affect_—had more moderate loadings even for its strongest-loading items (all loadings < `r abs(s1_results$efa$loadings[][,"MR4"]) %>% max() %>% round(., 2) + 0.01`) and accounted for only `r round_x(s1_results$efa$Vaccounted["Proportion Var","MR4"]*100, 0)`% of the total variance.
-Nonetheless, because we considered the general domain of _negative affect_ to be of particular theoretical and clinical interest, we opted to retain this factor in subsequent studies.
+Nonetheless, we opted to retain this factor in subsequent studies because we considered the general domain of _negative affect_ to be of particular theoretical and clinical interest.
+An individual’s propensity to negative affect in infancy and early childhood is a salient individual difference trait associated with risk for internalizing disorders [@gartstein.etal2012].
+Beyond this, positive and negatively valenced emotionality emerge at different developmental timescales: Signs of negative affect are present from birth (e.g., crying shortly following delivery), whereas signs of positive affect (e.g., social smiling, laughing) are not present for several weeks [@humphreys.etal2015], supporting both the relevance and distinctiveness of negative emotional expression in early life.
 
@@
 Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
+
+As a check on our choice of labels for these factors, we turned to OpenAI’s Generative Pre-trained Transformer 3 (GPT-3) [@brown.etal2020], an autoregressive transformer-based language prediction model trained on an enormous corpus of English-language text drawn primarily from “crawls” of the Internet as well as English-language novels and the open-source encyclopedia Wikipedia.
+GPT-3 is capable of generating remarkably human-like text in response to questions and other prompts.
+GPT-3, like other generative language models, was developed under the mandate of predicting the continuation of natural language sequences: Most concretely, then, its “responses” should be understood to reflect a sequence of words that is likely to follow the prompt it has been provided.
+In a more abstract sense, however, the content of these responses could be understood to represent the “common knowledge” embedded in the training data [for extended arguments relevant to this proposal, see @bhatia.richie2021; @lake.murphy2021; @petroni.etal2019].
+For example, if prompted with the questions “What do you get when you mix red and yellow?” or “What’s a good name for a vegetarian restaurant?,” GPT-3 will generate text like “When you mix red and yellow, you get orange” or “The Green Plate” (respectively).
+In continuing the language sequence, the model also provides novel content that reflects actual human knowledge, biases, associations, and intuitions.
+
+Using the openly available GPT-3 “playground” (https://beta.openai.com/playground), we provided a variety of prompts to the model to assess its “intuitions” about how to label the four categories of mental capacities suggested by the factor solution just described.
+One representative prompt read, “Name these four categories of mental capacities: Category 1 is […].
+Category 2 is […],” and so on, with the ellipses replaced by lists of all the items for which each factor (“Category”) was the dominant factor.
+The response generated by GPT-3 in this case was as follows: “Category 1: Executive functioning skills.
+Category 2: Social and emotional skills.
+Category 3: Physical needs and sensations.
+Category 4: Negative emotions.” In nearly every variation of our prompts, GPT-3’s labels for the factor we have labeled cognition and control included the phrase “executive function”; its labels for the factor we have labeled social connection always nearly always included the word “social” or “social-emotional”; its labels for the factor we have labeled bodily sensation nearly always included the words “sensations” (and often “physical needs” or “basic needs”); and its labels for the factor we have labeled negative affect nearly always included the phrase “negative emotion.” (See Supplemental Materials for the full text of these prompts and GPT-3’s responses.) The similarity.
+between our original labels (i.e.
+cognition and control, social connection, bodily sensations, and negative affect) and those generated by GPT-3 provide some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
+Nonetheless, we caution the reader to treat these labels as interpretations of empirical results, rather than empirical results themselves.
 
@@
 
-```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of participants’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
+```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of US adults’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
 knitr::include_graphics("../outputs/fig01.pdf")
@@
 
-In Study 2, we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development: What kinds of abilities do people believe are present at birth, and to what degree?
+In Study 2, we replicated the conceptual structure identified by Study 1 and then used it to chart how different aspects of mental life are perceived to change over development: What kinds of abilities do US adults believe are present at birth, and to what degree?
 To what extent are capacities for _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ perceived to change over childhood, and what is the shape of these perceived developmental trajectories?
@@
 The target ages for this study were based on the developmental milestone ages described in Study 1.
-Target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, and so forth.
+As in Study 1, target ages were presented in chronological order, with participants first assessing all 20 capacities for newborns, then 4-day-old infants, and so forth, with the primary goal of assessing beliefs about changes in these capacities over development.
+
+One limitation of this fixed-order design is that it makes it difficult to assess the stability of participants’ assessments of the fine-grained differences between specific points in development.
+See Supplemental Materials for a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (i.e., newborns, 9-month-olds, and 5-year-olds), which provides some sense of the stability of participants’ representations of these particular target ages.
 
@@
 
-A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors (see Supplemental Materials).
-Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1.
+A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors.
+(See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.’s (2017) factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings (≥ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
 Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
@@
 On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported smaller increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported smaller increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
 At the other extreme, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
@@
 In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
-Participants perceived development in the domains of _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
+Participants perceived development in the domains that we have labeled _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
 In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.
@@
 
-```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
+```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life among US adults (Studies 2-3).
 Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
@@
 On each trial, participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for 10 developmental mechanisms presented in a fixed order; see Results for all items.
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for the following 10 developmental mechanisms: “the child is biologically ‘preprogrammed’ to have this ability”; “the child has experiences in the womb that give them this ability”; “the child’s body grows and matures (for example, muscles get stronger, child gets taller)”; “the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)”; “the child’s senses improve (for example, vision gets sharper, hearing improves)”; “the child observes the objects and the physical world around him or her”; “the child observes the people around him or her”; “the child interacts with the people around him or her”; “people explicitly teach the child how to do this”; “the child actively experiments with how to do this.” These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
 Participants were also asked to choose among these 10 mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
@@
 Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to 8 in the current study to maintain an appropriate level of participant burden.
-We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain of _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain of _negative affect_.
+We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain that we have labeled _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain that we have labeled _negative affect_.
 Capacities were presented in a random order for each participant.
@@
 As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Again, participants attributed substantially greater capacities to newborns in the domains of _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain of _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
+Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain that we have labeled _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
 Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
@@
 
-Why do people believe certain aspects of mental life, but not others, to be present at birth?
-What do people perceive to be driving the development of capacities for _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_?
+Why do US adults believe certain aspects of mental life, but not others, to be present at birth?
+What do US adults perceive to be driving the development of capacities for what we have called _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_?
 As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
@@
 
-We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.
+[XXXX CUT We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.]
 
-A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials), which aligned nearly exactly with our _a priori_ ordering of these mechanisms from most "innate" or "biological" to most "learned" or "social" (see Study 3 preregistration).
+[XXXX CUT A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials), which aligned nearly exactly with our _a priori_ ordering of these mechanisms from most "innate" or "biological" to most "learned" or "social" (see Study 3 preregistration).
 First, there were what we will call _intrinsic mechanisms_: mechanisms rooted in innate predispositions or biological maturational processes, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
@@
 One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure 3).
+This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure 3).]
 
@@
 
-A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).
+[XXXX CUT A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).]
 
-For capacities in the domain of _bodily sensation_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
+[XXXX CUT For capacities in the domain of _bodily sensation_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
 In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`).
 In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
-See Figure 3, panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.
+See Figure 3, panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.]
 
@@
 
-Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure 3, Panel C.
+[XXXX CUT Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure 3, Panel C.
 Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensation_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensation", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
 On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
-Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).
+Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).]
 
-Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
+[XXXX CUT Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
 Capacities for _bodily sensation_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
 Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world.
-Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).
+Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).]
 
-```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
-intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
-intrinsic mechanisms as the 'most important' driver of development.
+[XXXX INSERT NEW ANALYSES]
+
+```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
+Panel A shows ratings for each developmental mechanism and each of the capacities within each domain; and Panel C shows the percentage of trials on which participants selected each developmental mechanism as the ‘most important’ driver of development for each capacity within each domain.
 Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains."}
+The dotted red line at the midpoint of the response scale in Panel A is intended to aid visual comparison across mechanisms."}
 knitr::include_graphics("../outputs/fig03.pdf")
 ```
+
+## Relationships between beliefs about developmental mechanisms and perceived developmental trajectories
+
+As a final exploration of participants’ representations of the development of mental life, we explored the relationships between beliefs about what mechanisms drive the development of the capacities included in this study and beliefs about the extent to which these capacities are present at different points in infancy and early childhood.
+We consider these exploratory analyses to offer some insight into the coherence of participants’ intuitive theories about the development of mental life.
+
+These relationships are visualized in Figure 4; see Supplemental Materials for a breakdown by individual capacity (e.g., “feeling pain,” “getting hungry,” and so forth), and for separate regression analyses for each developmental mechanism, taking into account differences across target ages and capacities, as well as individual differences across participants.
+
+```{r fig04, fig.cap="Relationships between US adults’ ratings of the importance of various developmental mechanisms and capacity ratings, collapsing across capacities (Study 3); see Supplemental Materials for a breakdown of these relationships by individual capacity.
+Light black points represent individual participants’ responses, with each participant contributing one datapoint for each capacity-mechanism pair (i.e., 80 datapoints per participant).
+Dark colorful lines correspond to smoothed conditional means (via GAMs), with shaded areas representing 95% confidence intervals.
+The dotted red line at the midpoint of the response scale is intended to aid visual comparison across target ages."}
+knitr::include_graphics("../outputs/fig04.pdf")
+```
+
+Our primary take-away from this analysis is that the nature of these relationships between mechanism and capacity ratings varied substantially across mechanisms.
+This is easiest to visualize at the youngest target age, newborns (Fig.
+4, first panel), where we observed three basic kinds of relationships.
+
+[XXXX INSERT NEW ANALYSES]
+
+In nearly all cases, the relationships just described between mechanism and capacity ratings were increasingly subtle over the target age range; this is readily apparent through visual inspection of Fig.
+4 (see also Supplemental Materials for estimates of interactions between mechanism rating and target age for each developmental mechanism).
+This is consistent with the fact that, across the target age range, mean capacity ratings increased, approaching the ceiling of our response scale, and variability across participants decreased—leaving less room to detect potential relationships with beliefs about developmental mechanisms.
+Put another way, by the older end of our target age range, participants had largely converged on an understanding that children were nearly fully capable of all of the capacities included in this study, regardless of what mechanisms had driven the development of these capacities.
+
+Taken together, these results provide some evidence for the existence of coherent intuitive theories of the development of mental life among US adults’: Individual differences in participants’ beliefs about the mechanisms that drive the development of various aspects of mental life were coherently related to their beliefs about how these aspects of mental life develop over infancy and early childhood (with the slight exception, perhaps, of beliefs about the influence of the child’s body growing and the child’s senses improving, as described above).
+To our eyes, these findings also hint at an intuitive distinction between developmental mechanisms that exert their influence during fetal development prior to birth (namely, biological “preprogramming” and experiences in the womb; the first pattern described above) vs.
+mechanisms that depend on the child observing and interacting with the world outside of the womb after birth (including various forms of observation, experimentation, and social interaction; the second pattern described above).
+We consider this distinction and its associated patterns of relationships to be intuitively sensical and reasonably closely aligned with scientific theories of fetal and neonatal development: To the extent that a capacity can emerge prior to birth, we would expect to observe it in the newborn child; while to the extent to that a capacity depends on experience in the outside world, we would expect not to observe it in the newborn child who lacks those experiences.
+Much like social scientists, different participants held different specific beliefs about which of these mechanisms were most relevant for which of the capacities included in this study, but they seemed to share a coherent understanding—an intuitive theory—of how mechanisms and capacity attributions are related in the abstract.
 
@@
 
-Beliefs about the development of the more social-emotional aspects of mental life—*negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
+Beliefs about the development of the more social-emotional aspects of mental life—what we have called *negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
 In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree from birth [consistent with recent findings on the perceived "innateness" of emotions, @berent.etal2020] but to continue developing rapidly over the first two years of life.
 Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
-We note that attributions of _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
+We note that attributions of what we have called _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
 This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
+
+## Comparison to previous work
 
@@
 
-However, these studies also highlight one way in which reasoning about the development of human mental life may diverge from reasoning about mental life in general: In their assessments of the mental lives of infants and children at different ages, participants differentiated between what we call _social connection_ (e.g., capacities for excitement, humor, and love) and what we call _negative affect_ (e.g., capacities for distress, helplessness, and frustration).
+However, these studies also highlight one way in which reasoning about the development of human mental life may diverge from reasoning about mental life in general: In their assessments of the mental lives of infants and children at different ages, US adults differentiated between what we have called _social connection_ (e.g., capacities for excitement, humor, and love) and what we have called _negative affect_ (e.g., capacities for distress, helplessness, and frustration).
 These two factors have no obvious precedents in previous studies of mind perception.
-In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart." This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials);  the narrower focus on humans as the targets of mind perception; or the emphasis on how mental capacities develop over time.
-Based on the findings of Studies 2 and 3, we propose that _social connection_ and _negative affect_ emerged as distinct factors because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
+In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart."
 
-What do these studies reveal about US adults' understanding of the contributions of nature vs.
+This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials); the emphasis on how mental capacities develop over time; or, more broadly, the exclusive focus on humans as the targets of mind perception.
+Indeed, one exciting line of work focusing on how laypeople think about other humans’ mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: “rationality” (capturing a distinction between cognitive and affective states); “social impact” (capturing the degree to which mental states involve social relationships); and “valence” (capturing the distinction between positive and negative states; @tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020).
+The domains that we have called _social connection_ and _negative affect_ align rather well with these latter two dimensions, capturing a conceptual distinction between the degree to which certain capacities shape and are shaped by interpersonal interactions and social relationships vs.
+the degree to which certain capacities shape and are shaped by firsthand experiences of negative valence.
+Based on the findings of Studies 2 and 3, we further propose that social connection and negative affect emerged as distinct factors not only because they demarcate different aspects of mental life, but also because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
+
+What do these studies reveal about participants' understanding of the contributions of nature vs.
 nurture to the development of human mental life?
@@
 In addition to _bodily sensation_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
-Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure 3).
+Indeed, in Study 3 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure 3).
 Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
 Further work on this topic would do well to integrate the cognitive processing mechanisms featured in the current studies with epistemic states that have been the focus of past research on laypeople’s beliefs about the innateness of "cognitive" abilities [@berent.etal2019; @wang.feigenson2019] to paint a more comprehensive picture of the ways in which intuitive theories of development do and do not align with scientific theories such as nativism, empiricism, and constructivism.
+
+## Limitations
+
+One important limitation of the current studies is that they relied exclusively on samples of US adults recruited via the crowdsourcing platform Amazon Mechanical Turk (MTurk).
+In other lines of work on mind perception using similar bottom-up approaches to identifying latent conceptual structures, MTurk samples have yielded factor solutions very similar to more representative samples of general population US adults collected in person in public settings (e.g., the Department of Motor Vehicles; @weisman.etal2021); given this, we would predict that the current findings would be replicated in more representative samples of predominantly White, middle-class US adults.
+Of great interest and importance is the question of how beliefs and intuitive theories about the development of mental life do and do not vary across cultural, ethnic, racial, socioeconomic, educational, generational, and other dimensions, both within the US and across national boundaries.
+Echoing recent work comparing concepts of mental life across diverse cultural settings [@weisman.etal2021], we speculate that representations of the development of the more affective and emotional aspects of mental life is where the largest differences across cultural and demographic groups would be found, while other aspects of these beliefs might be held in common—but this is of course a question deserving of careful empirical investigation.
+
+One of the most interesting future directions for this line of research will be to assess how the experience of raising a child might change caregivers’ representations of and intuitive theories about the development of mental life across infancy and early childhood.
+Unfortunately, the current datasets are well-suited to these explorations.
+Our samples tended to include more non-parents than parents, and to include a wide range of parents (including, e.g., parents of children ranging in age from newborns to middle-aged adults).
+We also strongly suspect that parent status in MTurk samples is likely confounded with many demographic variables (e.g., age, wealth, education level, geographical location within the US), most of which we did not measure in the current samples.
+For these reasons, we have opted not to include any analyses of parents vs.
+non-parents in the current manuscript, because we do not want to mislead readers with potential spurious results from these datasets.
+However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics crying out for further research.
+
+## Implications for caregiver-child interactions
 

### 2022-08-01 code/data_prep_s1.R
standardize format for response ids

@@ -217,7 +217,8 @@ d1_demo <- d1 %>%
                              "10 - 18 years",
                              "> 18 years",
                              "My Youngest child is deceased",
-                             "Prefer not to say")))  
+                             "Prefer not to say"))) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 # all assessments of ALL TARGETS, RepsonseId as rownames
 d1_all <- d1 %>% 

### 2022-08-01 code/data_prep_s2.R

@@ -218,7 +218,8 @@ d2_demo <- d2 %>%
                              "10 - 18 years",
                              "> 18 years",
                              "My Youngest child is deceased",
-                             "Prefer not to say")))  
+                             "Prefer not to say"))) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 # all assessments of ALL TARGETS, RepsonseId as rownames
 d2_all <- d2 %>% 

### 2022-08-01 code/data_prep_s3.R

@@ -356,7 +356,8 @@ d3_cap_rating <- d3 %>%
                                     "target60mo" = "5-year-olds")) %>%
   left_join(capacities_s3) %>%
   select(ResponseId, target, target_num, target_ord, 
-         domain, capacity, response)
+         domain, capacity, response) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 # dev_factor ratings for ALL TARGETS, ALL CAPACITIES
 d3_dev_factor_rating <- d3 %>% 
@@ -378,7 +379,8 @@ d3_dev_factor_rating <- d3 %>%
                                         "experiments",
                                         "observes_people",
                                         "interacts_people",
-                                        "people_teach")))
+                                        "people_teach"))) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 # dev_factor "most important" for ALL TARGETS, ALL CAPACITIES
 d3_dev_factor_most_important <- d3 %>% 
@@ -404,7 +406,8 @@ d3_dev_factor_most_important <- d3 %>%
 
 d3_dev_factor_most_important_choice <- d3_dev_factor_most_important %>%
   filter(!is.na(response), response != "", !grepl("free", question)) %>%
-  select(-dev_factor, -question)
+  select(-dev_factor, -question) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 # # check for duplicates/redundancies
 # d3_dev_factor_most_important_choice %>%
@@ -413,7 +416,8 @@ d3_dev_factor_most_important_choice <- d3_dev_factor_most_important %>%
 
 d3_dev_factor_most_important_free <- d3_dev_factor_most_important %>%
   filter(!is.na(response), response != "", grepl("free", question)) %>%
-  select(-dev_factor, -question)
+  select(-dev_factor, -question) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 rm(d3_dev_factor_most_important)
 
@@ -452,7 +456,8 @@ d3_dev_factor_other <- d3 %>%
          !grepl("nothing to add", tolower(response)),
          !grepl("can't think of any", tolower(response)),
          !grepl("don't think so", tolower(response)),
-         !grepl("don\\;t think so", tolower(response)))
+         !grepl("don\\;t think so", tolower(response))) %>%
+  mutate(ResponseId = as.character(ResponseId))
 
 d3 <- d3_cap_rating
 

### 2022-08-01 supplement/supplement-main.Rmd
begin updating analyses... should have committed earlier...

@@
 
-To assess which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
-intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_.
-We also conducted separate, analogous regression analyses for each domain separately.
-In these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
-(Note that these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see previous section.)
-
-The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall) (all domains), \@ref(tab:tabs3lmerbod) (*bodily sensation*), \@ref(tab:tabs3lmerneg) (*negative affect*), \@ref(tab:tabs3lmersoc) (*social connection*), and \@ref(tab:tabs3lmercog) (*cognition and control*); see also Figure 3 (main text).
+To supplement our visual assessment of which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a series of multilevel linear regression models, regressing responses to this question onto domain, including the maximal random effects structure that allowed the model to converge.
+Using the "lme4" package for R [@bates.etal2015], we specified these models as follows: _lmer(response ~ domain + (1 | participant) + (1 | capacity)_.
+In these analyses, domain and developmental mechanism were both effect-coded for comparisons to the grand mean collapsing across domains and mechanisms.
+
+The full results of these models are presented in Supplementary Tables xxxxxxx; see also Figure 3 (main text).
 
@@
                                 "COG" = "Cognition and control")) %>%
-  select(-domain) %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor %in% c("senses_improve", "body_grows", 
-                      "womb_experiences", "preprogrammed") ~ "intrinsic",
-    dev_factor %in% c("interacts_people", "observes_people", "observes_objects", 
-                      "people_teach", "experiments") ~ "extrinsic",
-    dev_factor == "brain_changes" ~ NA_character_,
-    TRUE ~ NA_character_
-  )) %>%
-  mutate(dev_factor_cluster = factor(dev_factor_cluster,
-                                     levels = c("intrinsic", "extrinsic")))
+  select(-domain)
 
@@
 
-contrasts(d3_mech_ratings$dev_factor_cluster) <- cbind(ext_gm = c(-1, 1))
+contrasts(d3_mech_ratings$dev_factor) <- cbind(
+  womb_gm = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
+  body_gm = c(-1, 0, 1, 0, 0, 0, 0, 0, 0, 0),
+  brai_gm = c(-1, 0, 0, 1, 0, 0, 0, 0, 0, 0),
+  sens_gm = c(-1, 0, 0, 0, 1, 0, 0, 0, 0, 0),
+  obso_gm = c(-1, 0, 0, 0, 0, 1, 0, 0, 0, 0),
+  expt_gm = c(-1, 0, 0, 0, 0, 0, 1, 0, 0, 0),
+  obsp_gm = c(-1, 0, 0, 0, 0, 0, 0, 1, 0, 0),
+  intp_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 1, 0),
+  teac_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 0, 1))
 ```
@@
 d3_mech_ratings_sum_a <- d3_mech_ratings %>%
-  filter(!is.na(dev_factor_cluster)) %>%
-  # participant-level mean of means for each cluster
-  group_by(ResponseId, dev_factor_cluster) %>%
+  # participant-level mean of means for each mechanism
+  group_by(ResponseId, dev_factor) %>%
   summarise(score_a = mean(response, na.rm = T)) %>%
   ungroup() %>%
-  # group-level mean of means for each cluster 
-  group_by(dev_factor_cluster) %>%
+  # group-level mean of means for each mechanism 
+  group_by(dev_factor) %>%
   summarise(median = median(score_a, na.rm = T),
@@
   ungroup() %>%
-  arrange(dev_factor_cluster)
+  arrange(dev_factor)
 
@@
 d3_mech_ratings_sum_b <- d3_mech_ratings %>%
-  filter(!is.na(dev_factor_cluster)) %>%
   # participant-level mean for each mechanism, for each domain
-  group_by(ResponseId, dev_factor_cluster, dev_factor, factor) %>%
+  group_by(ResponseId, dev_factor, factor) %>%
   summarise(score_a = mean(response, na.rm = T)) %>%
   ungroup() %>%
-  # participant-level mean of means for each cluster, for each domain
-  group_by(ResponseId, dev_factor_cluster, factor) %>%
-  summarise(score_b = mean(score_a, na.rm = T)) %>%
+  # group-level mean of means of means for each domain 
+  group_by(factor, dev_factor) %>%
+  summarise(median = median(score_a, na.rm = T),
+            mean = mean(score_a, na.rm = T),
+            sd = sd(score_a, na.rm = T)) %>%
   ungroup() %>%
-  # group-level mean of means of means for each domain 
-  group_by(dev_factor_cluster, factor) %>%
-  summarise(median = median(score_b, na.rm = T),
-            mean = mean(score_b, na.rm = T),
-            sd = sd(score_b, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(factor, dev_factor_cluster)
+  arrange(factor, dev_factor)
 
@@
   mutate_if(is.numeric, funs(round_x(., 2)))
-
-# mean DIFFERENCES by domain
-d3_mech_ratings_sum_c <- d3_mech_ratings %>%
-  filter(!is.na(dev_factor_cluster)) %>%
-  # participant-level mean for each cluster, for each capacity
-  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
-  summarise(score_a = mean(response, na.rm = T)) %>%
-  ungroup() %>%
-  # participant-level cluster differences for each capacity
-  spread(dev_factor_cluster, score_a) %>%
-  mutate(diff_a = extrinsic - intrinsic) %>%
-  select(-extrinsic, -intrinsic) %>%
-  # participant-level mean differences, for each domain
-  group_by(ResponseId, factor) %>%
-  summarise(diff_b = mean(diff_a, na.rm = T)) %>%
-  ungroup() %>%
-  # group-level mean of means of mean differences, for each domain 
-  group_by(factor) %>%
-  summarise(median = median(diff_b, na.rm = T),
-            mean = mean(diff_b, na.rm = T),
-            sd = sd(diff_b, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(factor)
-
-d3_mech_ratings_sum_c %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
-```
-
-##### All domains
-
-In brief, this analysis suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important, but that the difference between intrinsic and extrinsic mechanisms varied across domains (see interaction terms).
+```
+
+##### All mechanisms
+
+In brief, this analysis suggested that the perceived importance of these developmental mechanisms varied both overall (see main effects) and across domains (see interaction terms).
 
 ```{r s3 mech ratings lmer}
-s3_lmer <- lmer(response ~ dev_factor_cluster * factor + 
-                  (1 + dev_factor_cluster + factor | ResponseId) + 
-                  (1 | dev_factor) +
+s3_lmer <- lmer(response ~ dev_factor * factor + 
+                  (1 | ResponseId) + 
                   (1 | capacity),
@@
     TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorwomb_gm", "Mechanism (Experiences in the womb vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbody_gm", "Mechanism (Body grows and matures vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbrai_gm", "Mechanism (Brain changes vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorsens_gm", "Mechanism (Senses improve vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobso_gm", "Mechanism (Observes objects and physical world vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorexpt_gm", "Mechanism (Actively experiments vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobsp_gm", "Mechanism (Observes people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorintp_gm", "Mechanism (Interacts with people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorteac_gm", "Mechanism (People explicitly teach vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
@@
         caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
+        digits = 2, align = c("lrrrrrrrrrrrrrr")) %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-##### Bodily sensation
-
-For capacities in the domain of _bodily sensation_, this analysis suggested that participants rated intrinsic mechanisms as more important drivers of development than extrinsic mechanisms; see also Figure 3, panels A-B (main text).
-
-```{r s3 mech ratings lmer bod}
-s3_lmer_bod <- lmer(response ~ dev_factor_cluster + 
-                      (1 + dev_factor_cluster | ResponseId) + 
-                      (1 | dev_factor) + 
+##### Biologically 'preprogrammed'
+
+For the mechanism "the child is biologically 'preprogrammed' to have this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_.
+See also Figure 3, first row (main text).
+
+```{r s3 mech ratings lmer prep}
+s3_lmer_prep <- lmer(response ~ factor +
+                       (1 | ResponseId) +
                        (1 | capacity),
@@
                 data = d3_mech_ratings %>%
-                  filter(factor == "Bodily sensation"))
-
-summary(s3_lmer_bod)
-# model_parameters(s3_lmer)
-```
-
-```{r tabs3lmerbod, include = T, message = F, warning = F}
-model_parameters(s3_lmer_bod, standardize = "refit") %>%
+                  filter(dev_factor == "preprogrammed"))
+
+summary(s3_lmer_prep)
+# model_parameters(s3_lmer_prep)
+```
+
+```{r tabs3lmerprep, include = T, message = F, warning = F}
+model_parameters(s3_lmer_prep, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
     TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("dev_factor_clusterext_gm", "Mechanism type (Extrinsic vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (bodily sensation): Fixed effects.",
+        caption = "Study 3, multilevel linear model results (biologically 'preprogrammed'): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Negative affect
-
-For capacities in the domain of _negative affect_, this analysis suggested that participants rated intrinsic and extrinsic mechanisms as equally important drivers of development; see also Figure 3, panels A-B (main text).
-
-```{r s3 mech ratings lmer neg}
-s3_lmer_neg <- lmer(response ~ dev_factor_cluster + 
-                      (1 + dev_factor_cluster | ResponseId) + 
-                      (1 | dev_factor) + 
+##### Experiences in the womb
+
+For the mechanism "the child has experiences in the womb that give them this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_.
+See also Figure 3, second row (main text).
+
+```{r s3 mech ratings lmer womb}
+s3_lmer_womb <- lmer(response ~ factor +
+                       (1 | ResponseId) +
                        (1 | capacity),
@@
                 data = d3_mech_ratings %>%
-                  filter(factor == "Negative affect"))
-
-summary(s3_lmer_neg)
-# model_parameters(s3_lmer)
-```
-
-```{r tabs3lmerneg, include = T, message = F, warning = F}
-model_parameters(s3_lmer_neg, standardize = "refit") %>%
+                  filter(dev_factor == "womb_experiences"))
+
+summary(s3_lmer_womb)
+# model_parameters(s3_lmer_womb)
+```
+
+```{r tabs3lmerwomb, include = T, message = F, warning = F}
+model_parameters(s3_lmer_womb, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (negative affect): Fixed effects.",
+        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Social connection
-
-For capacities in the domain of _social connection_, this analysis suggested that participants rated extrinsic mechanisms as more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).
-
-```{r s3 mech ratings lmer soc}
-s3_lmer_soc <- lmer(response ~ dev_factor_cluster + 
-                      (1 + dev_factor_cluster | ResponseId) + 
-                      (1 | dev_factor) + 
+##### Body grows and matures
+
+For the mechanism "the child’s body grows and matures (for example, muscles get stronger, child gets taller)," this analysis revealed no significant differences in importance ratings across domains.
+See also Figure 3, third row (main text).
+
+```{r s3 mech ratings lmer body}
+s3_lmer_body <- lmer(response ~ factor +
+                       (1 | ResponseId) +
                        (1 | capacity),
@@
                 data = d3_mech_ratings %>%
-                  filter(factor == "Social connection"))
-
-summary(s3_lmer_soc)
-# model_parameters(s3_lmer)
-```
-
-```{r tabs3lmersoc, include = T, message = F, warning = F}
-model_parameters(s3_lmer_soc, standardize = "refit") %>%
+                  filter(dev_factor == "body_grows"))
+
+summary(s3_lmer_body)
+# model_parameters(s3_lmer_body)
+```
+
+```{r tabs3lmerbody, include = T, message = F, warning = F}
+model_parameters(s3_lmer_body, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (social connection): Fixed effects.",
+        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Cognition and control
-
-For capacities in the domain of _cognition and control_, this analysis suggested that participants rated extrinsic mechanisms as much more important drivers of development than intrinsic mechanisms; see also Figure 3, panels A-B (main text).
-
-```{r s3 mech ratings lmer cog}
-s3_lmer_cog <- lmer(response ~ dev_factor_cluster + 
-                      (1 + dev_factor_cluster | ResponseId) + 
-                      (1 | dev_factor) + 
+##### Brain changes
+
+For the mechanism "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)," this analysis suggested that participants rated this as a particularly important driver of development in the domains of _social connection_ and _cognition and control_.
+See also Figure 3, fourth row (main text).
+
+```{r s3 mech ratings lmer brai}
+s3_lmer_brai <- lmer(response ~ factor +
+                       (1 | ResponseId) +
                        (1 | capacity),
@@
                 data = d3_mech_ratings %>%
-                  filter(factor == "Cognition and control"))
-
-summary(s3_lmer_cog)
-# model_parameters(s3_lmer)
-```
-
-```{r tabs3lmercog, include = T, message = F, warning = F}
-model_parameters(s3_lmer_cog, standardize = "refit") %>%
+                  filter(dev_factor == "brain_changes"))
+
+summary(s3_lmer_brai)
+# model_parameters(s3_lmer_brai)
+```
+
+```{r tabs3lmerbrai, include = T, message = F, warning = F}
+model_parameters(s3_lmer_brai, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (cognition and control): Fixed effects.",
+        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-```{r fig03a, fig.width = 4.5, fig.asp = 1.5}
-fig03a <- d3_mech_ratings %>%
-  mutate(dev_factor_cluster = case_when(
-    is.na(dev_factor_cluster) ~ "Other",
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC mechanisms",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC mechanisms"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC mechanisms", 
-                                           "EXTRINSIC mechanisms",
-                                           "Other")),
-    dev_factor_text = recode_factor(
-      dev_factor,
-      "preprogrammed" = "biologically ‘preprogrammed'",
-      "womb_experiences" = "experiences in the womb",
-      "body_grows" = "body grows and matures",
-      "brain_changes" = "brain changes",
-      "senses_improve" = "senses improve",
-      "observes_objects" = "observes objects and physical world",
-      "experiments" = "actively experiments",
-      "observes_people" = "observes people",
-      "interacts_people" = "interacts with people",
-      "people_teach" = "people explicitly teach"),
-    capacity = str_wrap(gsub("_", " ", capacity), 14)) %>%
-  ggplot(aes(x = reorder(str_wrap(dev_factor_text, 20), 
-                         as.numeric(dev_factor)), 
-             y = response, color = factor)) +
-  facet_grid(rows = vars(reorder(capacity, as.numeric(factor))),
-             cols = vars(dev_factor_cluster),
-             scales = "free", space = "free") +
-  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
-  geom_jitter(alpha = 0.6, size = 0.02) +
-  geom_pointrange(data = . %>%
-                    group_by(factor, capacity, 
-                             dev_factor_cluster, 
-                             dev_factor, dev_factor_text) %>%
-                    multi_boot_standard(col = "response") %>%
-                    ungroup(),
-                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "black", fatten = 2) +
-  scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism",
-       y = "Response (0 = not at all important, 6 = extremely important)",
-       color = "Domain") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-```
-
-```{r fig03b, fig.width = 1.5, fig.asp = 6.75/1.5}
-fig03b <- d3_mech_ratings %>%
-  # filter(!is.na(dev_factor_cluster)) %>%
-  filter(!is.na(dev_factor)) %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor == "brain_changes" ~ "brain changes",
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC", 
-                                           "EXTRINSIC",
-                                           "brain changes"))) %>%  
-  # participant-level means for each cluster, by capacity
-  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
-  summarise(score_a = mean(response, na.rm = T)) %>%
-  ungroup() %>%
-  # participant-level mean of means for each cluster, by domain
-  group_by(ResponseId, dev_factor_cluster, factor) %>%
-  summarise(score_b = mean(score_a, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(blank_var = "  ") %>%
-  ggplot(aes(x = reorder(str_pad(dev_factor_cluster,
-                                 width = 28, side = "left"),
-                         as.numeric(dev_factor_cluster)),
-             y = score_b, color = factor)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(toupper(factor), as.numeric(factor))),
-             scales = "free", space = "free") +
-  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
-  geom_point(alpha = 0.6, size = 0.02,
-             position = position_jitter(width = 0.2,
-                                        height = 0,
-                                        seed = 94305)) +
-  geom_path(data = . %>%
-              filter(dev_factor_cluster != "brain changes"),
-            aes(group = ResponseId),
-            alpha = 0.1, size = 0.02,
-            position = position_jitter(width = 0.2,
-                                       height = 0,
-                                       seed = 94305)) +
-  # group-level mean of means of means for each cluster, by domain
-  geom_pointrange(data = . %>%
-                    group_by(factor, dev_factor_cluster) %>%
-                    multi_boot_standard(col = "score_b") %>%
-                    ungroup(),
-                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "black", fatten = 2) +
-  scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism type",
-       y = "Mean response (0 = not at all important, 6 = extremely important)",
-       color = "Domain") +
-  guides(color = guide_none())
-  # guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# fig03b
-
-# jpg version (darker)
-fig03b_jpg <- d3_mech_ratings %>%
-  # filter(!is.na(dev_factor_cluster)) %>%
-  filter(!is.na(dev_factor)) %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor == "brain_changes" ~ "brain changes",
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC", 
-                                           "EXTRINSIC",
-                                           "brain changes"))) %>%  
-  # participant-level means for each cluster, by capacity
-  group_by(ResponseId, dev_factor_cluster, factor, capacity) %>%
-  summarise(score_a = mean(response, na.rm = T)) %>%
-  ungroup() %>%
-  # participant-level mean of means for each cluster, by domain
-  group_by(ResponseId, dev_factor_cluster, factor) %>%
-  summarise(score_b = mean(score_a, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(blank_var = "  ") %>%
-  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
-                                 width = 28, side = "left"),
-                         as.numeric(dev_factor_cluster)), 
-             y = score_b, color = factor)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(toupper(factor), as.numeric(factor))),
-             scales = "free", space = "free") +
-  geom_hline(yintercept = 3, lty = 2, color = "darkred") +
-  geom_point(alpha = 0.6, size = 0.02,
-             position = position_jitter(width = 0.2, 
-                                        height = 0, 
-                                        seed = 94305)) +
-  geom_path(data = . %>%
-              filter(dev_factor_cluster != "brain changes"),
-            aes(group = ResponseId), 
-            alpha = 1, size = 0.02,
-            position = position_jitter(width = 0.2, 
-                                       height = 0, 
-                                       seed = 94305)) +
-  # group-level mean of means of means for each cluster, by domain
-  geom_pointrange(data = . %>%
-                    group_by(factor, dev_factor_cluster) %>%
-                    multi_boot_standard(col = "score_b") %>%
-                    ungroup(),
-                  aes(y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "black", fatten = 2) +
-  scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(breaks = seq(0, 6, 3), minor_breaks = seq(0, 6, 1)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism type",
-       y = "Mean response (0 = not at all important, 6 = extremely important)",
-       color = "Domain") +
-  guides(color = guide_none())
-  # guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# fig03b_jpg
-```
+##### Senses improve
+
+For the mechanism "the child’s senses improve (for example, vision gets sharper, hearing improves)," this analysis revealed no significant differences in importance ratings across domains.
+See also Figure 3, fifth row (main text).
+
+```{r s3 mech ratings lmer sens}
+s3_lmer_sens <- lmer(response ~ factor +
+                       (1 | ResponseId) +
+                       (1 | capacity),
+                control = lmerControl(optimizer = "bobyqa"),
+                data = d3_mech_ratings %>%
+                  filter(dev_factor == "senses_improve"))
+
+summary(s3_lmer_sens)
+# model_parameters(s3_lmer_brai)
+```
+
+```{r tabs3lmersens, include = T, message = F, warning = F}
+model_parameters(s3_lmer_sens, standardize = "refit") %>%
+  filter(Effects == "fixed") %>%
+  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
+  mutate(Parameter = case_when(
+    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
+    TRUE ~ Parameter)) %>%
+  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
+  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
+  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
+  select(-starts_with("CI")) %>%
+  select(Parameter, Coefficient, `95% CI`, everything()) %>%
+  rename(df = df_error) %>%
+  kable("latex", booktabs = T, longtable = T,
+        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
+        digits = 2, align = c("lrrrrrr")) %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 8)
+```
+
+XXXX BOOKMARK
 

### 2024-12-19 paper/paper.Rmd
massive overhaul

@@
 Do they love me?
-As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.
+As in other domains of reasoning[@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.
 
@@
 What is the cognitive architecture underlying laypeople’s beliefs about the origins of the human mind?
-How do laypeople "carve up" the various sensations, experiences, and abilities that make up human mental life, and—most crucially from the perspective of caregiving—how do laypeople understand changes in mental life across early development?
+How do laypeople “carve up” the various sensations, experiences, and abilities that make up human mental life, and—most crucially from the perspective of caregiving—how do laypeople understand changes in mental life across early development?
 
-In this paper, we examine how US adults conceptualize the developing minds of infants and children by drawing on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of "the mind," broadly construed.
+In this paper, we examine how US adults conceptualize the developing minds of infants and children by drawing on techniques developed in studies of mind perception, in which researchers use large datasets and modern statistical methods to reveal conceptual representations of “the mind,” broadly construed.
 In a groundbreaking study, Gray et al.
-asked participants to compare the mental capacities of a range of humans, animals, technologies, and other entities, and argued that participants’ judgments revealed a fundamental distinction between "agency" (e.g., capacities for self-control, moral reasoning, memory, and planning) and "experience" (e.g., capacities for hunger, fear, pain, and pleasure) [@gray.etal2007].
+asked participants to compare the mental capacities of a range of humans, animals, technologies, and other entities, and argued that participants’ judgments revealed a fundamental distinction between “agency” (e.g., capacities for self-control, moral reasoning, memory, and planning) and “experience” (e.g., capacities for hunger, fear, pain, and pleasure) [@gray.etal2007].
 More recently, Weisman et al.
-used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a; see @malle2019 for a similar three-factor solution].
+used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: “body” (physiological sensations such as hunger and pain), “heart” (social-emotional abilities such as embarrassment and pride), and “mind” (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a; see @malle2019 for a similar three-factor solution].
 Such findings have inspired subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
@@
 In the current studies we set out to shed new light on this important and understudied aspect of mind perception: how laypeople reason about the development of human mental life.
-In three studies, we assessed US adults’ folk beliefs about children’s developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of "mental life," broadly construed.
+In three studies, we assessed US adults’ folk beliefs about children’s developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of “mental life,” broadly construed.
 We focused on development between birth and age five years—a time of particularly dramatic maturation in perceptual acuity, emotional experience, cognitive ability, executive function, social engagement, and many other domains.
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
+Methods, inclusion/exclusion criteria, and analyses marked as “preregistered” were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
 All studies were approved by [IRB information removed to preserve anonymity].
@@
 Our primary analysis was a preregistered exploratory factor analysis (EFA) of participants’ capacity ratings.
-This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children.
+This analysis allowed us to examine which capacities tend to “hang together” in participants’ assessments of the mental lives of infants and young children.
 For example, when a participant indicated that newborns are highly capable of feeling scared, what other capacities did they tend to attribute to newborns?
@@
 In our view, these cross-loadings were generally sensible.
-The item "feeling distressed", for instance, loaded roughly equally strongly on both bodily sensations and negative affect—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
-Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
+The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensation_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
+Likewise, "seeing" loaded equally strongly on both _bodily sensation_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
 
-As a check on our choice of labels for these factors, we turned to OpenAI’s Generative Pre-trained Transformer 3 (GPT-3) [@brown.etal2020], an autoregressive transformer-based language prediction model trained on an enormous corpus of English-language text drawn primarily from “crawls” of the Internet as well as English-language novels and the open-source encyclopedia Wikipedia.
-GPT-3 is capable of generating remarkably human-like text in response to questions and other prompts.
-GPT-3, like other generative language models, was developed under the mandate of predicting the continuation of natural language sequences: Most concretely, then, its “responses” should be understood to reflect a sequence of words that is likely to follow the prompt it has been provided.
+As a check on our choice of labels for these factors, we turned to OpenAI’s Generative Pre-trained Transformer [ChatGPT, version 4o; @openAI2024], an autoregressive transformer-based language prediction model trained on an enormous corpus of English-language text drawn primarily from “crawls” of the Internet as well as English-language novels and the open-source encyclopedia Wikipedia.
+Like other generative language models, ChatGPT was developed under the mandate of predicting the continuation of natural language sequences: Most concretely, then, its “responses” should be understood to reflect a sequence of words that is likely to follow the prompt it has been provided.
 In a more abstract sense, however, the content of these responses could be understood to represent the “common knowledge” embedded in the training data [for extended arguments relevant to this proposal, see @bhatia.richie2021; @lake.murphy2021; @petroni.etal2019].
-For example, if prompted with the questions “What do you get when you mix red and yellow?” or “What’s a good name for a vegetarian restaurant?,” GPT-3 will generate text like “When you mix red and yellow, you get orange” or “The Green Plate” (respectively).
+For example, if prompted with the questions “What do you get when you mix red and yellow?” or “What’s a good name for a vegetarian restaurant?,” ChatGPT will generate text like “When you mix red and yellow, you get orange” or “The Green Plate” (respectively).
 In continuing the language sequence, the model also provides novel content that reflects actual human knowledge, biases, associations, and intuitions.
 
-Using the openly available GPT-3 “playground” (https://beta.openai.com/playground), we provided a variety of prompts to the model to assess its “intuitions” about how to label the four categories of mental capacities suggested by the factor solution just described.
-One representative prompt read, “Name these four categories of mental capacities: Category 1 is […].
-Category 2 is […],” and so on, with the ellipses replaced by lists of all the items for which each factor (“Category”) was the dominant factor.
-The response generated by GPT-3 in this case was as follows: “Category 1: Executive functioning skills.
-Category 2: Social and emotional skills.
-Category 3: Physical needs and sensations.
-Category 4: Negative emotions.” In nearly every variation of our prompts, GPT-3’s labels for the factor we have labeled cognition and control included the phrase “executive function”; its labels for the factor we have labeled social connection always nearly always included the word “social” or “social-emotional”; its labels for the factor we have labeled bodily sensation nearly always included the words “sensations” (and often “physical needs” or “basic needs”); and its labels for the factor we have labeled negative affect nearly always included the phrase “negative emotion.” (See Supplemental Materials for the full text of these prompts and GPT-3’s responses.) The similarity.
-between our original labels (i.e.
-cognition and control, social connection, bodily sensations, and negative affect) and those generated by GPT-3 provide some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
+Using ChatGPT version 4o (https://chatgpt.com/), we provided a variety of prompts to the model to assess its “intuitions” about how to label the four categories of mental capacities suggested by the factor solution just described.
+One representative prompt began, “You're a statistician and a psychologist, and I'd like your help interpreting my exploratory factor analysis results,” followed by the EFA output taken directly from our analysis in R (containing the full list of factor loadings, as well as other summary characteristics of the EFA solution).
+The immediate response generated by ChatGPT included comments on model fit, factor structure, factor interpretability, factor contributions, chi-squared and BIC, as well as suggestions for “next steps”; under interpretability, it read, “MR1 [the factor we have referred to as _cognition and control_, although this label was never provided to the model] has high loadings on items related to planning, self-control, and goal-oriented behaviors.
+It could represent Self-Regulation or Executive Function.
+MR3 [what we have called _social connection_] includes items related to emotions such as feeling excited, happy, or loved.
+This could reflect Positive Emotional Experiences.
+MR2 [*bodily sensation*] has high loadings on items like feeling hungry, tired, and uncomfortable.
+This factor might capture Physical States or Needs.
+MR4 [*negative affect*] captures items like feeling helpless, frustrated, and annoyed.
+It may reflect Negative Emotional Responses or Distress.” When asked to tailor labels for an audience of cognitive scientists and clinical psychologists, the model suggested names like “Self-Regulation and Cognitive Control,” “Positive Affect and Social Emotions,” “Physiological Awareness and Basic Needs,” and “Negative Affect and Emotional Distress.” (See https://chatgpt.com/share/675a0c61-d534-8006-a978-b731bc997572 for the full text of these prompts and ChatGPT’s responses; OpenAI, 2024.) The similarity between our original labels and those generated by ChatGPT provides some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
 Nonetheless, we caution the reader to treat these labels as interpretations of empirical results, rather than empirical results themselves.
@@
 
-One limitation of this fixed-order design is that it makes it difficult to assess the stability of participants’ assessments of the fine-grained differences between specific points in development.
-See Supplemental Materials for a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (i.e., newborns, 9-month-olds, and 5-year-olds), which provides some sense of the stability of participants’ representations of these particular target ages.
-
 ## Results
@@
 (See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.’s (2017) factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
-Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings (≥ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings ($\geq$ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
 Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
@@
 ```{r s2 gam results, include = F}
-s2_gam_ptab <- summary(s2_results$gam$gam)$p.table
-s2_gam_stab <- summary(s2_results$gam$gam)$s.table
+s2_gam_ptab <- summary(s2_results$gam)$p.table
+s2_gam_stab <- summary(s2_results$gam)$s.table
+s2_gam_parameters <- parameters(s2_results$gam)
 ```
 
-Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
-On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported smaller increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-At the other extreme, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
+On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically and non-linearly over the target age range--that is, including a smoothing term for target age (analogous to a slope in a linear regression) significantly reduced the deviance of the model ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`); and the fitted smooth had moderate non-linear complexity (estimated degrees of freedom $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(df) %>% round_x(., 2)`).
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`).
+In the domain of _negative affect_, participants attributed even greater capacities to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`) and smaller increases over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`).
+At the other extreme, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and the smallest increase increase in capacities over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(df) %>% round_x(., 2)`).
 
-Visual inspection of Figure 2, Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
+Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape these perceived developmental trajectories from the bottom up, without specifying in advance the shape of the curve (but see Supplemental Materials for traditional logistic regressions).
+One consequence of this analysis choice is the model output does not include formal statistical tests of differences in perceived trajectories across domains—but visual inspection of Figure 2, Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
 In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
 Participants perceived development in the domains that we have labeled _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
-In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.
+In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold at a relatively steadier rate across the full age range.
 
@@
 For example, if participants believe that development in the domain of _bodily sensation_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed.
-[See @berent.etal2019 for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
+[See @berent.etal2019, for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
 We explore these possibilities in Study 3.
@@
 ```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life among US adults (Studies 2-3).
-Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our multilevel generalized additive models.
 In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
@@
 On each trial, participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for the following 10 developmental mechanisms: “the child is biologically ‘preprogrammed’ to have this ability”; “the child has experiences in the womb that give them this ability”; “the child’s body grows and matures (for example, muscles get stronger, child gets taller)”; “the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)”; “the child’s senses improve (for example, vision gets sharper, hearing improves)”; “the child observes the objects and the physical world around him or her”; “the child observes the people around him or her”; “the child interacts with the people around him or her”; “people explicitly teach the child how to do this”; “the child actively experiments with how to do this.” These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for the following 10 developmental mechanisms in the following (fixed) order: “the child is biologically ‘preprogrammed’ to have this ability”; “the child has experiences in the womb that give them this ability”; “the child’s body grows and matures (for example, muscles get stronger, child gets taller)”; “the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)”; “the child’s senses improve (for example, vision gets sharper, hearing improves)”; “the child observes the objects and the physical world around him or her”; “the child observes the people around him or her”; “the child interacts with the people around him or her”; “people explicitly teach the child how to do this”; “the child actively experiments with how to do this.” This order reflects our rough sense of what might be considered the most innate or biological mechanisms of development, to what might be considered the most learned or social.
 Participants were also asked to choose among these 10 mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
@@
 ```{r s3 gam results, include = F}
-s3_gam_ptab <- summary(s3_results$gam$gam)$p.table
-s3_gam_stab <- summary(s3_results$gam$gam)$s.table
+s3_gam_ptab <- summary(s3_results$gam)$p.table
+s3_gam_stab <- summary(s3_results$gam)$s.table
+s3_gam_parameters <- parameters(s3_results$gam)
 ```
@@
 This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure 2, Panel B.
-As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain that we have labeled _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
-Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`).
+Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`); in Study 3, as in Study 2, participants reported substantial increases in the domain that we have labeled _social connection_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`) and relatively small increases over the target age range in the domain of _negative affect_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p), 3)))`).
+Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _Social connection_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and small increases in capacities for _bodily sensation_ over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p)  < 0.001, "< 0.001", paste("=", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`).
 
-Visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
+Again, we note that this modeling approach did not include formal statistical tests of differences in perceived trajectories across domains—but visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
 
@@
 We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-(For in-depth investigations of laypeople’s intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.)
+[For in-depth investigations of laypeople’s intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.]
 
-[XXXX CUT We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.]
+We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.
 
-[XXXX CUT A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials), which aligned nearly exactly with our _a priori_ ordering of these mechanisms from most "innate" or "biological" to most "learned" or "social" (see Study 3 preregistration).
-First, there were what we will call _intrinsic mechanisms_: mechanisms rooted in innate predispositions or biological maturational processes, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
-Participants clearly distinguished these intrinsic mechanisms from what we will call _extrinsic mechanisms_: mechanisms rooted in observations of and experiences in the world, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
-One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure 3).]
+Responses to questions about developmental mechanisms are visualized in Figure 3.
+
+```{r s3 mechanism choice summary stats, include = F}
+s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions by mechanism
+s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b # proportions by domain and mechanism
+s3_mech_choice_ss_c <- s3_results$mech_choice_ss_c # proportions by domain, capacity, and mechanism
+
+s3_mech_choice_modes <- s3_results$mech_choice_modes
+```
+
+In terms of selections of the “most important” mechanism driving the development of these capacities between 0-5 years, two explanations—biological preprogramming and brain changes—accounted for most of participants’ selections.
+Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3.
+(See also Supplemental Materials for a multinomial regression comparing the selection of most important mechanism across capacities.)
+
+The explanation that “the child is biologically ‘preprogrammed’ to have this ability” was a modal response for `r s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed") %>% nrow()` of the 8 capacities presented in this study, including all of the capacities chosen to represent the domains of _bodily sensation_ and _negative affect_, as well as one of the two capacities chosen to represent _social connection_.
+Consensus on this selection was particularly pronounced for capacities for hunger (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("hung", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), pain (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("pain", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), and distress (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("distress", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants).
+
+Meanwhile, the explanation that “the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)” was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including helplessness (in the domain of _negative affect_) and social learning (_social connection_), as well as emotional control and reasoning things (both in the domain of _cognition and control_).
+However, consensus about this selection was much lower (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(-1, prop) %>% pull(prop) %>% round(., 2))*100`-`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(1, prop) %>% pull(prop) %>% round(., 2))*100`% of participants across capacities).
+Instead, these capacities were characterized by a more diverse selection of mechanisms, including mechanisms that are not as directly tied to biology: For example, when considering what drives the development of a capacity to learn from other people, roughly equal numbers of participants selected brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), observations of the social world (`r (s3_mech_choice_ss_c %>% filter(grepl("observes people", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), and interactions with others (`r (s3_mech_choice_ss_c %>% filter(grepl("interacts", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%); and when considering the capacity for controlling one’s emotions, participants were nearly as likely to select explicit teaching (`r (s3_mech_choice_ss_c %>% filter(grepl("teach", dev_factor_text), grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%) as the most important developmental mechanism as they were to select brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%).
+
+Independent ratings of the importance of each developmental mechanism present a more nuanced—but largely consistent—picture of intuitive theories of development across these domains.
+See Figure 3, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.
 
 ```{r s3 mechanism ratings summary stats, include = F}
-s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means overall
+s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means by mechanism
 s3_mech_rat_ss_b <- s3_results$mech_rat_ss_b # means by domain
-s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # differences by domain
+s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # means by domain and mechanism
+s3_mech_rat_ss_d <- s3_results$mech_rat_ss_d # means by domain, capacity, and mechanism
 ```
@@
 
-[XXXX CUT A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).]
+For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child’s body grows and matures (for example, muscles get stronger, child gets taller)" (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as very unimportant for capacities in this domain, with particularly low ratings for "people explicitly teach the child how to do this” (median score: `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
 
-[XXXX CUT For capacities in the domain of _bodily sensation_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
-In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`).
-In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
-See Figure 3, panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.]
+For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+However, these two biological explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); “the child observes objects and the physical world” (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); “the child observes other people” (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant for capacities in this domain.
 
-```{r s3 mechanism choice summary stats, include = F}
-# s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions overall
-s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b %>% # proportions by domain
-  filter(!is.na(dev_factor_cluster)) %>%
-  group_by(factor) %>%
-  mutate(prop2 = n/sum(n)) %>%
-  ungroup()
-```
+For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and “the child observes other people” (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+These were closely followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability” (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
-```{r s3 glmer results, include = F}
-s3_glmer_tab <- model_parameters(s3_results$glmer, standardize = "refit")
-s3_glmer_bod_tab <- model_parameters(s3_results$glmer_bod) # no standardization
-s3_glmer_neg_tab <- model_parameters(s3_results$glmer_neg) # no standardization
-s3_glmer_soc_tab <- model_parameters(s3_results$glmer_soc) # no standardization
-s3_glmer_cog_tab <- model_parameters(s3_results$glmer_cog) # no standardization
-```
+Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row), many developmental mechanisms were rated as highly important.
+The highest-rated mechanisms were "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and “the child observes other people” (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and “the child actively experiments with how to do this” (median score: `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability” (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
-[XXXX CUT Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure 3, Panel C.
-Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensation_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensation", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
-On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
-Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).]
-
-[XXXX CUT Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
-Capacities for _bodily sensation_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
-Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world.
-Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).]
-
-[XXXX INSERT NEW ANALYSES]
-
-```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and each of the capacities within each domain; and Panel C shows the percentage of trials on which participants selected each developmental mechanism as the ‘most important’ driver of development for each capacity within each domain.
-Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panel A is intended to aid visual comparison across mechanisms."}
+```{r fig03, fig.cap="Figure 3: Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
+Small, lighter points represent individual participants’ ratings of how important each developmental mechanism is in the development of each capacity within a domain (top row: bodily sensation; second row: negative affect; third row: social connection; bottom row: cognition and control).
+Larger black and red points correspond to mean importance ratings across the sample, and error bars are bootstrapped 95% confidence intervals.
+On the right side of each panel are the percentages of participants who selected each developmental mechanism as the ‘most important’ driver of development for that capacity, with modal selections (including items within 10% of the mode) in red."}
 knitr::include_graphics("../outputs/fig03.pdf")
@@
 
-## Relationships between beliefs about developmental mechanisms and perceived developmental trajectories
-
-As a final exploration of participants’ representations of the development of mental life, we explored the relationships between beliefs about what mechanisms drive the development of the capacities included in this study and beliefs about the extent to which these capacities are present at different points in infancy and early childhood.
-We consider these exploratory analyses to offer some insight into the coherence of participants’ intuitive theories about the development of mental life.
-
-These relationships are visualized in Figure 4; see Supplemental Materials for a breakdown by individual capacity (e.g., “feeling pain,” “getting hungry,” and so forth), and for separate regression analyses for each developmental mechanism, taking into account differences across target ages and capacities, as well as individual differences across participants.
-
-```{r fig04, fig.cap="Relationships between US adults’ ratings of the importance of various developmental mechanisms and capacity ratings, collapsing across capacities (Study 3); see Supplemental Materials for a breakdown of these relationships by individual capacity.
-Light black points represent individual participants’ responses, with each participant contributing one datapoint for each capacity-mechanism pair (i.e., 80 datapoints per participant).
-Dark colorful lines correspond to smoothed conditional means (via GAMs), with shaded areas representing 95% confidence intervals.
-The dotted red line at the midpoint of the response scale is intended to aid visual comparison across target ages."}
-knitr::include_graphics("../outputs/fig04.pdf")
-```
-
-Our primary take-away from this analysis is that the nature of these relationships between mechanism and capacity ratings varied substantially across mechanisms.
-This is easiest to visualize at the youngest target age, newborns (Fig.
-4, first panel), where we observed three basic kinds of relationships.
-
-[XXXX INSERT NEW ANALYSES]
-
-In nearly all cases, the relationships just described between mechanism and capacity ratings were increasingly subtle over the target age range; this is readily apparent through visual inspection of Fig.
-4 (see also Supplemental Materials for estimates of interactions between mechanism rating and target age for each developmental mechanism).
-This is consistent with the fact that, across the target age range, mean capacity ratings increased, approaching the ceiling of our response scale, and variability across participants decreased—leaving less room to detect potential relationships with beliefs about developmental mechanisms.
-Put another way, by the older end of our target age range, participants had largely converged on an understanding that children were nearly fully capable of all of the capacities included in this study, regardless of what mechanisms had driven the development of these capacities.
-
-Taken together, these results provide some evidence for the existence of coherent intuitive theories of the development of mental life among US adults’: Individual differences in participants’ beliefs about the mechanisms that drive the development of various aspects of mental life were coherently related to their beliefs about how these aspects of mental life develop over infancy and early childhood (with the slight exception, perhaps, of beliefs about the influence of the child’s body growing and the child’s senses improving, as described above).
-To our eyes, these findings also hint at an intuitive distinction between developmental mechanisms that exert their influence during fetal development prior to birth (namely, biological “preprogramming” and experiences in the womb; the first pattern described above) vs.
-mechanisms that depend on the child observing and interacting with the world outside of the womb after birth (including various forms of observation, experimentation, and social interaction; the second pattern described above).
-We consider this distinction and its associated patterns of relationships to be intuitively sensical and reasonably closely aligned with scientific theories of fetal and neonatal development: To the extent that a capacity can emerge prior to birth, we would expect to observe it in the newborn child; while to the extent to that a capacity depends on experience in the outside world, we would expect not to observe it in the newborn child who lacks those experiences.
-Much like social scientists, different participants held different specific beliefs about which of these mechanisms were most relevant for which of the capacities included in this study, but they seemed to share a coherent understanding—an intuitive theory—of how mechanisms and capacity attributions are related in the abstract.
+In sum, we would characterize participants’ intuitive theories as follows.
+For capacities in the domain that we have called _bodily sensation_, there was broad consensus across participants that development between ages 0-5 years is driven almost exclusively by biological forces, particularly some form of biological “preprogramming.” For all other capacities, participants viewed development as the result of a combination of biological forces (including “preprogramming”) and experience in the physical and social world.
+In the domain that we have called _negative affect_, responses suggested that passive observation of the world might be considered sufficient to drive early development.
+In contrast, in the domains that we have called _social connection_ and _cognition and control_ there were some suggestions that a child must interact with the world in order to develop (for example, via social exchanges with other people or by conducting their own “experiments”).
 
@@
 We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019] [@berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019] [@berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by driven primarily by observation of and interactions with the physical and social world.
 
-Beliefs about the development of the more social-emotional aspects of mental life—what we have called *negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
+Beliefs about the development of the more social-emotional aspects of mental life—what we have called _negative affect_ (e.g., distress, frustration) and _social connection_ (e.g., happiness, love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
 In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree from birth [consistent with recent findings on the perceived "innateness" of emotions, @berent.etal2020] but to continue developing rapidly over the first two years of life.
-Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
-We note that attributions of what we have called _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
+Likewise, participants reported that development in these capacities was driven by a combination of biological forces (including “preprogramming”) and experience in the physical and social world.
+Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
+We note that attributions of what we have labeled _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
 This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
@@
 the degree to which certain capacities shape and are shaped by firsthand experiences of negative valence.
-Based on the findings of Studies 2 and 3, we further propose that social connection and negative affect emerged as distinct factors not only because they demarcate different aspects of mental life, but also because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
+Based on the findings of Studies 2 and 3, we further propose that _social connection_ and _negative affect_ emerged as distinct factors not only because they demarcate different aspects of mental life, but also because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
 

### 2024-12-19 supplement/supplement-main.Rmd
massive overhaul

@@
 author: "[authors removed for anonymous review]"
-date: "October 16, 2021"
+date: "2024-12-17"
 output:
@@
    - \usepackage{float}
+   - \usepackage{pdflscape}
 tables: yes
@@
 # do you want to resave the plots?
-# resave_plots <- T # uncomment if yes
-resave_plots <- F # uncomment if no
+resave_plots <- T # uncomment if yes
+# resave_plots <- F # uncomment if no
 ```
@@
 library(tidyverse)
+library(rsq)
+library(ggnewscale)
 ```
@@
 # suppress warnings and messages because dplyr is verbose
-suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", 
-                                         chdir = TRUE)))
-suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", 
-                                         chdir = TRUE)))
-suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", 
-                                         chdir = TRUE)))
+suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", chdir = TRUE)))
+suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", chdir = TRUE)))
+suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", chdir = TRUE)))
 ```
@@
 
-To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
-Attempting to model random slopes for domain or for target age resulted in model convergence problems.
-Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution.
+To test these hypotheses, we conducted a multilevel logistic regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gam(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
+Attempting to model random slopes via generalized additive mixed models for domain or for target age resulted in pathological models (e.g., introducing systematic bias in predicted responses).
 Domain was dummy-coded with _cognition and control_ as the baseline.
@@
 However, we now consider it misguided to model participants' responses using gaussian distribution, because—both in principle and in our empirical dataset—capacity ratings behaved asymptotically, plateauing near the ceiling of the scale (100, labeled "completely capable") at some point in development.
-The approach described here—using the beta distribution—is a far more accurate representation of these responses.
+The approach described here—using the binomial distribution—is a far more accurate representation of these responses.
 Using generalized additive models via the "mgcv" package for R [@wood2017] allowed us to fine-tune the shape of these perceived developmental trajectories via spline-based smoothing (analogous to fitting polynomial terms in the context of linear regression, but without specifying in advance the order of the polynomials included in the model).
@@
 
-Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
+Following Study 2, to test these hypotheses we conducted a multilevel logistic regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gam(responses ~ s(target age in years, by = domain) + domain + s(subject ID, bs = "re") + s(capacity, bs = "re")_.
 Again, attempting to model random slopes for domain or for target age resulted in model convergence problems.
@@
 
-(We note that, in contrast to Study 2, in Study 3 we did preregister this analysis, although we preregistered a linear regression rather than a beta regression via generalized additive model; see extended notes on our choice of this analysis approach under Study 2.)
+(We note that, in contrast to Study 2, in Study 3 we did preregister this analysis, although we preregistered a linear regression rather than a logistic regression via generalized additive model; see extended notes on our choice of this analysis approach under Study 2.)
 
@@
 Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*).
-We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs.
-intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_.
-We also conducted separate, analogous regression analyses for each domain separately.
-In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
-(Note that these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see main text.)
+We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto developmental mechanism, domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge.
+Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism * domain + (1 + mechanism + domain | participant) + (1 | mechanism) + (1 | capacity)_.
+We also conducted separate, analogous regression analyses for each mechanism separately.
+In all of these analyses, mechanism and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains.
 
@@
 ```{r s1 efa parallel analysis}
-s1_efa_par <- fa(d1_all, 
+s1_efa_par <- fa(
+  d1_all, 
   nfactors = s1_parallel$nfact, 
@@
 ```{r tabs1efaparload, include = T, warning = F, message = F}
-tabs1efaparload <- model_parameters(s1_efa_par, sort = T) %>% 
+tabs1efaparload <- parameters(s1_efa_par, sort = T) %>% 
   data.frame() %>% 
@@
   mutate(Capacity = gsub("_", " ", Capacity)) %>%
-  mutate_at(vars(starts_with("MR")),
-            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
+  mutate(across(
+    starts_with("MR"), 
+    ~ ifelse(. >= 0.6, TRUE, FALSE), 
+    .names = "{.col}_bold"
+  )) %>%
   rename(`Cog. Ctrl.` = MR1,
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 1, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
          `Social connection` = MR3,
-         `bodily sensation` = MR2,
+         `Bodily sensation` = MR2,
          `Negative affect` = MR4) %>%
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, factor solution suggested by parallel analysis: Variance accounted for.") %>%
+        caption = "\\text{Study 1, factor solution suggested by parallel analysis: Variance accounted for.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-```{r fig01 code, fig.width = 4.5, fig.asp = 1.2}
+```{r fig01 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s1_efa_par, 
@@
 ```{r tabs1efabicload, include = T, warning = F, message = F}
-tabs1efabicload <- model_parameters(s1_efa_bic, sort = T) %>% 
+tabs1efabicload <- parameters(s1_efa_bic, sort = T) %>% 
   data.frame() %>% 
@@
   mutate(Capacity = gsub("_", " ", Capacity)) %>%
-  mutate_at(vars(starts_with("MR")),
-            funs("bold" = ifelse(. >= 0.6, T, F)))
+  mutate(across(
+    starts_with("MR"), 
+    ~ ifelse(. >= 0.6, TRUE, FALSE), 
+    .names = "{.col}_bold"
+  ))
 
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 1, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, factor solution suggested by minimizing BIC: Variance accounted for.") %>%
+        caption = "\\text{Study 1, factor solution suggested by minimizing BIC: Variance accounted for.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-```{r figS01 code, fig.width = 4.5, fig.asp = 1.2}
+```{r figS01 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s1_efa_bic)
@@
 ```{r tabs1efawdmload, include = T, warning = F, message = F}
-tabs1efawdmload <- model_parameters(s1_efa_wdm, sort = T) %>% 
+tabs1efawdmload <- parameters(s1_efa_wdm, sort = T) %>% 
   data.frame() %>% 
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
 
-```{r figS02 code, fig.width = 4.5, fig.asp = 1.2}
+```{r figS02 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s1_efa_wdm)
@@
 ```{r tabs1efavarimaxload, include = T, warning = F, message = F}
-tabs1efavarimaxload <- model_parameters(s1_efa_4_varimax, sort = T) %>% 
+tabs1efavarimaxload <- parameters(s1_efa_4_varimax, sort = T) %>% 
   data.frame() %>% 
@@
   mutate(Capacity = gsub("_", " ", Capacity)) %>%
-  mutate_at(vars(starts_with("MR")),
-            funs("bold" = ifelse(. >= 0.6, T, F)))
+  mutate(Capacity = gsub("_", " ", Capacity)) %>%
+  mutate(across(
+    starts_with("MR"), 
+    ~ ifelse(. >= 0.6, TRUE, FALSE), 
+    .names = "{.col}_bold"
+  ))
 
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, four-factor solution after varimax rotation: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 1, four-factor solution after varimax rotation: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
          `Social connection` = MR1,
-         `bodily sensation` = MR2,
+         `Bodily sensation` = MR2,
          `Negative affect` = MR4) %>%
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 1, four-factor solution after varimax rotation: Variance accounted for.") %>%
+        caption = "\\text{Study 1, four-factor solution after varimax rotation: Variance accounted for.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
   group_by(capacity) %>%
-  top_n(1, abs(loading)) %>%
+  top_n(1, loading) %>% #alternatively, could do abs(loading) if there were strong negative loadings
   ungroup() %>%
-  mutate(factor = recode_factor(factor,
+  mutate(factor = recode_factor(
+    factor,
     "MR2" = "Bodily sensation",
@@
   separate(ResponseId_target, c("ResponseId", "target")) %>%
-  mutate(target_year = recode(target,
+  mutate(target_year = recode(
+    target,
     target00mo = 0, # newborns
-                              target0Xmo = 3/365, # 3 days
-                              target01mo = 1/12, # 1 month
-                              target02mo = 2/12, 
-                              target04mo = 4/12, 
-                              target06mo = 6/12, 
-                              target09mo = 9/12,
-                              target12mo = 12/12,
-                              target18mo = 18/12,
-                              target24mo = 24/12,
-                              target36mo = 36/12,
-                              target48mo = 48/12,
-                              target60mo = 60/12)) %>%
+    target09mo = 9/12, # 9 months
+    target60mo = 60/12) # 5 years
+  ) %>%
   gather(capacity, response, -ResponseId, -starts_with("target")) %>%
@@
             sd = sd(response, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(target_year, factor)
+  ungroup()
 
 d1_cap_ratings_sum %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
+  arrange(target_year, factor) %>%
+  left_join(d1_cap_ratings %>% distinct(target, target_year)) %>%
+  select(-target_year) %>%
+  select(target, factor, everything()) %>%
+  mutate(target = gsub("target", "", target),
+         target = gsub("mo", " months", target),
+         target = gsub("00 months", "newborn", target),
+         target = gsub("^0", "", target)) %>%
+  rename(`Target age` = target,
+         `Domain` = factor) %>%
+  kbl(digits = 2) %>%
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
 ```
@@
 ```{r s1 gam dataset}
-d1_gam <- d1_cap_ratings %>%
-  # implement correction for beta distribution
-  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
-                              response/100 > 0.995 ~ 0.995,
-                              TRUE ~ response/100))
-
-contrasts(d1_gam$factor) <- cbind(bod_cog = c(1, 0, 0, 0),
+d1_gam <- d1_cap_ratings
+
+contrasts(d1_gam$factor) <- cbind(
+  bod_cog = c(1, 0, 0, 0),
   neg_cog = c(0, 1, 0, 0),
@@
 
-```{r figS03 code, fig.width = 4, fig.asp = 0.5}
+```{r figS03 code, fig.width = 8, fig.asp = 0.5}
 d1_gam %>%
@@
             alpha = 0.2, size = 0.02) +
-  geom_path(data = . %>%
+  geom_path(
+    data = . %>%
       group_by(factor, target_year) %>%
@@
     color = "black", lty = 2) +
-            # color = "#160072",
-  geom_pointrange(data = . %>%
+  geom_pointrange(
+    data = . %>%
       group_by(factor, target_year) %>%
@@
     color = "black",
-                  # color = "#160072",
     fatten = 1) +
   scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(breaks = seq(0, 1, 0.25),
+  scale_y_continuous(breaks = seq(0, 100, 25),
                      labels = seq(0, 100, 25)) +
@@
 # save numerical results
-s1_results <- list(demo = d1_demo,
+s1_results <- list(
+  demo = d1_demo,
   efa = s1_efa_par,
@@
 ```{r tabs2efaparload, include = T, warning = F, message = F}
-tabs2efaparload <- model_parameters(s2_efa_par, sort = T) %>% 
+tabs2efaparload <- parameters(s2_efa_par, sort = T) %>% 
   data.frame() %>% 
@@
   mutate(Capacity = gsub("_", " ", Capacity)) %>%
-  mutate_at(vars(starts_with("MR")),
-            funs("bold" = ifelse(. >= 0.6, T, F))) %>%
+  mutate(Capacity = gsub("_", " ", Capacity)) %>%
+  mutate(across(
+    starts_with("MR"), 
+    ~ ifelse(. >= 0.6, TRUE, FALSE), 
+    .names = "{.col}_bold"
+  )) %>%
   rename(`Neg. Afft.` = MR1,
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 2, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 2, factor solution suggested by parallel analysis: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
   rename(`Negative affect` = MR1,
-         `bodily sensation` = MR3,
+         `Bodily sensation` = MR3,
          `Cognition and control` = MR2,
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 2, factor solution suggested by parallel analysis: Variance accounted for.") %>%
+        caption = "\\text{Study 2, factor solution suggested by parallel analysis: Variance accounted for.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-```{r figS04 code, fig.width = 4.5, fig.asp = 0.5}
+```{r figS04 code, fig.width = 9, fig.asp = 0.5}
 heatmap_fun(s2_efa_par, 
@@
 ```{r tabs2efabicload, include = T, warning = F, message = F}
-tabs2efabicload <- model_parameters(s2_efa_bic, sort = T) %>% 
+tabs2efabicload <- parameters(s2_efa_bic, sort = T) %>% 
   data.frame() %>% 
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 2, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.") %>%
+        caption = "\\text{Study 2, factor solution suggested by minimizing BIC: Factor loadings, complexity, and uniqueness.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "Study 2, factor solution suggested by minimizing BIC: Variance accounted for.") %>%
+        caption = "\\text{Study 2, factor solution suggested by minimizing BIC: Variance accounted for.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-```{r figS05 code, fig.width = 4.5, fig.asp = 1.2}
+```{r figS05 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s2_efa_bic)
@@
 
-To test these hypotheses, we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
-Attempting to model random slopes for domain or for target age resulted in model convergence problems.
-Responses were rescaled to range from 0.005 to 0.995 in order to satisfy the constraints of the beta distribution.
+To test these hypotheses, we conducted a multilevel logistic regression via a generalized additive model, regressing item-level responses onto the domain (i.e., which of the four "factors" this capacity was selected to represented) and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gam(response ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
+Attempting to model random slopes for domain or for target age resulted in pathological models.
 Domain was dummy-coded with _cognition and control_ as the baseline.
@@
   gather(factor, loading, -capacity) %>%
-  group_by(factor) %>%
-  top_n(5, loading) %>%
+  group_by(capacity) %>%
+  top_n(1, loading) %>%
   ungroup() %>%
-  mutate(factor = recode_factor(factor,
+  mutate(factor = recode_factor(
+    factor,
     "MR3" = "Bodily sensation",
@@
   separate(ResponseId_target, c("ResponseId", "target")) %>%
-  mutate(target_year = recode(target,
+  mutate(target_year = recode(
+    target,
     target00mo = 0, # newborns
-                              target0Xmo = 3/365, # 3 days
+    target0Xmo = 4/365, # 4 days
     target01mo = 1/12, # 1 month
@@
             sd = sd(response, na.rm = T)) %>%
-  ungroup() %>%
-  arrange(target_year, factor)
+  ungroup()
 
 d2_cap_ratings_sum %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
+  arrange(target_year, factor) %>%
+  left_join(d2_cap_ratings %>% distinct(target, target_year)) %>%
+  select(-target_year) %>%
+  select(target, factor, everything()) %>%
+  mutate(target = gsub("target", "", target),
+         target = gsub("mo", " months", target),
+         target = gsub("00 months", "newborn", target),
+         target = gsub("0X months", "4 days", target),
+         target = gsub("^0", "", target),
+         target = gsub("1 months", "1 month", target)) %>%
+  rename(`Target age` = target,
+         `Domain` = factor) %>%
+  kbl(digits = 2) %>%
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
 ```
@@
 d2_gam <- d2_cap_ratings %>%
-  # implement correction for beta distribution
-  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
-                              response/100 > 0.995 ~ 0.995,
-                              TRUE ~ response/100))
+  # implement rescaling for logistic regression
+  mutate(response = response/100) %>%
+  mutate(capacity = factor(capacity), 
+         ResponseId = factor(ResponseId))
 
@@
 if (!file.exists("../outputs/s2_gam.RDS")) {
-  # takes ~20 minutes to run
-  s2_gam <- gamm(response ~ s(target_year, by = factor) + factor, 
-                 random = list(ResponseId = ~1,
-                               capacity = ~1),
+  # takes ~25 minutes to run
+  s2_gam <- gam(
+    response ~ 
+      # fixed effects
+      s(target_year, by = factor, k = 12) + factor
+    # random intercepts
+    + s(capacity, bs = "re") + s(ResponseId, bs = "re")
+    ,
     data = d2_gam,
-                 family = betar,
+    family = binomial,
     method = "REML",
@@
 
-summary(s2_gam$gam)
-# model_parameters(s2_gam$gam)
+# summary(s2_gam)
+# parameters(s2_gam)
+# check.gam(s2_gam)
 ```
@@
 ```{r tabs2gam}
-tabs2gam <- model_parameters(s2_gam$gam)
+tabs2gam <- parameters(s2_gam)
 ```
@@
   kable("latex", booktabs = T, longtable = T, 
-        caption = "Study 2, GAM results: Parametric coefficients (fixed effects).",
+        caption = "\\text{Study 2, GAM results: Parametric coefficients (fixed effects).}",
         digits = 2, align = c("lrrrrrrr")) %>%
@@
   mutate(Parameter = case_when(
-    grepl("Bod", Parameter) ~ "Target year: bodily sensation",
+    grepl("Bod", Parameter) ~ "Target year: Bodily sensation",
     grepl("Neg", Parameter) ~ "Target year: Negative affect",
     grepl("Soc", Parameter) ~ "Target year: Social connection",
-    grepl("Cog", Parameter) ~ "Target year: Cognition and control"),
+    grepl("Cog", Parameter) ~ "Target year: Cognition and control",
+    grepl("capacity", Parameter) ~ "Capacity (random effect)",
+    grepl("ResponseId", Parameter) ~ "Participant (random effect)"),
     p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
@@
   kable("latex", booktabs = T, longtable = T, 
-        caption = "Study 2, GAM results: Approximate significance of smooth terms.",
+        caption = "\\text{Study 2, GAM results: Approximate significance of smooth terms.}",
         digits = 2, align = c("lrrr")) %>%
@@
 d2_gam_r1_pred <- d2_gam %>%
-  # # ridiculous hacky stuff to avoid having to re-run the GAM to correct typo in "bodily sensationS"
-  # mutate(factor = as.character(factor),
-  #        factor = gsub("Bodily sensation$", "Bodily sensations", factor),
-  #        factor = factor(factor, levels = c("Bodily sensations",
-  #                                           "Negative affect",
-  #                                           "Social connection",
-  #                                           "Cognition and control"))) %>%
-  mutate(pred = predict.gam(s2_gam$gam, type = "response", 
-                            newdata = d2_gam)) %>% #%>%
-                              # mutate(factor = as.character(factor),
-                              #        factor = gsub("Bodily sensation$", 
-                              #                      "Bodily sensations", factor),
-                              #        factor = factor(factor, 
-                              #                        levels = c("Bodily sensations",
-                              #                                   "Negative affect",
-                              #                                   "Social connection",
-                              #                                   "Cognition and control"))))) %>%
-  # mutate(factor = as.character(factor),
-  #        factor = gsub("Bodily sensations", "Bodily sensation", factor),
-  #        factor = factor(factor, levels = c("Bodily sensation",
-  #                                           "Negative affect",
-  #                                           "Social connection",
-  #                                           "Cognition and control"))) %>%
+  mutate(pred = predict.gam(s2_gam, type = "response", newdata = d2_gam)) %>% 
   group_by(ResponseId, factor, target_year) %>%
@@
 
-```{r fig02a, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 2).
-Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
-d2_gam_r1_rsq <- round_x(summary(s2_gam$gam)$r.sq, 2)
-
-fig02a <- d2_gam_r1_pred %>%
+```{r fig02a_gam, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 2).
+Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model.", fig.width = 8, fig.asp = 0.5}
+d2_gam_r1_rsq <- round_x(summary(s2_gam)$r.sq, 2)
+
+fig02a_gam <- d2_gam_r1_pred %>%
   ggplot(aes(x = target_year, y = score, color = factor)) +
@@
   geom_path(aes(group = ResponseId),
-            # color = "#160072",
             alpha = 0.2, size = 0.02) +
@@
               fill = NA, size = 1, lty = 1) +
-  geom_pointrange(data = . %>%
+  geom_pointrange(
+    data = . %>%
       group_by(factor, target_year) %>%
@@
     color = "black",
-                  # color = "#160072",
     fatten = 1) +
@@
 # make jpg version (darker)
-fig02a_jpg <- d2_gam_r1_pred %>%
+fig02a_gam_jpg <- d2_gam_r1_pred %>%
   ggplot(aes(x = target_year, y = score, color = factor)) +
@@
   geom_path(aes(group = ResponseId),
-            # color = "#160072",
             alpha = 1, size = 0.02) +
@@
 
-# # save plot
-# if (resave_plots == T | !file.exists("../outputs/fig02a.pdf")) {
-#   ggsave("../outputs/fig02a.svg")
-#   ggsave("../outputs/fig02a.pdf")
-# }
+# save plot
+if (resave_plots == T | !file.exists("../outputs/fig02a_gam.pdf")) {
+  ggsave("../outputs/fig02a_gam.svg")
+  ggsave("../outputs/fig02a_gam.pdf")
+  ggsave("../outputs/fig02a_gam.jpg")
+}
 ```
@@
 # save numerical results
-s2_results <- list(demo = d2_demo,
+s2_results <- list(
+  demo = d2_demo,
   efa = s2_efa_par,
@@
 
-In the main text, we presented the results of a generalized additive model (GAM) predicting participants' capacity ratings as a function of target age, domain, and interactions between them; briefly described the dimensionality reduction analyses we used to group developmental mechanisms into two types ("intrinsic" and "extrinsic"); presented the results of a multilevel linear regression model predicting participants' ratings of developmental mechanisms as a function of mechanism type, domain, and an interaction between them; briefly mentioned additional models of each domain separately; and provided visualizations of participants' selections of the "most important" mechanism for each capacity, by domain.
+In the main text, we presented the results of a generalized additive model (GAM) predicting participants' capacity ratings as a function of target age, domain, and interactions between them; and briefly presented the results of a series of multilevel linear regression models predicting participants' ratings of developmental mechanisms as a function of domain; and provided visualizations of participants' selections of the "most important" mechanism for each capacity, by domain.
 Here, we present the full results of all of these models, as well as the results of a multilevel logistic regression model of the selection of "most important" mechanism.
@@
 
-Following Study 2, to test these hypotheses we conducted a multilevel beta regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
-Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gamm(responses ~ s(target age in years, by = domain) + domain, random = list(subject ID = ~1, capacity = ~1)_.
-Again, attempting to model random slopes for domain or for target age resulted in model convergence problems.
-Again, responses were rescaled to range from 0.005 to 0.995, and domain was dummy-coded with _cognition and control_ as the baseline.
+Following Study 2, to test these hypotheses we conducted a multilevel logistic regression via a generalized additive model, regressing item-level responses onto the domain and a spline-based smooth of the target age of the child fitted separately for each domain, including the maximal random effects structure that would allow the model to converge.
+Using the "mgcv" package for R [@wood2017], we specified this model as follows: _gam(responses ~ s(target age in years, by = domain) + domain + s(subject ID, bs = "re") + s(capacity, bs = "re")_.
+Again, attempting to model random slopes for domain or for target age resulted in pathological models.
+Again, domain was dummy-coded with _cognition and control_ as the baseline.
 The full results of this model are presented in Supplementary Tables \@ref(tab:tabs3gamfixed) and \@ref(tab:tabs3gamsmooth); see Figure 2, Panel B (main text) for a visualization of these perceived trajectories.
@@
   mutate(target_year = target_num/12) %>%
-  mutate(factor = recode_factor(domain,
+  mutate(factor = recode_factor(
+    domain,
     "BOD" = "Bodily sensation",
@@
 d3_cap_ratings_sum %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
+  arrange(target_year, factor) %>%
+  left_join(d3_cap_ratings %>% distinct(target, target_year)) %>%
+  select(-target_year) %>%
+  select(target, factor, everything()) %>%
+  mutate(target = gsub("target", "", target),
+         target = gsub("mo", " months", target),
+         target = gsub("00 months", "newborn", target),
+         target = gsub("0X months", "4 days", target),
+         target = gsub("^0", "", target),
+         target = gsub("1 months", "1 month", target)) %>%
+  rename(`Target age` = target,
+         `Domain` = factor) %>%
+  kbl(digits = 2) %>%
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
 ```
@@
 d3_gam <- d3_cap_ratings %>%
-  # implement correction for beta distribution
-  mutate(response = case_when(response/100 < 0.005 ~ 0.005,
-                              response/100 > 0.995 ~ 0.995,
-                              TRUE ~ response/100))
+  # implement rescaling for logistic regression
+  mutate(response = response/100) %>%
+  mutate(capacity = factor(capacity),
+         ResponseId = factor(ResponseId))
 
@@
 if (!file.exists("../outputs/s3_gam.RDS")) {
-  # takes ~5 minutes to run
-  s3_gam <- gamm(response ~ s(target_year, by = factor) + factor, 
-                 random = list(ResponseId = ~1,
-                               capacity = ~1),
+  # takes ~16 minutes to run
+  s3_gam <- gam(
+    response ~ 
+      # fixed effects
+      s(target_year, by = factor, k = 12) + factor
+    # random intercepts
+    + s(capacity, bs = "re") + s(ResponseId, bs = "re")
+    ,
     data = d3_gam,
-                 family = betar,
+    family = binomial,
     method = "REML",
@@
 
-summary(s3_gam$gam)
+# summary(s3_gam)
 ```
@@
 ```{r tabs3gam}
-tabs3gam <- model_parameters(s3_gam$gam)
+tabs3gam <- parameters(s3_gam)
 ```
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, GAM results: Parametric coefficients (fixed effects).",
+        caption = "\\text{Study 3, GAM results: Parametric coefficients (fixed effects).}",
         digits = 2, align = c("lrrrrrrr")) %>%
@@
   select(-c(Coefficient, SE, starts_with("CI"), df_error, Component)) %>%
-  mutate(Parameter = case_when(
+  mutate(
+    Parameter = case_when(
       grepl("Bod", Parameter) ~ "Target year: Bodily sensation",
@@
       grepl("Soc", Parameter) ~ "Target year: Social connection",
-    grepl("Cog", Parameter) ~ "Target year: Cognition and control"),
+      grepl("Cog", Parameter) ~ "Target year: Cognition and control",
+      grepl("capacity", Parameter) ~ "Capacity (random effect)",
+      grepl("ResponseId", Parameter) ~ "Participant (random effect)"),
     p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
@@
   kable("latex", booktabs = T, longtable = T, 
-        caption = "Study 3, GAM results: Approximate significance of smooth terms.",
+        caption = "\\text{Study 3, GAM results: Approximate significance of smooth terms.}",
         digits = 2, align = c("lrrr")) %>%
@@
 d3_gam_r1_pred <- d3_gam %>%
-  # ridiculous hacky stuff to avoid having to re-run the GAM to correct typo in "bodily sensationS"
-  # mutate(factor = as.character(factor),
-  #        factor = gsub("Bodily sensation$", "Bodily sensations", factor),
-  #        factor = factor(factor, levels = c("Bodily sensations",
-  #                                           "Negative affect",
-  #                                           "Social connection",
-  #                                           "Cognition and control"))) %>%
-  mutate(pred = predict.gam(s3_gam$gam, type = "response", 
-                            newdata = d3_gam)) %>% # %>%
-  #                             mutate(factor = as.character(factor),
-  #                                    factor = gsub("Bodily sensation$", 
-  #                                                  "Bodily sensations", factor),
-  #                                    factor = factor(factor, 
-  #                                                    levels = c("Bodily sensations",
-  #                                                               "Negative affect",
-  #                                                               "Social connection",
-  #                                                               "Cognition and control"))))) %>%
-  # mutate(factor = as.character(factor),
-  #        factor = gsub("Bodily sensations", "Bodily sensation", factor),
-  #        factor = factor(factor, levels = c("Bodily sensation",
-  #                                           "Negative affect",
-  #                                           "Social connection",
-  #                                           "Cognition and control"))) %>%
+  mutate(pred = predict.gam(s3_gam, type = "response", newdata = d3_gam)) %>% 
   group_by(ResponseId, factor, target_year) %>%
@@
 
-```{r fig02b, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 3).
+```{r fig02b_gam, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 3).
 Scores were calculated by averaging a participant's responses to the two capacity items for each domain of mental life.
-Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model (beta regression).", fig.width = 4, fig.asp = 0.5}
-d3_gam_r1_rsq <- round_x(summary(s3_gam$gam)$r.sq, 2)
-
-fig02b <- d3_gam_r1_pred %>%
+Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive model.", fig.width = 8, fig.asp = 0.5}
+d3_gam_r1_rsq <- round_x(summary(s3_gam)$r.sq, 2)
+
+fig02b_gam <- d3_gam_r1_pred %>%
   ggplot(aes(x = target_year, y = score, color = factor)) +
@@
 # make jpg version (darker)
-fig02b_jpg <- d3_gam_r1_pred %>%
+fig02b_gam_jpg <- d3_gam_r1_pred %>%
   ggplot(aes(x = target_year, y = score, color = factor)) +
@@
 
-# # save plot
-# if (resave_plots == T | !file.exists("../outputs/fig02b.pdf")) {
-#   ggsave("../outputs/fig02b.svg")
-#   ggsave("../outputs/fig02b.pdf")
-# }
-```
+# save plot
+if (resave_plots == T | !file.exists("../outputs/fig02b_gam.pdf")) {
+  ggsave("../outputs/fig02b_gam.svg")
+  ggsave("../outputs/fig02b_gam.pdf")
+}
+```
+
+#### Figure 2
 
 ```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
-Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models.
 In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
-In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 0.7}
-plot_grid(fig02a, fig02b,
+In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 8, fig.asp = 0.7}
+plot_grid(fig02a_gam, fig02b_gam,
           ncol = 1, labels = "AUTO")
@@
   ggsave("../outputs/fig02.pdf")
+  ggsave("../outputs/fig02.jpg")
 }
@@
 ```{r fig02_jpg, fig.cap="Perceived developmental trajectories for four domains of mental life (Studies 2-3).
-Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models.
 In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
-In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 4, fig.asp = 0.7}
-plot_grid(fig02a_jpg, fig02b_jpg,
+In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity.", fig.width = 8, fig.asp = 0.7}
+plot_grid(fig02a_gam_jpg, fig02b_gam_jpg,
           ncol = 1, labels = "AUTO")
@@
 ### Developmental mechanisms: Ratings
-
-As a first step in assessing the intuitive theories underlying these perceptions of the development of human mental life, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study.
-We assessed a wide range of potential developmental mechanisms for children's capacities.
-We applied a variety of dimensionality reduction approaches in order to sort these developmental mechanisms into meaningful categories, and then modeled participants' ratings of the importance of these mechanism as a function of domain (_bodily sensation_, _negative affect_, _social connection_, and _cognition and control_).
 
@@
 
-#### Regression models
-
-To supplement our visual assessment of which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a series of multilevel linear regression models, regressing responses to this question onto domain, including the maximal random effects structure that allowed the model to converge.
-Using the "lme4" package for R [@bates.etal2015], we specified these models as follows: _lmer(response ~ domain + (1 | participant) + (1 | capacity)_.
-In these analyses, domain and developmental mechanism were both effect-coded for comparisons to the grand mean collapsing across domains and mechanisms.
-
-The full results of these models are presented in Supplementary Tables xxxxxxx; see also Figure 3 (main text).
-
 ```{r s3 mech ratings datasets b}
 d3_mech_ratings <- d3_dev_factor_rating %>%
-  mutate(factor = recode_factor(domain,
+  mutate(factor = recode_factor(
+    domain,
     "BOD"= "Bodily sensation",
@@
     "COG" = "Cognition and control")) %>%
-  select(-domain)
+  select(-domain) %>%
+  mutate(
+    dev_factor_text = recode_factor(
+      dev_factor,
+      "preprogrammed" = "biologically 'preprogrammed'",
+      "womb_experiences" = "experiences in the womb",
+      "body_grows" = "body grows and matures",
+      "brain_changes" = "brain changes",
+      "senses_improve" = "senses improve",
+      "observes_objects" = "observes objects and physical world",
+      "experiments" = "actively experiments",
+      "observes_people" = "observes people",
+      "interacts_people" = "interacts with people",
+      "people_teach" = "people explicitly teach"))
 
@@
 contrasts(d3_mech_ratings$dev_factor) <- cbind(
-  womb_gm = c(-1, 1, 0, 0, 0, 0, 0, 0, 0, 0),
-  body_gm = c(-1, 0, 1, 0, 0, 0, 0, 0, 0, 0),
-  brai_gm = c(-1, 0, 0, 1, 0, 0, 0, 0, 0, 0),
-  sens_gm = c(-1, 0, 0, 0, 1, 0, 0, 0, 0, 0),
-  obso_gm = c(-1, 0, 0, 0, 0, 1, 0, 0, 0, 0),
-  expt_gm = c(-1, 0, 0, 0, 0, 0, 1, 0, 0, 0),
-  obsp_gm = c(-1, 0, 0, 0, 0, 0, 0, 1, 0, 0),
-  intp_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 1, 0),
-  teac_gm = c(-1, 0, 0, 0, 0, 0, 0, 0, 0, 1))
-```
+  # baseline/drop: senses improve
+  prep_gm = c(1, 0, 0, 0, -1, 0, 0, 0, 0, 0),
+  womb_gm = c(0, 1, 0, 0, -1, 0, 0, 0, 0, 0),
+  body_gm = c(0, 0, 1, 0, -1, 0, 0, 0, 0, 0),
+  brai_gm = c(0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
+  obso_gm = c(0, 0, 0, 0, -1, 1, 0, 0, 0, 0),
+  obsp_gm = c(0, 0, 0, 0, -1, 0, 1, 0, 0, 0),
+  intp_gm = c(0, 0, 0, 0, -1, 0, 0, 1, 0, 0),
+  teac_gm = c(0, 0, 0, 0, -1, 0, 0, 0, 1, 0),
+  expt_gm = c(0, 0, 0, 0, -1, 0, 0, 0, 0, 1))
+```
+
+#### Summary tables
 
 ```{r s3 mech ratings summary stats}
-# overall
+# by mechanism (no domain)
 d3_mech_ratings_sum_a <- d3_mech_ratings %>%
-  # participant-level mean of means for each mechanism
-  group_by(ResponseId, dev_factor) %>%
+  # participant-level mean for each mechanism
+  group_by(ResponseId, dev_factor_text) %>%
   summarise(score_a = mean(response, na.rm = T)) %>%
@@
   # group-level mean of means for each mechanism 
-  group_by(dev_factor) %>%
+  group_by(dev_factor_text) %>%
   summarise(median = median(score_a, na.rm = T),
@@
   ungroup() %>%
-  arrange(dev_factor)
+  arrange(dev_factor_text) %>%
+  rename(`Developmental mechanism` = dev_factor_text)
 
 d3_mech_ratings_sum_a %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
-
-# by domain
+  kbl(digits = 2) %>% 
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
+
+# by domain (no mechanism)
 d3_mech_ratings_sum_b <- d3_mech_ratings %>%
-  # participant-level mean for each mechanism, for each domain
-  group_by(ResponseId, dev_factor, factor) %>%
+  # participant-level mean for each domain
+  group_by(ResponseId, factor) %>%
   summarise(score_a = mean(response, na.rm = T)) %>%
   ungroup() %>%
-  # group-level mean of means of means for each domain 
-  group_by(factor, dev_factor) %>%
+  # group-level mean of means for each domain 
+  group_by(factor) %>%
   summarise(median = median(score_a, na.rm = T),
@@
   ungroup() %>%
-  arrange(factor, dev_factor)
+  arrange(factor) %>%
+  rename(Domain = factor)
 
 d3_mech_ratings_sum_b %>%
-  mutate_if(is.numeric, funs(round_x(., 2)))
-```
-
-##### All mechanisms
+  kbl(digits = 2) %>% 
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
+
+# by mechanism and domain
+d3_mech_ratings_sum_c <- d3_mech_ratings %>%
+  # participant-level mean for each mechanism, for each domain
+  group_by(ResponseId, factor, dev_factor_text) %>%
+  summarise(score_a = mean(response, na.rm = T)) %>%
+  ungroup() %>%
+  # group-level mean of means for each domain 
+  group_by(factor, dev_factor_text) %>%
+  summarise(median = median(score_a, na.rm = T),
+            mean = mean(score_a, na.rm = T),
+            sd = sd(score_a, na.rm = T)) %>%
+  ungroup() %>%
+  arrange(factor, dev_factor_text) %>%
+  rename(Domain = factor,
+         `Developmental mechanism` = dev_factor_text)
+
+d3_mech_ratings_sum_c %>%
+  kbl(digits = 2) %>% 
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
+
+# by mechanism, domain, and capacity
+d3_mech_ratings_sum_d <- d3_mech_ratings %>%
+  # participant-level mean for each mechanism, for each domain
+  group_by(ResponseId, factor, capacity, dev_factor_text) %>%
+  summarise(score_a = mean(response, na.rm = T)) %>%
+  ungroup() %>%
+  # group-level mean of means for each domain 
+  group_by(factor, capacity, dev_factor_text) %>%
+  summarise(median = median(score_a, na.rm = T),
+            mean = mean(score_a, na.rm = T),
+            sd = sd(score_a, na.rm = T)) %>%
+  ungroup() %>%
+  arrange(factor, capacity, dev_factor_text) %>%
+  mutate(capacity = gsub("_", " ", capacity)) %>%
+  rename(Domain = factor,
+         Capacity = capacity,
+         `Developmental mechanism` = dev_factor_text)
+
+d3_mech_ratings_sum_d %>%
+  kbl(digits = 2) %>% 
+  kable_styling() %>%
+  collapse_rows(1:2, valign = "top")
+```
+
+#### Regression models
+
+To supplement our visual assessment of which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensation*, *negative affect*, *social connection*, and *cognition and control*), we conducted a series of multilevel linear regression models, regressing responses to this question onto domain, including the maximal random effects structure that allowed the model to converge.
+Using the "lme4" package for R [@bates.etal2015], we specified these models as follows: _lmer(response ~ domain + (1 | participant) + (1 | capacity)_.
+In these analyses, domain and developmental mechanism were both effect-coded for comparisons to the grand mean collapsing across domains and mechanisms.
+
+The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3lmerall), \@ref(tab:tabs3lmerbod), \@ref(tab:tabs3lmerneg), \@ref(tab:tabs3lmersoc), and \@ref(tab:tabs3lmercog); see also Figure 3 (main text).
+
+##### All domains
 
@@
 
-summary(s3_lmer)
-# model_parameters(s3_lmer)
-```
-
-```{r tabs3lmerall, include = T, message = F, warning = F}
-model_parameters(s3_lmer, standardize = "refit") %>%
+# summary(s3_lmer)
+# parameters(s3_lmer, standardize = "refit")
+```
+
+```{r tabs3lmerall, results = "asis", include = T, message = F, warning = F}
+cat("\\begin{landscape}")
+parameters(s3_lmer, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
     TRUE ~ Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorprep_gm", "Mechanism (Biologically 'preprogrammed' vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorwomb_gm", "Mechanism (Experiences in the womb vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbody_gm", "Mechanism (Body grows and matures vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbrai_gm", "Mechanism (Brain changes vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorsens_gm", "Mechanism (Senses improve vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobso_gm", "Mechanism (Observes objects and physical world vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorexpt_gm", "Mechanism (Actively experiments vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobsp_gm", "Mechanism (Observes people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorintp_gm", "Mechanism (Interacts with people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorteac_gm", "Mechanism (People explicitly teach vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
+  mutate(Parameter = str_wrap(Parameter, 80)) %>%
+  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
+  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
+  select(-starts_with("CI")) %>%
+  select(Parameter, Coefficient, `95% CI`, everything()) %>%
+  rename(df = df_error) %>%
+  kable("latex", booktabs = T, longtable = T,
+        caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
+        digits = 2, align = c("lrrrrrrrrrrrrrr")) %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 7.5)
+cat("\\end{landscape}")
+```
+
+##### Bodily sensation
+
+For capacities in the domain of _bodily sensation_, this analysis suggested that participants rated biological preprogramming, body changes, and brain changes as more important drivers of development than other mechanisms; see also Figure 3 (main text).
+
+```{r s3 mech ratings lmer bod}
+s3_lmer_bod <- lmer(response ~ dev_factor + 
+                      (1 | ResponseId) + 
+                      (1 | capacity),
+                    control = lmerControl(optimizer = "bobyqa"),
+                    data = d3_mech_ratings %>% 
+                      filter(factor == "Bodily sensation"))
+# summary(s3_lmer_bod)
+# parameters(s3_lmer_bod, standardize = "refit")
+```
+
+```{r tabs3lmerbod, include = T, message = F, warning = F}
+parameters(s3_lmer_bod, standardize = "refit") %>%
+  filter(Effects == "fixed") %>%
+  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
+  mutate(Parameter = case_when(
+    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
+    TRUE ~ Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorprep_gm", "Mechanism (Biologically 'preprogrammed' vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("dev_factorwomb_gm", "Mechanism (Experiences in the womb vs. GM)", Parameter)) %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (all domains): Fixed effects.",
-        digits = 2, align = c("lrrrrrrrrrrrrrr")) %>%
+        caption = "\\text{Study 3, multilevel linear model results (bodily sensation): Fixed effects.}",
+        digits = 2, align = c("lrrrrrr")) %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8)
@@
 
-##### Biologically 'preprogrammed'
-
-For the mechanism "the child is biologically 'preprogrammed' to have this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_.
-See also Figure 3, first row (main text).
-
-```{r s3 mech ratings lmer prep}
-s3_lmer_prep <- lmer(response ~ factor +
+##### Negative affect
+
+For capacities in the domain of _negative affect_, this analysis suggested that participants rated biological preprogramming, brain changes, social interactions, and observations of other people as more important drivers of development than other mechanisms; see also Figure 3 (main text).
+
+```{r s3 mech ratings lmer neg}
+s3_lmer_neg <- lmer(response ~ dev_factor + 
                       (1 | ResponseId) + 
@@
                     data = d3_mech_ratings %>% 
-                  filter(dev_factor == "preprogrammed"))
-
-summary(s3_lmer_prep)
-# model_parameters(s3_lmer_prep)
-```
-
-```{r tabs3lmerprep, include = T, message = F, warning = F}
-model_parameters(s3_lmer_prep, standardize = "refit") %>%
+                      filter(factor == "Negative affect"))
+
+# summary(s3_lmer_neg)
+# parameters(s3_lmer_neg, standardize = "refit")
+```
+
+```{r tabs3lmerneg, include = T, message = F, warning = F}
+parameters(s3_lmer_neg, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
     TRUE ~ Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorprep_gm", "Mechanism (Biologically 'preprogrammed' vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorwomb_gm", "Mechanism (Experiences in the womb vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbody_gm", "Mechanism (Body grows and matures vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorbrai_gm", "Mechanism (Brain changes vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorsens_gm", "Mechanism (Senses improve vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobso_gm", "Mechanism (Observes objects and physical world vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorexpt_gm", "Mechanism (Actively experiments vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorobsp_gm", "Mechanism (Observes people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorintp_gm", "Mechanism (Interacts with people vs. GM)", Parameter)) %>%
+  mutate(Parameter = gsub("dev_factorteac_gm", "Mechanism (People explicitly teach vs. GM)", Parameter)) %>%
   mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (biologically 'preprogrammed'): Fixed effects.",
+        caption = "\\text{Study 3, multilevel linear model results (negative affect): Fixed effects.}",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Experiences in the womb
-
-For the mechanism "the child has experiences in the womb that give them this ability," this analysis suggested that participants rated this as a particularly important driver of development in the domain of _bodily sensation_, and a relatively unimportant driver of development in the domain of _cognition and control_.
-See also Figure 3, second row (main text).
-
-```{r s3 mech ratings lmer womb}
-s3_lmer_womb <- lmer(response ~ factor +
+##### Social connection
+
+For capacities in the domain of _social connection_, this analysis suggested that participants rated social interactions, observations of other people, and brain changes as more important drivers of development than other mechanisms; see also Figure 3 (main text).
+
+```{r s3 mech ratings lmer soc}
+s3_lmer_soc <- lmer(response ~ dev_factor + 
                       (1 | ResponseId) + 
@@
                     data = d3_mech_ratings %>% 
-                  filter(dev_factor == "womb_experiences"))
-
-summary(s3_lmer_womb)
-# model_parameters(s3_lmer_womb)
-```
-
-```{r tabs3lmerwomb, include = T, message = F, warning = F}
-model_parameters(s3_lmer_womb, standardize = "refit") %>%
+                      filter(factor == "Social connection"))
+
+# summary(s3_lmer_soc)
+# parameters(s3_lmer_soc)
+```
+
+```{r tabs3lmersoc, include = T, message = F, warning = F}
+parameters(s3_lmer_soc, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
+        caption = "\\text{Study 3, multilevel linear model results (social connection): Fixed effects.}",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Body grows and matures
-
-For the mechanism "the child’s body grows and matures (for example, muscles get stronger, child gets taller)," this analysis revealed no significant differences in importance ratings across domains.
-See also Figure 3, third row (main text).
-
-```{r s3 mech ratings lmer body}
-s3_lmer_body <- lmer(response ~ factor +
+##### Cognition and control
+
+For capacities in the domain of _cognition and control_, this analysis suggested that participants rated brain changes, social interactions, observations of other people, explicit teaching, and active experimentation as more important drivers of development than other mechanisms; see also Figure 3 (main text).
+
+```{r s3 mech ratings lmer cog}
+s3_lmer_cog <- lmer(response ~ dev_factor + 
                       (1 | ResponseId) + 
@@
                     data = d3_mech_ratings %>% 
-                  filter(dev_factor == "body_grows"))
-
-summary(s3_lmer_body)
-# model_parameters(s3_lmer_body)
-```
-
-```{r tabs3lmerbody, include = T, message = F, warning = F}
-model_parameters(s3_lmer_body, standardize = "refit") %>%
+                      filter(factor == "Cognition and control"))
+
+# summary(s3_lmer_cog)
+# parameters(s3_lmer, standardize = "refit")
+```
+
+```{r tabs3lmercog, include = T, message = F, warning = F}
+parameters(s3_lmer_cog, standardize = "refit") %>%
   filter(Effects == "fixed") %>%
@@
   kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
+        caption = "\\text{Study 3, multilevel linear model results (cognition and control): Fixed effects.}",
         digits = 2, align = c("lrrrrrr")) %>%
@@
 
-##### Brain changes
-
-For the mechanism "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)," this analysis suggested that participants rated this as a particularly important driver of development in the domains of _social connection_ and _cognition and control_.
-See also Figure 3, fourth row (main text).
-
-```{r s3 mech ratings lmer brai}
-s3_lmer_brai <- lmer(response ~ factor +
-                       (1 | ResponseId) +
-                       (1 | capacity),
-                control = lmerControl(optimizer = "bobyqa"),
-                data = d3_mech_ratings %>%
-                  filter(dev_factor == "brain_changes"))
-
-summary(s3_lmer_brai)
-# model_parameters(s3_lmer_brai)
-```
-
-```{r tabs3lmerbrai, include = T, message = F, warning = F}
-model_parameters(s3_lmer_brai, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(df = df_error) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-##### Senses improve
-
-For the mechanism "the child’s senses improve (for example, vision gets sharper, hearing improves)," this analysis revealed no significant differences in importance ratings across domains.
-See also Figure 3, fifth row (main text).
-
-```{r s3 mech ratings lmer sens}
-s3_lmer_sens <- lmer(response ~ factor +
-                       (1 | ResponseId) +
-                       (1 | capacity),
-                control = lmerControl(optimizer = "bobyqa"),
-                data = d3_mech_ratings %>%
-                  filter(dev_factor == "senses_improve"))
-
-summary(s3_lmer_sens)
-# model_parameters(s3_lmer_brai)
-```
-
-```{r tabs3lmersens, include = T, message = F, warning = F}
-model_parameters(s3_lmer_sens, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, t, df_error, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(df = df_error) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel linear model results (experiences in the womb): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-XXXX BOOKMARK
-
 ### Developmental mechanisms: Selection of "most important"
@@
 As described in the main text, we also assessed participants' responses to forced-choice questions about the "most important" factor driving the development of each of these capacities.
-In the main text, we presented a visualization of these choices (Figure 3, Panel C).
-Here, we present multilevel generalized linear model (logistic regressions) to predict the likelihood of selecting extrinsic vs.
-intrinsic mechanisms by domain.
-Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _glmer(choice of extrinsic mechanism ~ domain + (1 | participant) + (1 | capacity)_.
-We also conducted separate, analogous regression analyses for each domain separately.
-In these analyses, domain was effect-coded for comparisons to the grand mean collapsing across domains.
-(As in the previous section, these analyses omitted the mechanism "the child's brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses.)
-
-The full results of these models are presented in Supplementary Tables \@ref(tab:tabs3glmerall) (all domains), \@ref(tab:tabs3glmerbod) (*bodily sensation*), \@ref(tab:tabs3glmerneg) (*negative affect*), \@ref(tab:tabs3glmersoc) (*social connection*), and \@ref(tab:tabs3glmercog) (*cognition and control*); see also Figure 3 (main text).
 
@@
 d3_mech_choice <- d3_dev_factor_most_important_choice %>%
-  mutate(factor = recode_factor(domain,
+  mutate(
+    factor = recode_factor(
+      domain,
       "BOD"= "Bodily sensation",
@@
       "The child observes the objects and the physical world around him or her" = "observes_objects",
-           "The child actively experiments with how to do this" = "experiments",
       "The child observes the people around him or her" = "observes_people",
@@
       "People explicitly teach the child how to do this" = "people_teach",
-           .default = "other")) %>%
-  select(-domain, -response) %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor %in% c("senses_improve", "body_grows", 
-                      "womb_experiences", "preprogrammed") ~ "intrinsic",
-    dev_factor %in% c("interacts_people", "observes_people", "observes_objects", 
-                      "people_teach", "experiments") ~ "extrinsic",
-    dev_factor == "brain_changes" ~ NA_character_,
-    TRUE ~ NA_character_
-  )) %>%
-  mutate(dev_factor_cluster = factor(dev_factor_cluster,
-                                     levels = c("intrinsic", "extrinsic")))
-
-contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, -1, 0, 0),
-                                           soc_gm = c(0, -1, 1, 0),
-                                           cog_gm = c(0, -1, 0, 1))
-
-# contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, 0, -1, 0),
-#                                            neg_gm = c(0, 1, -1, 0),
-#                                            cog_gm = c(0, 0, -1, 1))
-
-contrasts(d3_mech_choice$dev_factor_cluster) <- cbind(ext_gm = c(-1, 1))
-```
-
-```{r s3 mech choice summary stats}
-# overall
-d3_mech_choice_sum_a <- d3_mech_choice %>%
-  count(dev_factor_cluster) %>%
-  mutate(prop = n/sum(n))
-
-d3_mech_choice_sum_a %>%
-  mutate_at(vars(prop), funs(round_x(., 2)))
-
-# by domain
-d3_mech_choice_sum_b <- d3_mech_choice %>%
-  count(factor, dev_factor_cluster) %>%
-  group_by(factor) %>%
-  mutate(prop = n/sum(n)) %>%
-  ungroup()
-
-d3_mech_choice_sum_b %>%
-  mutate_at(vars(prop), funs(round_x(., 2)))
-```
-
-##### All domains
-
-This analysis suggested that participants' choice of extrinsic vs. intrinsic mechanisms as the "most important" driver of development varied by domain (see interaction terms).
-
-```{r s3 mech choice glmer}
-s3_glmer <- glmer(extrinsic ~ factor + 
-                    (1 | ResponseId) + 
-                    (1 | capacity),
-                  control = glmerControl(optimizer = "bobyqa"),
-                  data = d3_mech_choice %>%
-                    mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
-                                                 dev_factor_cluster == "intrinsic" ~ 0,
-                                                 is.na(dev_factor_cluster) ~ NA_real_,
-                                                 TRUE ~ NA_real_)),
-                  family = "binomial")
-
-summary(s3_glmer)
-# model_parameters(s3_glmer)
-```
-
-```{r tabs3glmerall, include = T, message = F, warning = F}
-model_parameters(s3_glmer, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(`Coefficient (log-odds)` = Coefficient) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (all domains): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-##### Bodily sensastions
-
-For capacities in the domain of _bodily sensation_, this analysis suggested that participants were much more likely to select intrinsic mechanisms than extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
-
-```{r s3 mech choice glmer bodily sensation}
-s3_glmer_bod <- glmer(extrinsic ~ 1 + 
-                        (1 | ResponseId) + 
-                        (1 | capacity),
-                      control = glmerControl(optimizer = "bobyqa"),
-                      data = d3_mech_choice %>%
-                        filter(factor == "Bodily sensation") %>%
-                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
-                                                     dev_factor_cluster == "intrinsic" ~ 0,
-                                                     is.na(dev_factor_cluster) ~ NA_real_,
-                                                     TRUE ~ NA_real_)),
-                      family = "binomial")
-
-summary(s3_glmer_bod)
-# model_parameters(s3_glmer)
-```
-
-```{r tabs3glmerbod, include = T, message = F, warning = F}
-model_parameters(s3_glmer_bod, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(`Coefficient (log-odds)` = Coefficient) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (bodily sensation): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-##### Negative affect
-
-For capacities in the domain of _negative affect_, this analysis suggested that participants were equally likely to select intrinsic and extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
-
-```{r s3 mech choice glmer negative affect}
-s3_glmer_neg <- glmer(extrinsic ~ 1 + 
-                        (1 | ResponseId) + 
-                        (1 | capacity),
-                      control = glmerControl(optimizer = "bobyqa"),
-                      data = d3_mech_choice %>%
-                        filter(factor == "Negative affect") %>%
-                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
-                                                     dev_factor_cluster == "intrinsic" ~ 0,
-                                                     is.na(dev_factor_cluster) ~ NA_real_,
-                                                     TRUE ~ NA_real_)),
-                      family = "binomial")
-
-summary(s3_glmer_neg)
-# model_parameters(s3_glmer)
-```
-
-```{r tabs3glmerneg, include = T, message = F, warning = F}
-model_parameters(s3_glmer_neg, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(`Coefficient (log-odds)` = Coefficient) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (negative affect): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-##### Social connection
-
-For capacities in the domain of _social connection_, this analysis suggested that participants were equally likely to select intrinsic and extrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
-
-```{r s3 mech choice glmer social connection}
-s3_glmer_soc <- glmer(extrinsic ~ 1 + 
-                        (1 | ResponseId) + 
-                        (1 | capacity),
-                      control = glmerControl(optimizer = "bobyqa"),
-                      data = d3_mech_choice %>%
-                        filter(factor == "Social connection") %>%
-                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
-                                                     dev_factor_cluster == "intrinsic" ~ 0,
-                                                     is.na(dev_factor_cluster) ~ NA_real_,
-                                                     TRUE ~ NA_real_)),
-                      family = "binomial")
-
-summary(s3_glmer_soc)
-# model_parameters(s3_glmer)
-```
-
-```{r tabs3glmersoc, include = T, message = F, warning = F}
-model_parameters(s3_glmer_soc, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(`Coefficient (log-odds)` = Coefficient) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (social connection): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-##### Cognition and control
-
-For capacities in the domain of _cognition and control_, this analysis suggested that participants were much more likely to select extrinsic mechanisms than intrinsic mechanisms as the most important drivers of development; see also Figure 3, panel C (main text).
-
-```{r s3 mech choice glmer cognition and control}
-s3_glmer_cog <- glmer(extrinsic ~ 1 + 
-                        (1 | ResponseId) + 
-                        (1 | capacity),
-                      control = glmerControl(optimizer = "bobyqa"),
-                      data = d3_mech_choice %>%
-                        filter(factor == "Cognition and control") %>%
-                        mutate(extrinsic = case_when(dev_factor_cluster == "extrinsic" ~ 1,
-                                                     dev_factor_cluster == "intrinsic" ~ 0,
-                                                     is.na(dev_factor_cluster) ~ NA_real_,
-                                                     TRUE ~ NA_real_)),
-                      family = "binomial")
-
-summary(s3_glmer_cog)
-# model_parameters(s3_glmer)
-```
-
-```{r tabs3glmercog, include = T, message = F, warning = F}
-model_parameters(s3_glmer_cog, standardize = "refit") %>%
-  filter(Effects == "fixed") %>%
-  select(Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
-  mutate(Parameter = case_when(
-    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
-    TRUE ~ Parameter)) %>%
-  mutate(Parameter = gsub("factorbod_gm", "Bodily sensation (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorsoc_gm", "Social connection (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("factorcog_gm", "Cognition and control (vs. GM)", Parameter)) %>%
-  mutate(Parameter = gsub("\\:", " x ", Parameter)) %>%
-  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
-  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
-  select(-starts_with("CI")) %>%
-  select(Parameter, Coefficient, `95% CI`, everything()) %>%
-  rename(`Coefficient (log-odds)` = Coefficient) %>%
-  kable("latex", booktabs = T, longtable = T,
-        caption = "Study 3, multilevel generalized linear model results (cognition and control): Fixed effects.",
-        digits = 2, align = c("lrrrrrr")) %>%
-  kable_styling(latex_options = c("repeat_header"), font_size = 8)
-```
-
-```{r figS08a, fig.width = 4.5, fig.asp = 1.5}
-figS08a <- d3_mech_choice %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC mechanisms",
-    is.na(dev_factor_cluster) ~ "Other",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC mechanisms"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC mechanisms", 
-                                           # "Other",
-                                           "EXTRINSIC mechanisms")),
+      "The child actively experiments with how to do this" = "experiments",
+      .default = "other"),
+    dev_factor = relevel(dev_factor, ref = "other"),
     dev_factor_text = recode_factor(
       dev_factor,
-      "preprogrammed" = "biologically ‘preprogrammed'",
+      "preprogrammed" = "biologically 'preprogrammed'",
       "womb_experiences" = "experiences in the womb",
@@
       "people_teach" = "people explicitly teach"),
-    capacity = str_wrap(gsub("_", " ", capacity), 14)) %>%
-  ggplot(aes(x = reorder(str_wrap(dev_factor_text, 20), 
-                         as.numeric(dev_factor)), 
-             fill = factor, color = factor)) +
-  facet_grid(rows = vars(reorder(capacity, as.numeric(factor))),
-             cols = vars(dev_factor_cluster),
-             scales = "free_x", space = "free_x") +
-  geom_bar(stat = "count", alpha = 0.6) +
-  scale_fill_viridis_d(end = 0.9, option = "viridis", 
-                       aesthetics = c("color", "fill")) +
-  scale_y_continuous(breaks = seq(0, 
-                                  d3_mech_choice %>% 
-                                    distinct(ResponseId) %>% 
-                                    count() %>% 
-                                    pull(n), 
-                                  100),
-                     limits = c(0, 
-                                d3_mech_choice %>% 
-                                  distinct(ResponseId) %>% 
-                                  count() %>% 
-                                  pull(n))) +
+    capacity = factor(
+      capacity,
+      levels = c(
+        "feeling_pain", "getting_hungry", 
+        "feeling_distressed", "feeling_helpless",
+        "feeling_happy", "learning_from_other_people",
+        "controlling_their_emotions", "reasoning_about_things"))) %>%
+  select(-domain, -response)
+
+# contrasts(d3_mech_choice$factor) <- cbind(neg_bod = c(0, 1, 0, 0),
+#                                           soc_bod = c(0, 0, 1, 0),
+#                                           cog_bod = c(0, 0, 0, 1))
+
+contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, -1, 0, 0),
+                                          soc_gm = c(0, -1, 1, 0),
+                                          cog_gm = c(0, -1, 0, 1))
+
+# contrasts(d3_mech_choice$factor) <- cbind(bod_gm = c(1, 0, -1, 0),
+#                                            neg_gm = c(0, 1, -1, 0),
+#                                            cog_gm = c(0, 0, -1, 1))
+
+contrasts(d3_mech_choice$dev_factor) <- cbind( # dummy = senses_improve
+  preprogrammed =     c(rep(0, 0), 1, rep(0, 3), -1, rep(0, 6)),
+  womb_experiences =  c(rep(0, 1), 1, rep(0, 2), -1, rep(0, 6)),
+  body_grows =        c(rep(0, 2), 1, rep(0, 1), -1, rep(0, 6)),
+  brain_changes =     c(rep(0, 3), 1, rep(0, 0), -1, rep(0, 6)),
+  observes_objects =  c(rep(0, 4), -1, rep(0, 0), 1, rep(0, 5)),
+  observes_people =   c(rep(0, 4), -1, rep(0, 1), 1, rep(0, 4)),
+  interacts_people =  c(rep(0, 4), -1, rep(0, 2), 1, rep(0, 3)),
+  people_teach =      c(rep(0, 4), -1, rep(0, 3), 1, rep(0, 2)),
+  experiments =       c(rep(0, 4), -1, rep(0, 4), 1, rep(0, 1)),
+  other =             c(rep(0, 4), -1, rep(0, 5), 1, rep(0, 0)))
+
+# contrasts(d3_mech_choice$dev_factor) <- cbind( # dummy = other
+#   preprogrammed =     c(rep(0, 0), 1, rep(0, 9), -1),
+#   womb_experiences =  c(rep(0, 1), 1, rep(0, 8), -1),
+#   body_grows =        c(rep(0, 2), 1, rep(0, 7), -1),
+#   brain_changes =     c(rep(0, 3), 1, rep(0, 6), -1),
+#   senses_improve =    c(rep(0, 4), 1, rep(0, 5), -1),
+#   observes_objects =  c(rep(0, 5), 1, rep(0, 4), -1),
+#   observes_people =   c(rep(0, 6), 1, rep(0, 3), -1),
+#   interacts_people =  c(rep(0, 7), 1, rep(0, 2), -1),
+#   people_teach =      c(rep(0, 8), 1, rep(0, 1), -1),
+#   experiments =       c(rep(0, 9), 1, rep(0, 0), -1))
+```
+
+#### Summary tables
+
+```{r s3 mech choice summary stats}
+# overall
+d3_mech_choice_sum_a <- d3_mech_choice %>%
+  count(dev_factor_text) %>%
+  complete(dev_factor_text, fill = list(n = 0)) %>%
+  mutate(prop = n/sum(n))
+
+d3_mech_choice_sum_a %>%
+  mutate(percent = scales::percent(n/sum(n), accuracy = 1)) %>%
+  select(-prop) %>%
+  arrange(dev_factor_text) %>%
+  rename(`Developmental mechanism` = dev_factor_text,
+         `%` = percent) %>%
+  kbl() %>%
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
+
+# by domain
+d3_mech_choice_sum_b <- d3_mech_choice %>%
+  count(factor, dev_factor_text) %>%
+  complete(dev_factor_text, nesting(factor), fill = list(n = 0)) %>%
+  group_by(factor) %>%
+  mutate(prop = n/sum(n)) %>%
+  ungroup() %>%
+  select(factor, everything())
+
+d3_mech_choice_sum_b %>%
+  mutate(percent = scales::percent(n/sum(n), accuracy = 1)) %>%
+  select(-prop) %>%
+  arrange(factor, dev_factor_text) %>%
+  rename(Domain = factor,
+         `Developmental mechanism` = dev_factor_text,
+         `%` = percent) %>%
+  kbl() %>%
+  kable_styling() %>%
+  collapse_rows(1, valign = "top")
+
+# by domain and capacity
+d3_mech_choice_sum_c <- d3_mech_choice %>%
+  count(factor, capacity, dev_factor_text) %>%
+  complete(dev_factor_text, nesting(factor, capacity), fill = list(n = 0)) %>%
+  group_by(factor, capacity) %>%
+  mutate(prop = n/sum(n)) %>%
+  ungroup() %>%
+  select(factor, capacity, everything())
+
+d3_mech_choice_sum_c %>%
+  mutate(percent = scales::percent(n/sum(n), accuracy = 1)) %>%
+  select(-prop) %>%
+  arrange(factor, capacity, dev_factor_text) %>%
+  mutate(capacity = gsub("_", " ", capacity)) %>%
+  rename(Domain = factor,
+         Capacity = capacity,
+         `Developmental mechanism` = dev_factor_text,
+         `%` = percent) %>%
+  kbl() %>%
+  kable_styling() %>%
+  collapse_rows(1:2, valign = "top")
+```
+
+```{r d3 mech choice modes}
+d3_mech_choice_modes_strict <- d3_mech_choice_sum_c %>% 
+  left_join(d3_mech_choice %>% distinct(dev_factor, dev_factor_text)) %>%
+  select(-n, -dev_factor_text) %>%
+  group_by(factor, capacity) %>%
+  slice_max(n = 1, order_by = prop, with_ties = T) %>%
+  ungroup() %>%
+  rename(modal_dev_factor = dev_factor,
+         modal_prop = prop) %>%
+  select(factor, capacity, modal_dev_factor, modal_prop)
+
+d3_mech_choice_modes_within10 <- d3_mech_choice_sum_c %>% 
+  left_join(d3_mech_choice %>% distinct(dev_factor, dev_factor_text)) %>%
+  select(-dev_factor_text) %>%
+  select(dev_factor, factor, capacity, prop) %>%
+  left_join(d3_mech_choice_modes_strict) %>%
+  mutate(prop_diff = modal_prop - prop) %>%
+  filter(abs(prop_diff) <= 0.10) %>%
+  select(factor, capacity, dev_factor, prop, everything())
+```
+
+#### Multinomial regression
+
+Here we present a multinomial log-linear model to predict the likelihood of selecting a mechanism by capacity Using the "nnet" package for R [@venables.ripley2002], we specified this model as follows: _multinom(choice of extrinsic mechanism ~ capacity_.
+(Note that this model was not equipped to represent the within-subjects nature of this dataset, and that capacities are not nested within domain for these purposes.) In this analysis, capacity was effect-coded for comparisons to the grand mean collapsing across capacities.
+The full results of this model are presented in Supplementary Table \@ref(tab:tabs3multinom).
+
+This analysis aligned with our observation that participants' choice of mechanisms as the "most important" driver of development varied by capacity.
+
+```{r multinom}
+# effect coding, drop feeling_helpless
+contrasts(d3_mech_choice$capacity) <- cbind(
+  feeling_pain =                c(rep(0, 0),  1, rep(0, 2), -1, rep(0, 4)),
+  getting_hungry =              c(rep(0, 1),  1, rep(0, 1), -1, rep(0, 4)),
+  feeling_distressed =          c(rep(0, 2),  1, rep(0, 0), -1, rep(0, 4)),
+  feeling_happy =               c(rep(0, 3), -1, rep(0, 0),  1, rep(0, 3)),
+  learning_from_other_people =  c(rep(0, 3), -1, rep(0, 1),  1, rep(0, 2)),
+  controlling_their_emotions =  c(rep(0, 3), -1, rep(0, 2),  1, rep(0, 1)),
+  reasoning_about_things =      c(rep(0, 3), -1, rep(0, 3),  1, rep(0, 0))
+)
+
+s3_multinom <- nnet::multinom(
+  dev_factor ~ capacity, 
+  data = d3_mech_choice)
+
+# summary(s3_multinom)
+# parameters(s3_multinom, standardize = "refit")
+```
+
+```{r tabs3multinom, results = "asis", include = T, message = F, warning = F}
+cat("\\begin{landscape}")
+parameters(s3_multinom, standardize = "refit") %>%
+  select(Response, Parameter, Coefficient, SE, CI_low, CI_high, z, p) %>%
+  rename(dev_factor = Response) %>%
+  left_join(d3_mech_choice %>% distinct(dev_factor, dev_factor_text)) %>%
+  select(-dev_factor) %>%
+  rename(Response = dev_factor_text) %>%
+  mutate(Parameter = case_when(
+    Parameter == "(Intercept)" ~ "Grand mean (GM) (intercept)",
+    TRUE ~ paste0("Capacity (", str_to_sentence(gsub("_", " ", gsub("capacity", "", Parameter))), " vs. GM)"))) %>%
+  mutate(p = ifelse(p < 0.001, "<0.001", round_x(p, 3))) %>%
+  mutate(`95% CI` = paste0("[", round_x(CI_low), ", ", round_x(CI_high), "]")) %>%
+  select(-starts_with("CI")) %>%
+  select(Response, Parameter, Coefficient, `95% CI`, everything()) %>%
+  kable("latex", booktabs = T, longtable = T,
+        # caption = "\\text{Study 3, multinomial model results.}",
+        caption = "Study 3, multinomial log linear model results.",
+        digits = 2, align = c("lrrrrrrrrrrrrrr")) %>%
+  kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
+  collapse_rows(1, valign = "top")
+cat("\\end{landscape}")
+```
+
+```{r multinom signif, include = F}
+# take a closer look at only those effects where p<0.01
+s3_multinom_signif <- parameters(s3_multinom, standardize = "refit") %>%
+  data.frame() %>% 
+  filter(p < 0.01) %>%
+  filter(!grepl("Intercept", Parameter)) %>%
+  mutate(Parameter = gsub("capacity", "", Parameter))
+
+s3_multinom_signif %>%
+  select(Parameter, Response, Coefficient) %>%
+  rename(capacity = Parameter,
+         dev_factor = Response) %>%
+  left_join(d3_cap_ratings %>% distinct(factor, capacity)) %>%
+  left_join(d3_mech_choice %>% distinct(dev_factor, dev_factor_text)) %>%
+  mutate(direction = ifelse(Coefficient > 0, "positive", "negative")) %>%
+  select(factor, direction, capacity, dev_factor_text, everything()) %>%
+  select(-dev_factor) %>%
+  arrange(factor, direction, capacity, desc(abs(Coefficient))) %>%
+  mutate(capacity = gsub("_", " ", capacity)) %>%
+  rename(Domain = factor,
+         Direction = direction,
+         Capacity = capacity,
+         `Develompental mechanism` = dev_factor_text) %>%
+  kbl(digits = 2) %>%
+  kable_styling() %>%
+  collapse_rows(1:3, valign = "top")
+```
+
+In brief, this analysis suggested that selections of what we would call "social" mechanisms of development (explicit teaching and interactions with people) were particularly uncommon for capacities in the domain of _bodily sensations_, and particularly common for capacities in the domain of _cognition and control_ (as well as one of the capacities in the domain of _social connection_).
+More broadly, many of the developmental mechanisms were selected more often for capacities in the domain of _cognition and control_ than capacities in other domains, reflecting the greater diversity of choices in this domain, including the (occasional) selection of mechanisms that were rarely if ever selected as 'most important' in other domains (e.g., active experimentation on the part of the child).
+
+```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
+Small, lighter points represent individual participants’ ratings of how important each developmental mechanism is in the development of each capacity within a domain (first row: bodily sensation; second row: negative affect; third row: social connection; fourth row: cognition and control).
+Larger black and red points correspond to mean importance ratings across the sample, and error bars are bootstrapped 95% confidence intervals.
+On the right side of each panel are the percentages of participants who selected each developmental mechanism as the ‘most important’ driver of development for that capacity, with modal selections in red.", fig.width = 10, fig.asp = 1.2}
+d3_mech_ratings %>%
+  left_join(d3_mech_choice_sum_c %>% select(dev_factor_text, factor, capacity, prop)) %>%
+  left_join(d3_mech_choice_modes_within10 %>% mutate(mode = T)) %>%
+  mutate(mode = ifelse(is.na(mode), F, T),
+         capacity = str_wrap(gsub("_", " ", capacity), 100)) %>% 
+  ggplot(aes(x = reorder(dev_factor_text, desc(as.numeric(dev_factor_text))), 
+             y = response)) +
+  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor))), ncol = 2,
+             scales = "free_x") + # to repeat axis labels
+  ggnewscale::new_scale_color() +
+  geom_jitter(
+    aes(color = factor), 
+    height = 0.2, size = 0.1, alpha = 0.2,
+    show.legend = F) +
+  scale_color_viridis_d(
+    name = "Domain:",
+    end = 0.9, option = "viridis") +
+  ggnewscale::new_scale_color() +
+  geom_pointrange( # 95% CIs
+    data = . %>%
+      group_by(factor, capacity, dev_factor_text, mode) %>%
+      multi_boot_standard(col = "response", na.rm = T) %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, color = mode)) +
+  # geom_pointrange( # standard deviations
+  #   data = . %>%
+  #     group_by(factor, capacity, dev_factor_text) %>%
+  #     summarise(mean = mean(response, na.rm = T),
+  #               sd = sd(response, na.rm = T),
+  #               n = n(),
+  #               ci_lower = mean - sd,
+  #               ci_upper = mean + sd) %>%
+  #     ungroup(),
+  #   aes(y = mean, ymin = ci_lower, ymax = ci_upper)) +
+  scale_color_manual(
+    name = "Modal choice of 'most important' developmental mechanism:", 
+    values = c("black", "#f94802")) +
+  geom_text(
+    data = . %>%
+      distinct(factor, capacity, dev_factor, dev_factor_text, prop, mode),
+    aes(y = 6.5, label = paste0(round(prop, 2)*100, "%"),
+        color = mode),
+    size = 2, hjust = 0,
+    show.legend = F) +
+  annotate(geom = "text", label = "'most important'\nmechanism", 
+           size = 2, hjust = 0.5, vjust = 0, 
+           x = 11, y = 6.5) +
   theme_minimal() + 
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism",
-       y = "Count of responses",
-       color = "Domain", fill = "Domain") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
-         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
-```
-
-```{r figS08b, fig.width = 1.5, fig.asp = 6.75/1.5}
-figS08b <- d3_mech_choice %>%
-  filter(!is.na(dev_factor_cluster)) %>%
-  count(dev_factor_cluster, factor) %>%
-  mutate(dev_factor_cluster = case_when(
-    # is.na(dev_factor_cluster) ~ "Other",
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC", 
-                                           "EXTRINSIC")),
-                                           # "Other")),
-    blank_var = "  ") %>%
-  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
-                                 width = 28, side = "left"),
-                         as.numeric(dev_factor_cluster)),
-             y = n,
-             fill = factor, color = factor)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(toupper(factor), as.numeric(factor))),
-             scales = "free_x", space = "free_x") +
-  geom_bar(stat = "identity", alpha = 0.6) +
-  scale_fill_viridis_d(end = 0.9, option = "viridis", aesthetics = c("color", "fill")) +
-  scale_y_continuous(breaks = seq(0, 
-                                  2 * d3_mech_choice %>% 
-                                    distinct(ResponseId) %>% 
-                                    count() %>% 
-                                    pull(n), 
-                                  2 * 100),
-                     limits = c(0, 
-                                2 * d3_mech_choice %>% 
-                                  distinct(ResponseId) %>% 
-                                  count() %>% 
-                                  pull(n))) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism type",
-       y = "Count of responses",
-       color = "Domain", fill = "Domain") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
-         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# figS08b
-```
-
-```{r figS08, fig.cap="Selection of the various mechanisms as the 'most important' driver of development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
-Panel A shows selections for each developmental mechanism and both of the capacities within each domain; Panel B shows selections for extrinsic vs.
-intrinsic mechanisms for each domain of capacities (identical to Figure 3, Panel C, main text).
-Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 4.5, fig.asp = 6.75/6}
-plot_grid(figS08a + guides(fill = guide_none(), color = guide_none()),
-          figS08b + guides(fill = guide_none(), color = guide_none()) + labs(y = NULL), 
-          nrow = 1, rel_widths = c(4.5, 1.5), labels = "AUTO")
-
-# save plot
-if (resave_plots == T | !file.exists("../outputs/figS08.pdf")) {
-  ggsave("../outputs/figS08.svg")
-  ggsave("../outputs/figS08.pdf")
-}
-```
-
-```{r fig03c, fig.width = 1.5, fig.asp = 6.75/1.5}
-fig03c <- d3_mech_choice %>%
-  # filter(!is.na(dev_factor_cluster)) %>%
-  filter(dev_factor != "other") %>%
-  mutate(dev_factor_cluster = case_when(
-    dev_factor == "brain_changes" ~ "brain changes",
-    dev_factor_cluster == "intrinsic" ~ "INTRINSIC",
-    dev_factor_cluster == "extrinsic" ~ "EXTRINSIC"),
-    dev_factor_cluster = factor(dev_factor_cluster,
-                                levels = c("INTRINSIC", 
-                                           "EXTRINSIC",
-                                           "brain changes"))) %>%
-  count(dev_factor_cluster, factor) %>%
-  mutate(blank_var = "  ") %>%
-  ggplot(aes(x = reorder(str_pad(dev_factor_cluster, 
-                                 width = 28, side = "left"),
-                         as.numeric(dev_factor_cluster)),
-             y = n,
-             fill = factor, color = factor)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(toupper(factor), as.numeric(factor))),
-             scales = "free_x", space = "free_x") +
-  geom_bar(stat = "identity", alpha = 0.6) +
-  scale_fill_viridis_d(end = 0.9, option = "viridis", aesthetics = c("color", "fill")) +
-  scale_y_continuous(breaks = seq(0, 
-                                  2 * d3_mech_choice %>% 
-                                    distinct(ResponseId) %>% 
-                                    count() %>% 
-                                    pull(n), 
-                                  2 * 100),
-                     limits = c(0, 
-                                2 * d3_mech_choice %>% 
-                                  distinct(ResponseId) %>% 
-                                  count() %>% 
-                                  pull(n))) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top",
-        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Developmental mechanism type",
-       y = "Count of responses",
-       color = "Domain", fill = "Domain") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)),
-         fill = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# fig03c
-```
-
-```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
-intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
-intrinsic mechanisms as the 'most important' driver of development.
-Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 5, fig.asp = 6.75/(4.5 + 1.5 + 1.5)}
-plot_grid(fig03a + guides(color = guide_none()),
-          NULL, # to adjust spacing between panels
-          fig03b, # + labs(x = " "),
-          NULL,
-          fig03c + 
-            labs(x = " ",
-                 y = "Selection of 'most important' mechanism") +
-            scale_y_continuous(limits = c(0, 2*nrow(d3_demo)),
-                               breaks = c(0, nrow(d3_demo), 2*nrow(d3_demo)),
-                               labels = c("0%", "50%", "100%")) +
-            guides(fill = guide_none(),
-                   color = guide_none()), 
-          nrow = 1, rel_widths = c(4.5, 0.1, 1.5, 0.1, 1.5), 
-          labels = c("A", "", "B", "", "C"))
+  theme(panel.border = element_rect(fill = NA, linewidth = 0.2),
+        panel.spacing.x = unit(2, "lines"),
+        legend.position = "bottom",
+        legend.box = "vertical",
+        legend.spacing = unit(0, unit = "lines"),
+        legend.box.spacing = unit(0, unit = "lines"),
+        plot.margin = unit(c(1,3,1,1), "lines")) +
+  scale_y_continuous(limits = c(NA, NA), breaks = seq(0, 6, 1)) +
+  coord_flip(ylim = c(0, 6), xlim = c(1, 10), clip = "off") +
+  labs(y = "\nImportance rating (0 = not at all important, 6 = extremely important)", 
+       x = "Developmental mechanism")
 
@@
 
-```{r fig03_jpg, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and both of the capacities within each domain; Panel B shows mean ratings for extrinsic vs.
-intrinsic mechanisms for each domain of capacities; and Panel C shows the percentage of trials on which participants selected extrinsic vs.
-intrinsic mechanisms as the 'most important' driver of development.
-Lighter points and lines represent individual participants' responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panels A and B is intended to aid visual comparison across domains.", fig.width = 5, fig.asp = 6.75/(4.5 + 1.5 + 1.5)}
-plot_grid(fig03a + guides(color = guide_none()),
-          NULL, # to adjust spacing between panels
-          fig03b_jpg, # + labs(x = " "),
-          NULL,
-          fig03c + 
-            labs(x = " ",
-                 y = "Selection of 'most important' mechanism") +
-            scale_y_continuous(limits = c(0, 2*nrow(d3_demo)),
-                               breaks = c(0, nrow(d3_demo), 2*nrow(d3_demo)),
-                               labels = c("0%", "50%", "100%")) +
-            guides(fill = guide_none(),
-                   color = guide_none()), 
-          nrow = 1, rel_widths = c(4.5, 0.1, 1.5, 0.1, 1.5), 
-          labels = c("A", "", "B", "", "C"))
+```{r fig03_jpg, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
+Small, lighter points represent individual participants’ ratings of how important each developmental mechanism is in the development of each capacity within a domain (first row: bodily sensation; second row: negative affect; third row: social connection; fourth row: cognition and control).
+Larger black and red points correspond to mean importance ratings across the sample, and error bars are bootstrapped 95% confidence intervals.
+On the right side of each panel are the percentages of participants who selected each developmental mechanism as the ‘most important’ driver of development for that capacity, with modal selections in red.", fig.width = 10, fig.asp = 1.2}
+d3_mech_ratings %>%
+  left_join(d3_mech_choice_sum_c %>% select(dev_factor_text, factor, capacity, prop)) %>%
+  left_join(d3_mech_choice_modes_within10 %>% mutate(mode = T)) %>%
+  mutate(mode = ifelse(is.na(mode), F, T),
+         capacity = str_wrap(gsub("_", " ", capacity), 100)) %>% 
+  ggplot(aes(x = reorder(dev_factor_text, desc(as.numeric(dev_factor_text))), 
+             y = response)) +
+  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor))), ncol = 2,
+             scales = "free_x") + # to repeat axis labels
+  ggnewscale::new_scale_color() +
+  geom_jitter(
+    aes(color = factor), 
+    height = 0.2, size = 0.1, alpha = 0.4,
+    show.legend = F) +
+  scale_color_viridis_d(
+    name = "Domain:",
+    end = 0.9, option = "viridis") +
+  ggnewscale::new_scale_color() +
+  geom_pointrange( # 95% CIs
+    data = . %>%
+      group_by(factor, capacity, dev_factor_text, mode) %>%
+      multi_boot_standard(col = "response", na.rm = T) %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, color = mode)) +
+  # geom_pointrange( # standard deviations
+  #   data = . %>%
+  #     group_by(factor, capacity, dev_factor_text) %>%
+  #     summarise(mean = mean(response, na.rm = T),
+  #               sd = sd(response, na.rm = T),
+  #               n = n(),
+  #               ci_lower = mean - sd,
+  #               ci_upper = mean + sd) %>%
+  #     ungroup(),
+  #   aes(y = mean, ymin = ci_lower, ymax = ci_upper)) +
+  scale_color_manual(
+    name = "Modal choice of 'most important' developmental mechanism:", 
+    values = c("black", "#f94802")) +
+  geom_text(
+    data = . %>%
+      distinct(factor, capacity, dev_factor, dev_factor_text, prop, mode),
+    aes(y = 6.5, label = paste0(round(prop, 2)*100, "%"),
+        color = mode),
+    size = 2, hjust = 0,
+    show.legend = F) +
+  annotate(geom = "text", label = "'most important'\nmechanism", 
+           size = 2, hjust = 0.5, vjust = 0, 
+           x = 11, y = 6.5) +
+  theme_minimal() + 
+  theme(panel.border = element_rect(fill = NA, linewidth = 0.2),
+        panel.spacing.x = unit(2, "lines"),
+        legend.position = "bottom",
+        legend.box = "vertical",
+        legend.spacing = unit(0, unit = "lines"),
+        legend.box.spacing = unit(0, unit = "lines"),
+        plot.margin = unit(c(1,3,1,1), "lines")) +
+  scale_y_continuous(limits = c(NA, NA), breaks = seq(0, 6, 1)) +
+  coord_flip(ylim = c(0, 6), xlim = c(1, 10), clip = "off") +
+  labs(y = "\nImportance rating (0 = not at all important, 6 = extremely important)", 
+       x = "Developmental mechanism")
 
@@
                    mech_rat_ss_c = d3_mech_ratings_sum_c,
+                   mech_rat_ss_d = d3_mech_ratings_sum_d,
                    gam = s3_gam, 
@@
                    mech_choice_ss_b = d3_mech_choice_sum_b,
-                   glmer = s3_glmer, 
-                   glmer_bod = s3_glmer_bod,
-                   glmer_neg = s3_glmer_neg,
-                   glmer_soc = s3_glmer_soc,
-                   glmer_cog = s3_glmer_cog)
+                   mech_choice_ss_c = d3_mech_choice_sum_c,
+                   mech_choice_modes = d3_mech_choice_modes_within10)
 
@@
 ```
-
-```{r}
-# ADDITIONAL EXPLORATORY ANALYSES  NOT DESCRIBED IN SUPPLEMENT
-```
-
-```{r figS09a, fig.width = 4.5, fig.asp = 0.4}
-figS09a <- d2_gam %>% 
-  group_by(factor, capacity, target_year) %>%
-  summarise(var = var(response, na.rm = T)) %>%
-  ungroup() %>%
-  ggplot(aes(x = target_year, y = var, color = factor)) +
-  facet_grid(cols = vars(factor)) +
-  geom_path(aes(group = capacity), 
-            alpha = 0.1, size = 0.5,
-            position = position_jitter(width = 0.2, 
-                                       height = 0, 
-                                       seed = 94305)) +
-  geom_point(alpha = 1, size = 0.5,
-             position = position_jitter(width = 0.2, 
-                                        height = 0, 
-                                        seed = 94305)) +
-  geom_text(data = . %>% 
-              filter(target_year == 5) %>%
-              group_by(factor) %>%
-              filter(var == max(var) | var == min(var)) %>%
-              ungroup(),
-            aes(x = 5.2, label = str_wrap(gsub("_", " ", capacity), 18)),
-            color = "black", hjust = 0, size = 2) +
-  geom_pointrange(data = . %>%
-                    group_by(factor) %>%
-                    multi_boot_standard(col = "var") %>%
-                    ungroup(),
-                  aes(x = 2.5, y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "black", shape = 15, size = 0.5) +
-  geom_pointrange(data = . %>%
-                    filter(target_year == 0) %>%
-                    group_by(factor) %>%
-                    multi_boot_standard(col = "var") %>%
-                    ungroup(),
-                  aes(x = -0.5, y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "#f94802", shape = 15, size = 0.3) +
-  scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_x_continuous(limits = c(NA, 9), breaks = seq(0, 5, 1)) +
-  scale_y_continuous(limits = c(0, 0.16)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA)) +
-  labs(x = "Target age (years)",
-       y = "Variance") +
-  guides(color = guide_none())
-```
-
-```{r figS09b, fig.width = 4.5, fig.asp = 0.4}
-figS09b <- d3_gam %>% 
-  group_by(factor, capacity, target_year) %>%
-  summarise(var = var(response, na.rm = T)) %>%
-  ungroup() %>%
-  ggplot(aes(x = target_year, y = var, color = factor)) +
-  facet_grid(cols = vars(factor)) +
-  geom_path(aes(group = capacity), 
-            alpha = 0.1, size = 0.5,
-            position = position_jitter(width = 0.2, 
-                                       height = 0, 
-                                       seed = 94305)) +
-  geom_point(alpha = 1, size = 0.5,
-             position = position_jitter(width = 0.2, 
-                                        height = 0, 
-                                        seed = 94305)) +
-  geom_text(data = . %>% filter(target_year == 5),
-            aes(x = 5.2, label = str_wrap(gsub("_", " ", capacity), 18)),
-            color = "black", hjust = 0, size = 2) +
-  geom_pointrange(data = . %>%
-                    group_by(factor) %>%
-                    multi_boot_standard(col = "var") %>%
-                    ungroup(),
-                  aes(x = 2.5, y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "black", shape = 15, size = 0.5) +
-  geom_pointrange(data = . %>%
-                    filter(target_year == 0) %>%
-                    group_by(factor) %>%
-                    multi_boot_standard(col = "var") %>%
-                    ungroup(),
-                  aes(x = -0.5, y = mean, ymin = ci_lower, ymax = ci_upper),
-                  color = "#f94802", shape = 15, size = 0.3) +
-  scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_x_continuous(limits = c(NA, 9), breaks = seq(0, 5, 1)) + 
-  scale_y_continuous(limits = c(0, 0.16)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA)) +
-  labs(x = "Target age (years)",
-       y = "Variance") +
-  guides(color = guide_none())
-```
-
-```{r figS09 code, fig.width = 4, fig.asp = 1.2}
-plot_grid(figS09a, figS09b,
-          ncol = 1, labels = "AUTO")
-
-# save plot
-if (resave_plots == T | !file.exists("../outputs/figS09.pdf")) {
-  ggsave("../outputs/figS09.svg")
-  ggsave("../outputs/figS09.pdf")
-}
-```
-
-```{r figS09, fig.cap="Variance of capacity attributions in four domains of mental life (Studies 2-3).
-Lighter dots and lines represent variance across participnts for a particular capacity at a particular target age, red points correpond to mean variance across capacities at birth, black points correspond to mean variance across capacities and across all target ages, and error bars are bootstrapped 95% confidence intervals.
-In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
-In Study 3 (Panel B), participants assessed 2 capacities within each domain, and assessed a single capacity for all target ages before moving on to the next capacity."}
-knitr::include_graphics("../outputs/figS09.pdf")
-```
-
-# Study comparison: Capacity attributions to newborns, 9-months, and 5-year-olds
-
-```{r}
-d123_gam <- full_join(
-  d1_gam %>% mutate(study = "Study 1"),
-  d2_gam %>% mutate(study = "Study 2")) %>%
-  mutate(target_num = target_year*12) %>%
-  left_join(d3_gam %>% distinct(target, target_ord)) %>%
-  full_join(d3_gam %>% mutate(study = "Study 3"))
-```
-
-```{r, fig.width = 5.5, fig.asp = 1}
-figS10a <- d123_gam %>%
-  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
-  filter(capacity %in% (d2_gam %>% distinct(capacity) %>% pull(capacity))) %>%
-  complete(
-    capacity, nesting(study, target, target_year, target_num, target_ord), 
-    fill = list(response = -1)) %>% # introduce -1 to align studies across panels
-  select(-factor) %>%
-  # left_join(d2_gam %>% distinct(capacity, factor)) %>%
-  left_join(d2_scales %>% select(-loading)) %>%
-  mutate(capacity_text = str_wrap(gsub("_", " ", capacity), 40)) %>%
-  ggplot(aes(x = target_ord, y = response, color = study)) +
-  facet_wrap(facets = vars(reorder(capacity_text, as.numeric(order))), nrow = 4) +
-  geom_point(
-    size = 0.02,
-    alpha = 0.6,
-    position = position_jitterdodge(
-      dodge.width = 0.8,
-      jitter.width = 0.2,
-      jitter.height = 0)) +
-  geom_pointrange(
-    data = . %>%
-      group_by(study, target, target_year, target_num, target_ord, 
-               factor, capacity, capacity_text, order) %>%
-      multi_boot_standard(col = "response") %>%
-      ungroup(),
-    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
-    color = "black", fatten = 2,
-    position = position_dodge(width = 0.8)) +
-  # scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(
-    limits = c(0, 1), # exclude the specious "-1" responses introduced above
-    breaks = seq(0, 1, 0.25),
-    labels = seq(0, 100, 25)) +
-  scale_x_discrete(labels = c("newborns", "9 months", "5 years")) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        legend.position = "top") +
-        # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Target age",
-       y = "Mean response\n0 = not at all capable, 100 = completely capable",
-       color = "Study") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# figS10a
-```
-
-```{r, fig.width = 5.5, fig.asp = 1}
-figS10b <- d123_gam %>%
-  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
-  filter(capacity %in% (d2_gam %>% distinct(capacity) %>% pull(capacity))) %>%
-  select(-factor) %>%
-  # left_join(d2_gam %>% distinct(capacity, factor)) %>%
-  left_join(d2_scales %>% select(-loading)) %>%
-  group_by(study, ResponseId, target_ord, factor) %>%
-  summarise(score = mean(response, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(blank_var = "(2-5 common capacities)",
-         factor_lab = toupper(factor)) %>%
-  ggplot(aes(x = target_ord, y = score, color = study)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(factor_lab, as.numeric(factor)))) +
-             # switch = "y") +
-  geom_point(
-    size = 0.02,
-    alpha = 0.6,
-    position = position_jitterdodge(
-      dodge.width = 0.8,
-      jitter.width = 0.2,
-      jitter.height = 0)) +
-  geom_pointrange(
-    data = . %>%
-      group_by(study, target_ord, factor, factor_lab) %>%
-      multi_boot_standard(col = "score") %>%
-      ungroup(),
-    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
-    color = "black", fatten = 7, shape = 18,
-    position = position_dodge(width = 0.8)) +
-  # scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(#position = "right",
-                     breaks = seq(0, 1, 0.25),
-                     labels = seq(0, 100, 25)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        # strip.placement = "outside",
-        panel.spacing.y = unit(1.6, "lines"),
-        legend.position = "top") +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Target age",
-       y = "Mean response\n0 = not at all capable, 100 = completely capable",
-       color = "Study") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# figS10b
-```
-
-```{r, fig.width = 4, fig.asp = 0.9}
-figS10c <- d123_gam %>%
-  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
-  group_by(study, ResponseId, target_ord, factor) %>%
-  summarise(score = mean(response, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(blank_var = "(all capacities, varies by study)",
-         factor_lab = toupper(factor)) %>%
-  ggplot(aes(x = target_ord, y = score, color = study)) +
-  facet_grid(cols = vars(blank_var),
-             rows = vars(reorder(factor_lab, as.numeric(factor)))) +
-  geom_point(
-    size = 0.02,
-    alpha = 0.6,
-    position = position_jitterdodge(
-      dodge.width = 0.8,
-      jitter.width = 0.2,
-      jitter.height = 0)) +
-  geom_pointrange(
-    data = . %>%
-      group_by(study, target_ord, factor, factor_lab) %>%
-      multi_boot_standard(col = "score") %>%
-      ungroup(),
-    aes(y = mean, ymin = ci_lower, ymax = ci_upper, group = study),
-    color = "black", fatten = 7, shape = 18,
-    position = position_dodge(width = 0.8)) +
-  # scale_color_viridis_d(end = 0.9, option = "viridis") +
-  scale_y_continuous(breaks = seq(0, 1, 0.25),
-                     labels = seq(0, 100, 25)) +
-  theme_minimal() +
-  theme(panel.background = element_rect(fill = NA), 
-        strip.text = element_text(vjust = 0),
-        panel.spacing.y = unit(1.6, "lines"),
-        legend.position = "top") +
-        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
-  labs(x = "Target age",
-       y = "Mean response\n0 = not at all capable, 100 = completely capable",
-       color = "Study") +
-  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-# figS10c
-```
-
-```{r figS10 code, fig.width = 8, fig.asp = 1}
-plot_grid(get_legend(figS10a),
-          plot_grid(figS10a + guides(color = guide_none()), 
-                    figS10b + guides(color = guide_none()) + 
-                      theme(axis.title.y = element_blank(),
-                            strip.text.y = element_blank()),
-                    figS10c + guides(color = guide_none()) +
-                      theme(axis.title.y = element_blank()),
-                    rel_widths = c(1, 0.25, 0.28),
-                    nrow = 1,
-                    labels = "AUTO"),
-          rel_heights = c(0.02, 1),
-          ncol = 1) ### xx bookmark
-
-# save plot
-if (resave_plots == T | !file.exists("../outputs/figS10.pdf")) {
-  ggsave("../outputs/figS10.svg")
-  ggsave("../outputs/figS10.pdf")
-}
-```
-
-```{r figS10, fig.cap="Comparison of capacity ratings across studies (Studies 1-3).
-Panel A is a visualization of responses for each of the capacities and target ages held in common across studies.
-Panel B is a visualization of the resulting 'scores' (mean capacity ratings) for each of the 4 domains identified in these studies (_bodily sensation_, _negative affect_, _social connection_, and _cognition and control_\\)\\, considering only those capacities depicted in Panel A.
-Panel C is a visualization of scores for each of these 4 domains considering all of the capacities included in each study.
-Lighter colorful represent individual participants’ responses or scores, black points correspond to mean responses or scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
-knitr::include_graphics("../outputs/figS10.pdf")
-```
-
-As described in the main text, all of the current studied employed a fixed-order design, in which all participants assessed target ages in a fixed order beginning with the youngest target age (newborns) and proceeding chronologically until the oldest target age (5-year-olds).
-This decision reflects the fact that our priority in these studies was to assess beliefs about the developmental trajectories of capacities, rather than beliefs about capacities at a specific point in development.
-However, one limitation of this fixed-order design is that it makes it difficult to assess the stability of participants’ assessments of the fine-grained differences between specific points in development.
-
-To provide some sense of the stability of participants' representations of specific target ages, Supplementary Figure \@ref(fig:figS10) presents a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds).
-As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here.
-In Study 2, participants assessed the 20 capacities depicted in Panel A, at 13 target ages (including but not limited to the 3 target ages depicted here).
-In Study 3, participants assessed 8 capacities (a subset of the 20 capacities depicted in Panel A), at 13 target ages (including but not limited to the 3 target ages depicted here).
 
@@
 d_cap_comp <- read_csv("../data/capacities_comparison.csv") %>%
-  mutate_if(is.character, funs(tolower(.))) %>%
-  mutate_if(is.character, funs(gsub("recognizing others.", "recognizing others'", .))) %>%
-  mutate_if(is.character, funs(gsub("self.control", "self-control", .))) %>%
+  mutate(across(where(is.character), ~tolower(.))) %>%
+  mutate(across(where(is.character), ~gsub("recognizing others.", "recognizing others'", .))) %>%
+  mutate(across(where(is.character), ~gsub("self.control", "self-control", .))) %>%
   left_join(d1_scales %>%
@@
          `Weisman et al. (2017, Proc. CogSci)` = `Weisman et al. (2017b)`) %>%
-  mutate_at(vars(`Weisman et al. (2017, PNAS)`, `Weisman et al. (2017, Proc. CogSci)`, 
+  mutate(across(c(`Weisman et al. (2017, PNAS)`, `Weisman et al. (2017, Proc. CogSci)`, 
                   `Gray et al. (2007)`, `Malle (2019, Study 1)`, `Malle (2019, Study 2)`),
-            funs(case_when(is.na(`Study 1`) & grepl("similar to", .) ~ NA_character_, TRUE ~ .))) %>%
+                ~case_when(is.na(`Study 1`) & grepl("similar to", .) ~ NA_character_, TRUE ~ .))) %>%
   arrange(order, `Weisman et al. (2017, PNAS)`, `Weisman et al. (2017, Proc. CogSci)`, 
@@
              is.na(`Malle (2019, Study 2)`))) %>%
-  mutate_if(is.character, funs(replace_na(., "-"))) %>%
+  mutate(across(where(is.character), ~replace_na(., "-"))) %>%
   mutate(factor = case_when(is.na(factor) ~ "Not included", TRUE ~ as.character(factor)),
@@
   mutate_all(~gsub("similar to .", "similar to \\`", .)) %>% 
-  mutate(`Study 1` = case_when(`Study 2` != "-" ~ paste0(`Study 1`, 
-                                                         footnote_marker_symbol(1)),
+  mutate(`Study 1` = case_when(
+    `Study 2` != "-" ~ paste0(`Study 1`, footnote_marker_symbol(1)),
     TRUE ~ `Study 1`)) %>%
-  mutate(`Study 1` = case_when(`Study 3` != "-" ~ paste0(`Study 1`, 
-                                                         footnote_marker_symbol(2)),
+  mutate(`Study 1` = case_when(
+    `Study 3` != "-" ~ paste0(`Study 1`, footnote_marker_symbol(2)),
     TRUE ~ `Study 1`)) %>%
   select(-`Study 2`, -`Study 3`) %>%
-  mutate_at(vars(`Gray et al. (2007)`),
-            funs(gsub("\\..*", "", .))) %>%
+  mutate(across(c(`Gray et al. (2007)`),
+                ~gsub("\\..*", "", .))) %>%
   kable("latex", booktabs = T, escape = F, longtable = T) %>%

### 2024-12-19 code/custom_funs.R

@@ -7,7 +7,7 @@ round_x <- function(n, x = 2) { format(round(n, x), nsmall = x) }
 heatmap_fun <- function(efa, factor_names = NA){
   
   # get factor names
-  if(is.na(factor_names)){
+  if(anyNA(factor_names)){
     factor_names <- paste("Factor", 1:efa$factors)
   }
   

### 2024-12-19 code/data_prep_s3.R

@@ -376,10 +376,10 @@ d3_dev_factor_rating <- d3 %>%
                                         "brain_changes",
                                         "senses_improve", 
                                         "observes_objects",
-                                        "experiments",
                                         "observes_people",
                                         "interacts_people",
-                                        "people_teach"))) %>%
+                                        "people_teach",
+                                        "experiments"))) %>%
   mutate(ResponseId = as.character(ResponseId))
 
 # dev_factor "most important" for ALL TARGETS, ALL CAPACITIES
@@ -400,9 +400,9 @@ d3_dev_factor_most_important <- d3 %>%
                                         "senses_improve", 
                                         "observes_objects",
                                         "observes_people",
-                                        "experiments",
                                         "interacts_people",
-                                        "people_teach")))
+                                        "people_teach",
+                                        "experiments")))
 
 d3_dev_factor_most_important_choice <- d3_dev_factor_most_important %>%
   filter(!is.na(response), response != "", !grepl("free", question)) %>%

### 2024-12-19 install-packages.R
updates to environment and readme

@@ -10,9 +10,9 @@ package_list <- c(
   "mgcv",
   "kableExtra",
   "parameters",
-  "ggdendro",
-  "dendextend",
   "cowplot",
+  "rsq",
+  "ggnewscale",
   "bookdown"
 )
 

### 2024-12-19 supplement/supplement-main.Rmd
rerun figure making and tweaks to supplement

@@
 
-# save plot
-if (resave_plots == T | !file.exists("../outputs/fig02a_gam.pdf")) {
-  ggsave("../outputs/fig02a_gam.svg")
-  ggsave("../outputs/fig02a_gam.pdf")
-  ggsave("../outputs/fig02a_gam.jpg")
-}
+# # save plot
+# if (resave_plots == T | !file.exists("../outputs/fig02a_gam.pdf")) {
+#   ggsave("../outputs/fig02a_gam.svg")
+#   ggsave("../outputs/fig02a_gam.pdf")
+#   ggsave("../outputs/fig02a_gam.jpg")
+# }
 ```
@@
 
-# save plot
-if (resave_plots == T | !file.exists("../outputs/fig02b_gam.pdf")) {
-  ggsave("../outputs/fig02b_gam.svg")
-  ggsave("../outputs/fig02b_gam.pdf")
-}
+# # save plot
+# if (resave_plots == T | !file.exists("../outputs/fig02b_gam.pdf")) {
+#   ggsave("../outputs/fig02b_gam.svg")
+#   ggsave("../outputs/fig02b_gam.pdf")
+# }
 ```
@@
 
+# Study comparison: Capacity attributions to newborns, 9-months, and 5-year-olds
+
+As described in the main text, all of the current studied employed a fixed-order design, in which all participants assessed target ages in a fixed order beginning with the youngest target age (newborns) and proceeding chronologically until the oldest target age (5-year-olds).
+This decision reflects the fact that our priority in these studies was to assess beliefs about the developmental trajectories of capacities, rather than beliefs about capacities at a specific point in development.
+However, one limitation of this fixed-order design is that it makes it difficult to assess the stability of participants’ assessments of the fine-grained differences between specific points in development.
+
+To provide some sense of the stability and reliability of US adults' representations of specific target ages across studies, Supplementary Figure \@ref(fig:figS06) presents a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds).
+As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here.
+In Study 2, participants assessed the 20 capacities depicted in Panel A, at 13 target ages (including but not limited to the 3 target ages depicted here).
+In Study 3, participants assessed 8 capacities (a subset of the 20 capacities depicted in Panel A), at 13 target ages (including but not limited to the 3 target ages depicted here).
+
+```{r}
+d123_gam <- full_join(
+  d1_gam %>% 
+    mutate(study = "Study 1"),
+  d2_gam %>% 
+    mutate(study = "Study 2") %>%
+    mutate(response = response*100)) %>%
+  left_join(
+    d3_gam %>% 
+      distinct(target, target_ord)) %>%
+  full_join(
+    d3_gam %>% 
+      mutate(study = "Study 3") %>%
+      mutate(response = response*100))
+```
+
+```{r figS06 code, fig.width = 10, fig.asp = 1.2}
+figS06 <- d123_gam %>%
+  filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
+  filter(capacity %in%
+           c(full_join(d2_gam %>% distinct(capacity),
+                       d3_gam %>% distinct(capacity)) %>%
+               distinct(capacity) %>%
+               pull(capacity) %>%
+               as.character())) %>%
+  complete(
+    capacity, nesting(study, target, target_year, target_num, target_ord),
+    fill = list(response = -1)) %>% # introduce -1 to align studies across panels
+  select(-factor) %>%
+  left_join(d2_gam %>% distinct(capacity, factor)) %>%
+  left_join(d2_scales %>% select(-loading)) %>%
+  mutate(capacity_text = str_wrap(gsub("_", " ", capacity), 40)) %>%
+  ggplot(aes(x = target_ord, y = response, 
+             color = factor)) +
+  facet_wrap(facets = vars(reorder(capacity_text, as.numeric(order))), nrow = 4) +
+  geom_point(
+    aes(group = study),
+    size = 0.02,
+    alpha = 0.6,
+    position = position_jitterdodge(
+      dodge.width = 0.8,
+      jitter.width = 0.6,
+      jitter.height = 0)) +
+  scale_color_viridis_d(end = 0.9, option = "viridis") +
+  geom_path(
+    data = . %>%
+      group_by(study, target, target_year, target_num, target_ord, 
+               factor, capacity, capacity_text, order) %>%
+      summarise(mean = mean(response, na.rm = T)) %>%
+      ungroup(),
+    aes(y = mean, group = study),
+    color = "black", lty = 2, 
+    position = position_dodge(width = 0.8)) +
+  geom_pointrange(
+    data = . %>%
+      group_by(study, target, target_year, target_num, target_ord, 
+               factor, capacity, capacity_text, order) %>%
+      multi_boot_standard(col = "response") %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper, 
+        group = study, fill = study),
+    color = "black", shape = 21, fatten = 6,
+    position = position_dodge(width = 0.8)) +
+  geom_text(
+    data = . %>%
+      group_by(study, target, target_year, target_num, target_ord, 
+               factor, capacity, capacity_text, order) %>%
+      summarise(mean = mean(response, na.rm = T)) %>%
+      ungroup(),
+    aes(y = mean, group = study, label = gsub("Study ", "", study)),
+    color = "white", size = 2.5, fontface = "bold", hjust = 0.5, vjust = 0.5,
+    position = position_dodge(width = 0.8)) +
+  scale_fill_manual(values = c("#9801a3", "#a3012f", "#a36501")) +
+  scale_y_continuous(
+    limits = c(-0.05, NA), # exclude the specious "-1" responses introduced above
+    breaks = seq(0, 100, 25),
+    labels = seq(0, 100, 25)) +
+  scale_x_discrete(labels = c("newborns", "9 months", "5 years")) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        legend.position = "top") +
+        # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Target age",
+       y = "Mean response\n0 = not at all capable, 100 = completely capable",
+       color = "Domain:",
+       fill = "Study:") +
+  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+figS06
+
+if (resave_plots == T | !file.exists("../outputs/figS06.pdf")) {
+  ggsave("../outputs/figS06.svg")
+  ggsave("../outputs/figS06.pdf")
+}
+```
+
+```{r figS06, fig.cap="Comparison of capacity ratings across studies (Studies 1-3).
+This visualization includes responses for each of the capacities and target ages held in common across at least two of our three studies.
+Lighter colorful represent individual participants’ responses or scores, larger points correspond to mean responses or scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
+knitr::include_graphics("../outputs/figS06.pdf")
+```
+
 # Selection of capacities: Comparison to previous studies
 
-Supplementary Table \@ref(tab:tabs1efaparload) provides an item-by-item comparison of the capacities included in this study to capacities included in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
+Supplementary Table \@ref(tab:tabcapcomp) provides an item-by-item comparison of the capacities used here to those used in previous studies of mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @malle2019].
 
@@
 
-```{r tabcapcomp, include = T, warning = F, message = F}
-d_cap_comp %>%
+```{r tabcapcomp, results = "asis", include = T, warning = F, message = F}
+cat("\\begin{landscape}")
+tabcapcomp <- d_cap_comp %>%
   select(-Domain) %>%
@@
                 ~gsub("\\..*", "", .))) %>%
-  kable("latex", booktabs = T, escape = F, longtable = T) %>%
+  kable("latex", booktabs = T, escape = F, longtable = T,
+        caption = "Item-by-item comparison of the capacities included in the current studies to capacities included in previous studies of mind perception.") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%
@@
                      "Previous studies" = 5)) %>%
-  column_spec(1, width = "4cm") %>%
-  column_spec(2:6, width = "2cm") %>%
+  # column_spec(1, width = "4cm") %>%
+  column_spec(2:6, width = "2.7cm") %>%
   pack_rows(group_label= "Bodily sensation", start_row = 1, end_row = 11) %>%
@@
            footnote_as_chunk = T)
+tabcapcomp
+cat("\\end{landscape}")
 ```

### 2024-12-19 paper/paper.Rmd
revisions

--- 2022-08-01 paper/paper.Rmd
@@
   pdf_document:  default
+  # word_document:
     # reference_docx: word-styles-ref.docx
-  # word_document:
 bibliography: ../supplement/references.bib
@@
 Caregiving relationships with infants and children are among the most common and most complex human social interactions.
-Adults’ perceptions of children’s mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children’s communication skills are limited and caregivers must infer children’s rapidly developing thoughts, feelings, and needs.
+Adults' perceptions of children's mental capacities have important consequences for the well-being of children in their care—particularly in the first few years of life, when children's communication skills are limited and caregivers must infer children's rapidly developing thoughts, feelings, and needs.
 In a series of studies, we assessed how US adults conceptualize the development of the human mind over the first five years of life.
-Exploratory factor analysis identified four core capacities that anchored participants’ representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
-Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms, such as biological “preprogramming,” physical maturation, passive observation, and social learning.
-The current studies shed light on this fascinating and understudied aspect of “mind perception” among US adults, in turn highlighting possibilities for theory-based interventions to encourage positive and responsive parenting behaviors.
+Exploratory factor analysis identified four core capacities that anchored participants' representations of the developing human mind: _bodily sensation_ (e.g., hunger, pain), _negative affect_ (e.g., distress, frustration), _social connection_ (e.g., love, learning from others), and _cognition and control_ (e.g., planning, self-control).
+Participants believed that these capacities were present to different degrees at birth, followed different developmental trajectories, and were driven by different developmental mechanisms, such as biological "preprogramming," physical maturation, passive observation, and social learning.
+The current studies shed light on this fascinating and understudied aspect of "mind perception" among US adults, in turn highlighting possibilities for theory-based interventions to encourage developmentally appropriate parenting behaviors.
 
@@
 Frustration, compassion, worry, humor, imagination, love—such experiences are fundamental parts of human life, but few people would assert that these capacities are fully developed at birth.
-In any given interaction with a child, adults come face to face with a being whose experience of the world is like their own, but different; whose mind is capable of some of the thoughts and feelings that an adult’s mind is, but perhaps not all of them.
-When an adult interacts with the same child over time, they witness innumerable changes in that child’s mental life: A sleepy newborn gradually becomes a child who experiences complex emotions and original ideas and develops personal memories and intricate plans.
-This familiar but remarkable transformation requires adults to make inferences about a given child’s developing mental capacities in order to interpret that child’s behaviors and respond appropriately.
+In any given interaction with a child, adults come face to face with a being whose experience of the world is like their own, but different; whose mind is capable of some of the thoughts and feelings that an adult's mind is, but perhaps not all of them.
+When an adult interacts with the same child over time, they witness innumerable changes in that child's mental life: A sleepy newborn gradually becomes a child who experiences complex emotions and original ideas and develops personal memories and intricate plans.
+This familiar but remarkable transformation requires adults to make inferences about a given child's developing mental capacities in order to interpret that child's behaviors and respond appropriately.
 
@@
 Do they love me?
-As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children’s behavior and development, with consequences for the well-being of children in their care.
+As in other domains of reasoning[@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children's behavior and development, with consequences for the well-being of children in their care.
 
@@
 A handful of recent studies have examined the extent to which cognitive abilities, knowledge, and emotions are thought to be innate vs.
-learned, with special attention to comparing laypeople’s beliefs about innateness to scientific evidence for or against innateness and universality [@wang.feigenson2019; @berent.etal2019; @berent.etal2020; see @berent2021 for discussion].
-These studies offer a fascinating glimpse of potential gaps, misconceptions, and biases in laypeople’s beliefs about the human mind, but they leave open many questions about the nature of the folk beliefs and intuitive theories themselves.
-What is the cognitive architecture underlying laypeople’s beliefs about the origins of the human mind?
+learned, with special attention to comparing laypeople's beliefs about innateness to scientific evidence for or against innateness and universality [@wang.feigenson2019; @berent.etal2019; @berent.etal2020; see @berent2021 for discussion].
+These studies offer a fascinating glimpse of potential gaps, misconceptions, and biases in laypeople's beliefs about the human mind, but they leave open many questions about the nature of the folk beliefs and intuitive theories themselves.
+What is the cognitive architecture underlying laypeople's beliefs about the origins of the human mind?
 How do laypeople "carve up" the various sensations, experiences, and abilities that make up human mental life, and—most crucially from the perspective of caregiving—how do laypeople understand changes in mental life across early development?
@@
 In a groundbreaking study, Gray et al.
-asked participants to compare the mental capacities of a range of humans, animals, technologies, and other entities, and argued that participants’ judgments revealed a fundamental distinction between "agency" (e.g., capacities for self-control, moral reasoning, memory, and planning) and "experience" (e.g., capacities for hunger, fear, pain, and pleasure) [@gray.etal2007].
+asked participants to compare the mental capacities of a range of humans, animals, technologies, and other entities, and argued that participants' judgments revealed a fundamental distinction between "agency" (e.g., capacities for self-control, moral reasoning, memory, and planning) and "experience" [e.g., capacities for hunger, fear, pain, and pleasure, @gray.etal2007].
 More recently, Weisman et al.
-used a similar empirical approach to argue that people’s conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" (perceptual-cognitive capacities such as vision and memory [@weisman.etal2017a; see @malle2019 for a similar three-factor solution].
+used a similar empirical approach to argue that people's conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" [perceptual-cognitive capacities such as vision and memory, @weisman.etal2017a; see @malle2019 for a similar three-factor solution].
 Such findings have inspired subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
@@
 In many studies, infants and children have simply not been included as targets for mental capacity attributions; instead, participants have been asked to reason about human adults alongside a range of non-human entities, including other animals, technologies, and supernatural beings.
-Even studies that have probed participants’ mental capacity attributions to infants and children have generally treated them as beings distinct from adults, rather than as snapshots of a single mind as it emerges and changes over time.
-For example, Gray et al.’s early work on mind perception suggested that a five-month-old infant is an entity that is generally considered to have experience but not agency—in contrast to, say, a five-year-old child (considered to have experience as well as limited agency), a human adult (considered to have maximal experience and agency), or a robot [considered to have agency but not experience; @gray.etal2007].
-Likewise, Weisman et al.’s studies characterized infants and young children—along with, e.g., chimpanzees, elephants, and dolphins—as entities that are perceived to be fully capable of physiological sensations but more limited in their perceptual-cognitive capacities and social-emotional abilities; this is in contrast to human adults, who are perceived to be fully capable across these domains [@weisman.etal2017a].
+Even studies that have probed participants' mental capacity attributions to infants and children have generally treated them as beings distinct from adults, rather than as snapshots of a single mind as it emerges and changes over time.
+For example, Gray et al.'s early work on mind perception suggested that a five-month-old infant is an entity that is generally considered to have experience but not agency—in contrast to, say, a five-year-old child (considered to have experience as well as limited agency), a human adult (considered to have maximal experience and agency), or a robot [considered to have agency but not experience, @gray.etal2007].
+Likewise, Weisman et al.'s studies characterized infants and young children—along with, e.g., chimpanzees, elephants, and dolphins—as entities that are perceived to be fully capable of physiological sensations but more limited in their perceptual-cognitive capacities and social-emotional abilities; this is in contrast to human adults, who are perceived to be fully capable across these domains [@weisman.etal2017a].
 Although such findings can be reinterpreted as providing preliminary evidence that people consider the minds of infants and children to differ from the minds of adults, they do not address how people conceptualize the development of the mind in early life.
@@
 In the current studies we set out to shed new light on this important and understudied aspect of mind perception: how laypeople reason about the development of human mental life.
-In three studies, we assessed US adults’ folk beliefs about children’s developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of "mental life," broadly construed.
+In three studies, we assessed US adults' folk beliefs about children's developing abilities for physiological sensation, perception, cognition, emotion, self-regulation, social interaction, and other aspects of "mental life," broadly construed.
 We focused on development between birth and age five years—a time of particularly dramatic maturation in perceptual acuity, emotional experience, cognitive ability, executive function, social engagement, and many other domains.
@@
 The first question we sought to address in this line of work was: What do US adults perceive to be the fundamental components of mental life, as they pertain to a developing human child?
-To this end, we began with an expansive exploration of US adults’ attributions of mental life to infants and young children in general; this laid the foundation for Studies 2-3, which we designed to assess the perceived developmental trajectories of these attributions across specific target ages.
+To this end, we began with an expansive exploration of US adults' attributions of mental life to infants and young children in general; this laid the foundation for Studies 2-3, which we designed to assess the perceived developmental trajectories of these attributions across specific target ages.
 
 Drawing inspiration from previous work on mind perception [@gray.etal2007; @weisman.etal2017a; @weisman.etal2017b; @weisman.etal2018] as well as standard assessments of infant temperament and behavior [@putnam.etal2006; @rothbart1978], we included a wide range of 60 capacities in this initial exploration, from basic physiological sensations, to capacities for perception, cognition, and emotion, to abilities for self-regulation and social interaction.
-We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants’ reasoning about the development of mental life.
+We asked participants to assess these capacities at three different ages (at birth, 9 months, and 5 years), with the goal of characterizing the conceptual structure underlying participants' reasoning about the development of mental life.
 
-We designed Study 1 to explore the correlational structure of participants’ responses, as a window into the underlying conceptual structure that might support their reasoning about the development of mental life.
-Our primary analysis was a preregistered exploratory factor analysis (EFA) of participants’ capacity ratings.
-This analysis allowed us to examine which capacities tend to "hang together" in participants’ assessments of the mental lives of infants and young children.
+We designed Study 1 to explore the correlational structure of participants' responses, as a window into the underlying conceptual structure that might support their reasoning about the development of mental life.
+Our primary analysis was a preregistered exploratory factor analysis (EFA) of participants' capacity ratings.
+This analysis allowed us to examine which capacities tend to "hang together" in participants' assessments of the mental lives of infants and young children.
 For example, when a participant indicated that newborns are highly capable of feeling scared, what other capacities did they tend to attribute to newborns?
-Following previous work on mind perception, we argue that the suites of capacities revealed by applying dimensionality reduction (in our case, EFA) to this covariance structure offer a meaningful approximation of the latent conceptual structure underlying participants’ reasoning about the developing human mind.
+Following previous work on mind perception, we argue that the suites of capacities revealed by applying dimensionality reduction (in our case, EFA) to this covariance structure offer a meaningful approximation of the latent conceptual structure underlying participants' reasoning about the developing human mind.
 
@@
 Participants predominantly identified as White (`r round((s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s1_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
-`r round(100*(s1_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree.
+`r round(100*(s1_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
 `r round(100*(s1_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
@@
 
-In planning this series of studies, we selected 13 target ages based on the developmental milestone ages identified by the CDC [@CDC2021] with the addition of the American Academy of Pediatrics’ recommendations for pediatrician visits before 2 months [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
+In planning this series of studies, we selected 13 target ages based on the developmental milestone ages identified by the CDC [@CDC2021] with the addition of the American Academy of Pediatrics' recommendations for pediatrician visits before 2 months [@AAP2018]: birth, 4 days, 1 month, 2 months, 4 months, 6 months, 9 months, 12 months, 18 months, 2 years, 3 years, 4 years, and 5 years.
 We limited Study 1 to just the youngest, median, and oldest target ages—presented to participants as "newborns," "9-month-olds" and "5-year-olds"—in order to maximize the number of capacities included in the study without over-burdening participants.
@@
 In this and all studies, we opted for this fixed-order design because our priority was to assess beliefs about the developmental trajectories of capacities, rather than beliefs about capacities at a specific point in development.
-The fixed order of target ages was intended to ensure that questions about developmental trajectories “flowed” in a coherent way [@krosnick.presser2009].
+The fixed order of target ages was intended to ensure that questions about developmental trajectories "flowed" in a coherent way [@krosnick.presser2009].
 
@@
 
-Following recent work on mind perception [@weisman.etal2021], our goal in this analysis was to derive a set of latent constructs that together give rise to people’s intuitions about the development of human mental life between 0-5 years.
+Following recent work on mind perception [@weisman.etal2021], our goal in this analysis was to derive a set of latent constructs that together give rise to people's intuitions about the development of human mental life between 0-5 years.
 We did not set out to sort each of the 60 capacities into discrete, non-overlapping categories of capacities.
@@
 This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors.
-See Supplemental Materials for more details about this analysis, including our decision to treat participants’ ratings of each of the three target ages as if they were a distinct source of data.
+See Supplemental Materials for more details about this analysis, including our decision to treat participants' ratings of each of the three target ages as if they were a distinct source of data.
 
-A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants’ and young children’s mental lives.
+A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants' capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants' and young children's mental lives.
 See Figure 1 for all factor loadings after oblique transformation.
@@
 The first factor corresponded primarily to capacities related to thinking, reasoning, agency, and executive function—a suite of capacities that we interpreted as reflecting a higher-order capacity for _cognition and control_.
-It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," "understanding what somebody else is thinking," "focusing on a goal," "feeling guilty," "feeling embarrassed," "feeling pride," "making choices," "calming themselves down," "detecting danger," and "feeling hopeless." (For this and the following factors, we list all of the items with loadings $\geq$ 0.60 in descending order by factor loading; see Figure 1 for the full set of loadings.) This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants’ capacity attributions.
+It was the dominant factor for such items as "planning," "having self-control," "thinking before they act," "having goals," "reasoning about things," "controlling their emotions," "telling right from wrong," "understanding what somebody else is thinking," "focusing on a goal," "feeling guilty," "feeling embarrassed," "feeling pride," "making choices," "calming themselves down," "detecting danger," and "feeling hopeless." (For this and the following factors, we list all of the items with loadings $\geq$ 0.60 in descending order by factor loading; see Figure 1 for the full set of loadings.) This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR1"]*100, 0)`% of the total variance in participants' capacity attributions.
 
 The second factor corresponded primarily to what we would describe as social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_.
-It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants’ sense of the infant awakening into the human social and cultural world.
-This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants’ capacity attributions.
+It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants' sense of the infant awakening into the human social and cultural world.
+This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants' capacity attributions.
 
 The third factor corresponded primarily to physiological sensations related to biological needs—a suite of capacities that we interpreted as reflecting a higher-order capacity for _bodily sensation_.
-It was the dominant factor for such items as "getting hungry", "feeling pain", "feeling tired", "feeling thirsty", "feeling too hot or too cold", "feeling physically uncomfortable", "hearing sounds", and "being comforted by physical touch", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR2"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR2"]*100, 0)`% of the total variance in participants’ capacity attributions.
+It was the dominant factor for such items as "getting hungry", "feeling pain", "feeling tired", "feeling thirsty", "feeling too hot or too cold", "feeling physically uncomfortable", "hearing sounds", and "being comforted by physical touch", and accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR2"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR2"]*100, 0)`% of the total variance in participants' capacity attributions.
 
@@
 Although there were no items that loaded more strongly than `r round_x(max(s1_results$efa$loadings[,"MR4"]))` on this factor, this factor was the dominant factor for the items "feeling helpless", "feeling overwhelmed", "feeling frustrated", "feeling annoyed", and "feeling neglected," and the items "feeling distressed", "feeling confused", "feeling worried", and "feeling lonely" also loaded relatively strongly on this factor (albeit slightly more strongly on other factors).
-This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants’ capacity attributions.
+This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR4"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR4"]*100, 0)`% of the total variance in participants' capacity attributions.
 
@@
 How robust are these findings?
-The factors we have called _bodily sensation_, _social connection_, and _cognition and control_ each had strong factor loadings ($\geq$ 0.60) for many individual items ($n$ = `r min(s1_strong_loadings$n)`-`r max(s1_strong_loadings$n)`) and each accounted for a substantial amount of the total variance in participants’ capacity attributions (`r round_x(min(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`-`r round_x(max(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`%), indicating three robustly distinct and interpretable factors.
+The factors we have called _bodily sensation_, _social connection_, and _cognition and control_ each had strong factor loadings ($\geq$ 0.60) for many individual items ($n$ = `r min(s1_strong_loadings$n)`-`r max(s1_strong_loadings$n)`) and each accounted for a substantial amount of the total variance in participants' capacity attributions (`r round_x(min(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`-`r round_x(max(s1_results$efa$Vaccounted["Proportion Var",c("MR1","MR3", "MR2")])*100, 0)`%), indicating three robustly distinct and interpretable factors.
 In contrast, the fourth factor—_negative affect_—had more moderate loadings even for its strongest-loading items (all loadings < `r abs(s1_results$efa$loadings[][,"MR4"]) %>% max() %>% round(., 2) + 0.01`) and accounted for only `r round_x(s1_results$efa$Vaccounted["Proportion Var","MR4"]*100, 0)`% of the total variance.
 Nonetheless, we opted to retain this factor in subsequent studies because we considered the general domain of _negative affect_ to be of particular theoretical and clinical interest.
-An individual’s propensity to negative affect in infancy and early childhood is a salient individual difference trait associated with risk for internalizing disorders [@gartstein.etal2012].
+An individual's propensity to negative affect in infancy and early childhood is a salient individual difference trait associated with risk for internalizing disorders [@gartstein.etal2012].
 Beyond this, positive and negatively valenced emotionality emerge at different developmental timescales: Signs of negative affect are present from birth (e.g., crying shortly following delivery), whereas signs of positive affect (e.g., social smiling, laughing) are not present for several weeks [@humphreys.etal2015], supporting both the relevance and distinctiveness of negative emotional expression in early life.
@@
 In our view, these cross-loadings were generally sensible.
-The item "feeling distressed", for instance, loaded roughly equally strongly on both bodily sensations and negative affect—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
-Likewise, "seeing" loaded equally strongly on both _bodily sensations_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
+The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensation_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
+Likewise, "seeing" loaded equally strongly on both _bodily sensation_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
 
-As a check on our choice of labels for these factors, we turned to OpenAI’s Generative Pre-trained Transformer 3 (GPT-3) [@brown.etal2020], an autoregressive transformer-based language prediction model trained on an enormous corpus of English-language text drawn primarily from “crawls” of the Internet as well as English-language novels and the open-source encyclopedia Wikipedia.
-GPT-3 is capable of generating remarkably human-like text in response to questions and other prompts.
-GPT-3, like other generative language models, was developed under the mandate of predicting the continuation of natural language sequences: Most concretely, then, its “responses” should be understood to reflect a sequence of words that is likely to follow the prompt it has been provided.
-In a more abstract sense, however, the content of these responses could be understood to represent the “common knowledge” embedded in the training data [for extended arguments relevant to this proposal, see @bhatia.richie2021; @lake.murphy2021; @petroni.etal2019].
-For example, if prompted with the questions “What do you get when you mix red and yellow?” or “What’s a good name for a vegetarian restaurant?,” GPT-3 will generate text like “When you mix red and yellow, you get orange” or “The Green Plate” (respectively).
+As a check on our choice of labels for these factors, we turned to OpenAI's Generative Pre-trained Transformer [ChatGPT, version 4o, @openAI2024], an autoregressive transformer-based language prediction model trained on an enormous corpus of English-language text drawn primarily from "crawls" of the Internet as well as English-language novels and the open-source encyclopedia Wikipedia.
+Like other generative language models, ChatGPT was developed under the mandate of predicting the continuation of natural language sequences: Most concretely, then, its "responses" should be understood to reflect a sequence of words that is likely to follow the prompt it has been provided.
+In a more abstract sense, however, the content of these responses could be understood to represent the "common knowledge" embedded in the training data [for extended arguments relevant to this proposal, see @bhatia.richie2021; @lake.murphy2021; @petroni.etal2019].
+For example, if prompted with the questions "What do you get when you mix red and yellow?" or "What's a good name for a vegetarian restaurant?," ChatGPT will generate text like "When you mix red and yellow, you get orange" or "The Green Plate" (respectively).
 In continuing the language sequence, the model also provides novel content that reflects actual human knowledge, biases, associations, and intuitions.
 
-Using the openly available GPT-3 “playground” (https://beta.openai.com/playground), we provided a variety of prompts to the model to assess its “intuitions” about how to label the four categories of mental capacities suggested by the factor solution just described.
-One representative prompt read, “Name these four categories of mental capacities: Category 1 is […].
-Category 2 is […],” and so on, with the ellipses replaced by lists of all the items for which each factor (“Category”) was the dominant factor.
-The response generated by GPT-3 in this case was as follows: “Category 1: Executive functioning skills.
-Category 2: Social and emotional skills.
-Category 3: Physical needs and sensations.
-Category 4: Negative emotions.” In nearly every variation of our prompts, GPT-3’s labels for the factor we have labeled cognition and control included the phrase “executive function”; its labels for the factor we have labeled social connection always nearly always included the word “social” or “social-emotional”; its labels for the factor we have labeled bodily sensation nearly always included the words “sensations” (and often “physical needs” or “basic needs”); and its labels for the factor we have labeled negative affect nearly always included the phrase “negative emotion.” (See Supplemental Materials for the full text of these prompts and GPT-3’s responses.) The similarity.
-between our original labels (i.e.
-cognition and control, social connection, bodily sensations, and negative affect) and those generated by GPT-3 provide some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
+We provided a variety of prompts to the model to assess its "intuitions" about how to label the four categories of mental capacities suggested by the factor solution just described.
+One representative prompt began, "You're a statistician and a psychologist, and I'd like your help interpreting my exploratory factor analysis results," followed by the EFA output taken directly from our analysis in R (containing the full list of factor loadings, as well as other summary characteristics of the EFA solution).
+The immediate response generated by ChatGPT included comments on model fit, factor structure, factor interpretability, factor contributions, chi-squared and BIC, as well as suggestions for "next steps"; under interpretability, it read, "MR1 [the factor we have referred to as _cognition and control_, although this label was never provided to the model] has high loadings on items related to planning, self-control, and goal-oriented behaviors.
+It could represent Self-Regulation or Executive Function.
+MR3 [what we have called _social connection_] includes items related to emotions such as feeling excited, happy, or loved.
+This could reflect Positive Emotional Experiences.
+MR2 [*bodily sensation*] has high loadings on items like feeling hungry, tired, and uncomfortable.
+This factor might capture Physical States or Needs.
+MR4 [*negative affect*] captures items like feeling helpless, frustrated, and annoyed.
+It may reflect Negative Emotional Responses or Distress." When asked to tailor labels for an audience of cognitive scientists and clinical psychologists, the model suggested names like "Self-Regulation and Cognitive Control," "Positive Affect and Social Emotions," "Physiological Awareness and Basic Needs," and "Negative Affect and Emotional Distress." (See https://chatgpt.com/share/675a0c61-d534-8006-a978-b731bc997572 for the full text of these prompts and ChatGPT's responses; OpenAI, 2024.) The similarity between our original labels and those generated by ChatGPT provides some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
 Nonetheless, we caution the reader to treat these labels as interpretations of empirical results, rather than empirical results themselves.
@@
 As described earlier, we take these factors to reflect latent constructs—fundamental components of mental life relevant to reasoning about human children.
-Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants’ perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development.
+Moreover, because each participant was asked to reason not just about some class of target characters (e.g., "chimpanzees," "robots"), but about the human child over development, we further propose that part of what contributed to the differentiation of these four factors was participants' perceptions of development: the extent to which different capacities are present at birth, the rate at which different capacities develop, and the mechanisms that drive this development.
 In Studies 2 and 3, we explore these possibilities in greater depth.
@@
 
-```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of US adults’ capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
+```{r fig01, fig.cap="Factor loadings from an exploratory factor analysis of US adults' capacity attributions to newborns, 9-month-old infants, and 5-year-old children in Study 1."}
 knitr::include_graphics("../outputs/fig01.pdf")
@@
 Participants predominantly identified as White (`r round((s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s2_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
-`r round(100*(s2_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree.
+`r round(100*(s2_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
 `r round(100*(s2_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
@@
 A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors.
-(See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.’s (2017) factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
-Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings (≥ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
+(See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.'s (2017) factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings ($\geq$ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
 Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
@@
 ```{r s2 gam results, include = F}
-s2_gam_ptab <- summary(s2_results$gam$gam)$p.table
-s2_gam_stab <- summary(s2_results$gam$gam)$s.table
+s2_gam_ptab <- summary(s2_results$gam)$p.table
+s2_gam_stab <- summary(s2_results$gam)$s.table
+s2_gam_parameters <- parameters(s2_results$gam)
 ```
 
-Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children’s capacities differed dramatically across domains.
-On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term, analogous to a slope in linear regression: $F$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`) and, accordingly, reported smaller increases over the target age range in both domains (average smoothing terms for _social connection_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s2_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`; for _negative affect_: $F$ = `r round_x(s2_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-At the other extreme, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s2_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s2_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s2_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children's capacities differed dramatically across domains.
+Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape these perceived developmental trajectories from the bottom up (see Figure 2), without specifying in advance the shape of the curve.
 
-Visual inspection of Figure 2, Panel A, clearly illustrates that the shape of perceived growth in children’s capacities varied substantially across domains.
-In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range, and what growth they did perceive occurred in the first year of life.
-Participants perceived development in the domains that we have labeled _negative affect_ and _social connection_ to be quite non-linear, characterized by rapid development over the first 1-2 years of life, at which point the curves level off dramatically.
-In contrast, participants perceived dramatic development in the domain of _cognition and control_, but perceived this development to unfold fairly steadily across the full age range.
+On one extreme, participants attributed very little capacity for _cognition and control_ to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically and non-linearly over the target age range--that is, including a smoothing term for target age (analogous to a slope in a linear regression) significantly reduced the deviance of the model ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`); and the fitted smooth had moderate non-linear complexity (estimated degrees of freedom $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(df) %>% round_x(., 2)`).
+A visual inspection of Figure 2 (Panel A, rightmost box) suggests that participants perceived a long and fairly steady developmental trajectory across the full target age range included in this study (birth to 5 years).
 
-We speculate that these differences in perceptions of growth in children’s capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), characterized by rapid development over the child's first year of life (see Figure 2, Panel A, third box from left).
+
+In the domain of _negative affect_, participants attributed even greater capacities to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`) and smaller increases over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`, $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), concentrated primarily between birth and the age of 2 years (see Figure 2, Panel A, second box from left).
+
+In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range; instead, participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and reported the smallest increase increase in capacities over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(df) %>% round_x(., 2)`).
+What growth they did perceive occurred in the first year (see Figure 2, Panel A, leftmost box).
+
+We speculate that these differences in perceptions of growth in children's capacities emerge from intuitive theories of development that specify different mechanisms or drivers of development for different domains.
 For example, if participants believe that development in the domain of _bodily sensation_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed.
-[See @berent.etal2019 for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
+[See @berent.etal2019, for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
 We explore these possibilities in Study 3.
@@
 ```{r fig02, fig.cap="Perceived developmental trajectories for four domains of mental life among US adults (Studies 2-3).
-Lighter lines represent individual participants’ responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our generalized additive models (beta regressions).
+Lighter lines represent individual participants' responses, black points correspond to mean responses across the sample, error bars are bootstrapped 95% confidence intervals, and thick red lines are predictions from our multilevel generalized additive models.
 In Study 2 (Panel A), participants assessed 5 capacities within each domain, and assessed all capacities for a given target age before moving on to the next target age.
@@
 In Study 2, participants focused on one target age at a time, assessing a variety of capacities for that age before proceeding to the next target age (from youngest to oldest).
-This design was intended to encourage participants to focus primarily on providing a holistic assessment of mental life at a given target age; the trajectories connecting target ages were likely not the participants’ primary concern in the moment of responding.
-In Study 3, we flipped the design to focus participants’ attention on development more explicitly: Participants were asked to provide judgments of a single capacity for the full range of target ages (arranged from youngest to oldest) on the same "trial," before proceeding to the next capacity.
+This design was intended to encourage participants to focus primarily on providing a holistic assessment of mental life at a given target age; the trajectories connecting target ages were likely not the participants' primary concern in the moment of responding.
+In Study 3, we flipped the design to focus participants' attention on development more explicitly: Participants were asked to provide judgments of a single capacity for the full range of target ages (arranged from youngest to oldest) on the same "trial," before proceeding to the next capacity.
 In addition to signaling more strongly to participants that we were interested in their perceptions of development, this approach gave participants the opportunity to view and adjust all of their responses for a given target capacity simultaneously, charting out their perceptions of the full developmental trajectory from birth to age 5 years.
@@
 Participants predominantly identified as White (`r round((s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity == "White") %>% pull(prop))*100, 0)`%; <`r round(100*(s3_results$demo %>% count(RaceEthnicity) %>% mutate(prop = n/sum(n)) %>% filter(RaceEthnicity != "White") %>% filter(prop == max(prop)) %>% pull(prop)) + 1, 0)`% identified as any other race/ethnicity, identified as more than one race/ethnicity, or declined to disclose).
-`r round(100*(s3_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor’s degree.
+`r round(100*(s3_results$demo %>% count(Education) %>% arrange(desc(Education)) %>% mutate(cumprop = cumsum(n)/sum(n)) %>% filter(grepl("Bachelor", Education)) %>% pull(cumprop)))`% of participants had obtained at least a Bachelor's degree.
 `r round(100*(s3_results$demo %>% count(Parent) %>% mutate(prop = n/sum(n)) %>% filter(Parent == "Yes") %>% pull(prop)))`% of participants indicated that they were parents.
@@
 On each trial, participants completed a set of questions about the possible mechanisms that drive development for the capacity in question.
-First, they were asked, "In your opinion, how important is each of the following factors in the development of children’s capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for the following 10 developmental mechanisms: “the child is biologically ‘preprogrammed’ to have this ability”; “the child has experiences in the womb that give them this ability”; “the child’s body grows and matures (for example, muscles get stronger, child gets taller)”; “the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)”; “the child’s senses improve (for example, vision gets sharper, hearing improves)”; “the child observes the objects and the physical world around him or her”; “the child observes the people around him or her”; “the child interacts with the people around him or her”; “people explicitly teach the child how to do this”; “the child actively experiments with how to do this.” These items were presented in a fixed order (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
+First, they were asked, "In your opinion, how important is each of the following factors in the development of children's capacity for [capacity]?" They provided independent ratings on a Likert-type scale from 0 (labeled "not at all important") to 6 ("extremely important"), for the following 10 developmental mechanisms in the following (fixed) order: "the child is biologically 'preprogrammed' to have this ability"; "the child has experiences in the womb that give them this ability"; "the child's body grows and matures (for example, muscles get stronger, child gets taller)"; "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)"; "the child's senses improve (for example, vision gets sharper, hearing improves)"; "the child observes the objects and the physical world around him or her"; "the child observes the people around him or her"; "the child interacts with the people around him or her"; "people explicitly teach the child how to do this"; "the child actively experiments with how to do this." This order reflects our rough sense of what might be considered the most innate or biological mechanisms of development, to what might be considered the most learned or social.
 Participants were also asked to choose among these 10 mechanisms (or to write in another mechanism) to answer the question, "If you had to choose just one, which of the following factors is the most important in the development of capacities for [capacity]?"
 
-Because Study 3 included additional questions probing participants’ theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to 8 in the current study to maintain an appropriate level of participant burden.
+Because Study 3 included additional questions probing participants' theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to eight (two capacities per domain) in the current study to maintain an appropriate level of participant burden.
 We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain that we have labeled _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain that we have labeled _negative affect_.
@@
 ```{r s3 gam results, include = F}
-s3_gam_ptab <- summary(s3_results$gam$gam)$p.table
-s3_gam_stab <- summary(s3_results$gam$gam)$s.table
+s3_gam_ptab <- summary(s3_results$gam)$p.table
+s3_gam_stab <- summary(s3_results$gam)$s.table
+s3_gam_parameters <- parameters(s3_results$gam)
 ```
 
-This approach yielded a very similar picture of US adults’ understanding of the development of human mental life; see Figure 2, Panel B.
-As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorCognition and control", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`).
-Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|t|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|t|)"], 3)))`); in Study 3, as in Study 2, participants reported relatively small increases over the target age range in the domain of _negative affect_ (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorNegative affect", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorNegative affect", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorNegative affect", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorCognition and control", "edf"], 2)`), but in this case they reported quite dramatic increases in the domain that we have labeled _social connection_ ($F$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorSocial connection", "p-value"] < 0.001, "< 0.001", paste("=",  round_x(s3_gam_stab["s(target_year):factorCognition and control", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorSocial connection", "edf"], 2)`).
-Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|t|)"], 3)))`) and a significant but small increase in capacities for _bodily sensation_ over the target age range (average smoothing term: $F$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "F"], 2)`, $p$ `r ifelse(s3_gam_stab["s(target_year):factorBodily sensation", "p-value"] < 0.001, "< 0.001", paste("=", round_x(s3_gam_stab["s(target_year):factorBodily sensation", "p"], 3)))`, $edf$ = `r round_x(s3_gam_stab["s(target_year):factorBodily sensation", "edf"], 2)`).
+This approach yielded a very similar picture of US adults' understanding of the development of human mental life; see Figure 2, Panel B.
+As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`).
+Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`); in Study 3, as in Study 2, participants reported substantial increases in the domain that we have labeled _social connection_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`) and relatively small increases over the target age range in the domain of _negative affect_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p), 3)))`).
+Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _Social connection_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and small increases in capacities for _bodily sensation_ over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`).
 
-Visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
+Again, we note that this modeling approach did not include formal statistical tests of differences in perceived trajectories across domains—but visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
 
@@
 We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-(For in-depth investigations of laypeople’s intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.)
+[For in-depth investigations of laypeople's intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.]
 
-[XXXX CUT We assessed a wide range of potential developmental mechanisms for children’s capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.]
+We assessed a wide range of potential developmental mechanisms for children's capacities, and gave participants opportunities to endorse nuanced (perhaps even internally inconsistent) theories of development by having them assess each of these developmental mechanisms for each capacity independently in addition to selecting the "most important" mechanism via forced choice.
 
-[XXXX CUT A variety of dimensionality reduction techniques converged to suggest that participants perceived the ten developmental mechanisms we included in this study as falling into two general categories (see Supplemental Materials), which aligned nearly exactly with our _a priori_ ordering of these mechanisms from most "innate" or "biological" to most "learned" or "social" (see Study 3 preregistration).
-First, there were what we will call _intrinsic mechanisms_: mechanisms rooted in innate predispositions or biological maturational processes, including those whose influence occurs prior to a child’s birth ("the child is biologically 'preprogrammed' to have this ability", "the child has experiences in the womb that give them this ability") and those whose influence continues into infancy and childhood ("the child’s body grows and matures [for example, muscles get stronger, child gets taller]", "the child’s senses improve [for example, vision gets sharper, hearing improves]").
-Participants clearly distinguished these intrinsic mechanisms from what we will call _extrinsic mechanisms_: mechanisms rooted in observations of and experiences in the world, which included both passive forms of learning ("the child observes the objects and the physical world around him or her", "the child observes the people around him or her", "the child interacts with the people around him or her") and more active forms of learning ("people explicitly teach the child how to do this", and "the child actively experiments with how to do this").
-One mechanism—"the child’s brain changes (for example, brain grows bigger, more or fewer connections between neurons)"—was difficult to categorize as "intrinsic" or "extrinsic," with different analyses suggesting different conclusions; indeed, on its face this item is more ambiguous and could refer both to intrinsic maturational processes and to the effects of external experiences influencing brain circuitry.
-This item was eliminated from the analyses that follow (but included in the visualizations presented in Figure 3).]
+Responses to questions about developmental mechanisms are visualized in Figure 3.
+
+```{r s3 mechanism choice summary stats, include = F}
+s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions by mechanism
+s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b # proportions by domain and mechanism
+s3_mech_choice_ss_c <- s3_results$mech_choice_ss_c # proportions by domain, capacity, and mechanism
+
+s3_mech_choice_modes <- s3_results$mech_choice_modes
+```
+
+In terms of selections of the "most important" mechanism driving the development of these capacities between 0-5 years, two explanations—biological preprogramming and brain changes—accounted for most of participants' selections.
+Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3.
+(See also Supplemental Materials for a multinomial regression comparing the selection of most important mechanism across capacities.)
+
+The explanation that "the child is biologically 'preprogrammed' to have this ability" was the modal response (or within 10% of the modal response) for `r s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed") %>% nrow()` of the 8 capacities presented in this study, including all of the capacities chosen to represent the domains of _bodily sensation_ and _negative affect_, as well as one of the two capacities chosen to represent _social connection_.
+Consensus on this selection was particularly pronounced for capacities for hunger (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("hung", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), pain (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("pain", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), and distress (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("distress", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants).
+
+Meanwhile, the explanation that "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including helplessness (in the domain of _negative affect_) and social learning (_social connection_), as well as emotional control and reasoning things (both in the domain of _cognition and control_).
+However, consensus about this selection was much lower (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(-1, prop) %>% pull(prop) %>% round(., 2))*100`-`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(1, prop) %>% pull(prop) %>% round(., 2))*100`% of participants across capacities).
+Instead, these capacities were characterized by a more diverse selection of mechanisms, including mechanisms that are not as directly tied to biology: For example, when considering what drives the development of a capacity to learn from other people, roughly equal numbers of participants selected brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), observations of the social world (`r (s3_mech_choice_ss_c %>% filter(grepl("observes people", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), and interactions with others (`r (s3_mech_choice_ss_c %>% filter(grepl("interacts", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%); and when considering the capacity for controlling one's emotions, participants were nearly as likely to select explicit teaching (`r (s3_mech_choice_ss_c %>% filter(grepl("teach", dev_factor_text), grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%) as the most important developmental mechanism as they were to select brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%).
+
+Independent ratings of the importance of each developmental mechanism present a more nuanced—but largely consistent—picture of intuitive theories of development across these domains.
+See Figure 3, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.
 
 ```{r s3 mechanism ratings summary stats, include = F}
-s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means overall
+s3_mech_rat_ss_a <- s3_results$mech_rat_ss_a # means by mechanism
 s3_mech_rat_ss_b <- s3_results$mech_rat_ss_b # means by domain
-s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # differences by domain
+s3_mech_rat_ss_c <- s3_results$mech_rat_ss_c # means by domain and mechanism
+s3_mech_rat_ss_d <- s3_results$mech_rat_ss_d # means by domain, capacity, and mechanism
 ```
@@
 
-[XXXX CUT A multilevel linear regression suggested that, collapsing across domains, intrinsic and extrinsic mechanisms were rated as equally important (median score for intrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "intrinsic") %>% pull(sd) %>% round_x(., 2)`; median score for extrinsic mechanisms: `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(median) %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_a %>% filter(dev_factor_cluster == "extrinsic") %>% pull(sd) %>% round_x(., 2)`; comparison: $\beta$ = `r round_x(s3_lmer_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_tab$CI_low[2], 2)`, `r round_x(s3_lmer_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_tab$p[2], 3)))`), but that the difference between intrinsic and extrinsic mechanisms varied across domains (interaction terms: |$\beta$| ranged from `r round_x(min(abs(s3_lmer_tab$Coefficient[6:8])), 2)`-`r round_x(max(abs(s3_lmer_tab$Coefficient[6:8])), 2)`, all $p$ < 0.001).]
+For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures (for example, muscles get stronger, child gets taller)" (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as very unimportant for capacities in this domain, with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
 
-[XXXX CUT For capacities in the domain of _bodily sensation_, participants rated intrinsic mechanisms as much more important drivers of development than extrinsic mechanisms (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(median), 2)` out of a maximum difference of $\pm$ 6 points, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Bodily sensation") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_bod_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_bod_tab$CI_low[2], 2)`, `r round_x(s3_lmer_bod_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_bod_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_bod_tab$p[2], 3)))`).
-In the domain of _negative affect_, participants rated intrinsic and extrinsic mechanisms as equally important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Negative affect") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_neg_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_neg_tab$CI_low[2], 2)`, `r round_x(s3_lmer_neg_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_neg_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_neg_tab$p[2], 3)))`).
-In the domain of _social connection_, participants rated extrinsic mechanisms as more important (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Social connection") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_soc_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_soc_tab$CI_low[2], 2)`, `r round_x(s3_lmer_soc_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_soc_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_soc_tab$p[2], 3)))`), and this was even more the case for capacities in the domain of _cognition and control_ (median of participant-level mean differences: `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(median), 2)`, $M_{diff}$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(mean), 2)`, $sd$ = `r round_x(s3_mech_rat_ss_c %>% filter(factor == "Cognition and control") %>% pull(sd), 2)`; comparison to 0 in separate multilevel regression model: $\beta$ = `r round_x(s3_lmer_cog_tab$Coefficient[2], 2)`, 95% CI: [`r round_x(s3_lmer_cog_tab$CI_low[2], 2)`, `r round_x(s3_lmer_cog_tab$CI_high[2], 2)`], $p$`r ifelse(s3_lmer_cog_tab$p[2] < 0.001, "< 0.001", paste("=", round_x(s3_lmer_cog_tab$p[2], 3)))`).
-See Figure 3, panels A-B, for a visualization of these differences, and Supplemental Materials for the full results of these analyses.]
+For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+However, these two biological explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant for capacities in this domain.
 
-```{r s3 mechanism choice summary stats, include = F}
-# s3_mech_choice_ss_a <- s3_results$mech_choice_ss_a # proportions overall
-s3_mech_choice_ss_b <- s3_results$mech_choice_ss_b %>% # proportions by domain
-  filter(!is.na(dev_factor_cluster)) %>%
-  group_by(factor) %>%
-  mutate(prop2 = n/sum(n)) %>%
-  ungroup()
-```
+For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+These were closely followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
-```{r s3 glmer results, include = F}
-s3_glmer_tab <- model_parameters(s3_results$glmer, standardize = "refit")
-s3_glmer_bod_tab <- model_parameters(s3_results$glmer_bod) # no standardization
-s3_glmer_neg_tab <- model_parameters(s3_results$glmer_neg) # no standardization
-s3_glmer_soc_tab <- model_parameters(s3_results$glmer_soc) # no standardization
-s3_glmer_cog_tab <- model_parameters(s3_results$glmer_cog) # no standardization
-```
-
-[XXXX CUT Participants’ intuitions that different aspects of mental life are driven by different mechanisms were also reflected in their responses to the forced-choice questions about the "most important" factor driving the development of each of these capacities; see Figure 3, Panel C.
-Participants overwhelmingly chose intrinsic mechanisms for capacities in the domain of _bodily sensation_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Bodily sensation", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of all responses), and also tended to choose intrinsic mechanisms for capacities in the domain of _negative affect_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Negative affect", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices; the remaining response fell outside of this categorization scheme).
-On the whole, participants demonstrated no strong preference for intrinsic or extrinsic mechanisms in the domain of _social connection_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Social connection", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% extrinsic choices).
-Finally, participants tended to choose extrinsic mechanisms for capacities in the domain of _cognition and control_ (`r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "extrinsic") %>% pull(prop)), 0)`% of responses, compared to `r round_x(100 * (s3_mech_choice_ss_b %>% filter(factor == "Cognition and control", dev_factor_cluster == "intrinsic") %>% pull(prop)), 0)`% intrinsic choices).]
-
-[XXXX CUT Taken together, we would argue that participants’ responses were consistent with the following intuitive theory: In all aspects of mental life, development is driven by a combination of intrinsic and extrinsic mechanisms, but the relative importance of these mechanisms varies across domains.
-Capacities for _bodily sensation_ are shaped primarily by intrinsic biological mechanisms, such as biological "preprogramming"; in other words, they are largely innate.
-Conversely, the development of capacities for _cognition and control_ is driven primarily by extrinsic mechanisms, i.e., by observing and interacting with the world.
-Capacities in the more social-emotional aspects of mental life are intermediate between these extremes, with both intrinsic and extrinsic mechanisms exerting substantial influence; but capacities for _social connection_ might be distinguished from capacities for _negative affect_ by their heightened sensitivity to extrinsic mechanisms (in particular, observing and interacting with other people).]
-
-[XXXX INSERT NEW ANALYSES]
+Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row), many developmental mechanisms were rated as highly important.
+The highest-rated mechanisms were "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
+Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
 ```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
-Panel A shows ratings for each developmental mechanism and each of the capacities within each domain; and Panel C shows the percentage of trials on which participants selected each developmental mechanism as the ‘most important’ driver of development for each capacity within each domain.
-Lighter points and lines represent individual participants’ responses, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
-The dotted red line at the midpoint of the response scale in Panel A is intended to aid visual comparison across mechanisms."}
+Small, lighter points represent individual participants' ratings of how important each developmental mechanism is in the development of each capacity within a domain (top row: bodily sensation; second row: negative affect; third row: social connection; bottom row: cognition and control).
+Larger black and red points correspond to mean importance ratings across the sample, and error bars are bootstrapped 95% confidence intervals.
+On the right side of each panel are the percentages of participants who selected each developmental mechanism as the 'most important' driver of development for that capacity, with modal selections (including items within 10% of the mode) in red."}
 knitr::include_graphics("../outputs/fig03.pdf")
@@
 
-## Relationships between beliefs about developmental mechanisms and perceived developmental trajectories
-
-As a final exploration of participants’ representations of the development of mental life, we explored the relationships between beliefs about what mechanisms drive the development of the capacities included in this study and beliefs about the extent to which these capacities are present at different points in infancy and early childhood.
-We consider these exploratory analyses to offer some insight into the coherence of participants’ intuitive theories about the development of mental life.
-
-These relationships are visualized in Figure 4; see Supplemental Materials for a breakdown by individual capacity (e.g., “feeling pain,” “getting hungry,” and so forth), and for separate regression analyses for each developmental mechanism, taking into account differences across target ages and capacities, as well as individual differences across participants.
-
-```{r fig04, fig.cap="Relationships between US adults’ ratings of the importance of various developmental mechanisms and capacity ratings, collapsing across capacities (Study 3); see Supplemental Materials for a breakdown of these relationships by individual capacity.
-Light black points represent individual participants’ responses, with each participant contributing one datapoint for each capacity-mechanism pair (i.e., 80 datapoints per participant).
-Dark colorful lines correspond to smoothed conditional means (via GAMs), with shaded areas representing 95% confidence intervals.
-The dotted red line at the midpoint of the response scale is intended to aid visual comparison across target ages."}
-knitr::include_graphics("../outputs/fig04.pdf")
-```
-
-Our primary take-away from this analysis is that the nature of these relationships between mechanism and capacity ratings varied substantially across mechanisms.
-This is easiest to visualize at the youngest target age, newborns (Fig.
-4, first panel), where we observed three basic kinds of relationships.
-
-[XXXX INSERT NEW ANALYSES]
-
-In nearly all cases, the relationships just described between mechanism and capacity ratings were increasingly subtle over the target age range; this is readily apparent through visual inspection of Fig.
-4 (see also Supplemental Materials for estimates of interactions between mechanism rating and target age for each developmental mechanism).
-This is consistent with the fact that, across the target age range, mean capacity ratings increased, approaching the ceiling of our response scale, and variability across participants decreased—leaving less room to detect potential relationships with beliefs about developmental mechanisms.
-Put another way, by the older end of our target age range, participants had largely converged on an understanding that children were nearly fully capable of all of the capacities included in this study, regardless of what mechanisms had driven the development of these capacities.
-
-Taken together, these results provide some evidence for the existence of coherent intuitive theories of the development of mental life among US adults’: Individual differences in participants’ beliefs about the mechanisms that drive the development of various aspects of mental life were coherently related to their beliefs about how these aspects of mental life develop over infancy and early childhood (with the slight exception, perhaps, of beliefs about the influence of the child’s body growing and the child’s senses improving, as described above).
-To our eyes, these findings also hint at an intuitive distinction between developmental mechanisms that exert their influence during fetal development prior to birth (namely, biological “preprogramming” and experiences in the womb; the first pattern described above) vs.
-mechanisms that depend on the child observing and interacting with the world outside of the womb after birth (including various forms of observation, experimentation, and social interaction; the second pattern described above).
-We consider this distinction and its associated patterns of relationships to be intuitively sensical and reasonably closely aligned with scientific theories of fetal and neonatal development: To the extent that a capacity can emerge prior to birth, we would expect to observe it in the newborn child; while to the extent to that a capacity depends on experience in the outside world, we would expect not to observe it in the newborn child who lacks those experiences.
-Much like social scientists, different participants held different specific beliefs about which of these mechanisms were most relevant for which of the capacities included in this study, but they seemed to share a coherent understanding—an intuitive theory—of how mechanisms and capacity attributions are related in the abstract.
+In sum, we would characterize participants' intuitive theories as follows.
+For capacities in the domain that we have called _bodily sensation_, there was broad consensus across participants that development between ages 0-5 years is driven almost exclusively by biological forces, particularly some form of biological "preprogramming." For all other capacities, participants viewed development as the result of a combination of biological forces (including "preprogramming") and experience in the physical and social world.
+In the domain that we have called _negative affect_, responses suggested that passive observation of the world might be considered sufficient to drive early development.
+In contrast, in the domains that we have called _social connection_ and _cognition and control_ there were some suggestions that a child must interact with the world in order to develop (for example, via social exchanges with other people or by conducting their own "experiments").
 
@@
 
-In a series of three large-scale studies, we identified four core capacities that anchor US adults’ conceptual representations of the development of human mental life over infancy and early childhood (Study 1); measured US adults’ perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child’s life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four domains (Study 3).
+In a series of three large-scale studies, we identified four core capacities that anchor US adults' conceptual representations of the development of human mental life from birth through early childhood (Study 1); measured US adults' perceptions of these capacities at birth and charted how they are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four domains (Study 3).
 
-We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant’s life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast—and in line with previous work on adults' intuitions about cognitive development [@wang.feigenson2019] [@berent.etal2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by what we called "extrinsic" mechanisms (e.g., observations and interactions with other people, explicit teaching, and active exploration on the part of the child).
+We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant's life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@berent.etal2019, @wang.feigenson2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by driven primarily by observation of and interactions with the physical and social world.
 
-Beliefs about the development of the more social-emotional aspects of mental life—what we have called *negative affect* (e.g., distress, frustration) and _social connection_ (e.g., love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
+Beliefs about the development of the more social-emotional aspects of mental life—what we have called _negative affect_ (e.g., distress, frustration) and _social connection_ (e.g., happiness, love, learning from others)—were intermediate between the extremes of _bodily sensation_ and _cognition and control_.
 In the aggregate, participants considered capacities for _negative affect_ and _social connection_ to be present to some degree from birth [consistent with recent findings on the perceived "innateness" of emotions, @berent.etal2020] but to continue developing rapidly over the first two years of life.
-Likewise, participants reported that development in these capacities was driven by a _combination_ of the extrinsic mechanisms just described and more "intrinsic" mechanisms, such as physical maturation and "preprogramming." Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
-We note that attributions of what we have called _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
+Likewise, participants reported that development in these capacities was driven by a combination of biological forces (including "preprogramming") and experience in the physical and social world.
+Both in their perceptions and in their explanations of development, participants' understanding of _negative affect_ were somewhat more similar to their responses to capacities for _bodily sensation_, while their responses to capacities for _social connection_ more closely resembled their understanding of _cognition and control_.
+We note that attributions of what we have labeled _negative affect_ and _social connection_ were particularly variable across individual participants, especially when it came to perceptions of the capacities of newborns; see Figure 2.
 This suggests that beliefs about development in these domains are especially sensitive to personal experience, social-cultural context, explicit education, or other forms of input.
@@
 These two factors have no obvious precedents in previous studies of mind perception.
-In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle’s (2019) framework [@malle2019], _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart."
+In the agency-experience framework [@gray.etal2007], _negative affect_ would likely fall under the umbrella of "experience," but _social connection_ seems to combine aspects of both "experience" (e.g., happiness, sadness) and "agency" (e.g., learning, recognition); similarly, in Malle's (2019) framework, _negative affect_ clearly resonates with "affect," but _social connection_ seems to combine aspects of both "regulation" and "reality interaction." Meanwhile, in the body-heart-mind framework [@weisman.etal2017a], _social connection_ and _negative affect_ might both be considered part of the social-emotional domain of the "heart."
 
 This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials); the emphasis on how mental capacities develop over time; or, more broadly, the exclusive focus on humans as the targets of mind perception.
-Indeed, one exciting line of work focusing on how laypeople think about other humans’ mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: “rationality” (capturing a distinction between cognitive and affective states); “social impact” (capturing the degree to which mental states involve social relationships); and “valence” (capturing the distinction between positive and negative states; @tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020).
+Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality" (capturing a distinction between cognitive and affective states); "social impact" (capturing the degree to which mental states involve social relationships); and "valence" [capturing the distinction between positive and negative states, @tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020].
 The domains that we have called _social connection_ and _negative affect_ align rather well with these latter two dimensions, capturing a conceptual distinction between the degree to which certain capacities shape and are shaped by interpersonal interactions and social relationships vs.
 the degree to which certain capacities shape and are shaped by firsthand experiences of negative valence.
-Based on the findings of Studies 2 and 3, we further propose that social connection and negative affect emerged as distinct factors not only because they demarcate different aspects of mental life, but also because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates over infancy and childhood, and are driven by different developmental mechanisms.
+Based on the findings of Studies 2 and 3, we further propose that _social connection_ and _negative affect_ emerged as distinct factors not only because they demarcate different aspects of mental life, but also because participants believed these two aspects of mental life develop differently: i.e., that they are present to different degrees at birth, develop at different rates, and are driven by different developmental mechanisms.
 
@@
 nurture to the development of human mental life?
-One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree.
-In addition to _bodily sensation_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
+One consistent finding across these studies is that participants attributed many capacities to newborn infants, at least to a moderate degree.
+In addition to _bodily sensation_ and _negative affect_—obvious aspects of a newborn's experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people".
 Indeed, in Study 3 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure 3).
 Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
-Further work on this topic would do well to integrate the cognitive processing mechanisms featured in the current studies with epistemic states that have been the focus of past research on laypeople’s beliefs about the innateness of "cognitive" abilities [@berent.etal2019; @wang.feigenson2019] to paint a more comprehensive picture of the ways in which intuitive theories of development do and do not align with scientific theories such as nativism, empiricism, and constructivism.
+Further work on this topic would do well to integrate the cognitive processing mechanisms featured in the current studies with epistemic states that have been the focus of past research on laypeople's beliefs about the innateness of "cognitive" abilities [@berent.etal2019; @wang.feigenson2019] to paint a more comprehensive picture of the ways in which intuitive theories of development do and do not align with scientific theories such as nativism, empiricism, and constructivism.
 
@@
 One important limitation of the current studies is that they relied exclusively on samples of US adults recruited via the crowdsourcing platform Amazon Mechanical Turk (MTurk).
-In other lines of work on mind perception using similar bottom-up approaches to identifying latent conceptual structures, MTurk samples have yielded factor solutions very similar to more representative samples of general population US adults collected in person in public settings (e.g., the Department of Motor Vehicles; @weisman.etal2021); given this, we would predict that the current findings would be replicated in more representative samples of predominantly White, middle-class US adults.
+In other lines of work on mind perception using similar bottom-up approaches to identifying latent conceptual structures, MTurk samples have yielded factor solutions very similar to more representative samples of general population US adults collected in person in public settings (e.g., the Department of Motor Vehicles, @weisman.etal2021); given this, we would predict that the current findings would be replicated in more representative samples of predominantly White, middle-class US adults.
 Of great interest and importance is the question of how beliefs and intuitive theories about the development of mental life do and do not vary across cultural, ethnic, racial, socioeconomic, educational, generational, and other dimensions, both within the US and across national boundaries.
@@
 
-One of the most interesting future directions for this line of research will be to assess how the experience of raising a child might change caregivers’ representations of and intuitive theories about the development of mental life across infancy and early childhood.
+One of the most interesting future directions for this line of research will be to assess how the experience of raising a child might change caregivers' representations of and intuitive theories about the development of mental life across infancy and early childhood.
 Unfortunately, the current datasets are well-suited to these explorations.
@@
 non-parents in the current manuscript, because we do not want to mislead readers with potential spurious results from these datasets.
-However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics crying out for further research.
+However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics warranting for further research.
 
-## Implications for caregiver-child interactions
+## Implications for caregiver–child interactions
 
-How might the four-way distinction proposed here inform caregiver-child interactions?
-Drawing on theoretical proposals from recent work in mind perception [@weisman.etal2017a], we would argue that what gives meaning to the four factors documented in the current studies is the possibility that they correspond to substantially different causal explanatory frameworks for interpreting, predicting, and responding to the behaviors of a young child—i.e., distinct lenses through which a caregiver might view and understand a child in a given moment.
-Consider a caregiver attempting to navigate the difficult situation of a toddler throwing a "temper tantrum." Through the lens of _bodily sensation_, the caregiver might understand the child as driven by basic biological needs, which could draw the caregiver’s attention to the possibility that the child is hungry, fatigued, injured, or ill, and focus the caregiver’s behaviors on the child’s physical wellbeing.
+How might the four-way distinction proposed here inform caregiver–child interactions?
+Drawing on theoretical proposals from other work in mind perception [@weisman.etal2017a], we would argue that what gives meaning to the four factors documented in the current studies is the possibility that they correspond to substantially different causal explanatory frameworks for interpreting, predicting, and responding to the behaviors of a toddler—i.e., distinct lenses through which a caregiver might view and understand a child in a given moment.
+Consider a caregiver attempting to navigate the difficult situation of a toddler throwing a "temper tantrum." Through the lens of _bodily sensation_, the caregiver might understand the child as driven by basic biological needs, which could draw the caregiver's attention to the possibility that the child is hungry, fatigued, injured, or ill, and focus the caregiver's behaviors on the child's physical wellbeing.
 Through the lens of _negative affect_, the caregiver might instead understand the child as a moral patient who deserves to be spared unpleasant and harmful experiences, drawing attention to the possibility that the child is upset or afraid and motivating the caregiver to provide comfort.
-Through the lens of _social connection_, the caregiver might understand the child as a social partner, interpreting the child’s distress as an indication that the relationship needs repair and seeking to remedy the disruption.
-And through the lens of _cognition and control_, the caregiver might understand the child as an intentional agent who has been thwarted in the pursuit of certain goals; the caregiver might offer the child assistance toward the goal, or age-appropriate techniques to regulate the child’s negative emotions.
-Of course, by the time a human reaches adulthood, all of these explanatory frameworks are reasonable modes of interpreting an individual’s behavior, because human adults are biological animals, moral patients, social partners, and intentional agents.
-But in the moment of dealing with a distressed child—especially when caring for that child requires making guesses about what kind of care is even required—these four modes of understanding might have important consequences for caregivers’ responses and, in turn, for children’s outcomes.
+Through the lens of _social connection_, the caregiver might understand the child as a social partner, interpreting the child's distress as an indication that the relationship needs repair and seeking to remedy the disruption.
+And through the lens of _cognition and control_, the caregiver might understand the child as an intentional agent who has been thwarted in the pursuit of certain goals; the caregiver might offer the child assistance toward the goal, or age-appropriate techniques to regulate the child's negative emotions.
+Of course, by the time a human reaches adulthood, all of these explanatory frameworks are reasonable modes of interpreting an individual's behavior, because human adults are biological animals, moral patients, social partners, and intentional agents.
+But when faced with a distressed toddler—especially when limited verbal skills require caregivers to make guesses what kind of care is required—these four modes of understanding might have important consequences for caregivers' responses and, in turn, for children's outcomes.
 
-In other words, adults’ intuitive theories are likely to have important consequences for the children in their care [see also @haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010].
-We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child’s life.
-During this period, caregivers cannot rely on children to clearly communicate through words; instead, caregivers often must _infer_ what children think and feel.
-These inferences critically depend on the adult’s understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable.
-There is ample evidence that representations of children’s mental lives—including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills—play a critical role in guiding adults’ expectations of a child, their reactions to that child’s actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].
-At a high level, caregivers’ "mind-mindedness"—that is, their capacity to form an accurate representation of their child’s internal states and to use this representation to guide their caregiving behavior—is positively associated with children’s wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
-The current studies reframe these and similar findings on mind-mindedness as reflecting not only an attentional focus on the part of the caregiver but also the intuitive theories that shape caregivers’ interpretations of and responses to children’s behaviors.
+In other words, adults' intuitive theories are likely to have important consequences for the children in their care [see also @haimovitz.dweck2016; @hembacher.etal2020; @mukhopadhyay.yeung2010].
+We suspect that intuitive theories of the development of mental life could play a particularly important role in the quality of caregiver–child relationships in the first few years of a child's life.
+During this period, caregivers often must _infer_ what children think and feel.
+These inferences critically depend on the adult's understanding of what the child is and is not capable of, and what scaffolding it would take for that child to become more capable.
+There is ample evidence that representations of children's mental lives—including their sensations, perceptions, emotions, cognitive abilities, executive function, and social skills—play a critical role in guiding adults' expectations of a child, their reactions to that child's actions, and the nature and development of their relationship with the child [@vreeswijk.etal2012; @feldman.reznick1996].
+At a high level, caregivers' "mind-mindedness"—that is, their capacity to form an accurate representation of their child's internal states and to use this representation to guide their caregiving behavior—is positively associated with children's wellbeing, including attachment security, theory of mind, and ultimately, school readiness [@meins.etal2012; @meins.etal2013; @bernier.etal2017].
+The current studies reframe these and similar findings on mind-mindedness as reflecting not only an attentional focus on the part of the caregiver but also the intuitive theories that shape caregivers' interpretations of and responses to children's behaviors.
 Our results further highlight the possibility that differentiating between different aspects of "mind" and developmental shifts in mind perception could push this highly influential research program in important new directions.
-For example, perceptions of a child’s capacities in different aspects of mental life might influence caregivers’ tendencies to demonstrate mind-mindedness in some contexts more than others (e.g., when the child is experiencing physical discomfort vs.
+For example, perceptions of a child's capacities in different aspects of mental life might influence caregivers' tendencies to demonstrate mind-mindedness in some contexts more than others (e.g., when the child is experiencing physical discomfort vs.
 emotional distress, when the child is working on a task vs.
@@
 
-We conclude by highlighting three related, but meaningfully distinct, approaches to studying the connections between adults’ intuitive theories, parenting behaviors, and children’s wellbeing.
-We introduce these approaches as open questions ripe for future research—and critical next steps for translating this basic research into useful interventions to promote positive caregiver-child relationships and child wellbeing.
+We conclude by highlighting three related, but meaningfully distinct, approaches to studying the connections between adults' intuitive theories, parenting behaviors, and children's wellbeing.
+We introduce these approaches as open questions ripe for future research—and critical next steps for translating this basic research into useful interventions to promote positive caregiver–child relationships and child wellbeing.
 
 First, are the beliefs and intuitive theories documented here accurate with respect to the current scientific understanding of human development?
-Comparing participants’ intuitions to empirical findings from scientific studies of child development has illuminated the ways in which lay people’s reasoning about cognitive development [@berent.etal2019; @wang.feigenson2019] and about emotions [@berent.etal2020] has proved a useful way of illuminating biases and misconceptions in laypeople’s beliefs about innateness.
+Comparing participants' intuitions to empirical findings from scientific studies of child development has illuminated the ways in which lay people's reasoning about cognitive development [@berent.etal2019; @wang.feigenson2019] and about emotions [@berent.etal2020] has proved a useful way of illuminating biases and misconceptions in laypeople's beliefs about innateness.
 Finding creative ways to determine the ground truth of the development of the range of capacities included in the current studies—many of which are phenomenal experiences—will be a particular challenge to this endeavor, but would be both deeply fascinating and of practical interest to predicting downstream consequences for children.
-All else being equal, we would predict that caregivers with more accurate representations of children’s developing minds would make more accurate inferences about their own children and interact with their children in ways that are more developmentally appropriate and better-suited to scaffolding further healthy development [see, e.g., @list.etal2021].
+All else being equal, we would predict that caregivers with more accurate representations of children's developing minds would make more accurate inferences about their own children and interact with their children in ways that are more developmentally appropriate and better-suited to scaffolding the child's development [see, e.g., @list.etal2021].
 
 However, accuracy is not the only criterion by which to assess intuitive theories in this domain.
-A second question that could drive extensions of the current work is: How do these beliefs and intuitive theories impact caregivers’ _affective experience_ of caregiving?
-For example, in a recent study drawing on a similar theoretical foundation to the current studies, parents who attributed greater mental capacities to young children in general expressed more interest in and curiosity about their own young child’s mental states, and, in turn, reported engaging in more positive parenting behaviors [@salo.etal2021; see also @laranjo.etal2008].
-It is unclear at this point whether this proposed causal pathway—from beliefs through interest and curiosity to behaviors—hinges on caregivers holding scientifically accurate theories of development and forming accurate representations of their own children’s mental lives, or whether even beliefs that do not align with modern scientific understandings of development (e.g., the belief that newborns love and care for their siblings, the belief that toddlers might remember previous lives) could still play a positive motivational role in sustaining caregivers’ interest in their children’s minds and encouraging positive parenting behaviors.
-In either case, based on these findings we would predict that educating parents about infants’ mental capacities and their rapid development might spark increased curiosity in new parents, with positive downstream consequences in their interactions with their children.
+A second question that could drive extensions of the current work is: How do these beliefs and intuitive theories impact caregivers' affective experience of caregiving?
+It is unclear whether even beliefs that do not align with modern scientific understandings of development (e.g., the belief that newborns love and care for their siblings, the belief that toddlers might remember previous lives) play a motivational role in sustaining caregivers' interest in their children's minds and encouraging positive parenting behaviors.
+In either case, based on these findings we would predict that educating parents about infants' mental capacities and their rapid development might spark increased curiosity in their parents, with positive downstream consequences in their interactions with their children.
 
-Finally, what set of folk beliefs and intuitive theories are most _adaptive_, i.e., most effective at facilitating the kinds of caregiving behaviors that are associated with positive outcomes for children?
-This question is of course deeply related to the issues of accuracy and affective experience just described; for example, under-attributions of any aspect of mental life on the part caregivers likely have negative consequences for the children in their care, while some biases and misconceptions may actually have positive downstream consequences for children.
+Finally, what set of folk beliefs and intuitive theories are most adaptive, i.e., most effective at facilitating developmentally appropriate caregiving behaviors and positive outcomes for children?
+This question is of course deeply related to the issues of accuracy and affective experience just described; for example, under-attributions of any aspect of mental life on the part caregivers might result in reduced opportunities for interaction and psychosocial stimulation for the children in their care.
 Aside from sparking caregivers’ interest in their children, certain over-attributions of mental life might foster among caregivers the very behaviors that create and nurture these nascent capacities.
-For example, crediting an infant with more of a capacity for _social connection_ than may be warranted by empirical research could lead a caregiver to engage in the warm, reciprocal interactions that jumpstart the development of early social skills; or (falsely) assuming that a toddler is capable of feeling and understanding complex emotions like guilt and embarrassment might lead the caregiver to use the kind of language that scaffolds the development of such sophisticated social-emotional representations.
-Conversely, over-attributions of the capacity for _cognition and control_ might result in caregivers attributing overt intentions to annoy or upset their caregiver and could lead caregivers to be overly punitive in their response to what they perceive as deliberate "acting out." We offer these speculative examples to illustrate the many possibilities that adopting the lens of adaptivity could open for researchers and interventionists interested in the effects of caregivers’ intuitive theories on their children’s well-being—but, of course, such interventions would require extensive research focused on caregivers rather than general-population adults, carefully situated within a particular setting so as to promote caregiving behaviors that are beneficial for the children in question.
+For example, crediting an infant with more of a capacity for _social connection_ than may be warranted by empirical research could lead a caregiver to engage in the warm, reciprocal interactions that jumpstart the development of early social skills.
+Falsely assuming that a toddler is capable of feeling and understanding complex emotions like guilt and embarrassment might lead the caregiver to use the kind of language that scaffolds the development of such sophisticated social-emotional representations.
+Conversely, over-attributions of the capacity for _cognition and control_ might result in caregivers attributing overt intentions to annoy or upset their caregiver and could lead caregivers to be overly punitive in their response to what they perceive as deliberate "acting out" [see @bugental.etal2002].
+We offer these speculative examples to illustrate the many possibilities that adopting the lens of adaptivity could open for researchers and interventionists interested in the effects of caregivers’ intuitive theories on their children’s well-being—but, of course, such interventions would require extensive research focused on caregivers rather than general-population adults, carefully situated within a particular setting so as to promote caregiving behaviors that are appropriate for the children in question.
 
-Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research, then, will involve assessing which aspects of adults’ beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers’ own values and goals.
-Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child’s abilities and thus misinterpret the child’s behaviors, miss opportunities to support the child’s development, become overly concerned about their child’s developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].
+Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research, then, will involve assessing which aspects of adults' beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers' own values and goals.
+Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child's abilities and thus misinterpret the child's behaviors, miss opportunities to support the child's development, become overly concerned about their child's developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].
 As is the case in many domains [@weisman.markman2017], interventions that leverage the power of intuitive theories to encourage positive and responsive caregiving behaviors hold great promise for creating meaningful and lasting behavioral changes in caregiver behavior, with important consequences for child wellbeing.

### 2024-12-30 paper/cover.tex
add cover pages and de-anonymize

\begin{titlepage}
    \begin{center}
        \vspace*{1in}
        {\Large Beliefs about the development of mental life} \\[2cm]

        Kara Weisman\\
        \textit{Department of Psychology, University of California, Riverside}\par
        \vspace{0.5cm}
        Lucy S. King\\
        \textit{Department of Psychology and Human Development, Vanderbilt University}\par
        \vspace{0.5cm}
        Kathryn Humphreys\\
        \textit{Department of Psychology and Human Development, Vanderbilt University}\par

    \end{center}
    \vfill
    \textbf{Author Note} \\
    \setlength{\parindent}{2em}
    \indent Kara Weisman: https://orcid.org/0000-0002-3706-7554. Lucy S. King: https://orcid.org/0000-0002-2552-0614. Kathryn Humphreys: https://orcid.org/0000-0002-5715-6597.

    \indent Study materials, preregistrations, data, analysis scripts, and links to the fully reproducible manuscript and supplemental materials are openly available via the project’s Open Science Framework page (https://osf.io/xrznd/; DOI: 10.17605/OSF.IO/XRZND). Funding was provided by the William R. and Sara Hart Kimball Stanford Graduate Fellowship (Weisman); the National Science Foundation (Weisman and King: Graduate Research Fellowships; Humphreys: CAREER 2042285), the National Institutes of Health (King: F32 HD105385), and the Jacobs Foundation (Humphreys: Early Career Research Fellowship 2017-1261-05).

    \indent Correspondence should be addressed to Kara Weisman at kgweisman@gmail.com.
\end{titlepage}

### 2024-12-30 paper/paper.Rmd
add cover pages and de-anonymize

@@
 ---
-title: "Beliefs about the development of mental life"
-author: '[authors removed for anonymous review]'
+# title: "Beliefs about the development of mental life"
+# author: 
+#   - "Kara Weisman\\newline University of California, Riverside\\newline ORCID: https://orcid.org/0000-0002-3706-7554"
+#   - "Lucy S. King\\newline Vanderbilt University\\newline ORCID: http://orcid.org/0000-0002-2552-0614"
+#   - "Kathryn Humphreys\\newline Vanderbilt University\\newline ORCID: https://orcid.org/0000-0002-5715-6597"
+# output:
+#   pdf_document:  default
+#   # word_document:
+#     # reference_docx: word-styles-ref.docx
 output:
-  pdf_document:  default
-  # word_document:
-    # reference_docx: word-styles-ref.docx
+  bookdown::pdf_document2:
+    includes:
+      in_header: header.tex
+      before_body: cover.tex
+    toc: false
+    number_sections: false
 bibliography: ../supplement/references.bib
@@
 - \linenumbers
+- \modulolinenumbers[5]
 - \usepackage{float}
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
-All studies were approved by [IRB information removed to preserve anonymity].
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
+All studies were approved by the Institution Review Board for Human Subjects at Stanford University.
 For extended descriptions of methods and results, see Supplemental Materials.
@@
 On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs.
-These photographs (and all materials used in these studies) are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52; DOI: 10.17605/OSF.IO/XRZND).
+These photographs (and all materials used in these studies) are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
 Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").

### 2024-12-30 supplement/supplement-main.Rmd
add cover pages and de-anonymize

@@
 ---
-title: "Beliefs about the development of mental life"
-subtitle: "Supplemental Materials"
-author: "[authors removed for anonymous review]"
-date: "2024-12-17"
+# title: "Beliefs about the development of mental life"
+# subtitle: "Supplemental Materials"
+# author: "Kara Weisman, Lucy S. King, and Kathryn Humphreys"
+# date: "2024-12-30"
 output:
   bookdown::pdf_document2:
+    includes:
+      in_header: header.tex
+      before_body: cover.tex
     latex_engine: xelatex
@@
    - \linenumbers
+   - \modulolinenumbers[5]
    - \usepackage{float}
@@
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261.
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
 
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website: (anonymized links for peer review: Study 1: https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34; Study 2: https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18; Study 3: https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4).
-
-All materials used in these studies are available in the following OSF repository (anonymized link: https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52 (DOI: 10.17605/OSF.IO/XRZND).
-
-All studies were approved by [IRB information removed to preserve anonymity].
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
+
+All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
+
+All studies were approved by the Institution Review Board for Human Subjects at Stanford University.
 
@@
   kable("latex", booktabs = T, escape = F, longtable = T, digits = 2,
-        caption = "\\text{Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria: Factor loadings, complexity, and uniqueness.}") %>%
+        caption = "\\text{Study 1, factor solution suggested by Weisman et al.'s (2017) factor retention criteria.}") %>%
   kable_styling(latex_options = c("repeat_header"), font_size = 8) %>%

### 2024-12-31 paper/paper.Rmd
typos and rerun from scratch

@@
 Do they love me?
-As in other domains of reasoning[@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children's behavior and development, with consequences for the well-being of children in their care.
+As in other domains of reasoning [@gerstenberg.tenenbaum2017; @gopnik.wellman1994; @wellman.gelman1992], people likely draw on folk beliefs and intuitive theories about how the mind develops to predict, explain, and respond to children's behavior and development, with consequences for the well-being of children in their care.
 
@@
 Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
-All studies were approved by the Institution Review Board for Human Subjects at Stanford University.
+All studies were approved by the Research Compliance Office, Human Subjects Panel (IRB) at Stanford University.
 For extended descriptions of methods and results, see Supplemental Materials.
@@
 The second factor corresponded primarily to what we would describe as social abilities and emotional experiences, particularly those with positive valence—a suite of capacities that we that we interpreted as reflecting a higher-order capacity for _social connection_.
-It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "getting pleasure from music," "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants' sense of the infant awakening into the human social and cultural world.
+It was the dominant factor for such items as "feeling excited", "finding something funny", "loving somebody", "learning from other people", "feeling happy", "feeling loved", "recognizing somebody else", "getting pleasure from music", "being afraid of somebody," and "listening to somebody." Although some of these capacities do not require the presence of another person, we use the term "social connection" both to reflect the fact that many of the highest-loading items do highlight overtly "social" capacities (e.g., humor, love, learning from others, recognizing others, fearing others, listening to others), and because we interpret this factor as indexing participants' sense of the infant awakening into the human social and cultural world.
 This factor accounted for `r round_x(s1_results$efa$Vaccounted["Proportion Explained", "MR3"]*100, 0)`% of the shared variance in the rotated `r s1_results$efa$factors`-factor solution and `r round_x(s1_results$efa$Vaccounted["Proportion Var", "MR3"]*100, 0)`% of the total variance in participants' capacity attributions.

### 2025-01-06 paper/paper.Rmd
typos and revisions

@@
 
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), characterized by rapid development over the child's first year of life (see Figure 2, Panel A, third box from left).
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domain that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), characterized by rapid development over the child's first year of life (see Figure 2, Panel A, third box from left).
 
@@
 
-Because Study 3 included additional questions probing participants' theories of developmental mechanisms, we reduced the set of mental capacities from 20 in Study 2 to eight (two capacities per domain) in the current study to maintain an appropriate level of participant burden.
+Because Study 3 included additional questions probing participants' theories of developmental mechanisms, to maintain an appropriate level of participant burden we reduced the set of mental capacities from 20 (5 capacities per domain) to 8 (2 capacities per domain).
 We chose "controlling their emotions" and "reasoning about things" to represent the domain of _cognition and control_; "getting hungry" and "feeling pain" to represent the domain of _bodily sensation_; "learning from other people" and "feeling happy" to represent the domain that we have labeled _social connection_; and "feeling distressed" and "feeling helpless" to represent the domain that we have labeled _negative affect_.
@@
 This approach yielded a very similar picture of US adults' understanding of the development of human mental life; see Figure 2, Panel B.
-As in Study 2, participants perceived that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`).
+As in Study 2, participants reported that newborns have very little capacity for _cognition and control_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Cognition and control") %>% pull(sd) %>% round_x(., 2)`), but reported that such capacities increase dramatically over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorCognition and control") %>% pull(p), 3)))`).
 Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`); in Study 3, as in Study 2, participants reported substantial increases in the domain that we have labeled _social connection_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`) and relatively small increases over the target age range in the domain of _negative affect_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p), 3)))`).
@@
 
-Again, we note that this modeling approach did not include formal statistical tests of differences in perceived trajectories across domains—but visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
+Again, visual inspection of Figure 2, Panel B, makes it clear that the shape of these perceived developmental trajectories varied substantially across domains, echoing quite precisely the results of our post-hoc exploratory analyses in Study 2.
 
@@
 
-Why do US adults believe certain aspects of mental life, but not others, to be present at birth?
+Why do US adults believe certain aspects of human mental life, but not others, to be present at birth?
 What do US adults perceive to be driving the development of capacities for what we have called _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_?
@@
 We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-[For in-depth investigations of laypeople's intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019; @berent.etal2019; @berent.etal2020.]
+[For in-depth investigations of laypeople's intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019, @berent.etal2019, @berent.etal2020.]
 
@@
 
-Meanwhile, the explanation that "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including helplessness (in the domain of _negative affect_) and social learning (_social connection_), as well as emotional control and reasoning things (both in the domain of _cognition and control_).
+Meanwhile, the explanation that "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including helplessness (in the domain of _negative affect_) and social learning (_social connection_), emotional control (_cognition and control_) and reasoning about things (_cognition and control_).
 However, consensus about this selection was much lower (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(-1, prop) %>% pull(prop) %>% round(., 2))*100`-`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(1, prop) %>% pull(prop) %>% round(., 2))*100`% of participants across capacities).
-Instead, these capacities were characterized by a more diverse selection of mechanisms, including mechanisms that are not as directly tied to biology: For example, when considering what drives the development of a capacity to learn from other people, roughly equal numbers of participants selected brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), observations of the social world (`r (s3_mech_choice_ss_c %>% filter(grepl("observes people", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), and interactions with others (`r (s3_mech_choice_ss_c %>% filter(grepl("interacts", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%); and when considering the capacity for controlling one's emotions, participants were nearly as likely to select explicit teaching (`r (s3_mech_choice_ss_c %>% filter(grepl("teach", dev_factor_text), grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%) as the most important developmental mechanism as they were to select brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%).
+Instead, these capacities were characterized by a more diverse selection of mechanisms, including mechanisms that are not as directly tied to biology: For example, when considering what drives the development of a capacity to learn from other people, roughly equal numbers of participants selected brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), observations of the social world (`r (s3_mech_choice_ss_c %>% filter(grepl("observes people", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%), and interactions with others (`r (s3_mech_choice_ss_c %>% filter(grepl("interacts", dev_factor_text), grepl("learn", capacity)) %>% pull(prop) %>% round(., 2))*100`%); and when considering the capacity for controlling one's emotions, participants were nearly as likely to select explicit teaching (`r (s3_mech_choice_ss_c %>% filter(grepl("teach", dev_factor_text), grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%) as they were to select brain changes (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes", grepl("control", capacity)) %>% pull(prop) %>% round(., 2))*100`%).
 
@@
 
-For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures (for example, muscles get stronger, child gets taller)" (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
-Most of the remaining mechanisms were rated as very unimportant for capacities in this domain, with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures (for example, muscles get stronger, child gets taller)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
 
-For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
-However, these two biological explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
-Most of the remaining mechanisms were rated as fairly unimportant for capacities in this domain.
+For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+However, these two biologically inflected explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were rated as fairly unimportant for capacities in this domain (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`).
 
-For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
-These were closely followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
-Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+These were closely followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
 Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row), many developmental mechanisms were rated as highly important.
-The highest-rated mechanisms were "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
-Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
-Most of the remaining mechanisms were rated as fairly unimportant, with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
+The highest-rated mechanisms were "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
-```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life among US adults (Study 3); see main text for the full text of each mechanism.
-Small, lighter points represent individual participants' ratings of how important each developmental mechanism is in the development of each capacity within a domain (top row: bodily sensation; second row: negative affect; third row: social connection; bottom row: cognition and control).
+```{r fig03, fig.cap="Perceived importance of various mechanisms in the development of four domains of mental life (Study 3); see main text for the full text of each mechanism.
+Small, lighter points represent individual participants' ratings of how important each  mechanism is in the development of each capacity within a domain (top row: bodily sensation; second row: negative affect; third row: social connection; bottom row: cognition and control).
 Larger black and red points correspond to mean importance ratings across the sample, and error bars are bootstrapped 95% confidence intervals.
-On the right side of each panel are the percentages of participants who selected each developmental mechanism as the 'most important' driver of development for that capacity, with modal selections (including items within 10% of the mode) in red."}
+On the right side of each panel are the percentages of participants who selected each  mechanism as the 'most important' driver of development for that capacity, with modal selections (including items within 10% of the mode) in red."}
 knitr::include_graphics("../outputs/fig03.pdf")
@@
 In some respects, the results of these studies resonate well with previous work on mind perception among US adults.
-The factors that we refer to as _bodily sensation_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a], and between "affect" and "regulation" [@malle2019].
+The factors that we refer to as _bodily sensation_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a; weisman.etal2021], and between "affect" and "regulation" [@malle2019].
 These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life.
-(See also @weisman.etal2021 for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.)
+[See also @weisman.etal2021, for evidence that a distinction between bodily sensation and cognition is held in common across diverse cultural settings.]
 
@@
 This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials); the emphasis on how mental capacities develop over time; or, more broadly, the exclusive focus on humans as the targets of mind perception.
-Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality" (capturing a distinction between cognitive and affective states); "social impact" (capturing the degree to which mental states involve social relationships); and "valence" [capturing the distinction between positive and negative states, @tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020].
+Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality", capturing a distinction between cognitive and affective states); "social impact", capturing the degree to which mental states involve social relationships; and "valence", capturing the distinction between positive and negative states [@tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020].
 The domains that we have called _social connection_ and _negative affect_ align rather well with these latter two dimensions, capturing a conceptual distinction between the degree to which certain capacities shape and are shaped by interpersonal interactions and social relationships vs.
@@
 One important limitation of the current studies is that they relied exclusively on samples of US adults recruited via the crowdsourcing platform Amazon Mechanical Turk (MTurk).
-In other lines of work on mind perception using similar bottom-up approaches to identifying latent conceptual structures, MTurk samples have yielded factor solutions very similar to more representative samples of general population US adults collected in person in public settings (e.g., the Department of Motor Vehicles, @weisman.etal2021); given this, we would predict that the current findings would be replicated in more representative samples of predominantly White, middle-class US adults.
+In other lines of work on mind perception using similar bottom-up approaches to identifying latent conceptual structures, MTurk samples have yielded factor solutions very similar to more representative samples of general population US adults collected in person in public settings [e.g., the Department of Motor Vehicles, @weisman.etal2021]; given this, we would predict that the current findings would be replicated in more representative samples of predominantly White, middle-class US adults.
 Of great interest and importance is the question of how beliefs and intuitive theories about the development of mental life do and do not vary across cultural, ethnic, racial, socioeconomic, educational, generational, and other dimensions, both within the US and across national boundaries.
@@
 non-parents in the current manuscript, because we do not want to mislead readers with potential spurious results from these datasets.
-However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics warranting for further research.
+However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics warranting further research.
 
@@
 
-How might the four-way distinction proposed here inform caregiver–child interactions?
+How might the distinctions between capacities for _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ inform caregiver–child interactions?
 Drawing on theoretical proposals from other work in mind perception [@weisman.etal2017a], we would argue that what gives meaning to the four factors documented in the current studies is the possibility that they correspond to substantially different causal explanatory frameworks for interpreting, predicting, and responding to the behaviors of a toddler—i.e., distinct lenses through which a caregiver might view and understand a child in a given moment.
@@
 
-However, accuracy is not the only criterion by which to assess intuitive theories in this domain.
 A second question that could drive extensions of the current work is: How do these beliefs and intuitive theories impact caregivers' affective experience of caregiving?
-It is unclear whether even beliefs that do not align with modern scientific understandings of development (e.g., the belief that newborns love and care for their siblings, the belief that toddlers might remember previous lives) play a motivational role in sustaining caregivers' interest in their children's minds and encouraging positive parenting behaviors.
-In either case, based on these findings we would predict that educating parents about infants' mental capacities and their rapid development might spark increased curiosity in their parents, with positive downstream consequences in their interactions with their children.
+On the whole, we would predict that educating parents about infants' mental capacities and their rapid development might spark increased curiosity about child development, with positive downstream consequences for parental well-being as well as the quality of parent-child interactions.
+We note, however, that even beliefs that do not align with modern scientific understandings of development—e.g., the belief that newborns love and care for their siblings, the belief that toddlers might remember previous lives—may play motivational roles in sustaining caregivers' interest in their children's minds and encouraging positive parenting behaviors; and, conversely, that some accurate beliefs—e.g., the belief that children will eventually forget most of what happens in infancy and toddlerhood—could be demotivating for caregivers.
 
-Finally, what set of folk beliefs and intuitive theories are most adaptive, i.e., most effective at facilitating developmentally appropriate caregiving behaviors and positive outcomes for children?
+This brings us to the third orienting question for extensions of this work: What set of folk beliefs and intuitive theories are most adaptive, i.e., most effective at facilitating developmentally appropriate caregiving behaviors and positive outcomes for children?
 This question is of course deeply related to the issues of accuracy and affective experience just described; for example, under-attributions of any aspect of mental life on the part caregivers might result in reduced opportunities for interaction and psychosocial stimulation for the children in their care.
@@
 
-Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research, then, will involve assessing which aspects of adults' beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers' own values and goals.
+Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research will involve assessing which aspects of adults' beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers' own values and goals.
 Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child's abilities and thus misinterpret the child's behaviors, miss opportunities to support the child's development, become overly concerned about their child's developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].

### 2025-01-06 paper/cover_anonymized.tex
make anonymized versions

\begin{titlepage}
    \begin{center}
        \vspace*{1in}
        {\Large Beliefs about the development of mental life} \\[2cm]

        [Author names omitted for anonymous review]

    \end{center}
    \vfill
    \textbf{Author Note} \\
    \setlength{\parindent}{2em}

    \indent Study materials, preregistrations, data, analysis scripts, and links to the fully reproducible manuscript and supplemental materials are openly available via the project’s Open Science Framework page (anonymized link for peer review: \url{https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52}). Funding sources and contact information omitted for anonymous review.

\end{titlepage}

### 2025-01-06 paper/paper_anonymized.Rmd
make anonymized versions

--- 2025-01-06 paper/paper.Rmd
@@
 ---
-# title: "Beliefs about the development of mental life"
-# author: 
-#   - "Kara Weisman\\newline University of California, Riverside\\newline ORCID: https://orcid.org/0000-0002-3706-7554"
-#   - "Lucy S. King\\newline Vanderbilt University\\newline ORCID: http://orcid.org/0000-0002-2552-0614"
-#   - "Kathryn Humphreys\\newline Vanderbilt University\\newline ORCID: https://orcid.org/0000-0002-5715-6597"
-# output:
-#   pdf_document:  default
-#   # word_document:
-#     # reference_docx: word-styles-ref.docx
 output:
@@
       in_header: header.tex
-      before_body: cover.tex
+      before_body: cover_anonymized.tex
     toc: false
@@
 - \usepackage{float}
+- \usepackage{url}
 ---
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
-All studies were approved by the Research Compliance Office, Human Subjects Panel (IRB) at Stanford University.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}).
+All studies were approved by [IRB information omitted for anonymous review].
 For extended descriptions of methods and results, see Supplemental Materials.
@@
 On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs.
-These photographs (and all materials used in these studies) are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
+These photographs (and all materials used in these studies) are available in the following OSF repository: \url{https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52} (anonymized link for peer review).
 Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").

### 2025-01-06 supplement/supplement-main_anonymized.Rmd
make anonymized versions

--- 2024-12-30 supplement/supplement-main.Rmd
@@
 ---
-# title: "Beliefs about the development of mental life"
-# subtitle: "Supplemental Materials"
-# author: "Kara Weisman, Lucy S. King, and Kathryn Humphreys"
-# date: "2024-12-30"
 output:
@@
       in_header: header.tex
-      before_body: cover.tex
+      before_body: cover_anonymized.tex
     latex_engine: xelatex
@@
    - \usepackage{float}
+   - \usepackage{url}
    - \usepackage{pdflscape}
@@
 Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.
 
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
-
-All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
-
-All studies were approved by the Institution Review Board for Human Subjects at Stanford University.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (anonymized links for peer review, Study 1: \url{https://osf.io/e6ajh/?view_only=f2539dbce3664172907aa7a381f62d34}; Study 2: \url{https://osf.io/j72dg/?view_only=7e4c01fec32f40a3b13c0ebc2b7ced18}; Study 3: \url{https://osf.io/xh8ce/?view_only=56649aff37aa4f1db2dc06b2e69576f4)}).
+
+All materials used in these studies are available in the following OSF repository: \url{https://osf.io/xrznd/?view_only=d9eb55e46028453cbd90534a003d3f52} (anonymized link for peer review).
+
+All studies were approved by [IRB information omitted for anonymous review].
 

### 2025-01-06 paper/paper.Rmd
fix typos, not sure why all figures are updated

@@
 A handful of recent studies have examined the extent to which cognitive abilities, knowledge, and emotions are thought to be innate vs.
-learned, with special attention to comparing laypeople's beliefs about innateness to scientific evidence for or against innateness and universality [@wang.feigenson2019; @berent.etal2019; @berent.etal2020; see @berent2021 for discussion].
+learned, with special attention to comparing laypeople's beliefs about innateness to scientific evidence for or against innateness and universality [@wang.feigenson2019; @berent.etal2019; @berent.etal2020; see @berent2021, for discussion].
 These studies offer a fascinating glimpse of potential gaps, misconceptions, and biases in laypeople's beliefs about the human mind, but they leave open many questions about the nature of the folk beliefs and intuitive theories themselves.
@@
 More recently, Weisman et al.
-used a similar empirical approach to argue that people's conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" [perceptual-cognitive capacities such as vision and memory, @weisman.etal2017a; see @malle2019 for a similar three-factor solution].
+used a similar empirical approach to argue that people's conceptions of mental life are anchored by three fundamental components: "body" (physiological sensations such as hunger and pain), "heart" (social-emotional abilities such as embarrassment and pride), and "mind" [perceptual-cognitive capacities such as vision and memory, @weisman.etal2017a; see @malle2019, for a similar three-factor solution].
 Such findings have inspired subsequent work on topics as wide-ranging as moral reasoning, dehumanization and stereotyping, beliefs about the afterlife, and human-robot interactions.
@@
 We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned.
-[For in-depth investigations of laypeople's intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @wang.feigenson2019, @berent.etal2019, @berent.etal2020.]
+[For in-depth investigations of laypeople's intuitions about the innateness of cognitive abilities, motor abilities, and emotions, see @berent.etal2019; @berent.etal2020; @wang.feigenson2019.]
 
@@
 We found that participants considered a core capacity for _bodily sensation_ (e.g., hunger, pain) to be present from very early in an infant's life—in many cases, "preprogrammed" and present at birth—leaving relatively little room for development over childhood.
-In contrast—and in line with previous work on adults' intuitions about cognitive development [@berent.etal2019, @wang.feigenson2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by driven primarily by observation of and interactions with the physical and social world.
+In contrast—and in line with previous work on adults' intuitions about cognitive development [@berent.etal2019; @wang.feigenson2019]—participants considered capacities for _cognition and control_ (e.g., planning, self-control) to be largely absent at birth and to develop steadily and gradually over the first five years of life, driven primarily by driven primarily by observation of and interactions with the physical and social world.
 
@@
 In some respects, the results of these studies resonate well with previous work on mind perception among US adults.
-The factors that we refer to as _bodily sensation_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a; weisman.etal2021], and between "affect" and "regulation" [@malle2019].
+The factors that we refer to as _bodily sensation_ and _cognition and control_ highlight a sharp distinction between embodied, physiological experiences and the more cognitive and agentic aspects of mental life experiences—reminiscent of previous distinctions between "experience" and "agency" [@gray.etal2007], between "body" and "mind" [@weisman.etal2017a; @weisman.etal2021], and between "affect" and "regulation" [@malle2019].
 These two factors were clearly evident in all of the factor solutions we examined, providing further evidence that this distinction is a particularly important aspect of how US adults reason about mental life.
@@
 This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials); the emphasis on how mental capacities develop over time; or, more broadly, the exclusive focus on humans as the targets of mind perception.
-Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality", capturing a distinction between cognitive and affective states); "social impact", capturing the degree to which mental states involve social relationships; and "valence", capturing the distinction between positive and negative states [@tamir.etal2016, @tamir.thornton2018, @thornton.tamir2020].
+Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality", capturing a distinction between cognitive and affective states); "social impact", capturing the degree to which mental states involve social relationships; and "valence", capturing the distinction between positive and negative states [@tamir.etal2016; @tamir.thornton2018; @thornton.tamir2020].
 The domains that we have called _social connection_ and _negative affect_ align rather well with these latter two dimensions, capturing a conceptual distinction between the degree to which certain capacities shape and are shaped by interpersonal interactions and social relationships vs.

### 2025-01-07 paper/paper.Rmd
final readthrough

@@
 See Figure 1 for all factor loadings after oblique transformation.
-(See also Supplemental Materials for the 8-factor solution suggested by minimizing the Bayesian Information Criterion [BIC], and the 2-factor solution suggested by implementing the factor retention criteria employed in [@weisman.etal2017a].)
+[See also Supplemental Materials for the 8-factor solution suggested by minimizing BIC, and the 2-factor solution suggested by implementing the factor retention criteria employed in @weisman.etal2017a.]
 
@@
 In our view, these cross-loadings were generally sensible.
-The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensation_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to frustration).
+The item "feeling distressed", for instance, loaded roughly equally strongly on both _bodily sensation_ and _negative affect_—perhaps reflecting the idea that "distress" might be experienced both as a physical sensation (similar to pain) and an affective state (similar to fear or frustration).
 Likewise, "seeing" loaded equally strongly on both _bodily sensation_ and _social connection_—perhaps reflecting an understanding of vision as both a basic sensory ability (closely tied to a particular body part) and a critical part of many social interactions (especially stereotypical interactions with infants, which often hinge on making eye contact, imitating facial expressions, playing peekaboo, etc.).
@@
 One representative prompt began, "You're a statistician and a psychologist, and I'd like your help interpreting my exploratory factor analysis results," followed by the EFA output taken directly from our analysis in R (containing the full list of factor loadings, as well as other summary characteristics of the EFA solution).
-The immediate response generated by ChatGPT included comments on model fit, factor structure, factor interpretability, factor contributions, chi-squared and BIC, as well as suggestions for "next steps"; under interpretability, it read, "MR1 [the factor we have referred to as _cognition and control_, although this label was never provided to the model] has high loadings on items related to planning, self-control, and goal-oriented behaviors.
-It could represent Self-Regulation or Executive Function.
-MR3 [what we have called _social connection_] includes items related to emotions such as feeling excited, happy, or loved.
-This could reflect Positive Emotional Experiences.
-MR2 [*bodily sensation*] has high loadings on items like feeling hungry, tired, and uncomfortable.
-This factor might capture Physical States or Needs.
-MR4 [*negative affect*] captures items like feeling helpless, frustrated, and annoyed.
-It may reflect Negative Emotional Responses or Distress." When asked to tailor labels for an audience of cognitive scientists and clinical psychologists, the model suggested names like "Self-Regulation and Cognitive Control," "Positive Affect and Social Emotions," "Physiological Awareness and Basic Needs," and "Negative Affect and Emotional Distress." (See https://chatgpt.com/share/675a0c61-d534-8006-a978-b731bc997572 for the full text of these prompts and ChatGPT's responses; OpenAI, 2024.) The similarity between our original labels and those generated by ChatGPT provides some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
+The response generated by ChatGPT included comments on factor loadings and structure, factor statistics, model fit, communalities and item complexity, factor score adequacy, key takeaways, and next steps.
+Under factor loadings, it read, "Factor 1 (MR1) includes items related to self-regulation and cognitive control, like 'controlling their emotions' and 'planning.' Factor 2 (MR2) encompasses physical sensations and discomfort, such as 'feeling physically uncomfortable' and 'getting hungry.' Factor 3 (MR3) relates to emotional experiences and social connection, with items like 'feeling happy' and 'loving somebody.' Factor 4 (MR4) is smaller but captures emotional reactivity and distress, such as 'feeling distressed' and 'feeling overwhelmed.'" Under key takeaways, it read, "Factor labels could be: MR1: Self-Regulation and Cognitive Control; MR2: Physical Sensations and Discomfort; MR3: Emotional Experiences and Social Connections; MR4: Emotional Reactivity and Distress." (See https://chatgpt.com/share/677d3926-b284-8006-a37a-ea7543a7a169 for the full text of these prompts and ChatGPT's responses.) The similarity between our original labels and those generated by ChatGPT provides some evidence that the labels used are consistent with common knowledge and intuitions reflected in the vast swath of English language text that constituted the training data for this model, and by extension with the common knowledge and intuitions shared by many lay people in the English-speaking world.
 Nonetheless, we caution the reader to treat these labels as interpretations of empirical results, rather than empirical results themselves.
@@
 A preregistered EFA yielded four factors very similar to the four factors from Study 1, with all capacity items loading strongly on the factors that they were selected to represent and less strongly on other factors.
-(See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.'s (2017) factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
-Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1 (including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings ($\geq$ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors).
+(See Supplemental Materials for this 4-factor solution, which was suggested by both parallel analysis and Weisman et al.'s [2017] factor retention criteria, as well as the 8-factor solution suggested by minimizing BIC).
+Minimally, this suggests that our selection of mental capacities for this study captured the essential meaning of the four factors revealed in Study 1, including the factor we have labeled _negative affect_: In Study 2, this factor accounted for fully `r round_x(s2_results$efa$Vaccounted["Proportion Explained", "MR1"]*100, 0)`% of the shared variance and had strong factor loadings ($\geq$ 0.60) for all 5 of the items selected to represent it, none of which loaded strongly on other factors.
 Beyond this, we consider these results to be a somewhat independent conceptual replication of Study 1 results and validation of our interpretation of these factors.
@@
 
-Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domain that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), characterized by rapid development over the child's first year of life (see Figure 2, Panel A, third box from left).
+Compared to these attributions of _cognition and control_, participants attributed substantially greater capacities to newborns in the domain that we have labeled _social connection_ (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`), but still perceived dramatic non-linear growth in this domain over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`, $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(df) %>% round_x(., 2)`), characterized by rapid development over the child's first year of life (see Figure 2, Panel A, third box from left).
 
@@
 
-In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range; instead, participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and reported the smallest increase increase in capacities over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`), $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(df) %>% round_x(., 2)`).
+In the domain of _bodily sensation_, participants perceived hardly any growth over the target age range; instead, participants attributed nearly maximal capacity to newborns (median score for newborns: `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s2_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _cognition and control_: $\beta$ = `r round_x(s2_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and reported the smallest increase increase in capacities over the target age range ($\chi^2$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`, $edf$ = `r s2_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(df) %>% round_x(., 2)`).
 What growth they did perceive occurred in the first year (see Figure 2, Panel A, leftmost box).
@@
 For example, if participants believe that development in the domain of _bodily sensation_ is primarily driven by innate biological forces, they might assume that most of this development is complete before birth, leaving little room for change over the target ages assessed.
-[See @berent.etal2019, for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., entry to preschool).
+[See @berent.etal2019, for empirical evidence in line with this speculation.] In contrast, in a domain where participants believe development depends on observation, exploration, or social learning, they might think that children need time in the world to change and grow, yielding lower estimates of capacities at birth and slower estimates of rates of change; or, in a domain where participants believe that development occurs through explicitly teaching the child something, they might perceive that development proceeds nonlinearly, such that large changes occur following specific milestones (e.g., beginning preschool).
 We explore these possibilities in Study 3.
@@
 Again, participants attributed substantially greater capacities to newborns in the domains that we have labeled _social connection_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Social connection") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorsoc_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorsoc_cog", "Pr(>|z|)"], 3)))`) and _negative affect_ (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Negative affect") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorneg_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorneg_cog", "Pr(>|z|)"], 3)))`); in Study 3, as in Study 2, participants reported substantial increases in the domain that we have labeled _social connection_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorSocial connection") %>% pull(p), 3)))`) and relatively small increases over the target age range in the domain of _negative affect_ ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorNegative affect") %>% pull(p), 3)))`).
-Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds relative to _Social connection_: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and small increases in capacities for _bodily sensation_ over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`).
+Finally, as in Study 2, in the domain of _bodily sensation_ participants attributed nearly maximal capacity to newborns (median score for newborns: `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(median) %>% round_x(., 2)` out of 100 points, $M$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(mean) %>% round_x(., 2)`, $sd$ = `r s3_cap_rat_newborns_ss %>% filter(factor == "Bodily sensation") %>% pull(sd) %>% round_x(., 2)`; increase in log-odds: $\beta$ = `r round_x(s3_gam_ptab["factorbod_cog", "Estimate"], 2)`, $p$ `r ifelse(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"] < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_ptab["factorbod_cog", "Pr(>|z|)"], 3)))`) and small increases in capacities for _bodily sensation_ over the target age range ($\chi^2$ = `r s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(z) %>% round_x(., 2)`, $p$ `r ifelse(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p)  < 0.001, " < 0.001", paste(" = ", round_x(s3_gam_parameters %>% filter(Parameter == "s(target_year):factorBodily sensation") %>% pull(p), 3)))`).
 
@@
 
-The explanation that "the child is biologically 'preprogrammed' to have this ability" was the modal response (or within 10% of the modal response) for `r s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed") %>% nrow()` of the 8 capacities presented in this study, including all of the capacities chosen to represent the domains of _bodily sensation_ and _negative affect_, as well as one of the two capacities chosen to represent _social connection_.
+The explanation that "the child is biologically 'preprogrammed' to have this ability" was the modal response (or within 10% of the modal response) for `r s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed") %>% nrow()` of the 8 capacities presented in this study, including all of the capacities chosen to represent the domains of _bodily sensation_ (pain, hunger) and _negative affect_ (distress, helplessness), as well as one of the two capacities chosen to represent _social connection_ (happiness).
 Consensus on this selection was particularly pronounced for capacities for hunger (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("hung", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), pain (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("pain", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants), and distress (`r (s3_mech_choice_modes %>% filter(dev_factor == "preprogrammed", grepl("distress", capacity)) %>% pull(prop) %>% round(., 2))*100`% of participants).
 
-Meanwhile, the explanation that "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including helplessness (in the domain of _negative affect_) and social learning (_social connection_), emotional control (_cognition and control_) and reasoning about things (_cognition and control_).
+Meanwhile, the explanation that "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" was a modal choice for `r s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% nrow()` of our 8 capacities, including one of the two capacities chosen to represent _negative affect_ (helplessness), one of the two capacities chosen to represent _social connection_ (learning from other people), and both of the capacities chosen to represent _cognition and control_ (emotional control, reasoning about things).
 However, consensus about this selection was much lower (`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(-1, prop) %>% pull(prop) %>% round(., 2))*100`-`r (s3_mech_choice_modes %>% filter(dev_factor == "brain_changes") %>% top_n(1, prop) %>% pull(prop) %>% round(., 2))*100`% of participants across capacities).
@@
 
-For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures (for example, muscles get stronger, child gets taller)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
-The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
 
-For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
-However, these two biologically inflected explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+However, these two biologically inflected explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
 The remaining mechanisms were rated as fairly unimportant for capacities in this domain (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`).
 
-For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
-These were closely followed by "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
-The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+These were closely followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
 Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row), many developmental mechanisms were rated as highly important.
-The highest-rated mechanisms were "the child's brain changes (for example, brain grows bigger, more or fewer connections between neurons)" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
-Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
-The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, sd = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
+The highest-rated mechanisms were "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
+The remaining mechanisms were generally rated as fairly unimportant (median scores: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; means: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)` - `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-5, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "the child has experiences in the womb that give them this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("womb", Parameter)) %>% pull(p), 3)))`).
 
@@
 This difference from previous work could have many (or multiple) causes, including the wider range of capacities included in this study (in particular, the inclusion of capacities for feelings of helplessness, frustration, annoyance, neglect, loneliness, boredom, confusion, and being overwhelmed; see Supplemental Materials); the emphasis on how mental capacities develop over time; or, more broadly, the exclusive focus on humans as the targets of mind perception.
-Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality", capturing a distinction between cognitive and affective states); "social impact", capturing the degree to which mental states involve social relationships; and "valence", capturing the distinction between positive and negative states [@tamir.etal2016; @tamir.thornton2018; @thornton.tamir2020].
+Indeed, one exciting line of work focusing on how laypeople think about other humans' mental states has surfaced a robust conceptual architecture in which mental states are organized in three dimensions: "rationality", capturing a distinction between cognitive and affective states; "social impact", capturing the degree to which mental states involve social relationships; and "valence", capturing the distinction between positive and negative states [@tamir.etal2016; @tamir.thornton2018; @thornton.tamir2020].
 The domains that we have called _social connection_ and _negative affect_ align rather well with these latter two dimensions, capturing a conceptual distinction between the degree to which certain capacities shape and are shaped by interpersonal interactions and social relationships vs.
@@
 Indeed, in Study 3 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely "cognitive" ability included in that study, reasoning about things (see Figure 3).
-Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
+Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021] or "intuitive nativists", then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.
 Further work on this topic would do well to integrate the cognitive processing mechanisms featured in the current studies with epistemic states that have been the focus of past research on laypeople's beliefs about the innateness of "cognitive" abilities [@berent.etal2019; @wang.feigenson2019] to paint a more comprehensive picture of the ways in which intuitive theories of development do and do not align with scientific theories such as nativism, empiricism, and constructivism.
@@
 Whether focused on improving accuracy, affective experience, or adaptiveness, critical next steps in this line of research will involve assessing which aspects of adults' beliefs and theories about the development of mental life facilitate the kinds of caregiving behaviors that are most beneficial for children according to experts, most appropriate in a given cultural setting, or most in line with caregivers' own values and goals.
-Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child's abilities and thus misinterpret the child's behaviors, miss opportunities to support the child's development, become overly concerned about their child's developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].
+Identifying the antecedents of individual and group-wise differences in these beliefs—especially those that might lead caregivers to over- or under-estimate a child's abilities and thus misinterpret the child's behaviors, miss opportunities to support the child's development, or become overly concerned about their child's developmental progress—will be an especially important step for such clinically-focused applications, including interventions to reduce risk for child abuse and neglect [@king.etal2021].
 As is the case in many domains [@weisman.markman2017], interventions that leverage the power of intuitive theories to encourage positive and responsive caregiving behaviors hold great promise for creating meaningful and lasting behavioral changes in caregiver behavior, with important consequences for child wellbeing.

### 2025-02-14 paper/paper_anonymized.Rmd
revisions for R&R

@@
 For extended descriptions of methods and results, see Supplemental Materials.
+Note: scripts for all analyses, figures, and tables are available in the .Rmd file that generated the fully reproducible Supplemental Materials document (supplement-main.Rmd), which can be found in the following GitHub repository (anonymized for peer review): \url{https://anonymous.4open.science/r/baby_mental_life_ms-C261/}.
 
@@
 This theoretical perspective motivated our choice of exploratory factor analysis as our dimensionality reduction technique (rather than, e.g., principal components analysis or cluster analysis); our choice of labels for each factor, in which we have attempted to describe what might be understood by participants as core components of the developing human mind (rather than attempting to label a category); and our interpretation of factor loadings, which focuses not only on capacities that load strongly on only one factor but also on capacities that cross-load on multiple factors.
-See Supplemental Materials for more details about this analysis, including our decision to treat participants' ratings of each of the three target ages as if they were a distinct source of data.
+See Supplemental Materials for more details about this analysis, including our decision to treat participants' ratings of each of the three target ages as if they were a distinct source of data, and solutions employing orthogonal (varimax) rotation rather than the oblique (oblimin) transformations presented here.
 
 A `r s1_results$efa$factors`-factor solution (as suggested by parallel analysis) accounted for `r round_x(s1_results$efa$Vaccounted["Cumulative Var", "MR4"]*100, 0)`% of the total variance in participants' capacity attributions, suggesting that four latent constructs can account for a substantial amount of the variability across target ages and across individual participants in perceptions of infants' and young children's mental lives.
-See Figure 1 for all factor loadings after oblique transformation.
-[See also Supplemental Materials for the 8-factor solution suggested by minimizing BIC, and the 2-factor solution suggested by implementing the factor retention criteria employed in @weisman.etal2017a.]
+See Figure 1 for all factor loadings after oblique transformation, and see Supplemental Materials for a scatterplot matrix ("pairs plot") and related plots visualizing the relationships among factor loadings across these four factors and the distributions of factor loadings across items (Figures S1-S7); as well as factor loading for the 8-factor solution suggested by minimizing BIC, and the 2-factor solution suggested by implementing the factor retention criteria employed in Weisman et al.
+(2017).
 
@@
 
-Regressing participants' item-level responses onto target age, domain, and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children's capacities differed dramatically across domains.
-Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape these perceived developmental trajectories from the bottom up (see Figure 2), without specifying in advance the shape of the curve.
+Regressing participants' item-level responses onto target age, domain (assigned a priori; see preregistration), and interactions between them via a multilevel generalized additive model (using a binomial distribution and the logit link function) confirmed both of our preregistered hypotheses: On average, participants rated older children as more capable, but perceptions of the development of children's capacities differed dramatically across domains.
+Modeling the effects of target age via smoothing terms allowed us to reconstruct the shape of these perceived developmental trajectories from the bottom up (see Figure 2), without specifying in advance the shape of the curve.
 
@@
 
-Responses to questions about developmental mechanisms are visualized in Figure 3.
+Responses to questions about developmental mechanisms are visualized in Figures 3 and 4.
 
@@
 In terms of selections of the "most important" mechanism driving the development of these capacities between 0-5 years, two explanations—biological preprogramming and brain changes—accounted for most of participants' selections.
-Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3.
-(See also Supplemental Materials for a multinomial regression comparing the selection of most important mechanism across capacities.)
+Percentage selections and modal responses for all developmental mechanisms are presented in Figure 3; a network graph summarizing the importance of each developmental mechanism for each capacity is presented in Figure 4.
+(See also Supplemental Materials for a multinomial regression comparing the selection of the most important mechanism across capacities.)
 
@@
 Independent ratings of the importance of each developmental mechanism present a more nuanced—but largely consistent—picture of intuitive theories of development across these domains.
-See Figure 3, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.
+See Figures 3-4, and see Supplemental Materials for the full results of the multilevel linear regression analyses briefly presented below.
 
@@
 
-For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _bodily sensation_ (Figure 3, top row; Figure 4, first and second capacities from the left), "the child is biologically 'preprogrammed' to have this ability" stood out as the highest-rated mechanism by far (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`), followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`), and "the child's body grows and matures" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("body", Parameter)) %>% pull(p), 3)))`).
 The remaining mechanisms were rated as quite unimportant for capacities in this domain (all medians $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, median) %>% top_n(1, median) %>% distinct(median) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`; all $M$ $\leq$ `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-7, mean) %>% top_n(1, mean) %>% distinct(mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`), with particularly low ratings for "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Bodily", Domain)) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_bod_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`).
 
-For capacities in the domain of _negative affect_ (Figure 3, second row), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain of _negative affect_ (Figure 3, second row; Figure 4, third and fourth capacities from the left), the two highest-rated mechanisms were again "the child is biologically 'preprogrammed' to have this ability" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("prep", Parameter)) %>% pull(p), 3)))`) and "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
 However, these two biologically inflected explanations were closely followed by explanations that are more social and observational in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); "the child observes objects and the physical world" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obso", Parameter)) %>% pull(p), 3)))`); "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Negative", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_neg_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
@@
 
-For capacities in the domain that we have called _social connection_ (Figure 3, third row), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+For capacities in the domain that we have called _social connection_ (Figure 3, third row; Figure 4, fifth and sixth capacities from the left), the two highest-rated mechanisms were both explicitly social in nature: "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`) and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
 These were closely followed by "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Social", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_soc_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`).
@@
 
-Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row), many developmental mechanisms were rated as highly important.
-The highest-rated mechanisms were "the child's brain changes " (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
+Finally, for capacities in the domain that we have called _cognition and control_ (Figure 3, bottom row; Figure 4, last two capacities on the right), many developmental mechanisms were rated as highly important.
+The highest-rated mechanisms were "the child's brain changes" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)` on a scale from 0-6, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)`, 95% CI: [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("brai", Parameter)) %>% pull(p), 3)))`); "the child interacts with the people around him or her" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(2, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("intp", Parameter)) %>% pull(p), 3)))`); and "the child observes other people" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(3, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("obsp", Parameter)) %>% pull(p), 3)))`).
 Of note, these were closely followed by two mechanisms that were not highly rated in other domains: "people explicitly teach the child how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(4, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("teac", Parameter)) %>% pull(p), 3)))`); and "the child actively experiments with how to do this" (median score: `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(median) %>% as.numeric() %>% round_x(., 2)`, $M$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(mean) %>% as.numeric() %>% round_x(., 2)`, $sd$ = `r s3_mech_rat_ss_c %>% filter(grepl("Cognit", Domain)) %>% top_n(5, mean) %>% top_n(-1, mean) %>% pull(sd) %>% as.numeric() %>% round_x(., 2)`; comparison to grand mean: $\beta$ = `r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(Coefficient) %>% as.numeric() %>% round_x(., 2)` [`r s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% data.frame() %>% select(CI_low, CI_high) %>% round_x(., 2) %>% unite(CI95, c(CI_low, CI_high), sep = ", ") %>% as.character()`], $p$ `r ifelse(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p) < 0.001, " < 0.001", paste(" = ", round_x(s3_lmer_cog_tab %>% filter(Effects == "fixed", grepl("expt", Parameter)) %>% pull(p), 3)))`).
@@
 knitr::include_graphics("../outputs/fig03.pdf")
+```
+
+```{r fig04, fig.cap="Network graph summarizing the importance of each developmental mechanism (along the bottom) for each capacity (along the top) among US adults (Study 3).
+Capacities are sorted and color-coded by domain (see Figures 2-3); developmental mechanisms are arranged in the fixed order of presentation (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
+See main text for the full text of each mechanism.", fig.width = 8, fig.asp = 0.8}
+knitr::include_graphics("../outputs/fig04.pdf")
 ```
@@
 
+Related to the issue of the cultural specificity of our findings is the issue of the specificity of our stimuli.
+In selecting photos for each target age, we aimed to have photos of the same (or very similar-looking) children at all target ages so as to emphasize the question of the development of mental capacities over the course of an individual child’s early life.
+We chose to illustrate each target age with two photos in order to emphasize that we were interested in children’s mental capacities in general, rather than the experiences of a particular child in a particular moment.
+We included one boy and one girl at each target age in order to generalize across potential perceived sex/gender differences in children’s early mental life.
+We used photographs of two (apparently) White, non-Hispanic children, for three reasons: (1) in order to avoid introducing spurious differences across target ages by confounding a target’s age and race/ethnicity; (2) in order to match the anticipated race/ethnicity of the majority of participants on MTurk; and (3) because of the limited set of high-resolution photographs of individual children of color at different points of development available to us.
+Conducting similar studies of adults’ perceptions of the development of mental life with more ethnically and racially diverse participants, and examining the effects of sex, gender, race, and ethnicity on adults’ perceptions of children’s mental life, will be important next steps in this line of research.
+
+On a similar note, although our instructions emphasized to participants that we were interested in their assessment of children in general, rather than the depicted children in particular, it is nearly inevitable that the particular photographs used as stimuli—not just race and ethnicity, but also facial expressions, attractiveness, cues to social class, and so on—would guide participants’ responses.
+Future research might employ a variety of approaches to address this concern, such as constructing a much larger and more diverse pool of visual stimuli and varying the subset of stimuli provided across participants; blurring children’s facial expressions; blurring or removing the background of the photographs; or removing all visual stimuli from the study (likely more appropriate for parents of young children than for a general population study).
+
 One of the most interesting future directions for this line of research will be to assess how the experience of raising a child might change caregivers' representations of and intuitive theories about the development of mental life across infancy and early childhood.
@@
 However, we consider careful comparisons of parents and non-parents, as well as close longitudinal explorations of the effects of caregiving on beliefs about the development of mental life, to be topics warranting further research.
+
+Finally, while our current analytical approach identifies key patterns in these developmental trajectories, future work could benefit from employing functional data analysis methods, such as functional principal components analysis (fPCA), which might capture smooth, continuous variations in temporal patterns and better account for the inherent time-dependency in developmental data [@ramsay.silverman2002].
+Such an approach might identify clusters of mental capacities that hang together not only in terms of overall covariance, but also in terms of the perceived timing and rate of development, or in terms of other temporal dynamics that our current approach might not detect.
+Employing such techniques would be an exciting next step in this line of research.
 
@@
 Comparing participants' intuitions to empirical findings from scientific studies of child development has illuminated the ways in which lay people's reasoning about cognitive development [@berent.etal2019; @wang.feigenson2019] and about emotions [@berent.etal2020] has proved a useful way of illuminating biases and misconceptions in laypeople's beliefs about innateness.
+The primary goal of the current studies was to characterize how US adults think about development, rather than to generate precise estimates of the age at which lay people consider each of these capacities to “come online”; nonetheless, each of these studies provides estimates of participants’ beliefs about children’s capacities at different ages, and the collection of these studies provides some indication of how stable these estimates are across different methods of administration; see Supplemental Materials for direct comparisons of developmental trajectories across studies at the level of the individual capacity (Figure S9) and the domain (Figure S10).
 Finding creative ways to determine the ground truth of the development of the range of capacities included in the current studies—many of which are phenomenal experiences—will be a particular challenge to this endeavor, but would be both deeply fascinating and of practical interest to predicting downstream consequences for children.

### 2025-02-14 supplement/BCV.Rmd
revisions for R&R

---
title: 'Baby mental life: Bi-cross-validation'
author: "Kara Weisman"
date: "2025-02-04"
output: html_document
---

```{r setup, set.seed(94305), include = F}
knitr::opts_chunk$set(cache = T)
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(include = F)
```

```{r load packages}
# library(ggdendro)
# library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(cowplot)
# library(fda)
library(rsq)
library(ggnewscale)
library(tidyverse)

library(softImpute)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
```

```{r load custom funs}
source("../code/custom_funs.R")
```

```{r load data}
# suppress warnings and messages because dplyr is verbose
suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", chdir = TRUE)))
```

\newpage
In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life. We identified four core capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).

In this RMarkdown file, we apply a "bi-cross-validation" approach to the EFA in Study 1.

```{r load custom funs}
source("../code/custom_funs.R")
```

```{r load data}
# suppress warnings and messages because dplyr is verbose
suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", chdir = TRUE)))
# suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", chdir = TRUE)))
# suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", chdir = TRUE)))
```

### BCV

```{r}
# had to instsall from source, not maintained on CRAN. retrieved from https://jingshuw.org/publication/owen-2016-aa/ (see also https://cran.r-project.org/web/packages/esaBcv/)
# install.packages("https://cran.r-project.org/src/contrib/Archive/esaBcv/esaBcv_1.2.1.1.tar.gz")

# library(esaBcv)
```

```{r}
# X <- as.matrix(d1_all)
# 
# bcv_res <- EsaBcv(X, center = F) # center adds intercept to model
# 
# plot(bcv_res)
```

```{r}
# bcv_res$best.r
# bcv_res$mu
```

```{r}
# bcv_res_esa <- ESA(Y = d1_all, r = bcv_res$best.r)
# 
# bcv_res_esa_V <- bcv_res_esa$estV
# colnames(bcv_res_esa_V) <- paste0("V", 1:bcv_res$best.r) 
# rownames(bcv_res_esa_V) <- colnames(d1_all)
# 
# fa.sort(bcv_res_esa_V)
```

```{r}
# bcv_res_efa <- fa(d1_all, nfactors = bcv_res$best.r, rotate = "oblimin")
```

```{r, fig.width = 10, fig.asp = 1.1}
# heatmap_fun(bcv_res_efa)
```

```{r}
# library(psych)
# library(dplyr)
# library(tidyr)

# Example Data: Assuming d1_all includes ParticipantID
X <- as.matrix(d1_all)  # Data matrix (participants x items)

# Step 1: Create Cross-Validation folds (leave out entire participants)
k_folds_row <- 5  # Number of participant folds
k_folds_col <- 5  # Number of item folds
set.seed(94025)  # For reproducibility

# Assign participants to folds_row
unique_participants <- unique(d1$ResponseId)

participant_folds <- sample(rep(1:k_folds_row, length.out = length(unique_participants)))
names(participant_folds) <- unique_participants

participant_folds_target00mo <- participant_folds
names(participant_folds_target00mo) <- paste(unique_participants, "target00mo", sep = "_")

participant_folds_target09mo <- participant_folds
names(participant_folds_target09mo) <- paste(unique_participants, "target09mo", sep = "_")

participant_folds_target60mo <- participant_folds
names(participant_folds_target60mo) <- paste(unique_participants, "target60mo", sep = "_")

participant_folds <- c(
  participant_folds_target00mo,
  participant_folds_target09mo,
  participant_folds_target60mo)

# Assign items (columns) to folds_col
unique_items <- colnames(X)

item_folds <- sample(rep(1:k_folds_col, length.out = length(unique_items)))
names(item_folds) <- unique_items

# Map fold assignments back to rows and columns
folds_row <- participant_folds[as.character(rownames(X))]  # Assign rows to folds based on participant ID
folds_col <- item_folds[as.character(colnames(X))]  # Assign columns to folds

# Step 2: Bi-Cross-Validation Function for Varying Number of Factors
nfact_range <- 1:12  # Test from 1 to 12 factors

# Initialize storage for results
bcv_results <- lapply(nfact_range, function(nfact) {
  fold_metrics_list <- lapply(1:k_folds_row, function(fold_row) {
    fold_metrics_col_list <- lapply(1:k_folds_col, function(fold_col) {

      # Training and Test Data
      train_data <- X
      test_data <- X[folds_row == fold_row, , drop = FALSE]  # Hold out participants (rows)

      train_data[folds_row == fold_row, ] <- NA  # Mask participant data
      train_data[, folds_col == fold_col] <- NA  # Mask item (column) data

      # Step 3: Remove items with excessive missing data
      missing_prop <- colMeans(is.na(train_data))
      items_to_keep <- names(missing_prop[missing_prop < 0.5])  # Keep items with <50% missingness
      train_data_filtered <- train_data[, items_to_keep, drop = FALSE]
      test_data_filtered <- test_data[, items_to_keep, drop = FALSE]

      # Check if enough items are left to perform EFA
      if (ncol(train_data_filtered) < nfact) return(rep(NA, 5))  # Return NA for all metrics

      # Step 4: Fit EFA on Training Data
      efa_fit <- tryCatch({
        fa(train_data_filtered, nfactors = nfact, 
           rotate = "oblimin", fm = "minres", missing = TRUE, scores = "tenBerge")
      }, error = function(e) { return(NULL) })

      # Skip fold if EFA did not converge
      if (is.null(efa_fit)) return(rep(NA, 5))

      # Step 5: Predict Factor Scores for Test Data Using Observed Values
      predicted_factor_scores <- tryCatch({
        factor.scores(test_data_filtered, efa_fit, method = "tenBerge")$scores
      }, error = function(e) { return(NULL) })

      # Skip fold if factor score prediction fails
      if (is.null(predicted_factor_scores)) return(rep(NA, 5))

      # Step 6: Reconstruct Test Data Using Predicted Factor Scores
      reconstructed_data <- predicted_factor_scores %*% t(efa_fit$loadings[])

      # Align reconstructed data with original test_data columns
      reconstructed_full <- matrix(NA, nrow = nrow(test_data), ncol = ncol(X))
      colnames(reconstructed_full) <- colnames(X)
      reconstructed_full[, items_to_keep] <- reconstructed_data

      # Identify positions with observed data in both matrices
      mask <- !is.na(test_data) & !is.na(reconstructed_full)

      # Step 7: Compute Multiple Evaluation Metrics
      if (sum(mask) > 0) {  
        mse <- mean((test_data[mask] - reconstructed_full[mask])^2)
        rmse <- sqrt(mse)
        mae <- mean(abs(test_data[mask] - reconstructed_full[mask]), na.rm = TRUE)
        srmr <- sqrt(mean((cor(test_data, use = "pairwise.complete.obs") - 
                           cor(reconstructed_full, use = "pairwise.complete.obs"))^2, na.rm = TRUE))
        correlation <- cor(as.vector(test_data[mask]), as.vector(reconstructed_full[mask]), use = "pairwise.complete.obs")
      } else {
        mse <- NA
        rmse <- NA
        mae <- NA
        srmr <- NA
        correlation <- NA
      }

      return(c(MSE = mse, RMSE = rmse, MAE = mae, SRMR = srmr, Correlation = correlation))

    })  # End column fold loop

    # Convert fold-level metrics to a data frame and take the mean across item folds
    fold_metrics_col_df <- do.call(rbind, fold_metrics_col_list)
    colMeans(fold_metrics_col_df, na.rm = TRUE)

  })  # End row fold loop

  # Convert row-level metrics to a data frame and take the mean across participant folds
  fold_metrics_df <- do.call(rbind, fold_metrics_list)
  colMeans(fold_metrics_df, na.rm = TRUE)
})

# Convert list to data frame with explicit column names
bcv_results_df <- as.data.frame(do.call(rbind, bcv_results)) %>%
  rownames_to_column("nfact") %>%
  mutate(nfact = as.numeric(nfact)) %>%
  select(nfact, everything())

colnames(bcv_results_df)[2:ncol(bcv_results_df)] <- c("MSE", "RMSE", "MAE", "SRMR", "Correlation")

# Display the full table of evaluation metrics
bcv_results_df %>%
  kable(digits = 2) %>%
  kable_styling()
```

```{r}
# library(ggplot2)
# library(dplyr)
# library(tidyr)

for(i in colnames(bcv_results_df)[2:ncol(bcv_results_df)]) {
  which_metric <- i

  # Compute first and second derivatives to detect the elbow point
  first_diff <- diff(bcv_results_df[[which_metric]])  # Use [[ ]] to subset correctly
  second_diff <- diff(first_diff)

  # Find the first local minimum of the second derivative
  if (i == "Correlation") {
    elbow_point <- which(diff(sign(diff(second_diff))) < 0)[1] + 1
  } else {
    elbow_point <- which(diff(sign(diff(second_diff))) > 0)[1] + 1
  }

  # Plot with the elbow point highlighted
  p <- bcv_results_df %>%
    ggplot(aes(x = nfact, y = .data[[which_metric]])) +  # Use .data[[ ]] for tidyverse
    geom_line() +
    geom_point() +
    scale_x_continuous("Number of factors", breaks = seq(0, 100, 1)) +
    annotate("point", x = elbow_point, y = bcv_results_df[[which_metric]][elbow_point],
             color = "red", shape = 4, size = 10) +
    theme_bw()

  print(p)
}
```

```{r, fig.width = 10, fig.asp = 1}
fa(d1_all, nfactors = 4, rotate = "geominQ") %>% heatmap_fun()
fa(d1_all, nfactors = 5, rotate = "geominQ") %>% heatmap_fun()
fa(d1_all, nfactors = 6, rotate = "geominQ") %>% heatmap_fun()
```

```{r, fig.width = 10, fig.asp = 1}
fa(d1_all, nfactors = 4) %>% loadings(cutoff = 0) %>% fa.sort()
fa(d1_all, nfactors = 5) %>% loadings(cutoff = 0) %>% fa.sort()
fa(d1_all, nfactors = 6) %>% loadings(cutoff = 0) %>% fa.sort()
```

### 2025-02-14 supplement/functional-PCA.Rmd
revisions for R&R

---
title: 'Baby mental life: fPCA'
author: "Kara Weisman"
date: "2025-02-03"
output: html_document
---

```{r setup, set.seed(94305), include = F}
knitr::opts_chunk$set(cache = T)
knitr::opts_chunk$set(echo = F)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(include = F)
```

```{r load packages}
library(ggdendro)
library(dendextend)
library(psych)
library(lme4)
library(mgcv)
library(kableExtra)
library(langcog)
library(parameters)
library(cowplot)
library(fda)
library(tidyverse)
library(rsq)
library(ggnewscale)
```

```{r load custom funs}
source("../code/custom_funs.R")
```

```{r load data}
# suppress warnings and messages because dplyr is verbose
suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", chdir = TRUE)))
```

\newpage
In a series of large-scale studies we assessed how US adults conceptualize the development of the human mind over the first five years of life. We identified four core capacities that are perceived by US adults to develop over human infancy and early childhood, _bodily sensation_, _negative affect_, _social connection_, and _cognition and control_ (Study 1); charted how these different aspects of mental life are perceived to change over the first five years of a child's life (Studies 2-3); and explored the intuitive theories that underlie the observed differences in the perceived developmental trajectories of these four aspects of mental life (Study 3).

In this RMarkdown file, we apply a "functional PCA" approach to analyzing the data from Study 2.

```{r load custom funs}
source("../code/custom_funs.R")
```

```{r load data}
# suppress warnings and messages because dplyr is verbose
# suppressWarnings(suppressMessages(source("../code/data_prep_s1.R", chdir = TRUE)))
suppressWarnings(suppressMessages(source("../code/data_prep_s2.R", chdir = TRUE)))
# suppressWarnings(suppressMessages(source("../code/data_prep_s3.R", chdir = TRUE)))
```

```{r}
d2_scales <- data.frame(
  capacity = colnames(d2_all)) %>%
  mutate(
    factor = case_when(
      capacity %in% c(
        "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
        "feeling_physically_uncomfortable") ~ "Bodily sensation",
      capacity %in% c(
        "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
        "feeling_helpless", "feeling_lonely") ~ "Negative affect",
      capacity %in% c(
        "feeling_happy", "finding_something_funny", "feeling_excited",
        "loving_somebody", "learning_from_other_people") ~ "Social connection",
      capacity %in% c(
        "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
        "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
  mutate(factor = factor(
    factor, 
    levels = c(
      "Bodily sensation", "Negative affect", 
      "Social connection", "Cognition and control"))) %>%
  arrange(factor) %>%
  mutate(loading = NA,
         order = 1:nrow(.))
```

```{r}
d2_cap_ratings <- d2_all %>%
  rownames_to_column("ResponseId_target") %>%
  separate(ResponseId_target, c("ResponseId", "target")) %>%
  mutate(target_year = recode(
    target,
    target00mo = 0, # newborns
    target0Xmo = 4/365, # 4 days
    target01mo = 1/12, # 1 month
    target02mo = 2/12, 
    target04mo = 4/12, 
    target06mo = 6/12, 
    target09mo = 9/12,
    target12mo = 12/12,
    target18mo = 18/12,
    target24mo = 24/12,
    target36mo = 36/12,
    target48mo = 48/12,
    target60mo = 60/12)) %>%
  gather(capacity, response, -ResponseId, -starts_with("target")) %>%
  left_join(d2_scales %>% distinct(factor, capacity))
```

### Functional PCA

```{r functional_pca_study2_multivariate, echo=TRUE, message=FALSE, warning=FALSE}
# # Step 1: Reshape the data to wide format (each Capacity × Target Age as a column)
# d2_ratings_matrix <- d2_cap_ratings %>%
#   dplyr::select(-c(target, factor)) %>%
#   unite("capacity_age", capacity, target_year, sep = "_") %>%
#   pivot_wider(names_from = capacity_age, values_from = response) %>%
#   column_to_rownames("ResponseId") %>%
#   as.matrix()

# Step 1: Define the target ages based on 'target_year'
ages <- sort(unique(d2_cap_ratings$target_year))  # Numeric ages in years

# Step 2: Create a B-spline basis for smoothing
basis <- create.bspline.basis(rangeval = range(ages), nbasis = 4)  # Adjust nbasis if needed

# Step 3: Get the list of unique capacities
capacities <- unique(d2_cap_ratings$capacity)

# Step 4: Smooth the data for each capacity separately
smoothed_list <- lapply(capacities, function(cap) {
  # Subset data for the current capacity and reshape to wide format
  ratings_submatrix <- d2_cap_ratings %>%
    filter(capacity == cap) %>%
    dplyr::select(-factor, -target, -capacity) %>%
    pivot_wider(names_from = target_year, values_from = response) %>%
    column_to_rownames("ResponseId") %>%
    as.matrix()

  # Apply smoothing
  smooth.basis(argvals = ages, y = t(ratings_submatrix), fdParobj = basis)$fd
})

# # Step 5: Combine smoothed data for multivariate functional PCA
# smoothed_data_combined <- do.call(cbind, smoothed_list)

# # Combine smoothed data into a multivariate functional data object
# # Stack the functional data using fd utilities
# fd_list_combined <- do.call(fd, lapply(smoothed_list, function(x) x$coefs))

# Step 1: Extract coefficients from each smoothed fd object
coef_matrix <- do.call(cbind, lapply(smoothed_list, function(fd_obj) fd_obj$coefs))

# Step 2: Use the same basis as before to create a new multivariate functional data object
combined_fd <- fd(coef_matrix, basis)

# Step 3: Perform functional PCA
fpca_result <- pca.fd(combined_fd, nharm = 4)  # Extract first 4 principal components

# Step 4: Visualize the principal components
plot(fpca_result$harmonics, main = "Multivariate Functional PCA (Study 2)")

# Step 5: Display variance explained by each principal component
fpca_result$varprop
```

```{r}
scores <- fpca_result$scores

plot(scores[,1], scores[,2], 
     xlab = "PC1 Scores", ylab = "PC2 Scores",
     main = "Participant Scores on PC1 vs PC2",
     pch = 19, col = "darkorange")
abline(h = 0, v = 0, lty = 2)
```

```{r}
# Compare PC1 loadings across capacities
plot(fpca_result$harmonics[1], col = "blue", lwd = 2, main = "PC1 Across Capacities")
plot(fpca_result$harmonics[2], col = "red", lwd = 2, main = "PC2 Across Capacities")
plot(fpca_result$harmonics[3], col = "green", lwd = 2, main = "PC3 Across Capacities")
plot(fpca_result$harmonics[4], col = "purple", lwd = 2, main = "PC4 Across Capacities")
```

```{r}
# Merge participant scores with the original data
participant_scores <- data.frame(
  ResponseId = unique(d2_cap_ratings$ResponseId),
  PC1_Score = fpca_result$scores[,1],
  PC2_Score = fpca_result$scores[,2],
  PC3_Score = fpca_result$scores[,3],
  PC4_Score = fpca_result$scores[,4])

# Merge with capacity data
merged_data <- d2_cap_ratings %>%
  left_join(participant_scores, by = "ResponseId")
```

```{r, fig.width = 10}
# Plot how PC1 scores relate to specific capacities (example with 'reasoning_about_things')
merged_data %>%
  mutate(score_cat = case_when(
    PC1_Score < 0 ~ "low",
    PC1_Score >= 0 ~ "high")) %>%
  mutate(capacity = str_wrap(gsub("_", " ", capacity), 20)) %>%
  ggplot(aes(x = target_year, y = response, color = score_cat)) +
  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor)))) +
  geom_smooth() +
  # geom_jitter(height = 0, width = 0.2, alpha = 0.05, size = 0.1) +
  # scale_color_gradient(low = "red", high = "blue") +
  theme_minimal() +
  labs(title = "PC1 Scores vs. Reasoning Ratings Across Ages",
       color = "PC1 score (cutoff: 0)",
       x = "Target Age (years)", y = "Rating")
```

```{r, fig.width = 10}
# Plot how PC2 scores relate to specific capacities (example with 'reasoning_about_things')
merged_data %>%
  mutate(score_cat = case_when(
    PC2_Score < 0 ~ "low",
    PC2_Score >= 0 ~ "high")) %>% 
  mutate(capacity = str_wrap(gsub("_", " ", capacity), 20)) %>%
  ggplot(aes(x = target_year, y = response, color = score_cat)) +
  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor)))) +
  geom_smooth() +
  # geom_jitter(height = 0, width = 0.2, alpha = 0.05, size = 0.1) +
  # scale_color_gradient(low = "red", high = "blue") +
  theme_minimal() +
  labs(title = "PC2 Scores vs. Reasoning Ratings Across Ages",
       color = "PC2 score (cutoff: 0)",
       x = "Target Age (years)", y = "Rating")
```

```{r, fig.width = 10}
# Plot how PC3 scores relate to specific capacities (example with 'reasoning_about_things')
merged_data %>%
  mutate(score_cat = case_when(
    PC3_Score < 0 ~ "low",
    PC3_Score >= 0 ~ "high")) %>% 
  mutate(capacity = str_wrap(gsub("_", " ", capacity), 20)) %>%
  ggplot(aes(x = target_year, y = response, color = score_cat)) +
  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor)))) +
  geom_smooth() +
  # geom_jitter(height = 0, width = 0.2, alpha = 0.05, size = 0.1) +
  # scale_color_gradient(low = "red", high = "blue") +
  theme_minimal() +
  labs(title = "PC3 Scores vs. Reasoning Ratings Across Ages",
       color = "PC3 score (cutoff: 0)",
       x = "Target Age (years)", y = "Rating")
```

```{r, fig.width = 10}
# Plot how PC4 scores relate to specific capacities (example with 'reasoning_about_things')
merged_data %>%
  mutate(score_cat = case_when(
    PC4_Score < 0 ~ "low",
    PC4_Score >= 0 ~ "high")) %>% 
  mutate(capacity = str_wrap(gsub("_", " ", capacity), 20)) %>%
  ggplot(aes(x = target_year, y = response, color = score_cat)) +
  facet_wrap(facets = vars(reorder(capacity, as.numeric(factor)))) +
  geom_smooth() +
  # geom_jitter(height = 0, width = 0.2, alpha = 0.05, size = 0.1) +
  # scale_color_gradient(low = "red", high = "blue") +
  theme_minimal() +
  labs(title = "PC4 Scores vs. Reasoning Ratings Across Ages",
       color = "PC4 score (cutoff: 0)",
       x = "Target Age (years)", y = "Rating")
```

```{r}
library(fda)  # Ensure functional data analysis tools are available
# Step 1: Reshape the data to wide format (each Capacity × Target Age as a column)
d2_ratings_matrix <- d2_cap_ratings %>%
  dplyr::select(-c(target, factor)) %>%
  unite("capacity_age", capacity, target_year, sep = "_") %>%
  pivot_wider(names_from = capacity_age, values_from = response) %>%
  column_to_rownames("ResponseId") %>%
  as.matrix()

# Extract observed eigenvalues from fPCA result
observed_eigenvalues <- fpca_result$values

# Set up parallel analysis
num_simulations <- 100  # Increase for better stability
random_eigenvalues <- matrix(NA, nrow = length(observed_eigenvalues), ncol = num_simulations)

# Generate randomized functional datasets and compute fPCA on them
set.seed(123)  # For reproducibility
for (i in 1:num_simulations) {
  shuffled_data <- d2_ratings_matrix[sample(nrow(d2_ratings_matrix)), ]  # Shuffle rows
  smoothed_random <- smooth.basis(argvals = ages, y = t(shuffled_data), fdParobj = basis)$fd
  fpca_random <- pca.fd(smoothed_random, nharm = length(observed_eigenvalues))
  random_eigenvalues[, i] <- fpca_random$values
}

# Compute 95th percentile (upper bound) of randomized eigenvalues
random_threshold <- apply(random_eigenvalues, 1, quantile, probs = 0.95, na.rm = TRUE)

# Plot observed vs. randomized eigenvalues
plot(observed_eigenvalues, type = "b", pch = 19, col = "blue",
     xlab = "Principal Component", ylab = "Eigenvalue",
     main = "Parallel Analysis for fPCA")
lines(random_threshold, type = "b", pch = 19, col = "red", lty = 2)

legend("topright", legend = c("Observed", "Randomized 95% CI"),
       col = c("blue", "red"), lty = c(1, 2), pch = 19)

# Determine optimal number of PCs (where observed > random)
optimal_pcs <- sum(observed_eigenvalues > random_threshold)
cat("Optimal Number of Functional PCs:", optimal_pcs, "\n")

```

### 2025-02-14 supplement/supplement-main_anonymized.Rmd
revisions for R&R

@@
    - \usepackage{pdflscape}
+   - \makeatletter
+   - \renewcommand{\fnum@figure}{Figure S\thefigure}
+   - \makeatother
 tables: yes
@@
 ```{r load packages}
-library(ggdendro)
-library(dendextend)
+# library(ggdendro)
+# library(dendextend)
 library(psych)
@@
 library(cowplot)
-library(tidyverse)
+# library(fda)
 library(rsq)
 library(ggnewscale)
+library(GGally)
+library(ggrepel)
+library(igraph)
+library(ggraph)
+library(tidyverse)
+
+conflicted::conflict_prefer("select", "dplyr")
+conflicted::conflict_prefer("filter", "dplyr")
 ```
@@
 
-Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.
+Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" and "bookdown" packages for R [@xie2016; @xie2021; @xie2024].
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document (supplement-main.Rmd), which can be found in the following GitHub repository (anonymized for peer review): https://anonymous.4open.science/r/baby_mental_life_ms-C261/.
 
@@
 
-To our knowledge, there is currently no consensus about how to account for within-participant variance alongside between-participant variance in the context of exploratory factor analysis or similar dimensionality reduction analyses.
-Thus, to conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
-(See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA.) We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].
+Traditional exploratory factor analysis techniques are not equipped to account for within-participant variance alongside between-participant variance.
+To conduct the EFAs reported in Results, we proceeded as if each participant's ratings of the 60 mental capacities for each of the three target ages were a distinct source of data; in other words, as if we had 903 participants assessing one target age each, instead of 301 participants assessing three target ages each.
+See [@weisman.etal2017a; @weisman.etal2021], for similar treatments of within-subjects data in the context of EFA; but see also [@owen.wang2016] for a bi-cross-validation technique, which might be adapted to address this repeated-measures design by structuring cross-validation folds to exclude all observations from a given participant within a given fold.
+(We thank a helpful reviewer for this suggestion.)
+
+We used Pearson correlations to obtain minimal residual solutions and applied an oblique transformation (oblimin) to the resulting factor structures, using the "psych" package for R [@revelle2021].
 
@@
 
-```{r fig01, fig.cap="Study 1, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
-# knitr::include_graphics("../outputs/fig01.pdf")
+```{r fig01, fig.cap="Study 1, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)", include = F}
+knitr::include_graphics("../outputs/fig01.pdf")
+```
+
+```{r figS01 code, fig.width = 8, fig.asp = 0.8}
+# custom density function with adjustable smoothing
+density_fn <- function(data, mapping, adj_val = 3, ...) {
+  filtered_data <- data %>%
+    filter(!is.na(factor))
+
+  ggplot(filtered_data, mapping) +
+    geom_density(
+      aes(color = factor, fill = factor),
+      alpha = 0.2, adjust = adj_val, inherit.aes = TRUE, ...)  # adjust controls smoothness
+}
+
+# custom points function with horizontal line
+points_fn <- function(data, mapping, ...) {
+  ggplot(data, mapping) +
+    geom_hline(
+      yintercept = 0, 
+      linetype = "dashed", 
+      color = "black",
+      size = 0.3) +
+    geom_point(
+      aes(color = factor, fill = factor),
+      alpha = 0.9, size = 1, inherit.aes = TRUE, ...)
+}
+
+# plot
+ggpairs(
+  legend = c(2, 1),
+  switch = "both",
+  s1_efa_par$loadings[] %>%
+    data.frame() %>%
+    rownames_to_column("capacity") %>%
+    mutate(
+      # a priori sorting of capacities (for Studies 2-3)
+      factor = case_when(
+        capacity %in% c(
+          "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
+          "feeling_physically_uncomfortable") ~ "Bodily sensation",
+        capacity %in% c(
+          "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
+          "feeling_helpless", "feeling_lonely") ~ "Negative affect",
+        capacity %in% c(
+          "feeling_happy", "finding_something_funny", "feeling_excited",
+          "loving_somebody", "learning_from_other_people") ~ "Social connection",
+        capacity %in% c(
+          "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
+          "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
+    mutate(factor = factor(
+      factor, 
+      levels = c(
+        "Bodily sensation", "Negative affect", 
+        "Social connection", "Cognition and control"))) %>%
+    mutate(capacity = gsub("_", " ", capacity)) %>%
+    select(MR2, MR4, MR3, MR1, everything()) %>%
+    rename(`Cognition and control` = MR1,
+           `Bodily sensation` = MR2,
+           `Social connection` = MR3,
+           `Negative affect` = MR4),
+  aes(color = factor, fill = factor),
+  columns = 1:4,
+  # upper = list(continuous = text_fn_filtered),
+  upper = list(continuous = points_fn),
+  lower = list(continuous = points_fn),
+  # diag = list(continuous = ggally_densityDiag),
+  diag = list(continuous = density_fn),
+  # diag = "blank",
+  showStrips = TRUE
+) +
+  geom_vline(xintercept = 0, lty = 2, color = "black", size = 0.3) +
+  # geom_hline(yintercept = 0, lty = 2, color = "black", size = 0.3) +
+  scale_color_viridis_d(
+    name = "Domain (Studies 2-3):",
+    end = 0.9, option = "viridis",
+    na.value = "gray80",
+    labels = c(
+      "Bodily sensation", "Negative affect", 
+      "Social connection", "Cognition and control", 
+      "Not used in Studies 2-3"),
+    aesthetics = c("color", "fill")
+  ) +
+  scale_x_continuous(breaks = seq(-100, 100, 100)) +
+  scale_y_continuous(breaks = seq(-100, 100, 100)) +
+  guides(color = guide_legend(override.aes = list(size = 3)),
+         fill = guide_legend(override.aes = list(size = 3))) +
+  # labs(color = "Domain (Studies 2-3):", fill = "Domain (Studies 2-3):") +
+  theme_minimal() +
+  theme(panel.border = element_rect(fill = NA, color = "black"),
+        panel.grid = element_blank(),
+        strip.placement = "outside",
+        legend.position = "right")
+
+# save plot
+if (resave_plots == T | !file.exists("../outputs/figS01.pdf")) {
+  ggsave("../outputs/figS01.jpg")
+  ggsave("../outputs/figS01.svg")
+  ggsave("../outputs/figS01.pdf")
+}
+```
+
+```{r figS01, fig.cap="Study 1, scatterplot matrix ('pairs plot') visualizing the relationships among factor loadings and the distributions of factor loadings across items for the four-factor solution suggested by parallel analysis (loadings presented in Figure 1).
+Along the diagonal are density plots showing, for each of the four factors, the distribution of factor loadings for the subset of capacities later used to represent each 'domain' in Studies 2-3.
+Panels in the upper and lower triangles are scatterplots of factor loadings on each pair of factors, including all of the capacities included in Study 1.", include = T}
+knitr::include_graphics("../outputs/figS01.pdf")
+```
+
+```{r figS02 function, fig.width = 10}
+figS02_fun <- function(domain1, domain2) {
+
+  domain1 <- sym(domain1)
+  domain2 <- sym(domain2)
+
+  d <- s1_efa_par$loadings[] %>%
+    data.frame() %>%
+    rownames_to_column("capacity") %>%
+    mutate(
+      factor = case_when(
+        capacity %in% c(
+          "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
+          "feeling_physically_uncomfortable") ~ "Bodily sensation",
+        capacity %in% c(
+          "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
+          "feeling_helpless", "feeling_lonely") ~ "Negative affect",
+        capacity %in% c(
+          "feeling_happy", "finding_something_funny", "feeling_excited",
+          "loving_somebody", "learning_from_other_people") ~ "Social connection",
+        capacity %in% c(
+          "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
+          "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
+    mutate(factor = factor(
+      factor, 
+      levels = c(
+        "Bodily sensation", "Negative affect", 
+        "Social connection", "Cognition and control"))) %>%
+    mutate(capacity = gsub("_", " ", capacity)) %>%
+    # gather(factor, loading, starts_with("MR")) %>%
+    rename("Cognition and control" = MR1,
+           "Bodily sensation" = MR2,
+           "Social connection" = MR3,
+           "Negative affect" = MR4)
+
+  p <- d %>%
+    ggplot(aes(x = !!domain1,
+               y = !!domain2)) +
+    geom_hline(yintercept = 0, lty = 2) +
+    geom_vline(xintercept = 0, lty = 2) +
+    geom_point(aes(color = factor)) +
+    ggrepel::geom_text_repel(
+      aes(label = capacity,
+          color = factor),
+      show.legend = F,
+      size = 3) +
+    # geom_text(aes(label = capacity)) +
+    scale_color_viridis_d(
+      name = "Domain (Studies 2-3):",
+      end = 0.9, option = "viridis", na.value = "gray70",
+      labels = c("Bodily sensation", "Negative affect", 
+                 "Social connection", "Cognition and control",
+                 "Not included in Studies 2-3")
+    ) +
+    scale_x_continuous(breaks = seq(-1, 1, 0.2)) +
+    scale_y_continuous(breaks = seq(-1, 1, 0.2)) +
+    coord_fixed() +
+    theme_minimal()
+
+  print(p)
+}
+```
+
+```{r figS02 code, fig.width = 10}
+for(i in c("Bodily sensation", "Negative affect", 
+           "Social connection", "Cognition and control")) {
+  for(j in c("Bodily sensation", "Negative affect", 
+             "Social connection", "Cognition and control")) {
+    if(i != j) {
+      figS02_fun(i, j)
+
+      # save plot
+      if (resave_plots == T | !file.exists(
+        paste0("../outputs/figS02_",
+               gsub(" ", "-", tolower(i)), "_",
+               gsub(" ", "-", tolower(j)),
+               ".pdf"))) {
+        ggsave(
+          paste0("../outputs/figS02_",
+                 gsub(" ", "-", tolower(i)), "_",
+                 gsub(" ", "-", tolower(j)),
+                 ".jpg"))
+        ggsave(
+          paste0("../outputs/figS02_",
+                 gsub(" ", "-", tolower(i)), "_",
+                 gsub(" ", "-", tolower(j)),
+                 ".svg"))
+        ggsave(
+          paste0("../outputs/figS02_",
+                 gsub(" ", "-", tolower(i)), "_",
+                 gsub(" ", "-", tolower(j)),
+                 ".pdf"))
+      }
+    }
+  }
+}
+```
+
+```{r figS02, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'negative affect' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_bodily-sensation_negative-affect.pdf")
+```
+
+```{r figS03, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'social connection' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_bodily-sensation_social-connection.pdf")
+```
+
+```{r figS04, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'bodily sensation' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_bodily-sensation_cognition-and-control.pdf")
+```
+
+```{r figS05, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'negative affect' and 'social connection' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_negative-affect_cognition-and-control.pdf")
+```
+
+```{r figS06, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'negative affect' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_negative-affect_cognition-and-control.pdf")
+```
+
+```{r figS07, fig.cap="Study 1, scatter plot visualizing the relationship between factor loadings on the factors we have labeled 'social connection' and 'cognition and control' in the factor solution suggested by parallel analysis (loadings presented in Figure 1).
+The subset of capacities used in Studies 2-3 are color-coded according to the domain they were selected to represent in those studies.", include = T}
+knitr::include_graphics("../outputs/figS02_social-connection_cognition-and-control.pdf")
 ```
@@
 
-```{r figS01 code, fig.width = 9, fig.asp = 1.2}
+```{r figS08 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s1_efa_bic)
@@
 # save plot
-if (resave_plots == T | !file.exists("../outputs/figS01.pdf")) {
-  ggsave("../outputs/figS01.svg")
-  ggsave("../outputs/figS01.pdf")
+if (resave_plots == T | !file.exists("../outputs/figS08.pdf")) {
+  ggsave("../outputs/figS08.svg")
+  ggsave("../outputs/figS08.pdf")
 }
@@
 
-```{r figS01, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
-knitr::include_graphics("../outputs/figS01.pdf")
+```{r figS08, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
+knitr::include_graphics("../outputs/figS08.pdf")
 ```
@@
 
-```{r figS02 code, fig.width = 9, fig.asp = 1.2}
+```{r figS09 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s1_efa_wdm)
@@
 # save plot
-if (resave_plots == T | !file.exists("../outputs/figS02.pdf")) {
-  ggsave("../outputs/figS02.svg")
-  ggsave("../outputs/figS02.pdf")
+if (resave_plots == T | !file.exists("../outputs/figS09.pdf")) {
+  ggsave("../outputs/figS09.svg")
+  ggsave("../outputs/figS09.pdf")
 }
@@
 
-```{r figS02, fig.cap="Study 1, factor solution suggested by minimizing BIC."}
-knitr::include_graphics("../outputs/figS02.pdf")
+```{r figS09, fig.cap="Study 1, factor solution suggested by minimizing BIC.", include = F}
+knitr::include_graphics("../outputs/figS09.pdf")
 ```
@@
 Study 1 also offered a first glimpse into US adults' perceptions of the development of mental life.
-Supplementary Figure \@ref(fig:figS03) provides a visualization of mean "scores" for each domain of mental life.
+Supplementary Figure \@ref(fig:figS10) provides a visualization of mean "scores" for each domain of mental life.
 To calculate these scores, we sorted each of the 60 mental capacities included in this study into on of the four domains (_bodily sensation_, _negative affect_, _social connection_ or _cognition and control_) according to the factor on which it loaded the most strongly and positively (see Supplementary Table \@ref(tab:tabs1efaparload)); for each participant, we then took the average of their responses to capacities in each domain at each target age.
@@
 
-```{r figS03 code, fig.width = 8, fig.asp = 0.5}
+```{r figS10 code, fig.width = 8, fig.asp = 0.5}
 d1_gam %>%
@@
 # save plot
-if (resave_plots == T | !file.exists("../outputs/figS03.pdf")) {
-  ggsave("../outputs/figS03.svg")
-  ggsave("../outputs/figS03.pdf")
+if (resave_plots == T | !file.exists("../outputs/figS10.pdf")) {
+  ggsave("../outputs/figS10.svg")
+  ggsave("../outputs/figS10.pdf")
 }
@@
 
-```{r figS03, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1).
+```{r figS10, fig.cap="Perceived developmental trajectories for four domains of mental life (Study 1).
 Lighter lines represent individual participants' scores, black points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
-knitr::include_graphics("../outputs/figS03.pdf")
+knitr::include_graphics("../outputs/figS10.pdf")
 ```
@@
 
-```{r figS04 code, fig.width = 9, fig.asp = 0.5}
+```{r figS11 code, fig.width = 9, fig.asp = 0.5}
 heatmap_fun(s2_efa_par, 
@@
 # save plot
-if (resave_plots == T | !file.exists("../outputs/figS04.pdf")) {
-  ggsave("../outputs/figS04.svg")
-  ggsave("../outputs/figS04.pdf")
+if (resave_plots == T | !file.exists("../outputs/figS11.pdf")) {
+  ggsave("../outputs/figS11.svg")
+  ggsave("../outputs/figS11.pdf")
 }
@@
 
-```{r figS04, fig.cap="Study 2, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)"}
-# knitr::include_graphics("../outputs/figS04.pdf")
+```{r figS11, fig.cap="Study 2, factor solution suggested by parallel analysis. (Identical to Figure 1 in main text.)", include = F}
+knitr::include_graphics("../outputs/figS11.pdf")
 ```
@@
 
-```{r figS05 code, fig.width = 9, fig.asp = 1.2}
+```{r figS12 code, fig.width = 9, fig.asp = 1.2}
 heatmap_fun(s2_efa_bic)
@@
 # save plot
-if (resave_plots == T | !file.exists("../outputs/figS05.pdf")) {
-  ggsave("../outputs/figS05.svg")
-  ggsave("../outputs/figS05.pdf")
+if (resave_plots == T | !file.exists("../outputs/figS12.pdf")) {
+  ggsave("../outputs/figS12.svg")
+  ggsave("../outputs/figS12.pdf")
 }
@@
 
-```{r figS05, fig.cap="Study 2, factor solution suggested by minimizing BIC.", include = F}
-knitr::include_graphics("../outputs/figS05.pdf")
+```{r figS12, fig.cap="Study 2, factor solution suggested by minimizing BIC.", include = F}
+knitr::include_graphics("../outputs/figS12.pdf")
 ```
@@
 ```{r s2 scales}
-d2_scales <- s2_efa_par$loadings[] %>%
-  data.frame() %>%
-  rownames_to_column("capacity") %>%
-  gather(factor, loading, -capacity) %>%
-  group_by(capacity) %>%
-  top_n(1, loading) %>%
-  ungroup() %>%
-  mutate(factor = recode_factor(
+d2_scales <- data.frame(
+  capacity = colnames(d2_all)) %>%
+  mutate(
+    factor = case_when(
+      capacity %in% c(
+        "getting_hungry", "feeling_pain", "feeling_tired", "hearing_sounds",
+        "feeling_physically_uncomfortable") ~ "Bodily sensation",
+      capacity %in% c(
+        "feeling_overwhelmed", "feeling_distressed", "feeling_frustrated",
+        "feeling_helpless", "feeling_lonely") ~ "Negative affect",
+      capacity %in% c(
+        "feeling_happy", "finding_something_funny", "feeling_excited",
+        "loving_somebody", "learning_from_other_people") ~ "Social connection",
+      capacity %in% c(
+        "having_self_control", "controlling_their_emotions", "telling_right_from_wrong",
+        "planning", "reasoning_about_things") ~ "Cognition and control")) %>%
+  mutate(factor = factor(
     factor, 
-    "MR3" = "Bodily sensation",
-    "MR1" = "Negative affect",
-    "MR4" = "Social connection",
-    "MR2" = "Cognition and control")) %>%
-  arrange(factor, desc(loading)) %>%
-  mutate(order = 1:nrow(.))
+    levels = c(
+      "Bodily sensation", "Negative affect", 
+      "Social connection", "Cognition and control"))) %>%
+  arrange(factor) %>%
+  mutate(loading = NA,
+         order = 1:nrow(.))
+
+# # alternatively, could define this based on study 1 data
+# d2_scales <- d1_scales %>%
+#   filter(capacity %in% colnames(d2_all))
+
+# # alternatively, could define this based on study 2 data
+# d2_scales <- s2_efa_par$loadings[] %>%
+#   data.frame() %>%
+#   rownames_to_column("capacity") %>%
+#   gather(factor, loading, -capacity) %>%
+#   group_by(capacity) %>%
+#   top_n(1, loading) %>%
+#   ungroup() %>%
+#   mutate(factor = recode_factor(
+#     factor,
+#     "MR3" = "Bodily sensation",
+#     "MR1" = "Negative affect",
+#     "MR4" = "Social connection",
+#     "MR2" = "Cognition and control")) %>%
+#   arrange(factor, desc(loading)) %>%
+#   mutate(order = 1:nrow(.))
 ```
@@
 
+```{r fig04, fig.cap="Network graph summarizing the importance of each developmental mechanism (along the bottom) for each capacity (along the top) among US adults (Study 3).
+Capacities are sorted and color-coded by domain (see Figures 2-3); developmental mechanisms are arranged in the fixed order of presentation (roughly, from what we perceived to be the most innate or biological mechanisms of development, to what we perceived to be the most learned or social).
+See main text for the full text of each mechanism.
+(Identical to Figure 4 in the main manuscript.)", fig.width = 8, fig.asp = 0.8}
+d3_mech_ratings_graph <- d3_mech_ratings %>%
+  mutate(dev_factor = as.character(dev_factor))
+
+# create nodes dataframe
+nodes <- tibble(
+  name = c(d2_scales$capacity[d2_scales$capacity %in% unique(d3_mech_ratings$capacity)],
+           levels(d3_mech_ratings$dev_factor))) %>%
+  mutate(type = ifelse(name %in% d3_mech_ratings_graph$dev_factor, TRUE, FALSE))
+
+# create bipartite graph
+g <- graph_from_data_frame(
+  d = d3_mech_ratings_graph %>%
+    select(capacity, dev_factor, response) %>%
+    # filter(!is.na(response), !is.na(dev_factor)) %>%
+    group_by(capacity, dev_factor) %>%
+    summarise(mean = mean(response, na.rm = T)) %>%
+    ungroup(),
+  vertices = nodes,
+  directed = FALSE
+)
+
+# plot network graph
+ggraph(g, layout = "bipartite") +
+  geom_edge_link(
+    aes(width = mean,
+        alpha = mean,
+        color = mean)) +
+  geom_node_point(
+    data = . %>%
+      mutate(name = factor(name, levels = nodes$name)),
+    aes(color = name),
+    size = 5) +
+  geom_node_text(aes(label = gsub("_", " ", name)),
+                 angle = 45,
+                 # vjust = -2,
+                 hjust = c(rep(0, 8), rep(1, 10)),
+                 nudge_x = c(rep(0.05, 8), rep(-0.05, 10)),
+                 nudge_y = c(rep(0.05, 8), rep(-0.05, 10)),
+                 # nudge_y = c(rep(-1, 8), rep(1, 10)),
+                 size = 3) +
+  scale_color_manual(
+    values = c(rep("#440154FF", 2),
+               rep("#35608DFF", 2),
+               rep("#22A884FF", 2),
+               rep("#BBDF27FF", 2),
+               c("#800080", "#8B1A6A", "#990033", "#A0002B", "#BD0026", 
+                 "#D31B1C", "#E31A1C", "#F03B20", "#FC4E2A", "#FD8D3C"))
+               # rep("#f94802", 10))
+  ) +
+  # scale_color_manual(
+  #   values = c("FALSE" = "black", "TRUE" = "#f94802"),
+  #   labels = c("Capacity", "Developmental mechanism"), name = "Node Type") +
+  scale_edge_width_continuous(range = c(0.01, 0.7), limits = c(0, 6)) +
+  scale_edge_alpha_continuous(range = c(0.05, 1), limits = c(0, 6), breaks = seq(0, 6, 1)) +
+  scale_edge_colour_gradient2(
+    # low = "gray95", high = "gray70",
+    low = "gray90", mid = "gray80", high = "gray10",
+    midpoint = 4,
+    limits = c(0, 6),
+    breaks = seq(0, 6, 1),
+    labels = c("0 (not at all important)", 1:5, "6 (extremely important)")) +
+  annotate("text", label = "Capacities", 
+           x = 5.5, 
+           y = Inf, vjust = 1, hjust = 0.5) +
+  annotate("text", label = "Developmental mechanisms", 
+           x = 5.5, 
+           y = -Inf, vjust = -1, hjust = 0.5) +
+  scale_x_continuous(limits = c(0, 11)) +
+  scale_y_continuous(limits = c(-0.3, 1.3)) +
+  theme_minimal() +
+  theme(axis.text = element_blank(),
+        axis.title = element_blank(),
+        panel.grid = element_blank(),
+        # plot.background = element_rect(fill = NA, color = "black"),
+        legend.position = "right"
+        ) +
+  guides(edge_width = guide_none(),
+         edge_alpha = guide_none(),
+         edge_color = guide_edge_colorbar(barwidth = 0.5, barheight = 10),
+         color = guide_none()) +
+  labs(#title = "Two-Mode Network: Capacities & developmental mechanisms",
+       # edge_width = "Mean rating:",
+       # edge_alpha = "Mean rating:",
+       edge_color = "Mean rating:\n")
+
+# save plot
+if (resave_plots == T | !file.exists("../outputs/fig04.pdf")) {
+  ggsave("../outputs/fig04.jpg")
+  ggsave("../outputs/fig04.svg")
+  ggsave("../outputs/fig04.pdf")
+}
+```
+
 ```{r s3 export results}
@@
 
-# Study comparison: Capacity attributions to newborns, 9-months, and 5-year-olds
+# Study comparison
 
@@
 
-To provide some sense of the stability and reliability of US adults' representations of specific target ages across studies, Supplementary Figure \@ref(fig:figS06) presents a comparison of capacity ratings and summary scores by domain at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds).
+To provide some sense of the stability and reliability of US adults' representations of specific target ages across studies, Supplementary Figure \@ref(fig:figS13) presents a comparison of capacity ratings at the three target ages that were included in all of the current studies (newborns, 9-month-olds, and 5-year-olds).
 As a reminder, in Study 1, participants assessed 60 capacities (including but not limited to the 20 capacities depicted in Panel A), at each of the 3 target ages depicted here.
@@
 
-```{r figS06 code, fig.width = 10, fig.asp = 1.2}
-figS06 <- d123_gam %>%
+```{r figS13 code, fig.width = 10, fig.asp = 1.2}
+figS13 <- d123_gam %>%
   filter(target_ord %in% c("newborns", "9-month-olds", "5-year-olds")) %>%
@@
   guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
-figS06
-
-if (resave_plots == T | !file.exists("../outputs/figS06.pdf")) {
-  ggsave("../outputs/figS06.svg")
-  ggsave("../outputs/figS06.pdf")
+figS13
+
+if (resave_plots == T | !file.exists("../outputs/figS13.pdf")) {
+  ggsave("../outputs/figS13.jpg")
+  ggsave("../outputs/figS13.svg")
+  ggsave("../outputs/figS13.pdf")
 }
@@
 
-```{r figS06, fig.cap="Comparison of capacity ratings across studies (Studies 1-3).
+```{r figS13, fig.cap="Comparison of capacity ratings across studies (Studies 1-3).
 This visualization includes responses for each of the capacities and target ages held in common across at least two of our three studies.
-Lighter colorful represent individual participants’ responses or scores, larger points correspond to mean responses or scores across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
-knitr::include_graphics("../outputs/figS06.pdf")
+Lighter colorful points represent individual participants’ responses, larger points correspond to mean responses across the sample, and error bars are bootstrapped 95% confidence intervals.", include = T}
+knitr::include_graphics("../outputs/figS13.pdf")
+```
+
+```{r}
+d23_gam_pred <- d2_gam_r1_pred %>%
+  mutate(study = "Study 2") %>%
+  full_join(d3_gam_r1_pred %>% mutate(study = "Study 3")) %>%
+  mutate(study = factor(study, levels = c("Study 1", "Study 2", "Study 3")))
+```
+
+```{r figS14 code, fig.width = 10, fig.asp = 0.5}
+figS14 <- d23_gam_pred %>%
+  full_join(
+    d1_gam %>%
+      mutate(study = "Study 1") %>%
+      group_by(study, ResponseId, factor, target, target_year) %>%
+      summarise(score = mean(response/100, na.rm = T))) %>%
+  ggplot(aes(x = target_year, y = score, 
+             color = study, fill = study)) +
+  facet_grid(cols = vars(factor)) +
+  geom_jitter(height = 0, width = 0.1, size = 0.01, alpha = 0.05) +
+  geom_smooth(aes(y = pred_score, color = study, fill = study), 
+              fill = NA, size = 0.8, lty = 1, 
+              show.legend = F) +
+  geom_path(
+    data = . %>%
+      filter(study == "Study 1") %>%
+      # filter(target_year %in% c(0, 9/12, 5)) %>%
+      group_by(study, target, target_year,
+               factor) %>%
+      summarise(mean = mean(score, na.rm = T)) %>%
+      ungroup(),
+    aes(y = mean, group = study),
+    color = "#1b9e77", lty = 2) +
+  geom_pointrange(
+    data = . %>%
+      # filter(study == "Study 1") %>%
+      filter(target_year %in% c(0, 9/12, 5)) %>%
+      group_by(study, target, target_year,
+               factor) %>%
+      multi_boot_standard(col = "score", na.rm = T) %>%
+      ungroup(),
+    aes(y = mean, ymin = ci_lower, ymax = ci_upper,
+        group = study, fill = study),
+    # color = "#1b9e77", 
+    shape = 21, fatten = 2,
+    show.legend = F) +
+  # geom_text(
+  #   data = . %>%
+  #     group_by(study, target, target_year, target_num, target_ord, 
+  #              factor) %>%
+  #     summarise(mean = mean(score, na.rm = T)) %>%
+  #     ungroup(),
+  #   aes(y = mean, group = study, label = gsub("Study ", "", study)),
+  #   color = "white", size = 2.5, fontface = "bold", hjust = 0.5, vjust = 0.5,
+  #   position = position_dodge(width = 0.8)) +
+  # scale_fill_manual(values = c("#9801a3", "#a3012f", "#a36501"), 
+  #                   aesthetics = c("color", "fill")) +
+  scale_fill_brewer(palette = "Dark2", aesthetics = c("color", "fill")) +
+  scale_y_continuous(
+    breaks = seq(0, 1, 0.25),
+    labels = seq(0, 100, 25)) +
+  # scale_x_discrete(labels = c("newborns", "9 months", "5 years")) +
+  # scale_x_discrete(labels = levels(d123_gam$target_ord)) +
+  # scale_x_continuous(breaks = seq(0, 5, 1)) +
+  theme_minimal() +
+  theme(panel.background = element_rect(fill = NA), 
+        strip.text = element_text(vjust = 0),
+        legend.position = "top") +
+        # axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
+        # plot.margin = unit(c(0.5, 0.5, 0.5, 1.1), "cm")) +
+  labs(x = "Target age (years)",
+       y = "Mean score across all capacities in domain\n0 = not at all capable, 100 = completely capable",
+       # caption = "Error bars are bootstrapped 95% CIs; solid lines are estimates from GAMs (Studies 1 and 2)",
+       color = "Study:",
+       fill = "Study:") +
+  guides(color = guide_legend(override.aes = list(alpha = 1, size = 2)))
+
+figS14
+
+if (resave_plots == T | !file.exists("../outputs/figS14.pdf")) {
+  ggsave("../outputs/figS14.jpg")
+  ggsave("../outputs/figS14.svg")
+  ggsave("../outputs/figS14.pdf")
+}
+```
+
+```{r figS14, fig.cap="Comparison of mean scores across studies (Studies 1-3).
+These scores incorporate responses to all of the capacities and target ages included in each study; this varies across studies.
+Lighter points represent individual participants’ scores, larger points correspond to mean scores across the sample, and error bars are bootstrapped 95% confidence intervals.
+The dotted line for Study 1 connects mean scores across target ages; the solid lines for Studies 2-3 reflect predictions from study-specific GAMs.", include = T}
+knitr::include_graphics("../outputs/figS14.pdf")
 ```

### 2025-02-27 paper/cover.tex
de-anonymize

@@
 
+    \indent Weisman, King, and Humphreys were affiliated with the Department of Psychology at Stanford University at the time of data collection.
+Weisman was affiliated with the Department of Psychology at the University of California, Riverside, at the time of submission, and is now affiliated with the Department of Psychology at Harvard University.
+King and Humphreys are now affiliated with the Department of Psychology and Human Development at Vanderbilt University.
+
     \indent Study materials, preregistrations, data, analysis scripts, and links to the fully reproducible manuscript and supplemental materials are openly available via the project’s Open Science Framework page (https://osf.io/xrznd/; DOI: 10.17605/OSF.IO/XRZND).

### 2025-02-27 paper/paper.Rmd
de-anonymize

@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
-All studies were approved by the Research Compliance Office, Human Subjects Panel (IRB) at Stanford University.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: \url{https://osf.io/e6ajh}; Study 2: \url{https://osf.io/j72dg}; Study 3: \url{https://osf.io/xh8ce)}).
+All studies were approved by the Stanford University Research Compliance Office (Human Subjects IRB).
 For extended descriptions of methods and results, see Supplemental Materials.
+Note: scripts for all analyses, figures, and tables are available in the .Rmd file that generated the fully reproducible Supplemental Materials document (supplement-main.Rmd), which can be found in the following GitHub repository: \url{https://github.com/kgweisman/baby_mental_life_ms}.
 
@@
 On each trial, they were shown two representative photographs of children at the target age (labeled "newborns," "9-month-olds," or "5-year-olds"), and asked to answer the following question for 60 capacities: "To what extent is a [newborn/9-month-old/5-year-old] capable of [this capacity]?" See Supplemental Materials for details about the selection of these photographs.
-These photographs (and all materials used in these studies) are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
+These photographs (and all materials used in these studies) are available in the following OSF repository: \url{https://osf.io/xrznd}.
 Participants responded on a sliding scale from 0 (labeled "not at all capable") to 100 ("completely capable").

### 2025-02-27 supplement/cover.tex
add cover pages and de-anonymize
de-anonymize

--- 2024-12-30 paper/cover.tex
@@
         \vspace*{1in}
-        {\Large Beliefs about the development of mental life} \\[2cm]
+        {\Large Beliefs about the development of mental life: Supplemental Materials} \\[2cm]
 

### 2025-02-27 supplement/supplement-main.Rmd
de-anonymize

@@
    - \usepackage{float}
+   - \usepackage{url}
    - \usepackage{pdflscape}
+   - \makeatletter
+   - \renewcommand{\fnum@figure}{Figure S\thefigure}
+   - \makeatother
 tables: yes
@@
 
-Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021].
-The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://github.com/kgweisman/baby_mental_life_ms.
+Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" and "bookdown" packages for R [@xie2016; @xie2021; @xie2024].
+The full, editable script for all analyses, figures, and tables (here and in the main text) is available in the .Rmd file that generated this document (supplement-main.Rmd), which can be found in the following GitHub repository: \url{https://github.com/kgweisman/baby_mental_life_ms}.
 
@@
 
-Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: https://osf.io/e6ajh; Study 2: https://osf.io/j72dg; Study 3: https://osf.io/xh8ce).
-
-All materials used in these studies are available in the following OSF repository: https://osf.io/xrznd/ (DOI: 10.17605/OSF.IO/XRZND).
-
-All studies were approved by the Institution Review Board for Human Subjects at Stanford University.
+Methods, inclusion/exclusion criteria, and analyses marked as "preregistered" were preregistered on the Open Science Framework (OSF) website (Study 1: \url{https://osf.io/e6ajh}; Study 2: \url{https://osf.io/j72dg}; Study 3: \url{https://osf.io/xh8ce)}).
+
+All materials used in these studies are available in the following OSF repository: \url{https://osf.io/xrznd}.
+
+All studies were approved by the Stanford University Research Compliance Office (Human Subjects IRB).
 
